### 2024-12-10 paper.tex
Computation for general linear groups

\documentclass[12pt, reqno]{amsart}

\usepackage{amsmath, amsthm, amssymb}
\usepackage{enumerate}
\tolerance=500
\setlength{\emergencystretch}{3em}
\usepackage[margin=1.0in]{geometry}
\usepackage{xcolor}
\definecolor{cite}{rgb}{0.30,0.60,1.00}
\definecolor{url}{rgb}{0.00,0.00,0.80}
\definecolor{link}{rgb}{0.40,0.10,0.20}
\usepackage[pdfusetitle,colorlinks,linkcolor=link,urlcolor=url,citecolor=cite,pagebackref,breaklinks]{hyperref}
\usepackage{graphicx}
\usepackage{cleveref}
\usepackage{mathdots}
\usepackage{tikz-cd}
\usepackage{comment}
\usepackage{xypic}
\usepackage{mathtools}

% new environment
\newtheorem{theorem}{Theorem}[section]
\newtheorem{claim}[theorem]{Claim}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\theoremstyle{definition}
\newtheorem{example}[theorem]{Example}

%% frequently used symbols
% Common math notions
\newcommand{\zIntegers}{\mathbb{Z}}
\newcommand{\rReal}{\mathbb{R}}
\newcommand{\cComplex}{\mathbb{C}}
\newcommand{\multiplicativegroup}[1]{#1^{\times}}
\newcommand{\RealPart}{\mathrm{Re}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\EndomorphismRing}{\operatorname{End}}
\newcommand{\Span}{\mathrm{span}}
\newcommand{\Supp}{\mathrm{supp}}
\newcommand{\Stab}{\mathrm{stab}}
\newcommand{\idmap}{\mathrm{id}}
\newcommand{\conjugate}[1]{\overline{#1}}
\newcommand{\indicatorFunction}[1]{\delta_{#1}}
\newcommand{\isomorphic}{\cong}
\newcommand{\lengthof}{\mathfrak{n}}
\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\sizeof}[1]{\left|#1\right|}
\newcommand{\lcm}{\operatorname{lcm}}

% Inner product
\newcommand{\innerproduct}[2]{\left\langle #1,#2\right\rangle}
\newcommand{\Norm}[1]{\left\Vert #1\right\Vert }
\newcommand{\standardForm}[2]{\left\langle #1,#2\right\rangle}

% Representation theory
\newcommand{\fieldCharacter}{\psi}
\newcommand{\centralCharacter}[1]{\omega_{#1}}
\newcommand{\Ind}[3]{\mathrm{Ind}_{#1}^{#2}\left(#3\right)}
\newcommand{\ind}[3]{\mathrm{ind}_{#1}^{#2}\left(#3\right)}
\newcommand{\Whittaker}{\mathcal{W}}
\newcommand{\Contragradient}[1]{#1^{\vee}}
\newcommand{\underlyingVectorSpace}[1]{V_{#1}}
\newcommand{\representationDeclaration}[1]{#1}
\newcommand{\besselFunction}{\mathcal{J}}
\newcommand{\besselFunctionOfFiniteFieldRepresentation}{\besselFunction_{\finiteFieldRepresentation, \fieldCharacter}}
\newcommand{\SpehRepresentation}[2]{\Delta\left(#1, #2\right)}

\newcommand{\gbesselSpehFunction}[2]{\mathcal{BS}_{#1, #2}}
\newcommand{\besselSpehFunction}[2]{\mathcal{BS}_{\SpehRepresentation{#1}{#2}, \fieldCharacter}}
\newcommand{\fourierTransform}[2]{\mathcal{F}_{#1}#2}
\newcommand{\GKGammaFactor}[3]{\gamma^{\mathrm{GK}}\left(#1 \times #2, #3\right)}
\newcommand{\LocalGKGammaFactor}[4]{\gamma^{\mathrm{GK}}\left(#1, #2 \times #3, #4\right)}

\newcommand{\GKPreGammaFactor}[3]{\Gamma^{\mathrm{GK}}\left(#1 \times #2, #3\right)}
\newcommand{\gGJPreGammaFactor}[3]{\Gamma\left(#1 \times #2, #3\right)}
\newcommand{\GJPreGammaFactor}[2]{\Gamma\left(#1, #2\right)}
\newcommand{\Irr}{\mathrm{Irr}}

% Group theory macros
\newcommand{\rquot}[2]{{#1}\slash{#2}}
\newcommand{\lquot}[2]{{#1}\backslash{#2}}
\newcommand{\grpIndex}[2]{\left[#1:#2\right]}

% Matrices macros
\newcommand{\transpose}[1]{\, {}^{t}#1}
\newcommand{\inverseTranspose}[1]{#1^{\iota}}
\newcommand{\IdentityMatrix}[1]{I_{#1}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\antidiag}{\operatorname{\mathrm{antidiag}}}
\newcommand{\trace}{\operatorname{tr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\UnipotentSubgroup}{U}
\newcommand{\UnipotentRadicalForWss}[2]{N_{\left(#2^{#1}\right)}}
\newcommand{\UnipotentRadicalForWssRecursion}[2]{\mathcal{Y}_{c,k}}
\newcommand{\UnipotentRadical}{N}
\newcommand{\ParabolicSubgroup}{P}

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\FieldTrace}{\mathrm{Tr}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\FieldExtension}[2]{{#1} \slash {#2}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\charactergroup}[1]{\widehat{\multiplicativegroup{\finiteFieldExtension{#1}}}}
\newcommand{\limitcharactergroup}{\Gamma}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\mathbb{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\frobeniusDegree}{\operatorname{deg}}
\newcommand{\Steinberg}{\operatorname{St}}
\newcommand{\ProjectionOperator}{\operatorname{pr}}
\newcommand{\SymmetricGroup}{\mathfrak{S}}
\newcommand{\whittakerVector}[1]{v_{#1, \fieldCharacter}}
\newcommand{\gwhittakerVector}[2]{v_{#1, #2}}
\newcommand{\WhittakerProjection}{\ProjectionOperator_{\mathrm{Wh}}}
\newcommand{\ParabolicForSpeh}[2]{P_{\left({#1}^{#2}\right)}}
\newcommand{\UnipotentForSpeh}[2]{N_{\left({#1}^{#2}\right)}}
\newcommand{\PoincarePolynomial}[2]{P_{#2}}

%Partition macros
\newcommand{\localField}{F}
\newcommand{\ringOfIntegers}{\mathfrak{o}}
\newcommand{\residueField}{\mathfrak{f}}
\newcommand{\maximalIdeal}{\mathfrak{p}}
\newcommand{\depthZeroRepresentation}{\mathcal{T}}
\newcommand{\differential}{\mathrm{d}}
\newcommand{\mdifferential}{\differential^{\times}}
\newcommand{\quotientMap}{\nu}
\newcommand{\Lift}{\mathcal{L}}
\newcommand{\uniformizer}{\varpi}
\newcommand{\VolumeOf}{\operatorname{Vol}}

\newcommand{\Erdelyi}{Erd{\'e}lyi}
\newcommand{\Toth}{T{\'o}th}

\newcommand{\parabolicSection}{\Phi^{\left(z_1, \dots, z_c\right)}}
\newcommand{\intertwiningOperator}{M^{\left(z_1, \dots, z_c\right)}}
\newcommand{\holomorphicRepresentation}{\depthZeroRepresentation^{\left(z_1, \dots, z_c\right)}}
\newcommand{\WhittakerFunctional}[1]{\ell_{#1, \fieldCharacter}}
\newcommand{\gWhittakerFunctional}[2]{\ell_{#1, #2}}
\newcommand{\gSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}, \fieldCharacter_{\UnipotentRadicalForWss{#2}{#3}}}}
\newcommand{\gShortSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblGaussSum}[2]{\mathcal{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
\newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
\newcommand{\GKGaussSumScalar}[3]{\mathrm{G}\left(#1 \times #2, #3\right)}
\newcommand{\fieldCharacterkc}[2]{\fieldCharacter_{\left({#2}^{#1}\right)}}
\newcommand{\ExoticKloosterman}{\mathrm{Kl}}
\newcommand{\GaussSumCharacter}[4]{\tau_{#1}\left(#2 \times #3, #4\right)}
\newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
\newcommand{\convolutionWithCompactSupport}{\boldsymbol{\mathrm{R}}}
\newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
\newcommand{\artinScrier}{\operatorname{AS}}
\newcommand{\KloostermanSumClassFunction}{\mathcal{K}}

\hypersetup{pdfauthor={Elad Zelingher},
	pdfsubject={Number theory, Representation theory},
	pdfkeywords={Kloosterman sums, Gauss sums}}

\title{Degenerate Gauss sums for $\GL_n\left(\finiteField_q\right)$}

\author{Elad Zelingher}
\address{Department of Mathematics, University of Michigan, 1844 East Hall, 530 Church Street, Ann Arbor, MI 48109-1043 USA}
\email{eladz@umich.edu}

\subjclass[2010]{20C33, 11L05, 11T24}

% 11L05    Gauss and Kloosterman sums; generalizations
% 11T24    Other character sums and Gauss sums
% 20C33    Representations of finite groups of Lie type

\begin{document}

\begin{abstract}
\end{abstract}
\maketitle

\section{Notation}
Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character. For any $r \ge 0$, let $B_r \subset \GL_r\left(\finiteField\right)$ be the standard Borel subgroup
$$B_r = \left\{ \begin{pmatrix}
	t_1 & \ast & \ast & \ast\\
	& t_2 & \ast & \ast \\
	& & \ddots & \ast\\
	& & & t_r
\end{pmatrix} \mid t_1,\dots,t_r \in \multiplicativegroup{\finiteField} \right\}.$$

\section{Degenerate Gauss sums}
Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. The purpose of this section is to study the following operator, which we refer to as a degenerate Gauss sum
$$\GaussSum{\pi}{\fieldCharacter}_r = \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(g \begin{pmatrix}
	0_{r}\\
	& \IdentityMatrix{n-r}
\end{pmatrix}\right)\right).$$
Notice that $\GaussSum{\pi}{\fieldCharacter}_0$ lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$ and therefore, $$\GaussSum{\pi}{\fieldCharacter} \coloneqq \GaussSum{\pi}{\fieldCharacter}_0 = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_\pi,$$
where $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$. The computation of this scalar is known due to Kondo.

We begin with the following simple observation. We have that for any $b \in B_r$ and any $X \in \Mat{r}{(n-r)}\left(\finiteField\right)$,
$$ \pi\begin{pmatrix}
b & X\\
& \IdentityMatrix{n-r}
\end{pmatrix} \circ \GaussSum{\pi}{\fieldCharacter}_r = \GaussSum{\pi}{\fieldCharacter}_r.$$
Therefore, we have that $\GaussSum{\pi}{\fieldCharacter}_r$ can be regarded as an operator $\GaussSum{\pi}{\fieldCharacter}_r \colon \pi \to J\left(\pi, r\right)$, where $$J\left(\pi, r\right) = \left\{ v \in \pi \mid \pi \begin{pmatrix}
	b & X\\
	& \IdentityMatrix{n-r}
\end{pmatrix} v = v, \forall b \in B_r, X \in \Mat{r}{(n-r)}\left(\finiteField\right) \right\},$$
which is a representation of the group $B_r \times \GL_{n-r}\left(\finiteField\right)$. This space is non-zero if and only if $\pi$ is subrepresentation of a parabolically induced representation of the form $1^{\circ r} \circ \tau = 1 \circ \dots \circ 1 \circ \tau$, where $\tau$ is an irreducible representation of $\GL_{n-r}\left(\finiteField\right)$.

It follows from this observation that if $\pi$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $1$ is not in the cuspidal support of $\pi$, then for any matrix $A$ with rank $< n$, 
$$\GaussSum{\pi}{\fieldCharacter}_A \coloneqq \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(A g\right)\right) = 0.$$

\section{Doubling method Gauss sums}

\subsection{The case of general linear groups}

Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.

Consider the following assignment $\GL_n\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$
$$\Phi_{\chi}\left(g\right) = \begin{dcases}
	\chi\left(\det\left(g-\IdentityMatrix{n}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{n}\right) \ne 0,\\
	0 & \text{otherwise.}
\end{dcases}$$
It is clear that $\Phi_{\chi}$ is a class function of $\GL_n\left(\finiteField\right)$. Given an irreducible representation $\pi$ of $\GL_n\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
$$\dblGaussSum{\pi}{\chi} = \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \pi\left(g\right).$$
Then $\dblGaussSum{\pi}{\chi}$ defines an element of $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$. Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\pi}{\chi} \in \cComplex$ such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$

The goal of this section is to express $\dblGaussSumScalar{\pi}{\chi}$ in terms of Kondo's Gauss sum.

Assume first that $1$ does not appear in the cuspidal support of $\pi$. Let us write
$$\dblGaussSum{\pi}{\chi} = \sum_{\substack{g \in \GL_n\left(\finiteField\right) \sum_{A \in \squareMatrix_n\left(\finiteField\right)}\\
\det\left(g - \IdentityMatrix{n}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{n}\right)\right) \pi\left(g\right).$$
We rewrite this using a Fourier transform type expression
$$\dblGaussSum{\pi}{\chi} = q^{-n^2} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$

Replacing $g$ with $h^{-1} g$, we arrive at the expression
\begin{align*}
	\dblGaussSum{\pi}{\chi} &= q^{-n^2} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
	& \circ \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(-\trace Ag\right).
\end{align*}
Since the last inner sum is $\GaussSum{\pi}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$. Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
\begin{align*}
	\dblGaussSum{\pi}{\chi} &= q^{-n^2} \centralCharacter{\pi}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter},
\end{align*}
which equals
\begin{align*}
	\dblGaussSum{\pi}{\chi} &= \left(-1\right)^{n-1} q^{-n^2} \centralCharacter{\pi}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter}.
\end{align*}

\bibliographystyle{abbrv}
\bibliography{references}
\end{document}

### 2024-12-11 paper.tex
Correction
Cleanup?

@@
 \section{Degenerate Gauss sums}
-Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. The purpose of this section is to study the following operator, which we refer to as a degenerate Gauss sum
-$$\GaussSum{\pi}{\fieldCharacter}_r = \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(g \begin{pmatrix}
+Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. For a matrix $A \in \squareMatrix_n\left(\finiteField\right)$, denote
+$$\GaussSum{\pi}{\fieldCharacter}_A \coloneqq q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(A g\right)\right).$$
+For any such $A$, there exist $h_1, h_2 \in \GL_n\left(\finiteField\right)$ and $0 \le r \le n$, such that $A = h_1 \begin{pmatrix}
+	0_r\\
+	& \IdentityMatrix{n-r}
+\end{pmatrix} h_2$. Changing variables, we see that $$\GaussSum{\pi}{\fieldCharacter}_A = \pi \left(h_2^{-1}\right) \circ \GaussSum{\pi}{\fieldCharacter}_r \circ \pi\left(h_1^{-1}\right),$$
+where
+$$\GaussSum{\pi}{\fieldCharacter}_r = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(g \begin{pmatrix}
 	0_{r}\\
@@
 Notice that $\GaussSum{\pi}{\fieldCharacter}_0$ lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$ and therefore, $$\GaussSum{\pi}{\fieldCharacter} \coloneqq \GaussSum{\pi}{\fieldCharacter}_0 = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_\pi,$$
-where $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$. The computation of this scalar is known due to Kondo.
+where $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$.
+The computation of this scalar is known due to Kondo.
+Let us also denote for a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the \emph{twisted Gauss sum}
+$$\GaussSum{\pi \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
+This element also lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$ and we denote
+$$\GaussSum{\pi \times \chi}{\fieldCharacter} = \GaussSumScalar{\pi \times \chi}{\fieldCharacter} \cdot \idmap_\pi,$$
+where $\GaussSumScalar{\pi \times \chi}{\fieldCharacter} \in \cComplex$.
 
-We begin with the following simple observation. We have that for any $b \in B_r$ and any $X \in \Mat{r}{(n-r)}\left(\finiteField\right)$,
+Let us show that if $A$ is singular and $\pi$ does not contain $1$ in its cuspidal support then $\GaussSum{\pi}{\fieldCharacter}_A = 0$.
+We begin with the following simple observation.
+We have that for any $b \in B_r$ and any $X \in \Mat{r}{(n-r)}\left(\finiteField\right)$,
 $$ \pi\begin{pmatrix}
@@
 
-It follows from this observation that if $\pi$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $1$ is not in the cuspidal support of $\pi$, then for any matrix $A$ with rank $< n$,
-$$\GaussSum{\pi}{\fieldCharacter}_A \coloneqq \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(A g\right)\right) = 0.$$
+It follows from this observation that if $\pi$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $1$ is not in the cuspidal support of $\pi$, then for any matrix $A$ with rank $< n$, we have $\GaussSum{\pi}{\fieldCharacter}_A = 0$.
 
@@
 
-Consider the following assignment $\GL_n\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$
+Consider the following assignment $\GL_n\left(\finiteField\right) \to \cComplex$
 $$\Phi_{\chi}\left(g\right) = \begin{dcases}
@@
 Given an irreducible representation $\pi$ of $\GL_n\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
-$$\dblGaussSum{\pi}{\chi} = \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \pi\left(g\right).$$
+$$\dblGaussSum{\pi}{\chi} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \pi\left(g\right).$$
 Then $\dblGaussSum{\pi}{\chi}$ defines an element of $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$.
@@
 Assume first that $1$ does not appear in the cuspidal support of $\pi$. Let us write
-$$\dblGaussSum{\pi}{\chi} = \sum_{\substack{g \in \GL_n\left(\finiteField\right) \sum_{A \in \squareMatrix_n\left(\finiteField\right)}\\
+$$\dblGaussSum{\pi}{\chi} = q^{-\frac{n^2}{2}} \sum_{\substack{g \in \GL_n\left(\finiteField\right) \\
 \det\left(g - \IdentityMatrix{n}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{n}\right)\right) \pi\left(g\right).$$
 We rewrite this using a Fourier transform type expression
-$$\dblGaussSum{\pi}{\chi} = q^{-n^2} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$
+$$\dblGaussSum{\pi}{\chi} = q^{-\frac{3n^2}{2}} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$
 
@@
 \begin{align*}
-	\dblGaussSum{\pi}{\chi} &= q^{-n^2} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
+	\dblGaussSum{\pi}{\chi} &= q^{-\frac{3n^2}{2}} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
 	& \circ \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(-\trace Ag\right).
 \end{align*}
-Since the last inner sum is $\GaussSum{\pi}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$.
+Since the last inner sum is $q^{\frac{n^2}{2}} \GaussSum{\pi}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$.
 Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
 \begin{align*}
-	\dblGaussSum{\pi}{\chi} &= q^{-n^2} \centralCharacter{\pi}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter},
+	\dblGaussSumScalar{\pi}{\chi} &= q^{-\frac{n^2}{2}} \centralCharacter{\pi}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter},
 \end{align*}
@@
 \begin{align*}
-	\dblGaussSum{\pi}{\chi} &= \left(-1\right)^{n-1} q^{-n^2} \centralCharacter{\pi}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter}.
+	\dblGaussSumScalar{\pi}{\chi} &=  \centralCharacter{\pi}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter}.
 \end{align*}

### 2024-12-12 paper.tex
Started writing about classical groups
Completing some computations

--- 2024-12-10 paper.tex
@@
 \newcommand{\lcm}{\operatorname{lcm}}
+\newcommand{\hermitianSpace}{\mathrm{V}}
+\newcommand{\xIsotropic}{\mathrm{X}}
+\newcommand{\yIsotropic}{\mathrm{Y}}
 
@@
 \newcommand{\KloostermanSumClassFunction}{\mathcal{K}}
+\newcommand{\IsometryGroup}{\mathrm{Isom}}
+\newcommand{\lieAlgebra}{\mathfrak{g}}
 
@@
 \section{Degenerate Gauss sums}
-Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. The purpose of this section is to study the following operator, which we refer to as a degenerate Gauss sum
-$$\GaussSum{\pi}{\fieldCharacter}_r = \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(g \begin{pmatrix}
+Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. For a matrix $A \in \squareMatrix_n\left(\finiteField\right)$, denote
+$$\GaussSum{\tau}{\fieldCharacter}_A \coloneqq q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(\trace\left(A g\right)\right).$$
+For any such $A$, there exist $h_1, h_2 \in \GL_n\left(\finiteField\right)$ and $0 \le r \le n$, such that $A = h_1 \begin{pmatrix}
+	0_r\\
+	& \IdentityMatrix{n-r}
+\end{pmatrix} h_2$. Changing variables, we see that $$\GaussSum{\tau}{\fieldCharacter}_A = \tau \left(h_2^{-1}\right) \circ \GaussSum{\tau}{\fieldCharacter}_r \circ \tau\left(h_1^{-1}\right),$$
+where
+$$\GaussSum{\tau}{\fieldCharacter}_r = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(\trace\left(g \begin{pmatrix}
 	0_{r}\\
@@
 \end{pmatrix}\right)\right).$$
-Notice that $\GaussSum{\pi}{\fieldCharacter}_0$ lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$ and therefore, $$\GaussSum{\pi}{\fieldCharacter} \coloneqq \GaussSum{\pi}{\fieldCharacter}_0 = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_\pi,$$
-where $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$. The computation of this scalar is known due to Kondo.
+Notice that $\GaussSum{\tau}{\fieldCharacter}_0$ lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore, $$\GaussSum{\tau}{\fieldCharacter} \coloneqq \GaussSum{\tau}{\fieldCharacter}_0 = \GaussSumScalar{\tau}{\fieldCharacter} \cdot \idmap_\tau,$$
+where $\GaussSumScalar{\tau}{\fieldCharacter} \in \cComplex$.
+The computation of this scalar is known due to Kondo.
+Let us also denote for a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the \emph{twisted Gauss sum}
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
+This element also lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and we denote
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau,$$
+where $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$.
 
-We begin with the following simple observation. We have that for any $b \in B_r$ and any $X \in \Mat{r}{(n-r)}\left(\finiteField\right)$,
-$$ \pi\begin{pmatrix}
+Let us show that if $A$ is singular and $\tau$ does not contain $1$ in its cuspidal support then $\GaussSum{\tau}{\fieldCharacter}_A = 0$.
+We begin with the following simple observation.
+We have that for any $b \in B_r$ and any $X \in \Mat{r}{(n-r)}\left(\finiteField\right)$,
+$$ \tau\begin{pmatrix}
 	b & X\\
 	& \IdentityMatrix{n-r}
-\end{pmatrix} \circ \GaussSum{\pi}{\fieldCharacter}_r = \GaussSum{\pi}{\fieldCharacter}_r.$$
-Therefore, we have that $\GaussSum{\pi}{\fieldCharacter}_r$ can be regarded as an operator $\GaussSum{\pi}{\fieldCharacter}_r \colon \pi \to J\left(\pi, r\right)$, where $$J\left(\pi, r\right) = \left\{ v \in \pi \mid \pi \begin{pmatrix}
+\end{pmatrix} \circ \GaussSum{\tau}{\fieldCharacter}_r = \GaussSum{\tau}{\fieldCharacter}_r.$$
+Therefore, we have that $\GaussSum{\tau}{\fieldCharacter}_r$ can be regarded as an operator $\GaussSum{\tau}{\fieldCharacter}_r \colon \tau \to J\left(\tau, r\right)$, where $$J\left(\tau, r\right) = \left\{ v \in \tau \mid \tau \begin{pmatrix}
 	b & X\\
@@
 which is a representation of the group $B_r \times \GL_{n-r}\left(\finiteField\right)$.
-This space is non-zero if and only if $\pi$ is subrepresentation of a parabolically induced representation of the form $1^{\circ r} \circ \tau = 1 \circ \dots \circ 1 \circ \tau$, where $\tau$ is an irreducible representation of $\GL_{n-r}\left(\finiteField\right)$.
+This space is non-zero if and only if $\tau$ is subrepresentation of a parabolically induced representation of the form $1^{\circ r} \circ \tau = 1 \circ \dots \circ 1 \circ \tau$, where $\tau$ is an irreducible representation of $\GL_{n-r}\left(\finiteField\right)$.
 
-It follows from this observation that if $\pi$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $1$ is not in the cuspidal support of $\pi$, then for any matrix $A$ with rank $< n$,
-$$\GaussSum{\pi}{\fieldCharacter}_A \coloneqq \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(\trace\left(A g\right)\right) = 0.$$
+It follows from this observation that if $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $1$ is not in the cuspidal support of $\tau$, then for any matrix $A$ with rank $< n$, we have $\GaussSum{\tau}{\fieldCharacter}_A = 0$.
 
@@
 It is clear that $\Phi_{\chi}$ is a class function of $\GL_n\left(\finiteField\right)$.
-Given an irreducible representation $\pi$ of $\GL_n\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
-$$\dblGaussSum{\pi}{\chi} = \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \pi\left(g\right).$$
-Then $\dblGaussSum{\pi}{\chi}$ defines an element of $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$.
-Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\pi}{\chi} \in \cComplex$ such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
+Given an irreducible representation $\tau$ of $\GL_n\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
+$$\dblGaussSum{\tau}{\chi} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
+Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$.
+Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblGaussSum{\tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
 
-The goal of this section is to express $\dblGaussSumScalar{\pi}{\chi}$ in terms of Kondo's Gauss sum.
+The goal of this section is to express $\dblGaussSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.
 
-Assume first that $1$ does not appear in the cuspidal support of $\pi$. Let us write
-$$\dblGaussSum{\pi}{\chi} = \sum_{\substack{g \in \GL_n\left(\finiteField\right) \sum_{A \in \squareMatrix_n\left(\finiteField\right)}\\
-\det\left(g - \IdentityMatrix{n}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{n}\right)\right) \pi\left(g\right).$$
+Assume first that $1$ does not appear in the cuspidal support of $\tau$. Let us write
+$$\dblGaussSum{\tau}{\chi} = q^{-\frac{n^2}{2}} \sum_{\substack{g \in \GL_n\left(\finiteField\right) \\
+		\det\left(g - \IdentityMatrix{n}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{n}\right)\right) \tau\left(g\right).$$
 We rewrite this using a Fourier transform type expression
-$$\dblGaussSum{\pi}{\chi} = q^{-n^2} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$
+$$\dblGaussSum{\tau}{\chi} = q^{-\frac{3n^2}{2}} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$
 
@@
 \begin{align*}
-	\dblGaussSum{\pi}{\chi} &= q^{-n^2} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \pi\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
-	& \circ \sum_{g \in \GL_n\left(\finiteField\right)} \pi\left(g\right) \fieldCharacter\left(-\trace Ag\right).
+	\dblGaussSum{\tau}{\chi} =& q^{-\frac{3n^2}{2}} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
+	& \circ \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(-\trace Ag\right).
 \end{align*}
-Since the last inner sum is $\GaussSum{\pi}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$.
+Since the last inner sum is $q^{\frac{n^2}{2}} \GaussSum{\tau}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$.
 Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
 \begin{align*}
-	\dblGaussSum{\pi}{\chi} &= q^{-n^2} \centralCharacter{\pi}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter},
+	\dblGaussSumScalar{\tau}{\chi} &= q^{-\frac{n^2}{2}} \centralCharacter{\tau}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter},
 \end{align*}
@@
 \begin{align*}
-	\dblGaussSum{\pi}{\chi} &= \left(-1\right)^{n-1} q^{-n^2} \centralCharacter{\pi}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\pi} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\pi}{\fieldCharacter}.
+	\dblGaussSumScalar{\tau}{\chi} &=  \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter}.
 \end{align*}
+This is probably also true if $1$ is in the cuspidal support of $\tau$ (return to this later: probably can follow from a multiplicativity arguments).
+In the meantime, we will check this for $\tau = 1$ the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have
+$$\dblGaussSum{1}{\chi} = q^{-\frac{1}{2}} \sum_{\substack{x \in \multiplicativegroup{\finiteField} \\
+		x \ne 1}} \chi\left(x - 1\right) = q^{-\frac{1}{2}}\left(-1 + \sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \right) = \begin{dcases}
+		-q^{-\frac{1}{2}} & \chi \ne 1\\
+		q^{-\frac{1}{2}} \left(q - 2\right) & \chi = 1
+	\end{dcases}.$$
+
+\subsection{The case of classical groups}
+
+Let $\hermitianSpace$ be a vector space of dimension $n$ over $\finiteField$, equipped with a non-degenerate bilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \finiteField$ which is either symmetric or anti-symmetric.
+Let $G = \IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \innerproduct{x}{AY} = 0$ for every $x, y \in \hermitianSpace$.
+
+Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.
+As before, the assignment $\Phi_{\chi} \colon \GL\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
+\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right) & \text{if }\det\left(g - \idmap_{\hermitianSpace}\right) \ne 0\\
+0 & \text{otherwise,}
+\end{dcases}$$
+is a class function of $\GL\left(\hermitianSpace\right)$.
+
+Let $\pi$ be an irreducible representation of $G$. Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right),$$
+where  Since $\Phi_{\chi}$ is a class function of $\GL\left(\hermitianSpace\right)$, it is also a class function of $G$, and therefore $\dblGaussSum{\pi}{\chi} \in \Hom_{G}\left(\pi, \pi\right)$.
+By Schur's lemma, there exists a constant $\dblGaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
+We call $\dblGaussSumScalar{\pi}{\chi}$ the \emph{doubling method Gauss sum}.
+
+\subsubsection{Multiplicativity property}
+Our next goal is to understand how the doubling method Gauss sum behaves under parabolic induction.
+
+Let $\xIsotropic$ and $\yIsotropic$ be isotropic spaces of $\hermitianSpace$ of dimension $k$, such that $\xIsotropic$ and $\yIsotropic$ are in duality with respect to form $\innerproduct{\cdot}{\cdot}$.
+Let us write $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
+where $\hermitianSpace' \subset \hermitianSpace$ is a non-degenerate subspace, orthogonal to $\xIsotropic$ and $\yIsotropic$.
+Let $P$ be the parabolic subgroup of $G$, consisting of all elements stabilizing the flag $$0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.$$
+Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$.
+Then $L$ is isomorphic to $G' \times \GL_k\left(\finiteField\right)$, where $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
+
+\begin{theorem}
+	Let $\pi'$ be an irreducible representation of $G'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$.
+Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi \ne 1$, we have
+	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \chi\left(-1\right)^k q^{\frac{k^2}{2}} \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
+\end{theorem}
+\begin{proof}
+	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$.
+Consider $f \in \rho$ defined as follows.
+The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$.
+The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
+We compute $\dblGaussSum{\pi}{\chi} f$.
+
+	Notice that for $x \in G$, $$\left(\dblGaussSum{\pi}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
+	which can be rewritten as
+	$$\left(\dblGaussSum{\pi}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
+	As before, we may write
+	$$\Phi_{\chi}\left(g\right) = q^{-n^2} \sum_{h \in \GL\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing\left(\hermitianSpace\right)} \chi^{-1}\left(\det h\right) \fieldCharacter\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
+	Hence, \begin{align*}
+		q^{n^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing\left(\hermitianSpace\right)} \sum_{h \in \GL\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace\left(Ah\right)\right) \\
+		& \times \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Assume that $\chi \ne 1$.
+Then since $\GaussSum{\chi_{\GL\left(\hermitianSpace\right)}}{\fieldCharacter}_A$ appears in the last equation, the sum can be reduced to $A \in \GL\left(\hermitianSpace\right)$.
+Let us replace $h$ with $A^{-1} h$.
+We get the sum
+	\begin{align*}
+		\sum_{A \in \GL\left(\hermitianSpace\right)} \chi^{-1}\left(\det A\right) \sum_{h \in \GL\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace h\right) \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
+	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
+	\begin{align*}
+		q^{n^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL\left(\hermitianSpace\right)}  \chi\left(\det\left(xh\right)\right) \fieldCharacter\left(\trace h\right) \\
+		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\det p'\right) \fieldCharacter\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P$.
+
+	Hence, we have that $\left(\dblGaussSum{\pi}{\chi} f\right)\left(x\right)$ is supported on $P$.
+We move to compute $\left(\dblGaussSum{\pi}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$.
+It is given by
+	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
+		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P\\
+				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 1}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+	\end{equation}
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
+	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
+	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
+	\begin{equation}
+		\frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \chi\left(-1\right)^k \sum_{a \in \GL_k\left(\finiteField\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+	\end{equation}
+	which in turn is
+	$$\chi\left(-1\right)^k q^{\frac{k^2}{2}} \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}.$$
+\end{proof}
 

### 2024-12-12 paper.tex
Stuck

@@
 
-\title{Degenerate Gauss sums for $\GL_n\left(\finiteField_q\right)$}
+\title{On exponential sums arising from the doubling method}
 
@@
 \end{align*}
-This is probably also true if $1$ is in the cuspidal support of $\tau$ (return to this later: probably can follow from a multiplicativity arguments).
+This is probably also true if $1$ is in the cuspidal support of $\tau$  and $\chi \ne 1$ (return to this later: probably can follow from a multiplicativity arguments).
 In the meantime, we will check this for $\tau = 1$ the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have

### 2024-12-12 paper.tex
Some corrections and an identity with Deligne--Lusztig

@@
 
+We actually use this later only for the case $\tau = \chi_{\GL_n}$, i.e., $\tau\left(g\right) = \chi\left(\det g\right)$ for some character $1 \ne \chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$.
+Maybe rewrite for this case.
+The argument is also simpler.
+
 \section{Doubling method Gauss sums}
@@
 \end{align*}
-This is probably also true if $1$ is in the cuspidal support of $\tau$  and $\chi \ne 1$ (return to this later: probably can follow from a multiplicativity arguments).
-In the meantime, we will check this for $\tau = 1$ the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have
+This is probably also true if $1$ is in the cuspidal support of $\tau$  and $\chi \ne 1$ (return to this later: should follow from a multiplicativity arguments).
+In the meantime, we will check this for $\tau = 1$, the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have
 $$\dblGaussSum{1}{\chi} = q^{-\frac{1}{2}} \sum_{\substack{x \in \multiplicativegroup{\finiteField} \\
-		x \ne 1}} \chi\left(x - 1\right) = q^{-\frac{1}{2}}\left(-1 + \sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \right) = \begin{dcases}
-		-q^{-\frac{1}{2}} & \chi \ne 1\\
+		x \ne 1}} \chi\left(x - 1\right) = q^{-\frac{1}{2}}\left(-\chi\left(-1\right) + \sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \right) = \begin{dcases}
+		-q^{-\frac{1}{2}} \chi\left(-1\right) & \chi \ne 1\\
 		q^{-\frac{1}{2}} \left(q - 2\right) & \chi = 1
@@
 
-	Hence, we have that $\left(\dblGaussSum{\pi}{\chi} f\right)\left(x\right)$ is supported on $P$.
-We move to compute $\left(\dblGaussSum{\pi}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$.
-It is given by
+	Hence, we have that $\dblGaussSum{\pi}{\chi} f$ is supported on $P$. We move to compute $\left(\dblGaussSum{\pi}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
 	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
@@
 	which in turn is
-	$$\chi\left(-1\right)^k q^{\frac{k^2}{2}} \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}.$$
+	\begin{align*}
+		&\chi\left(-1\right)^k q^{\frac{k^2}{2}} \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'} \\
+		=& \chi\left(-1\right)^k q^{\frac{k^2}{2}} \dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+	\end{align*}
+	The result now follows.
 \end{proof}
+
+\subsubsection{Computation for irreducible cuspidal representations}
+
+\begin{theorem}
+	Suppose that $\pi$ is an irreducible cuspidal representation of $G$, parameterized by a character $\theta = \theta_1 \times \dots \times \theta_r$ of a torus $T$ isomorphic to $$T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \finiteFieldExtension{2n_r}^1,$$
+	where $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace$ if $\dim \hermitianSpace$ is even or $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace - 1$ if $\dim \hermitianSpace$ is odd, and where $$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
+	Then up to some signs and some power of $\GaussSumScalar{\chi}{\fieldCharacter}$, we have $$\dblGaussSumScalar{\pi}{\chi}= \prod_{j=1}^r \tau\left( \theta_j \times \chi, \fieldCharacter_{2n_j} \right),$$
+	where $$\tau\left( \theta_j \times \chi, \fieldCharacter_{2n_j}\right) = -\sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
+\end{theorem}
 

### 2024-12-12 paper.tex
Correction
Some corrections

@@
 Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi \ne 1$, we have
-	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \chi\left(-1\right)^k q^{\frac{k^2}{2}} \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
+	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \chi\left(-1\right)^k \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P\\
-				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 1}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
 	\end{equation}
 	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
-	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
+	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
 	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
 	\begin{equation}
-		\frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \chi\left(-1\right)^k \sum_{a \in \GL_k\left(\finiteField\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\finiteField\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
 	\end{equation}
@@
 	\begin{align*}
-		&\chi\left(-1\right)^k q^{\frac{k^2}{2}} \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'} \\
-		=& \chi\left(-1\right)^k q^{\frac{k^2}{2}} \dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+		&\chi\left(-1\right)^k  \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'} \\
+		=& \chi\left(-1\right)^k \dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
 	\end{align*}
@@
 	where $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace$ if $\dim \hermitianSpace$ is even or $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace - 1$ if $\dim \hermitianSpace$ is odd, and where $$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
-	Then up to some signs and some power of $\GaussSumScalar{\chi}{\fieldCharacter}$, we have $$\dblGaussSumScalar{\pi}{\chi}= \prod_{j=1}^r \tau\left( \theta_j \times \chi, \fieldCharacter_{2n_j} \right),$$
-	where $$\tau\left( \theta_j \times \chi, \fieldCharacter_{2n_j}\right) = -\sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
+	Then up to some signs and some power of $\GaussSumScalar{\chi}{\fieldCharacter}$, we have $$\dblGaussSumScalar{\pi}{\chi}= \prod_{j=1}^r \tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j} \right),$$
+	where $\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{m_j}}\right)$ and $$\tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j}\right) = -\sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta'_j\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
 \end{theorem}

### 2024-12-12 paper.tex
Defining gamma factors

@@
 \newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
+\newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
 \newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
@@
 
-Consider the following assignment $\GL_n\left(\finiteField\right) \to \cComplex$
+Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
 $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-	\chi\left(\det\left(g-\IdentityMatrix{n}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{n}\right) \ne 0,\\
+	\chi\left(\det\left(g-\IdentityMatrix{k}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{k}\right) \ne 0,\\
 	0 & \text{otherwise.}
 \end{dcases}$$
-It is clear that $\Phi_{\chi}$ is a class function of $\GL_n\left(\finiteField\right)$.
-Given an irreducible representation $\tau$ of $\GL_n\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
-$$\dblGaussSum{\tau}{\chi} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
-Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$.
+It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.
+Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
+$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
+Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$.
 Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblGaussSum{\tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
@@
 Assume first that $1$ does not appear in the cuspidal support of $\tau$. Let us write
-$$\dblGaussSum{\tau}{\chi} = q^{-\frac{n^2}{2}} \sum_{\substack{g \in \GL_n\left(\finiteField\right) \\
-		\det\left(g - \IdentityMatrix{n}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{n}\right)\right) \tau\left(g\right).$$
+$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{\substack{g \in \GL_k\left(\finiteField\right) \\
+		\det\left(g - \IdentityMatrix{k}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{k}\right)\right) \tau\left(g\right).$$
 We rewrite this using a Fourier transform type expression
-$$\dblGaussSum{\tau}{\chi} = q^{-\frac{3n^2}{2}} \sum_{g, h \in \GL_n\left(\finiteField\right)} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{n} - h \left(g - \IdentityMatrix{n}\right)\right)\right)\right).$$
+$$\dblGaussSum{\tau}{\chi} = q^{-\frac{3k^2}{2}} \sum_{g, h \in \GL_k\left(\finiteField\right)} \sum_{A \in \squareMatrix_k\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{k} - h \left(g - \IdentityMatrix{k}\right)\right)\right)\right).$$
 
@@
 \begin{align*}
-	\dblGaussSum{\tau}{\chi} =& q^{-\frac{3n^2}{2}} \sum_{A \in \squareMatrix_n\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_n\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
-	& \circ \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(-\trace Ag\right).
+	\dblGaussSum{\tau}{\chi} =& q^{-\frac{3k^2}{2}} \sum_{A \in \squareMatrix_k\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_k\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
+	& \circ \sum_{g \in \GL_k\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(-\trace Ag\right).
 \end{align*}
-Since the last inner sum is $q^{\frac{n^2}{2}} \GaussSum{\tau}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_n\left(\finiteField\right)$.
+Since the last inner sum is $q^{\frac{k^2}{2}} \GaussSum{\tau}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_k\left(\finiteField\right)$.
 Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
 \begin{align*}
-	\dblGaussSumScalar{\tau}{\chi} &= q^{-\frac{n^2}{2}} \centralCharacter{\tau}\left(-1\right) \sum_{A \in \GL_n\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter},
+	\dblGaussSumScalar{\tau}{\chi} &= q^{-\frac{k^2}{2}} \centralCharacter{\tau}\left(-1\right) \sum_{A \in \GL_k\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter},
 \end{align*}
@@
 \begin{align*}
-	\dblGaussSumScalar{\tau}{\chi} &=  \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^n \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter}.
+	\dblGaussSumScalar{\tau}{\chi} &=  \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter}.
 \end{align*}
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
 	Let $\pi'$ be an irreducible representation of $G'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$.
 Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi \ne 1$, we have
-	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \chi\left(-1\right)^k \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
+	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 	\begin{align*}
-		&\chi\left(-1\right)^k  \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'} \\
-		=& \chi\left(-1\right)^k \dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+		&\chi\left(-1\right)^k \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}\\
+		=& \chi\left(-1\right)^k\dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
 	\end{align*}
@@
 
+\subsubsection{Gamma factors}
+In order to make the computations more tolerable, it is beneficial to work with fully multiplicative functions. We introduce the doubling method gamma factors.
+
+Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.
+
+For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left[\frac{\dim \hermitianSpace}{2}\right]}}.$$
+Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
+
+\begin{theorem}
+	\begin{enumerate}
+		\item If $\tau_1$ and $\tau_2$ are irreducible representations of $\GL_{k_1}\left(\finiteField\right)$ and $\GL_{k_2}\left(\finiteField\right)$, respectively, then for any irreducible subrepresentation $\tau$ of the parabolic induction $\tau_1 \circ \tau_2$, we have
+		$$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \dblGammaFactor{\tau_1}{\chi}{\fieldCharacter} \dblGammaFactor{\tau_2}{\chi}{\fieldCharacter}.$$
+		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\chi \ne 1$, then
+		$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \dblGammaFactor{\tau}{\chi}{\fieldCharacter}.$$
+	\end{enumerate}
+\end{theorem}
+
 \subsubsection{Computation for irreducible cuspidal representations}
@@
 \begin{theorem}
-	Suppose that $\pi$ is an irreducible cuspidal representation of $G$, parameterized by a character $\theta = \theta_1 \times \dots \times \theta_r$ of a torus $T$ isomorphic to $$T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \finiteFieldExtension{2n_r}^1,$$
+	Suppose that $\pi$ is an irreducible cuspidal representation of $G$, parameterized by a character $\theta = \theta_1 \times \dots \times \theta_r$ of a torus $T$ such that $$T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \times \finiteFieldExtension{2n_r}^1,$$
 	where $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace$ if $\dim \hermitianSpace$ is even or $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace - 1$ if $\dim \hermitianSpace$ is odd, and where $$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
-	Then up to some signs and some power of $\GaussSumScalar{\chi}{\fieldCharacter}$, we have $$\dblGaussSumScalar{\pi}{\chi}= \prod_{j=1}^r \tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j} \right),$$
-	where $\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{m_j}}\right)$ and $$\tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j}\right) = -\sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta'_j\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
+	Then up to maybe a sign, we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \prod_{j=1}^r \tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j} \right),$$
+	where $\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{n_j}}\right)$ and $$\tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j}\right) = -q^{-n_j} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta'_j\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
 \end{theorem}

### 2024-12-12 paper.tex
Adding Calvin

@@
 
-\hypersetup{pdfauthor={Elad Zelingher},
+\hypersetup{pdfauthor={Calvin Yost-Wolff, Elad Zelingher},
 	pdfsubject={Number theory, Representation theory},
@@
 
-\title{On exponential sums arising from the doubling method}
+\title{On exponential sums arising from the classical doubling method}
+
+\author{Calvin Yost-Wolff}
+\address{Department of Mathematics, University of Michigan, 3084 East Hall, 530 Church Street, Ann Arbor, MI 48109-1043 USA}
+\email{calvinyw@umich.edu}
 

### 2024-12-13 paper.tex
Cleanup
Slight correction

@@
 Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.
-
-For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left[\frac{\dim \hermitianSpace}{2}\right]}}.$$
+For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left[\frac{\dim \hermitianSpace}{2}\right]}}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

### 2024-12-16 paper.tex
Writing the basic Gauss sum computation of a torus

@@
 	Let $\pi'$ be an irreducible representation of $G'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$.
-Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi \ne 1$, we have
+Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\chi^2 \ne 1$, we have
 	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
@@
 
+\subsubsection{Basic torus computation}
+In this section we compute the doubling method Gauss sum for a torus of the form $\finiteFieldExtension{2m}^1$.
+
+If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
+where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} : \finiteField}$.
+
+Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters.
+Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
+		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right).$$
+
+As usual, we rewrite this sum as follows
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
+If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
+$$-q^{-m} \tau\left(\chi \circ \FieldNorm{2m}{1}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
+To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \finiteFieldExtension{2m}^1$ given by $t \mapsto t^{1 - q^m}$.
+This map is surjective, and its kernel is $\multiplicativegroup{\finiteFieldExtension{m}}$.
+Denote $\beta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\beta\left(t\right) = \theta\left(t^{1-q^m}\right)$.
+Replacing the sum over $x \in \finiteFieldExtension{2m}^1$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
+	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
+	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \beta \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
+\end{align*}
+Replacing $z$ with $t^{q^m} z$, this becomes
+\begin{align*}
+	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \beta \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
+\end{align*}
+Since $\chi \circ \FieldNorm{2m}{1} \ne \beta$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
+Hence, we may replace the sum over $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
+Using the fact that $\beta$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,
+\begin{align*}
+	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
+	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \beta \left(t\right) \fieldCharacter_{2m}\left(t\right).
+\end{align*}
+By the appendix, this equals
+\begin{align*}
+	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \beta \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
+\end{align*}
+
+To summarize, we have
+$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
+		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\beta \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+	where $\beta\left(t\right) = \theta\left(t^{1-q^m}\right)$.
+Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
+$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
+		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\beta \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+
 \subsubsection{Computation for irreducible cuspidal representations}
@@
 
+\appendix
+\section{Evaluation of an exponential sum}
+
+In this appendix, we evaluate the following exponential sum.
+Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+We compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
+	\trace_{\finiteFieldExtension{2} \slash \finiteField}\left(x\right) \ne 0}} \chi\left(\FieldNorm{2}{1}\left(\frac{x}{\trace_{\finiteFieldExtension{2} \colon \finiteField} x}\right) \right).$$
+As usual, we rewrite this sum as
+$$\frac{1}{q} \sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}} \chi\left(\FieldNorm{2}{1}\left(xy\right)\right) \fieldCharacter\left(z\left(y \trace_{\finiteFieldExtension{2} \slash \finiteField} x - 1\right)\right).$$
+It is clear that if $z = 0$, then the sum over $x$ will vanish.
+Hence, we may reduce the sum to a sum over $z \in \multiplicativegroup{\finiteField}$.
+By replacing $y$ with $z^{-1} y$ and then replacing $z$ with $-z$, we arrive at the sum
+$$\frac{1}{q} \sum_{y \in \multiplicativegroup{\finiteField}} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}} \chi\left(\FieldNorm{2}{1}\left(xy\right)\right) \fieldCharacter\left(y \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{z \in \multiplicativegroup{\finiteField}} \chi^{-2}\left(z\right)\fieldCharacter\left(z\right).$$
+Replacing $x$ with $y^{-1}x$, and using the Hasse--Davenport relation, we arrive at the sum
+$$q^{\frac{1}{2}} \left(q-1\right) \tau\left(\chi, \fieldCharacter\right)^2 \tau\left(\chi^{-2}, \fieldCharacter\right).$$
 \bibliographystyle{abbrv}

### 2024-12-16 paper.tex
Adding assumption

@@
 
-Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters.
+Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\theta \ne \chi \circ \FieldNorm{2m}{1}$.
 Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\

### 2024-12-16 paper.tex
Replacing \beta with \theta'

--- 2024-12-16 paper.tex
@@
 where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} : \finiteField}$.
+If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote
+$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right),$$
 
-Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters.
+Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \FieldNorm{2m}{1}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
 Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
@@
 This map is surjective, and its kernel is $\multiplicativegroup{\finiteFieldExtension{m}}$.
-Denote $\beta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\beta\left(t\right) = \theta\left(t^{1-q^m}\right)$.
+Define $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
 Replacing the sum over $x \in \finiteFieldExtension{2m}^1$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
 	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
-	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \beta \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
+	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
 \end{align*}
@@
 \begin{align*}
-	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \beta \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
+	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
 \end{align*}
-Since $\chi \circ \FieldNorm{2m}{1} \ne \beta$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
+Since $\chi \circ \FieldNorm{2m}{1} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
 Hence, we may replace the sum over $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
-Using the fact that $\beta$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,
+Using the fact that $\theta'$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,
 \begin{align*}
 	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
-	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \beta \left(t\right) \fieldCharacter_{2m}\left(t\right).
+	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
 \end{align*}
@@
 \begin{align*}
-	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \beta \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
+	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
 \end{align*}
@@
 $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\beta \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
-	where $\beta\left(t\right) = \theta\left(t^{1-q^m}\right)$.
+		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+	where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
 Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
 $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\beta \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
 

### 2024-12-20 paper.tex
Arriving at a new exotic Kloosterman sum!

@@
 \newcommand{\lieAlgebra}{\mathfrak{g}}
+\newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
 
@@
 $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
 	where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
@@
 $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter_m\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
 
@@
 \end{theorem}
+
+\subsubsection{Computation for Lusztig series}
+
+Let $T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \times \finiteFieldExtension{2n_r}^1 \times \multiplicativegroup{\finiteFieldExtension{m_1}} \times \dots \multiplicativegroup{\finiteFieldExtension{m_s}}$ be a torus such that $\sum_{i=1}^r 2n_i + \sum_{j=1}^s 2m_j = \dim_{\finiteField} \hermitianSpace$.
+Let $\theta = \alpha_1 \times \dots \times \alpha_r \times \beta_1 \times \dots \times \beta_s$.
+Consider the Deligne--Lusztig induction $\DeligneLusztigInduction{T}{G}\theta$.
+Write $$\DeligneLusztigInduction{T}{G}\theta = \sum_{\pi} c_{\pi} \cdot \trace \pi,$$
+where $\pi$ goes over all the irreducible representations of $G$ and $c_{\pi} \in \zIntegers$.
+Then for any irreducible $\pi$ such that $c_{\pi} \ne 0$, and any $\chi$ such that $\chi^2 \ne 1$, we have
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = q^{-\frac{\dim \hermitianSpace}{2}} \prod_{j=1}^r \GaussSumScalar{\alpha'_j \times \chi^{-1}}{\fieldCharacter_{2n_j}} \prod_{i=1}^s \GaussSumScalar{\beta_i \times \chi^{-1}}{\fieldCharacter_{m_i}} \GaussSumScalar{\beta_i^{-1} \times \chi^{-1}}{\fieldCharacter_{m_i}}.$$
+
+\subsection{Kloosterman type sums}
+
+Let $\chi_1, \dots, \chi_k \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\chi_i^2 \ne 1$ for any $i$.
+Consider the assignment $K \colon G \to \cComplex$ given by $$K\left(x\right) = K_{\chi_1,\dots,\chi_k}\left(x\right) = \sum_{\substack{g_1, \dots, g_k \in G\\
+g_1 \dots g_k = x}} \Phi_{\chi_1}\left(g_1\right) \dots \Phi_{\chi_k}\left(g_k\right).$$
+It is clear that $K$ is a class function of $G$. Let $\pi$ be an irreducible representation of $G$. Then \begin{align*}
+	 \innerproduct{K}{\conjugate{\trace \pi}} &= \frac{1}{\sizeof{G}}\trace \left(\sum_{g_1,\dots,g_k \in G} \Phi_{\chi_1}\left(g_1\right) \dots \Phi_{\chi_k}\left(g_k\right) \pi\left(g_1 \dots g_k\right) \right) \\
+	 &= \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}}}{\sizeof{G}} \trace\left( \dblGaussSum{\pi}{\chi_1} \circ \dots \dblGaussSum{\pi}{\chi_k} \right).
+\end{align*}
+Thus $$\innerproduct{K}{\conjugate{\trace \pi}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \dim \pi}{\sizeof{G}} \cdot \prod_{j=1}^k \dblGaussSumScalar{\pi}{\chi_j}.$$
+It follows that if
+$$\DeligneLusztigInduction{T}{G}\theta = \sum_{\pi} c_{\pi} \cdot \trace \pi,$$
+then $$\innerproduct{K}{\conjugate{\DeligneLusztigInduction{T}{G}\theta}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblGaussSumScalar{\pi}{\chi_j}}{\sizeof{G}} \sum_{\pi} c_{\pi} \dim \pi = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblGaussSumScalar{\pi}{\chi_j}}{\sizeof{G}} \left(\DeligneLusztigInduction{T}{G}\theta\right)\left(1\right),$$
+where $\pi$ is any irreducible representation of $G$ such that $c_{\pi} \ne 0$.
+
+Suppose that $T \cong \finiteFieldExtension{m}^1$, and let $t \in T$ be an element such that $t$ is contained only in the torus $T$. Then
+$$K\left(t\right) = \sum_{\theta} \theta\left(t\right) \innerproduct{K}{\DeligneLusztigInduction{T}{G}\left(\theta\right)},$$
+where the sum is over all the characters of $T$.
+Using the formula $$\dblGaussSumScalar{\pi}{\chi} = \tau\left( \theta' \times \chi^{-1}, \fieldCharacter_{2m} \right) \theta\left(-1\right) \tau\left(\chi^2, \fieldCharacter\right)^m,$$
+we get
+$$K\left(t\right) = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \cdot \DeligneLusztigInduction{T}{G}\left(\theta\right)\left(1\right)}{\sizeof{G}} \sum_{\theta} \theta\left( \left(-1\right)^k t\right) \prod_{j=1}^k \tau\left(\theta' \times \chi_j^{-1}, \fieldCharacter_{2m}\right) \tau\left(\chi_j^2, \fieldCharacter\right)^m.$$
+
+Expanding the last sum, we have
+\begin{align*}
+	K\left(t\right) = & \frac{\left(-1\right)^k q^{-km}  \sizeof{\lieAlgebra}^{\frac{k}{2}} \DeligneLusztigInduction{T}{G}\left(\theta\right)\left(1\right)}{\sizeof{G}} \cdot \prod_{j=1}^k \tau\left(\chi_j^2, \fieldCharacter\right)^m \\
+	 & \times \sum_{\theta} \sum_{\xi_1,\dots,\xi_k \in \multiplicativegroup{\finiteFieldExtension{2m}}} \theta\left( \left(-1\right)^k t \xi_1^{1-q^m} \dots \xi_k^{1-q^m} \right) \fieldCharacter_{2m}\left(\sum_{j=1}^k \xi_j\right) \prod_{j=1}^k \chi_j\left(\FieldNorm{2m}{1}\left(\xi_1^{-1} \right)\right).
+\end{align*}
+The sum on the second row becomes
+$$\sum_{\substack{\xi_1,\dots,\xi_k \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
+\prod_{j=1}^k \xi_j^{1-q^m} = \left(-1\right)^k t^{-1}}} \left(\prod_{j=1}^k \chi_j^{-1}\left(\FieldNorm{2m}{1}\left(\xi_j \right)\right)\right) \fieldCharacter_{2m}\left(\sum_{j=1}^k \xi_j\right).$$
 

### 2025-01-01 paper.tex
Minor corrections

@@
 
-Let $\pi$ be an irreducible representation of $G$. Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right),$$
-where  Since $\Phi_{\chi}$ is a class function of $\GL\left(\hermitianSpace\right)$, it is also a class function of $G$, and therefore $\dblGaussSum{\pi}{\chi} \in \Hom_{G}\left(\pi, \pi\right)$.
+Let $\pi$ be an irreducible representation of $G$. Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
+Since $\Phi_{\chi}$ is a class function of $\GL\left(\hermitianSpace\right)$, it is also a class function of $G$, and therefore $\dblGaussSum{\pi}{\chi} \in \Hom_{G}\left(\pi, \pi\right)$.
 By Schur's lemma, there exists a constant $\dblGaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
@@
 The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
-We compute $\dblGaussSum{\pi}{\chi} f$.
+We compute $\dblGaussSum{\rho}{\chi} f$.
 
-	Notice that for $x \in G$, $$\left(\dblGaussSum{\pi}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
+	Notice that for $x \in G$, $$\left(\dblGaussSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
 	which can be rewritten as
-	$$\left(\dblGaussSum{\pi}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
+	$$\left(\dblGaussSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
 	As before, we may write
@@
 
-	Hence, we have that $\dblGaussSum{\pi}{\chi} f$ is supported on $P$. We move to compute $\left(\dblGaussSum{\pi}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
+	Hence, we have that $\dblGaussSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblGaussSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
 	\begin{equation}\label{eq:recursive-doubling-gauss-sum}

### 2025-01-24 paper.tex
Nicer proof

@@
 Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-For any $r \ge 0$, let $B_r \subset \GL_r\left(\finiteField\right)$ be the standard Borel subgroup
-$$B_r = \left\{ \begin{pmatrix}
-	t_1 & \ast & \ast & \ast\\
-	& t_2 & \ast & \ast \\
-	& & \ddots & \ast\\
-	& & & t_r
-\end{pmatrix} \mid t_1,\dots,t_r \in \multiplicativegroup{\finiteField} \right\}.$$
 
-\section{Degenerate Gauss sums}
-Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. For a matrix $A \in \squareMatrix_n\left(\finiteField\right)$, denote
-$$\GaussSum{\tau}{\fieldCharacter}_A \coloneqq q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(\trace\left(A g\right)\right).$$
-For any such $A$, there exist $h_1, h_2 \in \GL_n\left(\finiteField\right)$ and $0 \le r \le n$, such that $A = h_1 \begin{pmatrix}
-	0_r\\
-	& \IdentityMatrix{n-r}
-\end{pmatrix} h_2$. Changing variables, we see that $$\GaussSum{\tau}{\fieldCharacter}_A = \tau \left(h_2^{-1}\right) \circ \GaussSum{\tau}{\fieldCharacter}_r \circ \tau\left(h_1^{-1}\right),$$
-where
-$$\GaussSum{\tau}{\fieldCharacter}_r = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(\trace\left(g \begin{pmatrix}
-	0_{r}\\
-	& \IdentityMatrix{n-r}
-\end{pmatrix}\right)\right).$$
-Notice that $\GaussSum{\tau}{\fieldCharacter}_0$ lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore, $$\GaussSum{\tau}{\fieldCharacter} \coloneqq \GaussSum{\tau}{\fieldCharacter}_0 = \GaussSumScalar{\tau}{\fieldCharacter} \cdot \idmap_\tau,$$
-where $\GaussSumScalar{\tau}{\fieldCharacter} \in \cComplex$.
-The computation of this scalar is known due to Kondo.
-Let us also denote for a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the \emph{twisted Gauss sum}
+\section{Kondo Gauss sums}
+Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. 
+For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
 $$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
-This element also lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and we denote
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau,$$
-where $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$.
-
-Let us show that if $A$ is singular and $\tau$ does not contain $1$ in its cuspidal support then $\GaussSum{\tau}{\fieldCharacter}_A = 0$.
-We begin with the following simple observation.
-We have that for any $b \in B_r$ and any $X \in \Mat{r}{(n-r)}\left(\finiteField\right)$,
-$$ \tau\begin{pmatrix}
-	b & X\\
-	& \IdentityMatrix{n-r}
-\end{pmatrix} \circ \GaussSum{\tau}{\fieldCharacter}_r = \GaussSum{\tau}{\fieldCharacter}_r.$$
-Therefore, we have that $\GaussSum{\tau}{\fieldCharacter}_r$ can be regarded as an operator $\GaussSum{\tau}{\fieldCharacter}_r \colon \tau \to J\left(\tau, r\right)$, where $$J\left(\tau, r\right) = \left\{ v \in \tau \mid \tau \begin{pmatrix}
-	b & X\\
-	& \IdentityMatrix{n-r}
-\end{pmatrix} v = v, \forall b \in B_r, X \in \Mat{r}{(n-r)}\left(\finiteField\right) \right\},$$
-which is a representation of the group $B_r \times \GL_{n-r}\left(\finiteField\right)$.
-This space is non-zero if and only if $\tau$ is subrepresentation of a parabolically induced representation of the form $1^{\circ r} \circ \tau = 1 \circ \dots \circ 1 \circ \tau$, where $\tau$ is an irreducible representation of $\GL_{n-r}\left(\finiteField\right)$.
-
-It follows from this observation that if $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $1$ is not in the cuspidal support of $\tau$, then for any matrix $A$ with rank $< n$, we have $\GaussSum{\tau}{\fieldCharacter}_A = 0$.
-
-We actually use this later only for the case $\tau = \chi_{\GL_n}$, i.e., $\tau\left(g\right) = \chi\left(\det g\right)$ for some character $1 \ne \chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$.
-Maybe rewrite for this case.
-The argument is also simpler.
+This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
 
@@
 
-Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.
+Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
 
@@
 It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.
+
 Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
@@
 
-Assume first that $1$ does not appear in the cuspidal support of $\tau$. Let us write
-$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{\substack{g \in \GL_k\left(\finiteField\right) \\
-		\det\left(g - \IdentityMatrix{k}\right) \ne 0}} \chi\left(\det\left(g - \IdentityMatrix{k}\right)\right) \tau\left(g\right).$$
-We rewrite this using a Fourier transform type expression
-$$\dblGaussSum{\tau}{\chi} = q^{-\frac{3k^2}{2}} \sum_{g, h \in \GL_k\left(\finiteField\right)} \sum_{A \in \squareMatrix_k\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(g\right) \fieldCharacter\left(\trace\left(A \left(\IdentityMatrix{k} - h \left(g - \IdentityMatrix{k}\right)\right)\right)\right).$$
+\begin{proposition}
+	We have the identity
+	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
+\end{proposition}
+\begin{proof}
+	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+	We claim that for a singular matrix $X \in \squareMatrix_k\left(\finiteField\right)$ the inner sum vanishes. To show this, write $$X = h_1 \begin{pmatrix}
+		\IdentityMatrix{k-r}\\
+		& 0_r
+	\end{pmatrix} h_2,$$
+	where $1 \le r \le k$ and $h_1, h_2 \in \GL_k\left(\finiteField\right)$. Then
+	$$\fieldCharacter\left(\trace Xh\right) = \fieldCharacter\left(\trace\left( \begin{pmatrix}
+		\IdentityMatrix{k-r}\\
+		& 0_r
+	\end{pmatrix} h_2 h h_1\right)\right).$$
+	Changing variables $h \mapsto h_2^{-1} h h_1^{-1},$
+	we obtain the inner sum
+	$$\sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
+		\IdentityMatrix{k-r}\\
+		& 0_r
+	\end{pmatrix} h \right) \chi\left(\det h\right),$$
+	which equals
+	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
+		\IdentityMatrix{k-r}\\
+		& 0_r
+	\end{pmatrix} \begin{pmatrix}
+		\IdentityMatrix{k-1}\\
+		& a
+	\end{pmatrix} h \right) \chi\left(\det h\right).$$
+	Changing variables $h \mapsto \left(\begin{smallmatrix}
+		\IdentityMatrix{k-1}\\
+		& a^{-1}
+	\end{smallmatrix}\right) h$, we get the inner sum $$\sum_{a \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(a\right),$$
+	which vanishes because $\chi \ne 1$.
+	Hence, we have
+	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+	Changing variables $h \mapsto X^{-1} h$, we get
+	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
+	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get the equality 
+	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
+\end{proof}
 
-Replacing $g$ with $h^{-1} g$, we arrive at the expression
-\begin{align*}
-	\dblGaussSum{\tau}{\chi} =& q^{-\frac{3k^2}{2}} \sum_{A \in \squareMatrix_k\left(\finiteField\right)} \fieldCharacter\left(\trace A\right) \sum_{h \in \GL_k\left(\finiteField\right)} \chi^{-1}\left(\det h\right) \tau\left(h^{-1}\right) \fieldCharacter\left(\trace\left(Ah\right)\right)\\
-	& \circ \sum_{g \in \GL_k\left(\finiteField\right)} \tau\left(g\right) \fieldCharacter\left(-\trace Ag\right).
-\end{align*}
-Since the last inner sum is $q^{\frac{k^2}{2}} \GaussSum{\tau}{\fieldCharacter}_{-A}$, we have that the sum can be reduced to $A \in \GL_k\left(\finiteField\right)$.
-Replacing $h$ with $A^{-1} h$ and $g$ with $-A^{-1} g$, we get the sum
-\begin{align*}
-	\dblGaussSumScalar{\tau}{\chi} &= q^{-\frac{k^2}{2}} \centralCharacter{\tau}\left(-1\right) \sum_{A \in \GL_k\left(\finiteField\right)} \chi\left(\det A\right) \fieldCharacter\left(\trace A\right) \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter},
-\end{align*}
-which equals
-\begin{align*}
-	\dblGaussSumScalar{\tau}{\chi} &=  \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\tau}{\fieldCharacter}.
-\end{align*}
-This is probably also true if $1$ is in the cuspidal support of $\tau$  and $\chi \ne 1$ (return to this later: should follow from a multiplicativity arguments).
-In the meantime, we will check this for $\tau = 1$, the trivial representation of $\GL_1\left(\finiteField\right)$, in which case we have
-$$\dblGaussSum{1}{\chi} = q^{-\frac{1}{2}} \sum_{\substack{x \in \multiplicativegroup{\finiteField} \\
-		x \ne 1}} \chi\left(x - 1\right) = q^{-\frac{1}{2}}\left(-\chi\left(-1\right) + \sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \right) = \begin{dcases}
-		-q^{-\frac{1}{2}} \chi\left(-1\right) & \chi \ne 1\\
-		q^{-\frac{1}{2}} \left(q - 2\right) & \chi = 1
-	\end{dcases}.$$
+We now use this to compute $\dblGaussSum{\tau}{\chi}$.
+We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
+The last equality implies $$\dblGaussSum{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSum{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
 

### 2025-02-07 paper.tex
Started writing about Saito-Shinoda

@@
 \newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblVirtualGaussSumScalar}[2]{\mathrm{g}^{\mathrm{dbl}}\left(#1, #2\right)}
 \newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
@@
 \newcommand{\DeligneLusztigInduction}[2]{\mathrm{R}_{#1}^{#2}}
+\newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
 
@@
 
+\subsection{Computation in terms of Deligne--Lusztig data}
+
+The goal of this section is to compute $\dblGaussSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
+
+Let us realize $G$ as the fixed points of the Frobenius map $\Frobenius$ acting on a connected reductive algebraic group $\algebraicGroup{G}$.
+
+Given a class function $F \colon G \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualGaussSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
+
+It is clear that if $\pi$ is an irreducible representation of $G$ then $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \dim \pi.$$
+Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in G$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
+\begin{proposition}
+	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{G}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
+	$$ \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{G}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+\end{proposition}
+In particular, if $\theta$ is in general position, then $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $G$ and we have that for this $\pi$,
+$$\dblGaussSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \sizeof{G}_p \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+Here $\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{G}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{G}_p$ is the size of the $p$-Sylow group of $G$, where $p$ is the characteristic of $\finiteField$.
+
 \subsubsection{Basic torus computation}

### 2025-02-07 paper.tex
Some corrections

@@
 \end{proposition}
-In particular, if $\theta$ is in general position, then $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $G$ and we have that for this $\pi$,
-$$\dblGaussSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \sizeof{G}_p \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $G$ and we have that for this $\pi$,
+$$\dblGaussSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{G}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
 Here $\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{G}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{G}_p$ is the size of the $p$-Sylow group of $G$, where $p$ is the characteristic of $\finiteField$.

### 2025-02-07 paper.tex
Trying to reduce to Kondo's

@@
 We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
-The last equality implies $$\dblGaussSum{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSum{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+The last equality implies the following result.
+\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
+	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+\end{theorem}
 
@@
 
-\subsubsection{Basic torus computation}
+\subsubsection{General linear groups computation}
+Suppose that $F \colon \GL_k\left(\finiteField\right) \to \cComplex$ is a class function.
+If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a non-trivial character, we define $$\dblVirtualGaussSumScalar{F}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) F\left(g\right).$$
+It is clear that for an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we have $$\dblVirtualGaussSumScalar{\trace \tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \dim \tau.$$
+Since the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ depends only on the semisimple part of $g$, by \cite[Theorem in Section 1.2]{SaitoShinoda2000} we have that if $T \cong \multiplicativegroup{\finiteFieldExtension{k}}$ and if $\theta \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ is a character then
+$$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2}{2}}} \sum_{\substack{t \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+t \ne 1}} \theta\left(t\right) \chi\left(\FieldNorm{k}{1}\left(t-1\right)\right).$$
+Using \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} and the fact that Kondo's Gauss sum is the same for every subrepresentation of $R_{T, \theta}$, we have the equality $$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \left(-1\right)^k \theta\left(-1\right) q^{-k} R_{T, \theta}\left(1\right) \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+
+\subsubsection{Split torus computation}
+In this section we compute the doubling method Gauss sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
+Let $\theta \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\chi^2 \ne 1$.
+Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(x^{-1} - 1\right)\right).$$
+
+This can be rewritten as
+$$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+		x \ne 1}} \theta \left(x\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(x\right)\right) \chi^2\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
+Denote by $\theta_{\chi^{-1}} \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ the character $$\theta_{\chi^{-1}}\left(x\right) = \theta\left(x\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(x\right)\right).$$
+
+Hence we get
+$$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(x^{-1} - 1\right)\right) = \frac{q^{\frac{k^2}{2}}}{\grpIndex{\GL_k\left(\finiteField\right)}{T}} \dblVirtualGaussSumScalar{R_{T, \theta_{\chi^{-1}}}}{\chi^2},$$
+which by the results of the previous section equals
+%$$R_{T,\theta}\left(1\right) = \left(-1\right)^{k-1} \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2 - k}{2}}}$$
+$$-\theta\left(-1\right) q^{-\frac{k}{2}} \tau\left(\chi^4, \fieldCharacter\right)^k \tau\left(\theta \times \chi^{-1}, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+
+\subsubsection{Elliptic torus computation}
 In this section we compute the doubling method Gauss sum for a torus of the form $\finiteFieldExtension{2m}^1$.
@@
 
-Suppose that $T \cong \finiteFieldExtension{m}^1$, and let $t \in T$ be an element such that $t$ is contained only in the torus $T$. Then
+Suppose that $T \cong \finiteFieldExtension{2m}^1$, and let $t \in T$ be an element such that $t$ is contained only in the torus $T$. Then
 $$K\left(t\right) = \sum_{\theta} \theta\left(t\right) \innerproduct{K}{\DeligneLusztigInduction{T}{G}\left(\theta\right)},$$

### 2025-02-07 paper.tex
Some corrections

@@
 \newcommand{\ExoticKloosterman}{\mathrm{Kl}}
-\newcommand{\GaussSumCharacter}[4]{\tau_{#1}\left(#2 \times #3, #4\right)}
+\newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
 \newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
@@
 t \ne 1}} \theta\left(t\right) \chi\left(\FieldNorm{k}{1}\left(t-1\right)\right).$$
-Using \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} and the fact that Kondo's Gauss sum is the same for every subrepresentation of $R_{T, \theta}$, we have the equality $$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \left(-1\right)^k \theta\left(-1\right) q^{-k} R_{T, \theta}\left(1\right) \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+Using \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} and the fact that Kondo's Gauss sum is the same for every subrepresentation of $R_{T, \theta}$, we have the equality $$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \left(-1\right)^k \theta\left(-1\right) q^{-\frac{3k}{2}} R_{T, \theta}\left(1\right) \tau\left(\chi, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
 
@@
 which by the results of the previous section equals
+%$$\frac{q^{\frac{k^2}{2}}}{\grpIndex{\GL_k\left(\finiteField\right)}{T}} \left(-1\right)^k \theta\left(-1\right) q^{-\frac{3k}{2}} R_{T, \theta}\left(1\right) \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).
+$$
+%$$\frac{q^{\frac{k^2}{2}}}{\grpIndex{\GL_k\left(\finiteField\right)}{T}} \left(-1\right)^k \theta\left(-1\right) q^{-\frac{3k}{2}} \left(-1\right)^{k-1} \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2 - k}{2}}} \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
 %$$R_{T,\theta}\left(1\right) = \left(-1\right)^{k-1} \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2 - k}{2}}}$$
-$$-\theta\left(-1\right) q^{-\frac{k}{2}} \tau\left(\chi^4, \fieldCharacter\right)^k \tau\left(\theta \times \chi^{-1}, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+$$-\theta\left(-1\right) q^{-k} \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta \times \chi^{-1}, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
 
@@
 If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} : \finiteField}$.
+where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
 If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote
@@
 Then for any irreducible $\pi$ such that $c_{\pi} \ne 0$, and any $\chi$ such that $\chi^2 \ne 1$, we have
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = q^{-\frac{\dim \hermitianSpace}{2}} \prod_{j=1}^r \GaussSumScalar{\alpha'_j \times \chi^{-1}}{\fieldCharacter_{2n_j}} \prod_{i=1}^s \GaussSumScalar{\beta_i \times \chi^{-1}}{\fieldCharacter_{m_i}} \GaussSumScalar{\beta_i^{-1} \times \chi^{-1}}{\fieldCharacter_{m_i}}.$$
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = q^{-\frac{\dim \hermitianSpace}{2}} \prod_{j=1}^r \GaussSumCharacter{\alpha'_j}{\chi^{-1}}{\fieldCharacter_{2n_j}} \prod_{i=1}^s \GaussSumCharacter{\beta_i}{\chi^{-1}}{\fieldCharacter_{m_i}} \GaussSumCharacter{\beta_i^{-1}}{\chi^{-1}}{\fieldCharacter_{m_i}}.$$
 

### 2025-02-09 paper.tex
Update from overleaf

@@
 	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
-	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get the equality 
+	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
 	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
@@
 t \ne 1}} \theta\left(t\right) \chi\left(\FieldNorm{k}{1}\left(t-1\right)\right).$$
-Using \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} and the fact that Kondo's Gauss sum is the same for every subrepresentation of $R_{T, \theta}$, we have the equality $$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \left(-1\right)^k \theta\left(-1\right) q^{-\frac{3k}{2}} R_{T, \theta}\left(1\right) \tau\left(\chi, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+Using \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} and the fact that Kondo's Gauss sum is the same for every subrepresentation of $R_{T, \theta}$, we have the equality $$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \left(-1\right)^k \theta\left(-1\right) R_{T, \theta}\left(1\right) \tau\left(\chi, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
 
@@
 which by the results of the previous section equals
-%$$\frac{q^{\frac{k^2}{2}}}{\grpIndex{\GL_k\left(\finiteField\right)}{T}} \left(-1\right)^k \theta\left(-1\right) q^{-\frac{3k}{2}} R_{T, \theta}\left(1\right) \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).
-$$
-%$$\frac{q^{\frac{k^2}{2}}}{\grpIndex{\GL_k\left(\finiteField\right)}{T}} \left(-1\right)^k \theta\left(-1\right) q^{-\frac{3k}{2}} \left(-1\right)^{k-1} \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2 - k}{2}}} \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
-%$$R_{T,\theta}\left(1\right) = \left(-1\right)^{k-1} \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2 - k}{2}}}$$
-$$-\theta\left(-1\right) q^{-k} \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta \times \chi^{-1}, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+$$-\theta\left(-1\right) q^{\frac{k}{2}} \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta \times \chi^{-1}, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
 
@@
 We compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-	\trace_{\finiteFieldExtension{2} \slash \finiteField}\left(x\right) \ne 0}} \chi\left(\FieldNorm{2}{1}\left(\frac{x}{\trace_{\finiteFieldExtension{2} \colon \finiteField} x}\right) \right).$$
+	\trace_{\finiteFieldExtension{2} \slash \finiteField}\left(x\right) \ne 0}} \chi\left(\FieldNorm{2}{1}\left(\frac{x}{\trace_{\finiteFieldExtension{2} \slash \finiteField} x}\right) \right).$$
 As usual, we rewrite this sum as

### 2025-02-09 paper.tex
Adding computation for split tori

@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
 	We have the identity
@@
 
-\subsubsection{General linear groups computation}
-Suppose that $F \colon \GL_k\left(\finiteField\right) \to \cComplex$ is a class function.
-If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a non-trivial character, we define $$\dblVirtualGaussSumScalar{F}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) F\left(g\right).$$
-It is clear that for an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we have $$\dblVirtualGaussSumScalar{\trace \tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \dim \tau.$$
-Since the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ depends only on the semisimple part of $g$, by \cite[Theorem in Section 1.2]{SaitoShinoda2000} we have that if $T \cong \multiplicativegroup{\finiteFieldExtension{k}}$ and if $\theta \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ is a character then
-$$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{\GL_k\left(\finiteField\right)}{T}}{q^{\frac{k^2}{2}}} \sum_{\substack{t \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-t \ne 1}} \theta\left(t\right) \chi\left(\FieldNorm{k}{1}\left(t-1\right)\right).$$
-Using \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} and the fact that Kondo's Gauss sum is the same for every subrepresentation of $R_{T, \theta}$, we have the equality $$\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \left(-1\right)^k \theta\left(-1\right) R_{T, \theta}\left(1\right) \tau\left(\chi, \fieldCharacter\right)^k \tau\left(\theta, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+\subsubsection{Gauss sum notations}
+If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
+where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
+$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
 
-\subsubsection{Split torus computation}
-In this section we compute the doubling method Gauss sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
-Let $\theta \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\chi^2 \ne 1$.
+If $m \ge 1$, we denote 
+$$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
+
+\subsubsection{Split torus computation I}
+Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ be a character and let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+
+The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right).$$
+Let us rewrite this as
+$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
+Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
+$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
+Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$, this becomes
+$$q^{-k} \alpha\left(-1\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
+Hence, we have the identity
+$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi_{\GL_k}, \fieldCharacter_k\right).$$
+
+\subsubsection{Split torus computation II}
+We use the results from the previous section to compute the doubling method Gauss sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
+Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\chi^2 \ne 1$.
 Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(x^{-1} - 1\right)\right).$$
-
+		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(x^{-1} - 1\right)\right).$$
 This can be rewritten as
 $$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \theta \left(x\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(x\right)\right) \chi^2\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
-Denote by $\theta_{\chi^{-1}} \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ the character $$\theta_{\chi^{-1}}\left(x\right) = \theta\left(x\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(x\right)\right).$$
-
-Hence we get
-$$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(x^{-1} - 1\right)\right) = \frac{q^{\frac{k^2}{2}}}{\grpIndex{\GL_k\left(\finiteField\right)}{T}} \dblVirtualGaussSumScalar{R_{T, \theta_{\chi^{-1}}}}{\chi^2},$$
-which by the results of the previous section equals
-$$-\theta\left(-1\right) q^{\frac{k}{2}} \tau\left(\chi^2, \fieldCharacter\right)^k \tau\left(\theta \times \chi^{-1}, \fieldCharacter\right) \tau\left(\theta^{-1} \times \chi^{-1}, \fieldCharacter\right).$$
+		x \ne 1}} \alpha \left(x\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(x\right)\right) \chi^2\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
+By the previous section, this equals
+$$- q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \GaussSumCharacter{\alpha}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\chi^2, \fieldCharacter\right)^k.$$
 
@@
 
-If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
-If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote
-$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right),$$
-
-Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \FieldNorm{2m}{1}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
+Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$.
+It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \FieldNorm{2m}{1}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
 Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\

### 2025-02-09 paper.tex
Rephrasing
Writing the Hasse--Davenport relation for our case

@@
 By the previous section, this equals
-$$- q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \GaussSumCharacter{\alpha}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\chi^2, \fieldCharacter\right)^k.$$
+\begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
+	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \GaussSumCharacter{\alpha}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\chi^2, \fieldCharacter\right)^k.
+\end{equation}
+
+Notice that if $k = md$ and $\alpha = \beta \circ \FieldNorm{k}{m}$ where $\beta \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ is a character, then \eqref{eq:identity-for-multiplicative-group-of-f-k-gauss-sum} equals
+$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_m} \GaussSumCharacter{\beta}{\chi^{-1}}{\fieldCharacter_m} \tau\left(\chi^2, \fieldCharacter\right)^m\right)^{d}.$$
 
@@
 Since $\chi \circ \FieldNorm{2m}{1} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
-Hence, we may replace the sum over $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
+Hence, we may reduce the sum over $z$ to $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
 Using the fact that $\theta'$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,

### 2025-02-09 paper.tex
Updating progress

@@
 Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in G$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
-\begin{proposition}
+\begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
 	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{G}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
@@
 
-\subsubsection{Computation for irreducible cuspidal representations}
+\subsubsection{Computation for Deligne--Lusztig characters}
+Combining the results of the previous sections with \Cref{prop:reduction-of-gauss-sum-to-torus} and the fact that $$R_{T,\theta}\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ we arrive at the following result.
 
-\begin{theorem}
-	Suppose that $\pi$ is an irreducible cuspidal representation of $G$, parameterized by a character $\theta = \theta_1 \times \dots \times \theta_r$ of a torus $T$ such that $$T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \times \finiteFieldExtension{2n_r}^1,$$
-	where $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace$ if $\dim \hermitianSpace$ is even or $2n_1 + 2n_2 + \dots + 2n_r = \dim \hermitianSpace - 1$ if $\dim \hermitianSpace$ is odd, and where $$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
-	Then up to maybe a sign, we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \prod_{j=1}^r \tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j} \right),$$
-	where $\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{n_j}}\right)$ and $$\tau\left( \theta'_j \times \chi, \fieldCharacter_{2n_j}\right) = -q^{-n_j} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2n_j}}} \theta'_j\left(x\right) \chi\left(\FieldNorm{2n_j}{1}\left(x\right)\right)\fieldCharacter\left(\trace_{\finiteFieldExtension{2n_j} \slash \finiteField}\left(x\right)\right).$$
-\end{theorem}
-
-\subsubsection{Computation for Lusztig series}
-
-Let $T \cong \finiteFieldExtension{2n_1}^1 \times \finiteFieldExtension{2n_2}^1 \times \dots \times \finiteFieldExtension{2n_r}^1 \times \multiplicativegroup{\finiteFieldExtension{m_1}} \times \dots \multiplicativegroup{\finiteFieldExtension{m_s}}$ be a torus such that $\sum_{i=1}^r 2n_i + \sum_{j=1}^s 2m_j = \dim_{\finiteField} \hermitianSpace$.
-Let $\theta = \alpha_1 \times \dots \times \alpha_r \times \beta_1 \times \dots \times \beta_s$.
-Consider the Deligne--Lusztig induction $\DeligneLusztigInduction{T}{G}\theta$.
-Write $$\DeligneLusztigInduction{T}{G}\theta = \sum_{\pi} c_{\pi} \cdot \trace \pi,$$
-where $\pi$ goes over all the irreducible representations of $G$ and $c_{\pi} \in \zIntegers$.
-Then for any irreducible $\pi$ such that $c_{\pi} \ne 0$, and any $\chi$ such that $\chi^2 \ne 1$, we have
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = q^{-\frac{\dim \hermitianSpace}{2}} \prod_{j=1}^r \GaussSumCharacter{\alpha'_j}{\chi^{-1}}{\fieldCharacter_{2n_j}} \prod_{i=1}^s \GaussSumCharacter{\beta_i}{\chi^{-1}}{\fieldCharacter_{m_i}} \GaussSumCharacter{\beta_i^{-1}}{\chi^{-1}}{\fieldCharacter_{m_i}}.$$
+\begin{proposition}
+	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \times \left[\{\pm 1\}\right]$ is a maximal torus of $G$.
+Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_s \times \theta_1 \times \dots \times \theta_r$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+Then
+	\begin{align*}
+		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& \sizeof{\lieAlgebra}^{-\frac{1}{2}} \left(q^{\frac{1}{2}} \tau\left(\chi^2, \fieldCharacter\right)\right)^{\left[\frac{\dim \hermitianSpace}{2}\right]} \sizeof{G}_p \varepsilon_{\algebraicGroup{G}} \left(-1\right)^r R_{T,\theta}\left(1\right) \\
+		& \times \prod_{i=1}^s \theta_i\left(-1\right) \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \\
+		& \times  \prod_{j=1}^r \alpha_j\left(-1\right)  \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}\\
+		& \times \left[\chi\left(-2\right)\right],
+	\end{align*}
+	where the factors $\{\pm 1\}$ and $\chi\left(-2\right)$ only appear in the odd orthogonal group case.
+\end{proposition}
 

### 2025-02-10 paper.tex
Cleaning up the statement

@@
 For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left[\frac{\dim \hermitianSpace}{2}\right]}}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor}}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 \subsubsection{Computation for Deligne--Lusztig characters}
-Combining the results of the previous sections with \Cref{prop:reduction-of-gauss-sum-to-torus} and the fact that $$R_{T,\theta}\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ we arrive at the following result.
+Combining the results of the previous sections with \Cref{prop:reduction-of-gauss-sum-to-torus}, we arrive at the following result.
 
 \begin{proposition}
-	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \times \left[\{\pm 1\}\right]$ is a maximal torus of $G$.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_s \times \theta_1 \times \dots \times \theta_r$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ is a maximal torus of $G$.
+Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
 Then
 	\begin{align*}
-		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& \sizeof{\lieAlgebra}^{-\frac{1}{2}} \left(q^{\frac{1}{2}} \tau\left(\chi^2, \fieldCharacter\right)\right)^{\left[\frac{\dim \hermitianSpace}{2}\right]} \sizeof{G}_p \varepsilon_{\algebraicGroup{G}} \left(-1\right)^r R_{T,\theta}\left(1\right) \\
+		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor} \\
 		& \times \prod_{i=1}^s \theta_i\left(-1\right) \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \\
 		& \times  \prod_{j=1}^r \alpha_j\left(-1\right)  \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}\\
-		& \times \left[\chi\left(-2\right)\right],
+		& \left[\times \epsilon\left(-1\right) \chi\left(-2\right)\right],
 	\end{align*}
-	where the factors $\{\pm 1\}$ and $\chi\left(-2\right)$ only appear in the odd orthogonal group case.
+	where the terms in $\left[\right]$ only appear in the odd orthogonal group case.
 \end{proposition}
+\begin{proof}
+	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor},$$
+	the facts \begin{equation*}
+		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor},
+	\end{equation*}
+	and finally from $$\GaussSumScalar{\chi^2}{\fieldCharacter} = -\tau\left(\chi^2, \fieldCharacter\right).$$
+\end{proof}
 

### 2025-02-10 paper.tex
Some cleanup
Lusztig series are hard

@@
 For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor}}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor}}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 
-\begin{proposition}
+\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
 	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ is a maximal torus of $G$.
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Then
+Denote $$g_T\left(\theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
 	\begin{align*}
-		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor} \\
-		& \times \prod_{i=1}^s \theta_i\left(-1\right) \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \\
-		& \times  \prod_{j=1}^r \alpha_j\left(-1\right)  \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}\\
+		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} g_T\left(\theta, \fieldCharacter\right) \\
+		& \times \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right) \\
 		& \left[\times \epsilon\left(-1\right) \chi\left(-2\right)\right],
@@
 	where the terms in $\left[\right]$ only appear in the odd orthogonal group case.
-\end{proposition}
+\end{theorem}
 \begin{proof}
-	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor},$$
+	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},$$
 	the facts \begin{equation*}
-		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\lfloor\frac{\dim \hermitianSpace}{2}\rfloor},
+		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},
 	\end{equation*}
 	and finally from $$\GaussSumScalar{\chi^2}{\fieldCharacter} = -\tau\left(\chi^2, \fieldCharacter\right).$$
+\end{proof}
+
+\subsubsection{Computation for Lusztig series}
+
+Using \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig, we are able to determine $\dblGaussSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
+
+\begin{theorem}
+	Let $T \subset G$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\pi} c_{\pi} \trace \pi,$$
+	where $\pi$ goes over all the irreducible representations of $G$ and $c_{\pi} \in \zIntegers$.
+Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.
+Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
+\end{theorem}
+\begin{proof}
+	We will prove this by induction on $\dim \hermitianSpace$.
+Let us keep the notation as in \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
+If $\left(T,\theta\right)$ is in general position, then $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T,\theta} = \trace \pi$ and $$\dim \pi \cdot \dblGaussSumScalar{\pi}{\chi} = \dblVirtualGaussSumScalar{\trace \pi}{\chi} = \varepsilon_{\algebraicGroup{T}} \varepsilon_{\algebraicGroup{G}} \dblVirtualGaussSumScalar{R_{T,\theta}}{\chi}.$$ We also have in this case $$\centralCharacter{\pi}\left(-1\right) = \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_j\left(-1\right).$$
+	Hence from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, $$\dblGaussSumScalar{\pi}{\chi} = \frac{\dblVirtualGaussSumScalar{R_{T,\theta}}{\chi}}{R_{T,\theta}\left(1\right)} = \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},$$
+	which implies that $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\epsilon, \fieldCharacter\right)$.
+
+	Suppose that $\left(T,\theta\right)$ is not in general position and that $\pi$ is such that $c_{\pi} \ne 0$.
+Fix an isomorphism $T^{\ast} \cong T$, where $T$ is the dual torus of $T$ and let $s$ be the image of $\theta$ under this isomorphism.
+Then $\pi$ belongs to the Lusztig series $\mathcal{E}\left(G, s\right)$.
+Suppose first that $\pi$ is not cuspidal.
+Then $\pi$ appears in a Harish--Chandra series of the form $\left(L, \sigma\right)$, where $L$ is a Levi subgroup of $G$ and where $\sigma$ belongs to the Lusztig--Series $\mathcal{E}\left(L, s\right)$.
+We may write $L \cong \GL_{t_1}\left(\finiteField\right) \times \dots \times \GL_{t_\ell}\left(\finiteField\right) \times G'$, where $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
+By the multiplicativity property we have
 \end{proof}

### 2025-02-10 paper.tex
Trying to prove something about Lustzig series

@@
 \newcommand{\algebraicGroup}[1]{\boldsymbol{\mathrm{#1}}}
+\newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
 
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:multiplicativity-in-terms-of-gamma-factors}
 	\begin{enumerate}
@@
 \end{proof}
+\begin{remark}
+	Suppose that $\pi$ is any irreducible representation of $G$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
+	$$ \centralCharacter{\pi}\left(-1\right) = \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).$$
+	Thus \begin{align*}
+		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right) \\
+		& \left[\times \epsilon\left(-1\right) \chi\left(-2\right)\right].
+	\end{align*}
+\end{remark}
 
@@
 \begin{theorem}
-	Let $T \subset G$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\pi} c_{\pi} \trace \pi,$$
-	where $\pi$ goes over all the irreducible representations of $G$ and $c_{\pi} \in \zIntegers$.
+	Let $T \subset G$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
+	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
 Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.
@@
 \end{theorem}
+In order to prove this theorem, we will use the theory of Lusztig series.
+
+TODO: Fix isomorphism for all tori and their dual that are compatible in the sense that inclusion corresponds to the norm map.
+
+TODO: Define $g_{\GL}\left(s, \fieldCharacter\right)$ for $\GL_n$.
+
+Fix an isomorphism $T^{\ast} \cong T$, where $T$ is the dual torus of $T$.
+If the image of $\theta$ is $s$ under the above isomorphism, define $g\left(s, \fieldCharacter\right) = g_T\left(\theta, \fieldCharacter\right)$.
+The Hasse--Davenport relation shows that this does not depend on the torus $T$.
+
+The \emph{Lusztig series} $\LusztigSeries{G}{s}$ consists of the irreducible representations $\pi$ of $R_{T, \theta}$ with $c_{\pi} \ne 0$ as in the theorem.
+
+Let $L \subset G$ be a Levi subgroup of $G$, and suppose that $L \cong \prod_{j=1}^\ell \GL_{t_j}\left(\finiteField\right) \times G'$ where $G' = \IsometryGroup\left(\hermitianSpace'\right)$ where $\hermitianSpace'$ is a non-degenerate hermitian subspace and $\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic$, where $\xIsotropic$ and $\yIsotropic$ are totally isotropic subspace in duality.
+Suppose that $s \in T$ is such that $s \in L$, and denote by $s_i$ the projection of $s$ to $\GL_{t_i}\left(\finiteField\right)$ for $1 \le i \le \ell$ and by $s_0$ the projection of $s$ to $G'$.
+We denote
+$$\LusztigSeries{L}{s} = \left(\bigotimes_{j=1}^{\ell} \LusztigSeries{\GL_{t_j}\left(\finiteField\right)}{s_j}\right) \otimes \LusztigSeries{G'}{s_0}.$$
+It is clear that $$g\left(s, \fieldCharacter\right) = g\left(s_0,\fieldCharacter\right) \cdot \prod_{j=1}^r g_{\GL}\left(s_j, \fieldCharacter\right).$$
+
+We will need the following two facts:
+\begin{enumerate}
+	\item For classical groups $G$ (as the ones we consider in this paper), the Lusztig series $\LusztigSeries{G}{s}$ contains at most one irreducible cuspidal representation.
+	\item The Lustzig series $\LusztigSeries{G}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $G$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
+\end{enumerate}
+Our theorem is equivalent to the following statement.
+\begin{proposition}
+	Keep the notations as above.
+Suppose that $P$ is a parabolic subgroup of $G$ with Levi part $L$.
+Then for any irreducible cuspidal $\sigma \in \LusztigSeries{L}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{P}{G}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g\left(s, \fieldCharacter\right).$$
+\end{proposition}
 \begin{proof}
-	We will prove this by induction on $\dim \hermitianSpace$.
-Let us keep the notation as in \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
-If $\left(T,\theta\right)$ is in general position, then $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T,\theta} = \trace \pi$ and $$\dim \pi \cdot \dblGaussSumScalar{\pi}{\chi} = \dblVirtualGaussSumScalar{\trace \pi}{\chi} = \varepsilon_{\algebraicGroup{T}} \varepsilon_{\algebraicGroup{G}} \dblVirtualGaussSumScalar{R_{T,\theta}}{\chi}.$$ We also have in this case $$\centralCharacter{\pi}\left(-1\right) = \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_j\left(-1\right).$$
-	Hence from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, $$\dblGaussSumScalar{\pi}{\chi} = \frac{\dblVirtualGaussSumScalar{R_{T,\theta}}{\chi}}{R_{T,\theta}\left(1\right)} = \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},$$
-	which implies that $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\epsilon, \fieldCharacter\right)$.
+	The proof is by induction on $\dim \hermitianSpace$.
 
-	Suppose that $\left(T,\theta\right)$ is not in general position and that $\pi$ is such that $c_{\pi} \ne 0$.
-Fix an isomorphism $T^{\ast} \cong T$, where $T$ is the dual torus of $T$ and let $s$ be the image of $\theta$ under this isomorphism.
-Then $\pi$ belongs to the Lusztig series $\mathcal{E}\left(G, s\right)$.
-Suppose first that $\pi$ is not cuspidal.
-Then $\pi$ appears in a Harish--Chandra series of the form $\left(L, \sigma\right)$, where $L$ is a Levi subgroup of $G$ and where $\sigma$ belongs to the Lusztig--Series $\mathcal{E}\left(L, s\right)$.
-We may write $L \cong \GL_{t_1}\left(\finiteField\right) \times \dots \times \GL_{t_\ell}\left(\finiteField\right) \times G'$, where $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
-By the multiplicativity property we have
+	Suppose first that $L \ne G$.
+Then by using the multiplicativity property repeatedly (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}), we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \cdot \prod_{j=1}^r g_{\GL}\left(s_j, \fieldCharacter\right),$$
+	where $\pi'$ is an irreducible cuspidal representation of $G'$ that lies in the Lustzig series $\LusztigSeries{\pi'}{s_0}$.
+By the induction hypothesis, we have $$\dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} = g\left(s_0, \fieldCharacter\right),$$
+	which implies the result.
+
+	Next, suppose that $L = G$ and that $\pi = \sigma$ is an irreducible cuspidal representation. Let us write $$R_{T, \theta} = \sum_{\Pi} c_\Pi \trace \Pi,$$
+	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
+For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
+	$$c_{\pi} \cdot \dblVirtualGaussSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
+	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+	Since $\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblGaussSumScalar{\pi}{\chi}$, the result follows.
 \end{proof}

### 2025-02-10 paper.tex
Lusztig

@@
 	\item For classical groups $G$ (as the ones we consider in this paper), the Lusztig series $\LusztigSeries{G}{s}$ contains at most one irreducible cuspidal representation.
-	\item The Lustzig series $\LusztigSeries{G}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $G$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
+	\item The Lusztig series $\LusztigSeries{G}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $G$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
 \end{enumerate}
@@
 Then by using the multiplicativity property repeatedly (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}), we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \cdot \prod_{j=1}^r g_{\GL}\left(s_j, \fieldCharacter\right),$$
-	where $\pi'$ is an irreducible cuspidal representation of $G'$ that lies in the Lustzig series $\LusztigSeries{\pi'}{s_0}$.
+	where $\pi'$ is an irreducible cuspidal representation of $G'$ that lies in the Lusztig series $\LusztigSeries{\pi'}{s_0}$.
 By the induction hypothesis, we have $$\dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} = g\left(s_0, \fieldCharacter\right),$$
@@
 	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
 	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$

### 2025-02-10 paper.tex
\theta\left(-1\right)

@@
 	Suppose that $\pi$ is any irreducible representation of $G$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
-	$$ \centralCharacter{\pi}\left(-1\right) = \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).$$
+	$$ \centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) = \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).$$
 	Thus \begin{align*}

### 2025-02-11 paper.tex
Using the characteristic polynomial to establish Gauss sum identity

--- 2025-02-10 paper.tex
@@
 \newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
+\newcommand{\ToriDualToriIsomorphism}{\kappa}
+\newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
+
+\newcommand{\calvin}[1]{\textcolor{orange}{\sffamily ((CALVIN: #1))}}
+\newcommand{\elad}[1]{\textcolor{blue}{\sffamily ((ELAD: #1))}}
 
@@
 
-\subsection{Computation in terms of Deligne--Lusztig data}
+\subsection{Computation of character sums attached Deligne--Lusztig data}
 
-The goal of this section is to compute $\dblGaussSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
+The goal of the next two sections is to compute $\dblGaussSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
+
+In this section, we focus on the computing the analogous character sum corresponding to $\dblGaussSumScalar{\pi}{\fieldCharacter}$ for the virtual character $R_{T,\theta}$.
+
+\calvin{I kinda prefer the normalization where we divide by $|G|$. I guess both for little and upper $G$. That way it is the honest product of characters in the representation ring.}
 
@@
 \end{theorem}
+    \calvin{What does the $\chi(-2)$ come from? I didn't quite get that when I was messing around}
 \begin{proof}
@@
 	Suppose that $\pi$ is any irreducible representation of $G$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
-	$$ \centralCharacter{\pi}\left(-1\right) = \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).$$
+	\begin{align*}
+		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right)\\
+		& \times \left[\epsilon\left(-1\right)\right].
+	\end{align*}
 	Thus \begin{align*}
 		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right) \\
-		& \left[\times \epsilon\left(-1\right) \chi\left(-2\right)\right].
+		& \left[\times \chi\left(-2\right)\right].
 	\end{align*}
@@
 
-\subsubsection{Computation for Lusztig series}
+\subsection{Computation for Lusztig series}
 
-Using \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig, we are able to determine $\dblGaussSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
+The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblGaussSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
 
@@
 
-TODO: Fix isomorphism for all tori and their dual that are compatible in the sense that inclusion corresponds to the norm map.
+\subsubsection{Tori isomorphism}
+
+For any finite abelian group $G$, let $\widehat{G}$ be the character group of $G$, consisting of characters $\theta \colon G \to \multiplicativegroup{\cComplex}$.
+
+Let $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ be a family of isomorphisms $\ToriDualToriIsomorphism_k \colon \charactergroup{k} \to \multiplicativegroup{\finiteFieldExtension{k}}$ such that if $k' \mid k$ then $\ToriDualToriIsomorphism_k^{-1}\left(\xi_{k'}\right) = \ToriDualToriIsomorphism_{k'}^{-1}\left(\xi_{k'}\right) \circ \FieldNorm{k}{k'}$ for any $\xi_{k'} \in \multiplicativegroup{\finiteFieldExtension{k'}}$.
+
+Using the Hilbert 90 isomorphism $\finiteFieldExtension{2m} \slash \finiteFieldExtension{m} \to \finiteFieldExtension{2m}^{1}$ given by $$x \mapsto \frac{x}{x^{q^m}} = x^{1 - q^m},$$ we see that characters of $\finiteFieldExtension{2m}^1$ are in bijection with characters of $\multiplicativegroup{\finiteFieldExtension{2m}}$ such that their restriction to $\multiplicativegroup{\finiteFieldExtension{m}}$ is trivial.
+Using the surjective norm map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\finiteFieldExtension{m}}$, such characters are precisely characters $\theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ such that $\theta \circ \FieldNorm{2m}{m} = \theta^{1 + q^m} = 1$.
+By realizing the character group $\widehat{\finiteFieldExtension{2m}^1}$ as the subgroup of $\charactergroup{2m}$ given by $$\left\{ \theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex} \mid \theta^{1+q^m} = 1\right\},$$
+we have that $$\ToriDualToriIsomorphism_{2m}\left(\widehat{\finiteFieldExtension{2m}^1}\right) = \left\{\xi \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \xi^{1+q^m} = 1\right\} = \finiteFieldExtension{2m}^1.$$
+Let us denote the restriction of $\ToriDualToriIsomorphism_{2m}$ to $\widehat{\finiteFieldExtension{2m}^1}$ by $\ToriDualToriIsomorphism_{2m}^1 \colon \widehat{\finiteFieldExtension{2m}^1} \to \finiteFieldExtension{2m}^1$.
+
+The family $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ allows us to define $\ToriDualToriIsomorphism_T \colon \widehat{T} \to T$ for any maximal torus $T$ of $G$.
+Recall that for a maximal torus $T$ of $G$ there exists an isomorphism of groups $$e_T \colon T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1,$$
+satisfying that if the image of $t \in T$ in $\GL\left(\hermitianSpace\right)$ has an $\finiteField$-characteristic polynomial $\characteristicPolynomial_{t}\left(X\right)$ and $$e_T\left(t\right) = \left(t_1,\dots,t_r,u_1,\dots,u_s\right)$$ then $$\characteristicPolynomial_{t}\left(X\right) = \prod_{j=1}^r \characteristicPolynomial_{t_j, \finiteFieldExtension{k_j}}\left(X\right) \characteristicPolynomial_{t_j^{-1}, \finiteFieldExtension{k_j}}\left(X\right) \cdot \prod_{i=1}^s \characteristicPolynomial_{u_i, \finiteFieldExtension{2 m_i}}\left(X\right),$$
+where for $\xi \in \multiplicativegroup{\finiteFieldExtension{k}}$, $\characteristicPolynomial_{\xi, \finiteFieldExtension{k}}\left(X\right)$ is the $\finiteField$-characteristic polynomial of the multiplication by $\xi$ map $\finiteFieldExtension{k} \to \finiteFieldExtension{k}$.
+
+The isomorphism $e_T$ induces an isomorphism for the character group $$e_{\widehat{T}} \colon \widehat{T} \to \prod_{j=1}^r \charactergroup{k_j} \times \prod_{i=1}^s \widehat{\finiteFieldExtension{2m_i}^1},$$
+given by
+$$e_{\widehat{T}}\left(\theta\right) = \theta \circ e_T^{-1}.$$
+Using the isomorphisms $\ToriDualToriIsomorphism_{k_j} \colon \charactergroup{k_j} \to \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $\ToriDualToriIsomorphism_{2m_i} \colon \widehat{\finiteFieldExtension{2m_i}^1} \to \finiteFieldExtension{2m_i}^1$ and using $e_T$ and $r_{\widehat{T}}$, we obtain an isomorphism $\ToriDualToriIsomorphism_{T} \colon \widehat{T} \to T$.
+Note that this construction depends on the family $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ and on the isomorphism $e_T$.
+
+\subsubsection{Gauss sums attached to semisimple elements}
+
+Let $T$ be as in the previous section.
+Let $t \in T$ and suppose that $\ToriDualToriIsomorphism_{T}^{-1}\left(t\right) = \theta$ is given by $$\theta = \left(\alpha_1,\dots,\alpha_r,\theta_1,\dots,\theta_s\right) \circ e_T,$$ where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+We define $$g_T\left(t, \fieldCharacter\right) = g_T\left(\theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$
+We claim that this definition only depends on $t$ and not on the maximal torus $T$ containing it.
+
+To see this, suppose that $\deg \alpha_1 = d_1$, $\dots$, $\deg \alpha_k = d_k$, $\deg \theta'_1 = d'_1$, $\dots$, $\deg \theta'_s = d'_s$ and that $k_1 = b_1 d_1$, $\dots$, $k_r = b_r d_r$, $2m_1 = b'_1 d'_1$, $\dots$, $2m_s = b'_s d'_s$.
+Then for every $j$
+$\alpha_j = \beta_j \circ \FieldNorm{b_j d_j}{d_j}$ for some $\beta_j \colon \multiplicativegroup{\finiteFieldExtension{d_j}} \to \multiplicativegroup{\cComplex}$, and similarly for every $i$ $\theta'_i = \vartheta_i \circ \FieldNorm{b'_i d'_i}{d'_i}$ for some $\vartheta_i \colon \multiplicativegroup{\finiteFieldExtension{d'_i}} \to \multiplicativegroup{\cComplex}$.
+By the Hasse--Davenport relation we have \begin{equation}\label{eq:hasse-davenport-for-semisimple-elements}
+	g_T\left(t, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\vartheta_i}{\chi^{-1}}{\fieldCharacter_{d'_i}}^{b'_i} \cdot  \prod_{j=1}^r \GaussSumCharacter{\beta_j}{\chi^{-1}}{\fieldCharacter_{d_j}}^{b_j} \GaussSumCharacter{\beta_j^{-1}}{\chi^{-1}}{\fieldCharacter_{d_j}}^{b_j}.
+\end{equation}
+On the other hand, let $$e_T\left(t\right) = \left(t_1,\dots,t_r,u_1,\dots,u_s\right),$$
+where $t_j \in \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $u_i \in \finiteFieldExtension{2m_i}^1$ for every $i$ and $j$.
+Then since $\ToriDualToriIsomorphism_k$ preserves degrees of Frobenius orbits, we have that $t_j \in \multiplicativegroup{\finiteFieldExtension{d_j}}$ and $u_i \in \multiplicativegroup{\finiteFieldExtension{d'_i}}$ for every $i$ and $j$ (and they do not belong to smaller field extensions).
+Thus
+\begin{equation}\label{eq:characteristic-polynomial-equality-for-semisimple-elements}
+	\characteristicPolynomial_{t}\left(X\right) = \prod_{i=1}^s \characteristicPolynomial_{u_i, \finiteFieldExtension{d'_i}}\left(X\right)^{b'_i} \cdot \prod_{j=1}^r \characteristicPolynomial_{t_j, \finiteFieldExtension{d_j}}\left(X\right)^{b_j}\characteristicPolynomial_{t_j^{-1}, \finiteFieldExtension{d_j}}\left(X\right)^{b_j}.
+\end{equation}
+The equalities \eqref{eq:hasse-davenport-for-semisimple-elements} and \eqref{eq:characteristic-polynomial-equality-for-semisimple-elements} imply that may define $g_T\left(t,\fieldCharacter\right)$ using the $\finiteField$-characteristic polynomial of $t$ (viewed as an element of $\GL\left(\hermitianSpace\right)$) by defining a fully multiplicative function $\tau_{\chi, \fieldCharacter} \colon \finiteField\left[X\right]_{\mathrm{monic}} \to \cComplex$, sending $1$ to $1$ and any monic irreducible polynomial $p\left(X\right)$ of degree $d \ge 1$ to $\GaussSumCharacter{\ToriDualToriIsomorphism_{d}^{-1}\left(\xi\right)}{\chi}{\fieldCharacter_d}$, where $\xi \in \multiplicativegroup{\finiteFieldExtension{d}}$ is any root of the polynomial $P\left(X\right)$.
+This map is well defined because Gauss sums are constant on Frobenius orbits of characters.
+
+If $s \in \GL_n\left(\finiteField\right)$ is semisimple, we denote $$\tau_{\chi, \GL_n\left(\finiteField\right)}\left(s\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_s\left(X\right)\right),$$
+
+Since the $\finiteField$-characteristic polynomial of $t$ does not depend on the maximal torus $T$ containing $t$, we conclude that the map $t \mapsto g_T\left(t, \fieldCharacter\right)$ does not depend on $t$ and we denote for any semisimple element $s \in G$, $$\tau_{G, \chi, \fieldCharacter}\left(s, \fieldCharacter\right) = g_T\left(s, \fieldCharacter\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_{s}\left(X\right)\right),$$
+where $T$ is any maximal torus containing $s$ and $\characteristicPolynomial_{s}$ is the $\finiteField$-characteristic polynomial of $s$, viewed as an element of $\GL\left(\hermitianSpace\right)$.
+
+\subsubsection{Proof of the main result}
+
+\begin{proposition}
+\label{prop:geoconj}
+    Let $(T,\theta)$ be geometrically conjugate to $(T',\theta')$ inside $G^\vee$ i.e.
+there exists $g \in T(\mathbb{F}_n)$ such that $gTg^{-1} = T'$ and $\theta'(Nm_{n:1}(x)) = \theta(Nm_{n:1}(g^{-1}xg))$ for $x \in T'(\mathbb{F}_n)$.
+Then $g_T(\theta,\psi_{tr}) = g_{T'}(\theta',\psi_{tr})$
+\end{proposition}
+
+\calvin{here is the geometric idea:}
+\begin{lemma}
+    Let $\mathcal{F} := \mathcal{L}(\theta) \otimes tr^{*}\mathcal{L}(\psi)$. Then
+    \[
+        dim H_c^i(T,\mathcal{F}) = \begin{cases}
+        0    & i \neq dim(T) \\
+        1    & i = dim(T)
+        \end{cases}
+    \]
+\end{lemma}
+\calvin{Might exist in literature somewhere otherwise is a little bit of a pain. It should be analogous to the fact that the Guass sum on a field of size $p^d$ is of magnitude $\sqrt{p^d}$.}
+Combining this with Grothendieck-Lefschetz we get
+\begin{corollary}
+    $g_T(\theta,\psi)^k = g_T(\theta \circ Nm_{k:1},\psi)$.
+\end{corollary}
+\calvin{there might be a simple non-geometric way to do this corollary not sure.}
+\calvin{The corollary plus the definition of geometric conjugacy imply $g_T(\theta,\psi) = \mu_kg_{T'}(\theta',\psi)$ for some $k$-th root of unity $\mu_k$. Not sure how to finish from here.}
 
 TODO: Define $g_{\GL}\left(s, \fieldCharacter\right)$ for $\GL_n$.
-
+\calvin{this is a good idea but I'm not sure it'll work.
+I guess you can cancel some stuff out to get the Guass sum over the norm one elements via adding some characters from composing with Nm.
+Similarly you need to cancel stuff on the other side.}
 Fix an isomorphism $T^{\ast} \cong T$, where $T$ is the dual torus of $T$.

### 2025-02-11 paper.tex
Some cleanup

@@
 
-\subsection{Computation of character sums attached Deligne--Lusztig data}
+\subsection{Computation of character sums attached to Deligne--Lusztig data}
 
@@
 $$e_{\widehat{T}}\left(\theta\right) = \theta \circ e_T^{-1}.$$
-Using the isomorphisms $\ToriDualToriIsomorphism_{k_j} \colon \charactergroup{k_j} \to \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $\ToriDualToriIsomorphism_{2m_i} \colon \widehat{\finiteFieldExtension{2m_i}^1} \to \finiteFieldExtension{2m_i}^1$ and using $e_T$ and $r_{\widehat{T}}$, we obtain an isomorphism $\ToriDualToriIsomorphism_{T} \colon \widehat{T} \to T$.
+Using the isomorphisms $\ToriDualToriIsomorphism_{k_j} \colon \charactergroup{k_j} \to \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $\ToriDualToriIsomorphism_{2m_i} \colon \widehat{\finiteFieldExtension{2m_i}^1} \to \finiteFieldExtension{2m_i}^1$ and using $e_T$ and $e_{\widehat{T}}$, we obtain an isomorphism $\ToriDualToriIsomorphism_{T} \colon \widehat{T} \to T$.
 Note that this construction depends on the family $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ and on the isomorphism $e_T$.
+
+%I just sent you an email about a similar idea which I think makes the writeup a little easier and you don't need the isomorphism between T and Tdual.
+I have to prepare for a seminar talk tomoro but later this week or early next we can talk
+
+%% Okay cool! good luck with your talk
 
@@
 To see this, suppose that $\deg \alpha_1 = d_1$, $\dots$, $\deg \alpha_k = d_k$, $\deg \theta'_1 = d'_1$, $\dots$, $\deg \theta'_s = d'_s$ and that $k_1 = b_1 d_1$, $\dots$, $k_r = b_r d_r$, $2m_1 = b'_1 d'_1$, $\dots$, $2m_s = b'_s d'_s$.
-Then for every $j$
-$\alpha_j = \beta_j \circ \FieldNorm{b_j d_j}{d_j}$ for some $\beta_j \colon \multiplicativegroup{\finiteFieldExtension{d_j}} \to \multiplicativegroup{\cComplex}$, and similarly for every $i$ $\theta'_i = \vartheta_i \circ \FieldNorm{b'_i d'_i}{d'_i}$ for some $\vartheta_i \colon \multiplicativegroup{\finiteFieldExtension{d'_i}} \to \multiplicativegroup{\cComplex}$.
+Then for every $j$,
+$\alpha_j = \beta_j \circ \FieldNorm{b_j d_j}{d_j}$ for some $\beta_j \colon \multiplicativegroup{\finiteFieldExtension{d_j}} \to \multiplicativegroup{\cComplex}$, and similarly for every $i$, $\theta'_i = \vartheta_i \circ \FieldNorm{b'_i d'_i}{d'_i}$ for some $\vartheta_i \colon \multiplicativegroup{\finiteFieldExtension{d'_i}} \to \multiplicativegroup{\cComplex}$.
 By the Hasse--Davenport relation we have \begin{equation}\label{eq:hasse-davenport-for-semisimple-elements}
@@
 
-If $s \in \GL_n\left(\finiteField\right)$ is semisimple, we denote $$\tau_{\chi, \GL_n\left(\finiteField\right)}\left(s\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_s\left(X\right)\right),$$
+If $s \in \GL_n\left(\finiteField\right)$ is semisimple, we denote $$\tau_{\GL_n\left(\finiteField\right), \chi, \fieldCharacter}\left(s\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_s\left(X\right)\right),$$
 
@@
 \begin{corollary}
-    $g_T(\theta,\psi)^k = g_T(\theta \circ Nm_{k:1},\psi)$.
+	$g_T(\theta,\psi)^k = g_T(\theta \circ Nm_{k:1},tr_{k:1} \circ \psi)$.
 \end{corollary}
@@
 \calvin{The corollary plus the definition of geometric conjugacy imply $g_T(\theta,\psi) = \mu_kg_{T'}(\theta',\psi)$ for some $k$-th root of unity $\mu_k$. Not sure how to finish from here.}
-
-TODO: Define $g_{\GL}\left(s, \fieldCharacter\right)$ for $\GL_n$.
-\calvin{this is a good idea but I'm not sure it'll work.
-I guess you can cancel some stuff out to get the Guass sum over the norm one elements via adding some characters from composing with Nm.
-Similarly you need to cancel stuff on the other side.}
-Fix an isomorphism $T^{\ast} \cong T$, where $T$ is the dual torus of $T$.
-If the image of $\theta$ is $s$ under the above isomorphism, define $g\left(s, \fieldCharacter\right) = g_T\left(\theta, \fieldCharacter\right)$.
-The Hasse--Davenport relation shows that this does not depend on the torus $T$.
 
@@
 $$\LusztigSeries{L}{s} = \left(\bigotimes_{j=1}^{\ell} \LusztigSeries{\GL_{t_j}\left(\finiteField\right)}{s_j}\right) \otimes \LusztigSeries{G'}{s_0}.$$
-It is clear that $$g\left(s, \fieldCharacter\right) = g\left(s_0,\fieldCharacter\right) \cdot \prod_{j=1}^r g_{\GL}\left(s_j, \fieldCharacter\right).$$
+It is clear that $$\tau_{G, \chi, \fieldCharacter}\left(s\right) = \tau_{G', \chi, \fieldCharacter}\left(s_0\right) \cdot \prod_{j=1}^r \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j\right) \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j^{-1}\right).$$
 
@@
 Suppose that $P$ is a parabolic subgroup of $G$ with Levi part $L$.
-Then for any irreducible cuspidal $\sigma \in \LusztigSeries{L}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{P}{G}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g\left(s, \fieldCharacter\right).$$
+Then for any irreducible cuspidal $\sigma \in \LusztigSeries{L}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{P}{G}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 \end{proposition}
@@
 	Suppose first that $L \ne G$.
-Then by using the multiplicativity property repeatedly (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}), we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \cdot \prod_{j=1}^r g_{\GL}\left(s_j, \fieldCharacter\right),$$
+Then by using the multiplicativity property repeatedly (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}), we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \cdot \prod_{j=1}^r \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j\right) \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j^{-1}\right),$$
 	where $\pi'$ is an irreducible cuspidal representation of $G'$ that lies in the Lusztig series $\LusztigSeries{\pi'}{s_0}$.
-By the induction hypothesis, we have $$\dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} = g\left(s_0, \fieldCharacter\right),$$
+By the induction hypothesis, we have $$\dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} = \tau_{G', \chi, \fieldCharacter}\left(s_0\right),$$
 	which implies the result.
@@
 	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
-	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
 	$$c_{\pi} \cdot \dblVirtualGaussSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
-	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
-	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot g\left(s, \fieldCharacter\right).$$
+	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblGaussSumScalar{\pi}{\chi}$, the result follows.

### 2025-02-11 paper.tex
Some typos

@@
 \end{equation}
-The equalities \eqref{eq:hasse-davenport-for-semisimple-elements} and \eqref{eq:characteristic-polynomial-equality-for-semisimple-elements} imply that may define $g_T\left(t,\fieldCharacter\right)$ using the $\finiteField$-characteristic polynomial of $t$ (viewed as an element of $\GL\left(\hermitianSpace\right)$) by defining a fully multiplicative function $\tau_{\chi, \fieldCharacter} \colon \finiteField\left[X\right]_{\mathrm{monic}} \to \cComplex$, sending $1$ to $1$ and any monic irreducible polynomial $p\left(X\right)$ of degree $d \ge 1$ to $\GaussSumCharacter{\ToriDualToriIsomorphism_{d}^{-1}\left(\xi\right)}{\chi}{\fieldCharacter_d}$, where $\xi \in \multiplicativegroup{\finiteFieldExtension{d}}$ is any root of the polynomial $P\left(X\right)$.
+The equalities \eqref{eq:hasse-davenport-for-semisimple-elements} and \eqref{eq:characteristic-polynomial-equality-for-semisimple-elements} imply that may define $g_T\left(t,\fieldCharacter\right)$ using the $\finiteField$-characteristic polynomial of $t$ (viewed as an element of $\GL\left(\hermitianSpace\right)$) by defining a fully multiplicative function $\tau_{\chi, \fieldCharacter} \colon \finiteField\left[X\right]_{\mathrm{monic}} \to \cComplex$, sending $1$ to $1$ and any monic irreducible polynomial $p\left(X\right)$ of degree $d \ge 1$ to $\GaussSumCharacter{\ToriDualToriIsomorphism_{d}^{-1}\left(\xi\right)}{\chi^{-1}}{\fieldCharacter_d}$, where $\xi \in \multiplicativegroup{\finiteFieldExtension{d}}$ is any root of the polynomial $P\left(X\right)$.
 This map is well defined because Gauss sums are constant on Frobenius orbits of characters.
 
-If $s \in \GL_n\left(\finiteField\right)$ is semisimple, we denote $$\tau_{\GL_n\left(\finiteField\right), \chi, \fieldCharacter}\left(s\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_s\left(X\right)\right),$$
+If $s \in \GL_n\left(\finiteField\right)$ is semisimple, we denote $$\tau_{\GL_n\left(\finiteField\right), \chi, \fieldCharacter}\left(s\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_s\left(X\right)\right).$$
 

### 2025-02-11 paper.tex
Some corrections

@@
 
-The \emph{Lusztig series} $\LusztigSeries{G}{s}$ consists of the irreducible representations $\pi$ of $R_{T, \theta}$ with $c_{\pi} \ne 0$ as in the theorem.
+Let $\ToriDualToriIsomorphism_T \colon \widehat{T} \to T$ be as in the previous sections.
+Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that $\ToriDualToriIsomorphism_T\left(\theta\right) = s$.
+The \emph{Lusztig series} $\LusztigSeries{G}{s}$ consists of (equivalence classes of) the irreducible representations $\pi$ of $R_{T, \theta}$ with $c_{\pi} \ne 0$ as in the theorem.
 
 Let $L \subset G$ be a Levi subgroup of $G$, and suppose that $L \cong \prod_{j=1}^\ell \GL_{t_j}\left(\finiteField\right) \times G'$ where $G' = \IsometryGroup\left(\hermitianSpace'\right)$ where $\hermitianSpace'$ is a non-degenerate hermitian subspace and $\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic$, where $\xIsotropic$ and $\yIsotropic$ are totally isotropic subspace in duality.
-Suppose that $s \in T$ is such that $s \in L$, and denote by $s_i$ the projection of $s$ to $\GL_{t_i}\left(\finiteField\right)$ for $1 \le i \le \ell$ and by $s_0$ the projection of $s$ to $G'$.
+Suppose that $s \in L$, and denote by $s_i$ the projection of $s$ to $\GL_{t_i}\left(\finiteField\right)$ for $1 \le i \le \ell$ and by $s_0$ the projection of $s$ to $G'$.
 We denote

### 2025-02-17 paper.tex
Calvin's changes

@@
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
+Denote $$g_T\left(\theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ \calvin{we should add a $\chi$ as a variable to the left hand side of the above} Then
 	\begin{align*}
@@
 \end{remark}
+\subsection{Independence of geometric conjugacy for Gauss sums}
+\calvin{here is the section I am adding in.}
+\subsubsection{Geomtric Conjugacy and Lusztig Series}
+(following chapter 13 of Digne and Michel's Representations of Finite Groups of Lie Type)
+Let $\mathbb{G}$ be a reductive group over $\mathbb{F}$ and fix a torus $\mathbb{T}$ defined over $\mathbb{F}$.
+A \emph{dual group over $\mathbb{F}$} $\mathbb{G}^*$ with a dual torus $\mathbb{T}^*$ is a group with an isomorphism $X_*(T) \cong X^*(T^*)$ which is compatible with the action of Frobenius and sends roots to coroots \calvin{check if I flipped upper and lower star}.
+
+Associated with a torus character pair $(T,\theta)$ is a  Frobenius stable $W(\mathbb{T})$ orbit in $X_*(\mathbb{T}) = X^*(\mathbb{T}^*)$.
+Under a choice of $\overline{\mathbb{F}}^\times \cong \left(\mathbb{Q}/\mathbb{Z}\right)_{p'}$, $X^*(\mathbb{T}^*) \otimes \left(\mathbb{Q}/\mathbb{Z}\right)_{p'} \cong \mathbb{T}^*(\overline{\mathbb{F}})$, this associates to $(T,\theta)$ a Frobenius stable semisimple conjugacy class in $\mathbb{G}^*$.
+
+\begin{definition}
+    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \in \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ pair associated to $(s)$.
+\end{definition}
+
+\begin{center}
+\begin{tabular}{ c c c c c c}
+ Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
+ $Sp(2n)$ & $(\mathbb{F}^\times)^n$ & 1 & 1 &$SO(2n+1)$ & $(\mathbb{F}^\times)^n$\\  
+ $GSp(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\mathbb{F}^\times)^{n+1}$ \\
+ $SO(2n)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$SO(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
+ $GO(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\
+ $SO(2n+1)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
+ $GO(2n+1)$ & $(\mathbb{F}^\times)^{n+1}$ &1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\ 
+  $U(n)$ & $(\mathbb{F}_2^{Nm=1})^{n}$ & -1 & 1 & $U(n)$ &  $(\mathbb{F}_2^{Nm=1})^{n}$ 
+\end{tabular}
+\end{center}
+
+The pairs $(T,\theta),(T',\theta')$ are said to be geometrically conjugate if they are associated to the same Frobenius stable geometric conjugacy class.
+The main point of this section is the following
+
+\begin{proposition}
+\label{prop:geoconj}
+Suppose that $(T,\theta)(T',\theta')$ are maximal torus, character pairs of $G$ for a classical group $G$ which are geometrically conjugate. Then $g_T(\theta,\psi_{tr}) = g_{T'}(\theta',\psi_{tr})$.
+\end{proposition}
+
+\subsubsection{Guass sums attatched to semisimple elements in $GL_n$}
+Copy over the gauss sums attatched to semisimple elements section.
+
+\subsubsection{Proof of proposition \ref{prop:geoconj}}
+First we fix representations $\Phi$ of the dual groups:
+\begin{center}
+\begin{tabular}{ c c}
+ Group & Dual group representations $\Phi$ \\ 
+ $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
+ $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
+ $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
+ $GO(2n)$ & ? \\
+ $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
+ $GO(2n+1)$ & ? \\ 
+  $U(n)$  & $U(n) \to GL(2n)$  
+\end{tabular}
+\end{center}
+
+\begin{lemma}
+\label{lem:reducetoGLn}
+Let $(T,\theta)$ be a torus character pair in $G$ with associated Frobenius stable semisimple conjugacy class $(s) \subset G^*$. Then   
+    \[
+    g_T(\theta,\psi) = c\cdot g(\Phi(s),\psi),
+    \]
+where $c = g(1,\psi_1)$ if $G=Sp$ or $GSp$ and otherwise $c=1$.
+\end{lemma}
+Before proving this we recal that in the type B Weyl group the conjugacy classes of permutations are given by two partitions $(\lambda,\lambda')$ where $\lambda$ corresponds to cycles with an even number of sign changes and $\lambda'$ corresponds to cycles with an odd number of sign changes.
+In type D some of these classes split into two but for our purposes we will only care about the union of such classes.
+
+\begin{proof}
+We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
+Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ with $k_1 \geq k_2 \hdots \geq k_r$ and $m_1 \geq m_2 \hdots \geq m_r$ and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
+Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by $((k_1,k_2, \hdots, k_r), (m_1,m_2 \hdots m_s))$.
+The map $\Phi$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
+Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
+Then
+\[
+    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = \begin{cases}
+        g_T(\theta,\psi)  & G \neq Sp \textnormal{ or } GSp\\
+        g_T(\theta,\psi) \cdot g(1,\psi_1) & G = Sp \textnormal{ or } GSp
+    \end{cases}.
+\]
+Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$. \\
+Now for the unitary case: \calvin{this needs to be checked... I used engineers induction to guess at how the Weyl group conjugacy classes match the torus}
+Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s (\finiteFieldExtension{2m_i}^1)^2$ with $k_i$'s even and $m_i$'s odd \calvin{this is what I need to check...
+what tori you can get here} and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
+Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by having even cycles of lengths $k_1,k_2 \hdots k_r$ and odd cycles of lengths $m_1,m_1,m_2,m_2, \hdots, m_s,m_s$.
+The map $\Phi$ sends this conjugacy class to the conjugacy class with even cycles $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and odd cycles $m_1,m_1,m_1,m_1,m_2,m_2,m_2,m_2, \hdots, m_s,m_s,m_s,m_s$.
+Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class with all even cycles of lengths $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and $2m_1,2m_1,2m_2,2m_2, \hdots, 2m_s,2m_s$.
+Then $\Phi(s)$ is in this torus \calvin{write out what that means} giving a character $\tilde{\theta}$ on it and
+\[
+    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = g_T(\theta,\psi).
+\]
+Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
+\end{proof}
+
+This completes the proof of proposition \ref{prop:geoconj}.
 
@@
 Then for every $j$,
-$\alpha_j = \beta_j \circ \FieldNorm{b_j d_j}{d_j}$ for some $\beta_j \colon \multiplicativegroup{\finiteFieldExtension{d_j}} \to \multiplicativegroup{\cComplex}$, and similarly for every $i$, $\theta'_i = \vartheta_i \circ \FieldNorm{b'_i d'_i}{d'_i}$ for some $\vartheta_i \colon \multiplicativegroup{\finiteFieldExtension{d'_i}} \to \multiplicativegroup{\cComplex}$.
+$\alpha_j = \beta_j \circ \FieldNorm{b_j d_j}{d_j}$ for some regular character $\beta_j \colon \multiplicativegroup{\finiteFieldExtension{d_j}} \to \multiplicativegroup{\cComplex}$, and similarly for every $i$, $\theta'_i = \vartheta_i \circ \FieldNorm{b'_i d'_i}{d'_i}$ for some regular character $\vartheta_i \colon \multiplicativegroup{\finiteFieldExtension{d'_i}} \to \multiplicativegroup{\cComplex}$.
 By the Hasse--Davenport relation we have \begin{equation}\label{eq:hasse-davenport-for-semisimple-elements}
@@
 where $t_j \in \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $u_i \in \finiteFieldExtension{2m_i}^1$ for every $i$ and $j$.
-Then since $\ToriDualToriIsomorphism_k$ preserves degrees of Frobenius orbits, we have that $t_j \in \multiplicativegroup{\finiteFieldExtension{d_j}}$ and $u_i \in \multiplicativegroup{\finiteFieldExtension{d'_i}}$ for every $i$ and $j$ (and they do not belong to smaller field extensions).
+Then we have that $t_j \in \multiplicativegroup{\finiteFieldExtension{d_j}}$ and $u_i \in \multiplicativegroup{\finiteFieldExtension{d'_i}}$ for every $i$ and $j$ (and these elements do not belong to smaller field extensions).
 Thus
@@
 
-\begin{proposition}
-\label{prop:geoconj}
-    Let $(T,\theta)$ be geometrically conjugate to $(T',\theta')$ inside $G^\vee$ i.e.
-there exists $g \in T(\mathbb{F}_n)$ such that $gTg^{-1} = T'$ and $\theta'(Nm_{n:1}(x)) = \theta(Nm_{n:1}(g^{-1}xg))$ for $x \in T'(\mathbb{F}_n)$.
-Then $g_T(\theta,\psi_{tr}) = g_{T'}(\theta',\psi_{tr})$
-\end{proposition}
-
+\begin{comment}
 \calvin{here is the geometric idea:}
@@
 \calvin{The corollary plus the definition of geometric conjugacy imply $g_T(\theta,\psi) = \mu_kg_{T'}(\theta',\psi)$ for some $k$-th root of unity $\mu_k$. Not sure how to finish from here.}
-
+\end{comment}
 Let $\ToriDualToriIsomorphism_T \colon \widehat{T} \to T$ be as in the previous sections.
@@
 	\item For classical groups $G$ (as the ones we consider in this paper), the Lusztig series $\LusztigSeries{G}{s}$ contains at most one irreducible cuspidal representation.
+\calvin{False for $SL_2$?
+True for GSP though.
+Maybe true with connected center?}
+    \elad{No assumption on the center}\calvin{what about the two representations of $SL_2$ in anisotropic torus with the $-1$ character?}\elad{Maybe one of them is not cuspidal (has unipotent fixed vectors).
+See Lusztig's paper Irreducible Representations of Finite Classical Groups page 172}\calvin{I'm pretty sure neither has them.
+I haven't read this paper but my guess is the problem is that the centralizer of the $s$ in its Lusztig series is not connected: it is a seimdirect product of $\mathbb{G}_m$ and $\mathbb{Z}/2\mathbb{Z}$.}\elad{You are right, I checked Lusztig's paper and he takes $q$ to be a power of $2$ in the cases with disconnected center.
+I guess we have to switch to the similitude groups (for which Lusztig explains that we have unique cuspidals)}
 	\item The Lusztig series $\LusztigSeries{G}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $G$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.

### 2025-02-23 paper.tex
Calvin edits

@@
 Let $\mathbb{G}$ be a reductive group over $\mathbb{F}$ and fix a torus $\mathbb{T}$ defined over $\mathbb{F}$.
-A \emph{dual group over $\mathbb{F}$} $\mathbb{G}^*$ with a dual torus $\mathbb{T}^*$ is a group with an isomorphism $X_*(T) \cong X^*(T^*)$ which is compatible with the action of Frobenius and sends roots to coroots \calvin{check if I flipped upper and lower star}.
+The \emph{dual group over $\mathbb{F}$} of $\mathbb{G}$ with respect to the torus $\mathbb{T}$ corresponds to the group $\mathbb{G}^*$ with a dual torus $\mathbb{T}^*$ and root datum
+\[
+    (X^*(\mathbb{T}^*),\Phi_{\mathbb{T}^*},X_*(\mathbb{T}^*),\Phi_{\mathbb{T}^*}^\vee) \cong (X_*(\mathbb{T}),\Phi_{\mathbb{T}}^\vee,X^*(\mathbb{T}),\Phi_{\mathbb{T}})
+\]
+such that the isomorphism respects the Frobenius action on $X^*$ and $X_*$.
 
-Associated with a torus character pair $(T,\theta)$ is a  Frobenius stable $W(\mathbb{T})$ orbit in $X_*(\mathbb{T}) = X^*(\mathbb{T}^*)$.
+Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\overline{\mathbb{F}}^\times \cong \overline{\mathbb{Q}_\ell}^\times$.
+By homing the exact sequence
+\[
+    0 \to T \to \mathbb{T}(\overline{\mathbb{F}}) \to_{F-1} \mathbb{T}(\overline{\mathbb{F}}) \to 0
+\]
+into $\mathbb{G}_m(\overline{\mathbb{F}})$, we get an exact sequence
+\[
+    1 \to X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to_{F-1}X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to \mathrm{Irr}(T) \to 1
+\]
+(the last map is surjective by including $T$ into $\mathbb{T}$ as a finite set of points and giving a surjection of group algebras).
+
+Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element of 
+\[
+\frac{(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}}{\{(\tilde{F}-1)x: x \in (\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}\}}
+\]
+where $\tilde{F}$ is the Frobeinus twisted by a Weyl group element.
+
+Frobenius stable $W(\mathbb{T})$ orbit in $X_*(\mathbb{T}) = X^*(\mathbb{T})$.
 Under a choice of $\overline{\mathbb{F}}^\times \cong \left(\mathbb{Q}/\mathbb{Z}\right)_{p'}$, $X^*(\mathbb{T}^*) \otimes \left(\mathbb{Q}/\mathbb{Z}\right)_{p'} \cong \mathbb{T}^*(\overline{\mathbb{F}})$, this associates to $(T,\theta)$ a Frobenius stable semisimple conjugacy class in $\mathbb{G}^*$.

### 2025-02-24 paper.tex
Calvin changes

@@
 Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\overline{\mathbb{F}}^\times \cong \overline{\mathbb{Q}_\ell}^\times$. 
-By homing the exact sequence
-\[
-    0 \to T \to \mathbb{T}(\overline{\mathbb{F}}) \to_{F-1} \mathbb{T}(\overline{\mathbb{F}}) \to 0
-\]
-into $\mathbb{G}_m(\overline{\mathbb{F}})$, we get an exact sequence
-\[
-    1 \to X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to_{F-1}X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to \mathrm{Irr}(T) \to 1
-\]
-(the last map is surjective by including $T$ into $\mathbb{T}$ as a finite set of points and giving a surjection of group algebras).
+We get an isomorphism
+\begin{align*}
+\label{eq:DL}
+0 \to X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to_{F-1} X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to \mathbb{T}(\overline{\mathbb{F}}) \to 0
+\end{align*}
+with the last map being $y \mapsto N_{\mathbb{F}^n/\mathbb{F}}(y(\zeta))$
+for the $\zeta=q^n-1$-root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\mathbb{T}$ is split).
 
-Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element of 
-\[
-\frac{(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}}{\{(\tilde{F}-1)x: x \in (\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}\}}
-\]
-where $\tilde{F}$ is the Frobeinus twisted by a Weyl group element.
-
-Frobenius stable $W(\mathbb{T})$ orbit in $X_*(\mathbb{T}) = X^*(\mathbb{T})$.
-Under a choice of $\overline{\mathbb{F}}^\times \cong \left(\mathbb{Q}/\mathbb{Z}\right)_{p'}$, $X^*(\mathbb{T}^*) \otimes \left(\mathbb{Q}/\mathbb{Z}\right)_{p'} \cong \mathbb{T}^*(\overline{\mathbb{F}})$, this associates to $(T,\theta)$ a Frobenius stable semisimple conjugacy class in $\mathbb{G}^*$.
+Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by treating $\theta$ as a linear functional on $Y(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by composing with the map to $\mathbb{T}(\mathbb{F})$.
+This is well defined up to the Weyl group, and in fact there is a correspondence between $(T',\theta')$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Coloarry 13.9].
+By composing with \ref{eq:DL}, we assocaited to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
 
 \begin{definition}
-    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \in \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ pair associated to $(s)$.
+    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} if their associated semisimple conjugacy classes in $G^*$ are the same.
+    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ pair associated to $(s)$.
 \end{definition}
@@
 The pairs $(T,\theta),(T',\theta')$ are said to be geometrically conjugate if they are associated to the same Frobenius stable geometric conjugacy class.
-The main point of this section is the following
+The main point of this section is the following:
+
+For a torus $T$ is a classical group $G$ embedded in $GL_n$ via $\rho$, define
+\[
+    g_{T,\rho}(\theta,\psi,\chi) := \frac{\sum_{t\in T} \theta(t)\chi(det(\rho(t)-1))}{}
+\]
 
@@
 \label{prop:geoconj}
-Suppose that $(T,\theta)(T',\theta')$ are maximal torus, character pairs of $G$ for a classical group $G$ which are geometrically conjugate. Then $g_T(\theta,\psi_{tr}) = g_{T'}(\theta',\psi_{tr})$.
+Suppose that $(T,\theta)(T',\theta')$ are maximal torus, character pairs of $G$ for a classical group $G$ which are geometrically conjugate.
+Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$ where $\rho$ is the natural embedding of $GL_n$
 \end{proposition}
 
-\subsubsection{Guass sums attatched to semisimple elements in $GL_n$}
-Copy over the gauss sums attatched to semisimple elements section.
+\subsubsection{Gauss sums attached to semisimple elements}
 
-\subsubsection{Proof of proposition \ref{prop:geoconj}}
+\subsubsection{General case of \ref{prop:geoconj}}
 First we fix representations $\Phi$ of the dual groups:

### 2025-02-25 paper.tex
Calvin changes

@@
 \end{remark}
-\subsection{Independence of geometric conjugacy for Gauss sums}
-\calvin{here is the section I am adding in.}
 \subsubsection{Geomtric Conjugacy and Lusztig Series}
@@
 
-Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\overline{\mathbb{F}}^\times \cong \overline{\mathbb{Q}_\ell}^\times$. 
+Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$. 
 We get an isomorphism
@@
 \end{align*}
-with the last map being $y \mapsto N_{\mathbb{F}^n/\mathbb{F}}(y(\zeta))$
-for the $\zeta=q^n-1$-root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\mathbb{T}$ is split).
+with the last map being $y \mapsto N_{T(\mathbb{F}^n):T(\mathbb{F})}(y(\zeta_n))$
+for the $\zeta_n=q^n-1$-root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\mathbb{T}$ is split).
 
-Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by treating $\theta$ as a linear functional on $Y(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by composing with the map to $\mathbb{T}(\mathbb{F})$.
+Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element $x_{T,\theta}$ of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+\[
+    exp(\langle x_{T,\theta},y\rangle) = \theta(N_{T(\mathbb{F}^n):T(\mathbb{F})}(y(\zeta_n)))
+\]
+for large enough $n$.
 This is well defined up to the Weyl group, and in fact there is a correspondence between $(T',\theta')$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Coloarry 13.9].
-By composing with \ref{eq:DL}, we assocaited to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
+By composing with \ref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
 
 \begin{definition}
-    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} if their associated semisimple conjugacy classes in $G^*$ are the same.
-    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ pair associated to $(s)$.
+    Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(T,\theta)$ by $(s_{T,\theta})$.
+Similarly denote the Frobenius stable Weyl group element of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta})$
+    \\
+    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta}), (s_{T,\theta'})$ are equal.\\
+    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
 \end{definition}
@@
 
-The pairs $(T,\theta),(T',\theta')$ are said to be geometrically conjugate if they are associated to the same Frobenius stable geometric conjugacy class.
-The main point of this section is the following:
+For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\mathbb{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to  GL_n$.
+Fix a Frobenius stable maximal torus $\mathbb{T}^* \subset G^*$ and a Frobenius stable maximal torus $\mathbb{T} \subset GL_n$ which contains $\rho(\mathbb{T}^*)$.
+Let $\tilde{T}$ be the torus of $GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\mathbb{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$.
+Define
+\[
+    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
+    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(det(t))\psi(tr(t)).
+\]
+The following lemma shows that this is well defined.
+\begin{lemma}
+\label{lemma:gl_invariance}
+\begin{enumerate}[(i)]
+	\item In the case $G = GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
+	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+(i) In this case when $T = \Pi_{i} \mathbb{F}^{n_i}$ and $\theta = \Pi_{i} \alpha_i$, we recover the Gauss sum
+\[
+	g_{T,\rho}(\theta,\psi,\chi)  = \varepsilon_{\algebraicGroup{T}} \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi) .
+\]
+By by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
+\\
+(ii) For a Frobenius stable semisimple conjugacy class $(s)$ in $GL_n$ in $GL_n$, we define
+\[
+	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
+\]
+By (i) this is well defined. Then
+\[
+	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
+\]
+which is independent of of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
+\end{proof}
 
-For a torus $T$ is a classical group $G$ embedded in $GL_n$ via $\rho$, define
+\begin{corollary}
+\label{cor:geoconj}
+Suppose that $(T,\theta)(T',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$.
+\end{corollary}
+\begin{proof}
+Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
+\end{proof}
+
+\subsubsection{Invariance under geometric conjugacy in Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}}
+The main result of this subsection is 
+\begin{theorem}
+\label{thm:indep_geo_conj}
+	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+\end{theorem}
+
+The idea of the proof is that the formula from Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for an appropriate $\rho$.
+We will need the following computation:
+\begin{lemma}
+\label{lem:cochar_computation}
+    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
+    \begin{enumerate}
+        \item $x_{\mathbb{F}_n^\times \times \mathbb{F}_n^\times,\alpha \times \alpha^{-1}} = \phi(x_{\mathbb{F}_n,\alpha})$
+        \item $x_{\mathbb{F}_{2n}^\times,\theta'}=\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta})$
+    \end{enumerate}
+    where $\theta'(t) = \theta(t^{1-q^m})$.
+\end{lemma}
+\begin{proof}
+Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
 \[
-    g_{T,\rho}(\theta,\psi,\chi) := \frac{\sum_{t\in T} \theta(t)\chi(det(\rho(t)-1))}{}
+    exp(\langle x_{T,\theta},y\rangle) = \theta(y(Nm_{T(\mathbb{F}_m):T(\mathbb{F})}(y(\zeta_m))).
 \]
+Thus the result follows from the computations:\\
+(i)
+\begin{align*}
+    exp(\langle\phi(x_{\mathbb{F}_n,\alpha}),(y_1,y_2)\rangle) &= exp(\langle x_{\mathbb{F}_n,\alpha},\phi^*(y_1,y_2)\rangle) \\
+    &= \alpha\left(Nm_{mn:n}(y_1(\zeta_{mn})\right) \alpha\left(Nm_{mn:n}(y_2(\zeta_{mn})\right)^{-1} \\
+    &= \left(\alpha\times\alpha^{-1}\right)\left(Nm_{mn:n}((y_1,y_2)(\zeta_{mn}))\right)
+\end{align*}
+(ii)
+\begin{align*}
+    exp(\langle\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta}),(y_1,y_2)\rangle) &= exp(\langle x_{(\mathbb{F}_{2n})^{Nm=1},\theta},\phi^*(y_1,y_2)\rangle) \\
+    &= \theta\left(\frac{Nm_{2mn:2n}(y_1(\zeta_{2mn})}{Nm_{2mn:2n}(y_1(\zeta_{2mn})^{q^n}}\right) \theta\left(\frac{Nm_{2mn:2n}(y_2(\zeta_{2mn})}{Nm_{2mn:2n}(y_2(\zeta_{2mn})^{q^n}}\right)^{-1} \\
+    &= \theta'\left(Nm_{2mn:2n}((y_1,y_2)(\zeta_{mn}))\right)
+\end{align*}
+\end{proof}
 
-\begin{proposition}
-\label{prop:geoconj}
-Suppose that $(T,\theta)(T',\theta')$ are maximal torus, character pairs of $G$ for a classical group $G$ which are geometrically conjugate.
-Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$ where $\rho$ is the natural embedding of $GL_n$
-\end{proposition}
-
-\subsubsection{Gauss sums attached to semisimple elements}
-
-\subsubsection{General case of \ref{prop:geoconj}}
-First we fix representations $\Phi$ of the dual groups:
+Now we fix representations $\rho$ of the dual groups:
 \begin{center}
 \begin{tabular}{ c c}
- Group & Dual group representations $\Phi$ \\ 
+ Group & Dual group representations $\rho$ \\ 
  $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
@@
 \end{center}
+Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
+In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
+In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
+In all these cases we can apply lemma \ref{lem:cochar_computation}:
 
-\begin{lemma}
-\label{lem:reducetoGLn}
-Let $(T,\theta)$ be a torus character pair in $G$ with associated Frobenius stable semisimple conjugacy class $(s) \subset G^*$. Then   
+\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] Let $T$ be a torus in $G$ and suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
+We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\mathbb{T}^*$ in $G^*$ including into the split torus $\mathbb{T}'$ in $GL$ in the non unitary case and in the unitary case we use the tori $\mathbb{T}^*$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus $\mathbb{T}'$ in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$.
+We then define $\tilde{T}$ as the $\mathbb{F}$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\mathbb{T}')$ where $(w)$ inside $W(\mathbb{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
+Lemma \ref{lem:cochar_computation} above implies that
 \[
-    g_T(\theta,\psi) = c\cdot g(\Phi(s),\psi),
+g_{T,\rho}(\theta,\psi,\chi)= \varepsilon_{\algebraicGroup{T}}\varepsilon_{\algebraicGroup{\tilde{T}}}g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
+        1  & G \neq Sp, GSp\\
+        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
+    \end{cases}
 \]
-where $c = g(1,\psi_1)$ if $G=Sp$ or $GSp$ and otherwise $c=1$.
-\end{lemma}
-Before proving this we recal that in the type B Weyl group the conjugacy classes of permutations are given by two partitions $(\lambda,\lambda')$ where $\lambda$ corresponds to cycles with an even number of sign changes and $\lambda'$ corresponds to cycles with an odd number of sign changes.
-In type D some of these classes split into two but for our purposes we will only care about the union of such classes.
+where $g_T(\theta,\psi,\chi)$ is the expression from theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
+\calvin{how does $\epsilon$ depend on $w$?
+Is the product always one?}.
+Corollary \ref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.
+Now the formula for $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}$ in theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} finishes the proof.
+\begin{comment}
+We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
 
-\begin{proof}
-We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
 Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ with $k_1 \geq k_2 \hdots \geq k_r$ and $m_1 \geq m_2 \hdots \geq m_r$ and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
 Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by $((k_1,k_2, \hdots, k_r), (m_1,m_2 \hdots m_s))$.
-The map $\Phi$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
+The map $\rho$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
 Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
-Then
+Then by theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
 \[
@@
 Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
+\end{comment}
 \end{proof}
-
-This completes the proof of proposition \ref{prop:geoconj}.
 

### 2025-02-28 paper.tex
Calvin comments
Calvin changes

@@
 
-Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element $x_{T,\theta}$ of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\mathbb{T}$ to a fixed torus $\mathbb{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $X^*(\mathbb{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
 \[
@@
 for large enough $n$.
-This is well defined up to the Weyl group, and in fact there is a correspondence between $(T',\theta')$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Coloarry 13.9].
+This is well defined up to the Weyl group, and in fact there is a correspondence between $(T,\theta)$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Corollary 13.9].
 By composing with \ref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
@@
 \]
-The following lemma shows that this is well defined.
+\calivn{check $\epsilon$ factors and Hasse-Davenport} The following lemma shows that this is well defined.
 \begin{lemma}
@@
     \end{enumerate}
-    where $\theta'(t) = \theta(t^{1-q^m})$.
+    where $\theta'(t) = \theta(t^{1-q^n})$.
 \end{lemma}

### 2025-02-28 paper.tex
Typo
Adding similitude stuff

--- 2025-02-24 paper.tex
@@
 \newcommand{\yIsotropic}{\mathrm{Y}}
+\newcommand{\similitudeCharacter}{\operatorname{sim}}
 
@@
 \newcommand{\inverseTranspose}[1]{#1^{\iota}}
+\newcommand{\involution}[1]{#1^{c}}
 \newcommand{\IdentityMatrix}[1]{I_{#1}}
@@
 \newcommand{\ParabolicSubgroup}{P}
+\newcommand{\GroupExtension}[1]{{#1}^{\mathrm{ext}}}
 
@@
 \newcommand{\finiteField}{\mathbb{F}}
+\newcommand{\quadraticExtension}{\mathbb{E}}
 \newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
@@
 
-Let $\hermitianSpace$ be a vector space of dimension $n$ over $\finiteField$, equipped with a non-degenerate bilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \finiteField$ which is either symmetric or anti-symmetric.
-Let $G = \IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
-Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \innerproduct{x}{AY} = 0$ for every $x, y \in \hermitianSpace$.
+Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$.
+Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.
+
+Let $\hermitianSpace$ be a vector space of dimension $n$ over $\quadraticExtension$, equipped with a non-degenerate sesquilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \quadraticExtension$ which is $\epsilon$-symmetric for $\epsilon \in \left\{\pm 1\right\}$.
+By this we mean that:
+\begin{enumerate}
+	\item For every $x_1,x_2,y \in \hermitianSpace$, $$\innerproduct{x_1 + x_2}{y} = \innerproduct{x_1}{y} + \innerproduct{x_2}{y}.$$
+	\item For every $x,y \in \hermitianSpace$ and $t \in \quadraticExtension$, $$\innerproduct{tx}{y} = t\innerproduct{x}{y}.$$
+	\item ($\epsilon$-symmetric) For every $x,y \in \hermitianSpace$, $$\innerproduct{x}{y} = \epsilon \involution{\innerproduct{y}{x}}.$$
+	\item (non-degenerate) For every $0 \ne x \in \hermitianSpace$ there exists $y \in \hermitianSpace$ such that $$\innerproduct{x}{y} \ne 0.$$
+\end{enumerate}
+Let $\IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+We denote by $G$ the identity component of $\IsometryGroup\left(\hermitianSpace\right)$.
+Let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
+Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
 
@@
 
-Let $\pi$ be an irreducible representation of $G$. Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
-Since $\Phi_{\chi}$ is a class function of $\GL\left(\hermitianSpace\right)$, it is also a class function of $G$, and therefore $\dblGaussSum{\pi}{\chi} \in \Hom_{G}\left(\pi, \pi\right)$.
+Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
+Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
+Since $\Phi_{\chi}$ is a class function of $\GL\left(\hermitianSpace\right)$, it is also a class function of $G$.
+Since $G$ is a normal subgroup of $H$, we have that $\dblGaussSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
 By Schur's lemma, there exists a constant $\dblGaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
@@
 where $\hermitianSpace' \subset \hermitianSpace$ is a non-degenerate subspace, orthogonal to $\xIsotropic$ and $\yIsotropic$.
-Let $P$ be the parabolic subgroup of $G$, consisting of all elements stabilizing the flag $$0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.$$
+Let $P$ be the parabolic subgroup of $H$, consisting of all elements stabilizing the flag $$0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.$$
+Let $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
 Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$.
-Then $L$ is isomorphic to $G' \times \GL_k\left(\finiteField\right)$, where $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
+Then $L$ is isomorphic to $H' \times \GL_k\left(\finiteField\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.
 
 \begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
-	Let $\pi'$ be an irreducible representation of $G'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$.
-Then for any irreducible representation $\pi$ of $G$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{G}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\chi^2 \ne 1$, we have
+	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$.
+Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\chi^2 \ne 1$, we have
 	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
@@
 	\end{align*}
-	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P$.
+	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.
 
@@
 	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
-		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P\\
+		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
 				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
 	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
 	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
@@
 \end{remark}
-\subsection{Independence of geometric conjugacy for Gauss sums}
-\calvin{here is the section I am adding in.}
-\subsubsection{Geomtric Conjugacy and Lusztig Series}
-(following chapter 13 of Digne and Michel's Representations of Finite Groups of Lie Type)
-Let $\mathbb{G}$ be a reductive group over $\mathbb{F}$ and fix a torus $\mathbb{T}$ defined over $\mathbb{F}$.
-The \emph{dual group over $\mathbb{F}$} of $\mathbb{G}$ with respect to the torus $\mathbb{T}$ corresponds to the group $\mathbb{G}^*$ with a dual torus $\mathbb{T}^*$ and root datum
-\[
-    (X^*(\mathbb{T}^*),\Phi_{\mathbb{T}^*},X_*(\mathbb{T}^*),\Phi_{\mathbb{T}^*}^\vee) \cong (X_*(\mathbb{T}),\Phi_{\mathbb{T}}^\vee,X^*(\mathbb{T}),\Phi_{\mathbb{T}})
-\]
-such that the isomorphism respects the Frobenius action on $X^*$ and $X_*$.
-
-Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\overline{\mathbb{F}}^\times \cong \overline{\mathbb{Q}_\ell}^\times$. 
-We get an isomorphism
-\begin{align*}
-\label{eq:DL}
-0 \to X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to_{F-1} X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to \mathbb{T}(\overline{\mathbb{F}}) \to 0
-\end{align*}
-with the last map being $y \mapsto N_{\mathbb{F}^n/\mathbb{F}}(y(\zeta))$
-for the $\zeta=q^n-1$-root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\mathbb{T}$ is split).
-
-Hence for a torus character pair $(T',\theta')$ for $G$, we may conjugate $\mathbb{T}'$ to a fixed torus $\mathbb{T}$ and associate to $\theta$ to an element of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by treating $\theta$ as a linear functional on $Y(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by composing with the map to $\mathbb{T}(\mathbb{F})$.
-This is well defined up to the Weyl group, and in fact there is a correspondence between $(T',\theta')$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Coloarry 13.9].
-By composing with \ref{eq:DL}, we assocaited to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
-
-\begin{definition}
-    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} if their associated semisimple conjugacy classes in $G^*$ are the same.
-    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ pair associated to $(s)$.
-\end{definition}
-
-\begin{center}
-\begin{tabular}{ c c c c c c}
- Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
- $Sp(2n)$ & $(\mathbb{F}^\times)^n$ & 1 & 1 &$SO(2n+1)$ & $(\mathbb{F}^\times)^n$\\  
- $GSp(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\mathbb{F}^\times)^{n+1}$ \\
- $SO(2n)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$SO(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
- $GO(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\
- $SO(2n+1)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
- $GO(2n+1)$ & $(\mathbb{F}^\times)^{n+1}$ &1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\ 
-  $U(n)$ & $(\mathbb{F}_2^{Nm=1})^{n}$ & -1 & 1 & $U(n)$ &  $(\mathbb{F}_2^{Nm=1})^{n}$ 
-\end{tabular}
-\end{center}
-
-The pairs $(T,\theta),(T',\theta')$ are said to be geometrically conjugate if they are associated to the same Frobenius stable geometric conjugacy class.
-The main point of this section is the following:
-
-For a torus $T$ is a classical group $G$ embedded in $GL_n$ via $\rho$, define
-\[
-    g_{T,\rho}(\theta,\psi,\chi) := \frac{\sum_{t\in T} \theta(t)\chi(det(\rho(t)-1))}{}
-\]
-
-\begin{proposition}
-\label{prop:geoconj}
-Suppose that $(T,\theta)(T',\theta')$ are maximal torus, character pairs of $G$ for a classical group $G$ which are geometrically conjugate.
-Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$ where $\rho$ is the natural embedding of $GL_n$
-\end{proposition}
-
-\subsubsection{Gauss sums attached to semisimple elements}
-
-\subsubsection{General case of \ref{prop:geoconj}}
-First we fix representations $\Phi$ of the dual groups:
-\begin{center}
-\begin{tabular}{ c c}
- Group & Dual group representations $\Phi$ \\ 
- $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
- $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
- $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
- $GO(2n)$ & ? \\
- $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
- $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to GL(2n)$  
-\end{tabular}
-\end{center}
-
-\begin{lemma}
-\label{lem:reducetoGLn}
-Let $(T,\theta)$ be a torus character pair in $G$ with associated Frobenius stable semisimple conjugacy class $(s) \subset G^*$. Then   
-    \[
-    g_T(\theta,\psi) = c\cdot g(\Phi(s),\psi),
-    \]
-where $c = g(1,\psi_1)$ if $G=Sp$ or $GSp$ and otherwise $c=1$.
-\end{lemma}
-Before proving this we recal that in the type B Weyl group the conjugacy classes of permutations are given by two partitions $(\lambda,\lambda')$ where $\lambda$ corresponds to cycles with an even number of sign changes and $\lambda'$ corresponds to cycles with an odd number of sign changes.
-In type D some of these classes split into two but for our purposes we will only care about the union of such classes.
-
-\begin{proof}
-We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
-Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ with $k_1 \geq k_2 \hdots \geq k_r$ and $m_1 \geq m_2 \hdots \geq m_r$ and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
-Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by $((k_1,k_2, \hdots, k_r), (m_1,m_2 \hdots m_s))$.
-The map $\Phi$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
-Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
-Then
-\[
-    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = \begin{cases}
-        g_T(\theta,\psi)  & G \neq Sp \textnormal{ or } GSp\\
-        g_T(\theta,\psi) \cdot g(1,\psi_1) & G = Sp \textnormal{ or } GSp
-    \end{cases}.
-\]
-Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$. \\
-Now for the unitary case: \calvin{this needs to be checked... I used engineers induction to guess at how the Weyl group conjugacy classes match the torus}
-Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s (\finiteFieldExtension{2m_i}^1)^2$ with $k_i$'s even and $m_i$'s odd \calvin{this is what I need to check...
-what tori you can get here} and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
-Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by having even cycles of lengths $k_1,k_2 \hdots k_r$ and odd cycles of lengths $m_1,m_1,m_2,m_2, \hdots, m_s,m_s$.
-The map $\Phi$ sends this conjugacy class to the conjugacy class with even cycles $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and odd cycles $m_1,m_1,m_1,m_1,m_2,m_2,m_2,m_2, \hdots, m_s,m_s,m_s,m_s$.
-Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class with all even cycles of lengths $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and $2m_1,2m_1,2m_2,2m_2, \hdots, 2m_s,2m_s$.
-Then $\Phi(s)$ is in this torus \calvin{write out what that means} giving a character $\tilde{\theta}$ on it and
-\[
-    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = g_T(\theta,\psi).
-\]
-Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
-\end{proof}
-
-This completes the proof of proposition \ref{prop:geoconj}.
 

### 2025-02-28 paper.tex
Even orthogonal groups
Defining the extension only for cases needed

@@
 Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
+If $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace = 2n$ is even, then $\GroupExtension{G}$ consists of all element in $G$ satisfying $\similitudeCharacter\left(g\right) = \left(\det g\right)^n$.
 Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
+
+We will assume that $\dim_{\finiteField} \hermitianSpace$ is even.
+This is automatic for all case, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$, in which case we will only consider even special orthogonal groups.
 
@@
 
-Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
+Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$ if $\quadraticExtension = \finiteField$ and $H = G$ if $\quadraticExtension \ne \finiteField$.
 Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$

### 2025-02-28 paper.tex
Corrections

@@
 \newcommand{\ParabolicSubgroup}{P}
-\newcommand{\GroupExtension}[1]{{#1}^{\mathrm{ext}}}
+\newcommand{\GroupExtension}[1]{\widetilde{#1}}
 
@@
 Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
-If $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace = 2n$ is even, then $\GroupExtension{G}$ consists of all element in $G$ satisfying $\similitudeCharacter\left(g\right) = \left(\det g\right)^n$.
+If $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace = 2n$ is even, then $\GroupExtension{G}$ consists of all elements in $\GroupExtension{\IsometryGroup\left(G\right)}$ satisfying $\similitudeCharacter\left(g\right) = \left(\det g\right)^n$.
 Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.

### 2025-02-28 paper.tex
Update paper.tex

@@
 We will assume that $\dim_{\finiteField} \hermitianSpace$ is even.
-This is automatic for all case, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$, in which case we will only consider even special orthogonal groups.
+This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$, in which case we will only consider even special orthogonal groups.
 

### 2025-03-01 paper.tex
Adding a vanishing lemma

@@
 
+\begin{lemma}\label{lem:sum-vanishes-for-singular-matrices}
+	For any singular matrix $X \in \squareMatrix_n\left(\finiteField\right)$ and any $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the sum
+	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter\left(\trace\left(Xh\right)\right)$$
+	is zero.
+\end{lemma}
+\begin{proof}
+	Write $$X = h_1 \begin{pmatrix}
+		\IdentityMatrix{n-r}\\
+		& 0_r
+	\end{pmatrix} h_2,$$
+	where $1 \le r \le n$ and $h_1, h_2 \in \GL_n\left(\finiteField\right)$. Then
+	$$\fieldCharacter\left(\trace Xh\right) = \fieldCharacter\left(\trace\left( \begin{pmatrix}
+		\IdentityMatrix{n-r}\\
+		& 0_r
+	\end{pmatrix} h_2 h h_1\right)\right).$$
+	Changing variables $h \mapsto h_2^{-1} h h_1^{-1},$
+	we obtain the inner sum
+	$$\sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
+		\IdentityMatrix{n-r}\\
+		& 0_r
+	\end{pmatrix} h \right) \chi\left(\det h\right),$$
+	which equals
+	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
+		\IdentityMatrix{n-r}\\
+		& 0_r
+	\end{pmatrix} \begin{pmatrix}
+		\IdentityMatrix{n-1}\\
+		& a
+	\end{pmatrix} h \right) \chi\left(\det h\right).$$
+	Changing variables $h \mapsto \left(\begin{smallmatrix}
+		\IdentityMatrix{n-1}\\
+		& a^{-1}
+	\end{smallmatrix}\right) h$, we get the inner sum $$\sum_{a \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(a\right),$$
+	which vanishes because $\chi \ne 1$.
+\end{proof}
+
 \section{Doubling method Gauss sums}
@@
 	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
-	We claim that for a singular matrix $X \in \squareMatrix_k\left(\finiteField\right)$ the inner sum vanishes. To show this, write $$X = h_1 \begin{pmatrix}
-		\IdentityMatrix{k-r}\\
-		& 0_r
-	\end{pmatrix} h_2,$$
-	where $1 \le r \le k$ and $h_1, h_2 \in \GL_k\left(\finiteField\right)$. Then
-	$$\fieldCharacter\left(\trace Xh\right) = \fieldCharacter\left(\trace\left( \begin{pmatrix}
-		\IdentityMatrix{k-r}\\
-		& 0_r
-	\end{pmatrix} h_2 h h_1\right)\right).$$
-	Changing variables $h \mapsto h_2^{-1} h h_1^{-1},$
-	we obtain the inner sum
-	$$\sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
-		\IdentityMatrix{k-r}\\
-		& 0_r
-	\end{pmatrix} h \right) \chi\left(\det h\right),$$
-	which equals
-	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
-		\IdentityMatrix{k-r}\\
-		& 0_r
-	\end{pmatrix} \begin{pmatrix}
-		\IdentityMatrix{k-1}\\
-		& a
-	\end{pmatrix} h \right) \chi\left(\det h\right).$$
-	Changing variables $h \mapsto \left(\begin{smallmatrix}
-		\IdentityMatrix{k-1}\\
-		& a^{-1}
-	\end{smallmatrix}\right) h$, we get the inner sum $$\sum_{a \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(a\right),$$
-	which vanishes because $\chi \ne 1$.
-	Hence, we have
-	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$.
+Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	Changing variables $h \mapsto X^{-1} h$, we get
@@
 	\end{align*}
-	Assume that $\chi \ne 1$.
-Then since $\GaussSum{\chi_{\GL\left(\hermitianSpace\right)}}{\fieldCharacter}_A$ appears in the last equation, the sum can be reduced to $A \in \GL\left(\hermitianSpace\right)$.
-Let us replace $h$ with $A^{-1} h$.
-We get the sum
+	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
 	\begin{align*}

### 2025-03-01 paper.tex
Quadratic extension. Quadratic extension everywhere!

@@
 \end{enumerate}
-Let $\IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+Let $\IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
 We denote by $G$ the identity component of $\IsometryGroup\left(\hermitianSpace\right)$.
-Let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+Let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
 Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
@@
 
-Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.
-As before, the assignment $\Phi_{\chi} \colon \GL\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
+Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
+As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
 \chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right) & \text{if }\det\left(g - \idmap_{\hermitianSpace}\right) \ne 0\\
@@
 \end{dcases}$$
-is a class function of $\GL\left(\hermitianSpace\right)$.
+is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
 
@@
 Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
-Since $\Phi_{\chi}$ is a class function of $\GL\left(\hermitianSpace\right)$, it is also a class function of $G$.
+Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$.
 Since $G$ is a normal subgroup of $H$, we have that $\dblGaussSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
@@
 Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$.
-Then $L$ is isomorphic to $H' \times \GL_k\left(\finiteField\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.
+Then $L$ is isomorphic to $H' \times \GL_k\left(\quadraticExtension\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.
 
 \begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
-	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\finiteField\right)$.
+	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$.
 Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\chi^2 \ne 1$, we have
@@
 	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-n^2} \sum_{h \in \GL\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing\left(\hermitianSpace\right)} \chi^{-1}\left(\det h\right) \fieldCharacter\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\det h\right) \fieldCharacter\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
 	Hence, \begin{align*}
-		q^{n^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing\left(\hermitianSpace\right)} \sum_{h \in \GL\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace\left(Ah\right)\right) \\
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace\left(Ah\right)\right) \\
 		& \times \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
-	Assume that $\chi \ne 1$. By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL\left(\hermitianSpace\right)$. Let us replace $h$ with $A^{-1} h$. We get the sum
+	Assume that $\chi \ne 1$.
+By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
+Let us replace $h$ with $A^{-1} h$.
+We get the sum
 	\begin{align*}
-		\sum_{A \in \GL\left(\hermitianSpace\right)} \chi^{-1}\left(\det A\right) \sum_{h \in \GL\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace h\right) \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\det A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace h\right) \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 	\begin{align*}
-		q^{n^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL\left(\hermitianSpace\right)}  \chi\left(\det\left(xh\right)\right) \fieldCharacter\left(\trace h\right) \\
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\det\left(xh\right)\right) \fieldCharacter\left(\trace h\right) \\
 		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\det p'\right) \fieldCharacter\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
@@
 	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\finiteField\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
 	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
@@
 	\begin{equation}
-		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\finiteField\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
 	\end{equation}

### 2025-03-01 paper.tex
Another \quadraticExtension

@@
 If $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace = 2n$ is even, then $\GroupExtension{G}$ consists of all elements in $\GroupExtension{\IsometryGroup\left(G\right)}$ satisfying $\similitudeCharacter\left(g\right) = \left(\det g\right)^n$.
-Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
+Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
 

### 2025-03-01 paper.tex
More corrections

@@
 
-Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a character.
-For an irreducible representation  $\tau$ of $\GL_k\left(\finiteField\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
+Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
+For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
 For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor}}.$$

### 2025-03-01 paper.tex
Removing \left[\right] factors

@@
 \begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ is a maximal torus of $G$.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ \calvin{we should add a $\chi$ as a variable to the left hand side of the above} Then
+	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$.
+Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
 	\begin{align*}
-		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} g_T\left(\theta, \fieldCharacter\right) \\
-		& \times \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right) \\
-		& \left[\times \epsilon\left(-1\right) \chi\left(-2\right)\right],
+		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
 	\end{align*}
-	where the terms in $\left[\right]$ only appear in the odd orthogonal group case.
 \end{theorem}
-    \calvin{What does the $\chi(-2)$ come from? I didn't quite get that when I was messing around}
 \begin{proof}
@@
 	\begin{align*}
-		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right)\\
-		& \times \left[\epsilon\left(-1\right)\right].
+		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
 	\end{align*}
 	Thus \begin{align*}
-		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right) \\
-		& \left[\times \chi\left(-2\right)\right].
+		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
 	\end{align*}

### 2025-03-01 paper.tex
Resolving some issues, probably creating new issues

@@
 For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor}}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor}}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 
-Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$.
-It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \FieldNorm{2m}{1}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
+Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$.
+It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
 Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right).$$
 
 As usual, we rewrite this sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
 If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
-$$-q^{-m} \tau\left(\chi \circ \FieldNorm{2m}{1}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
+$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
 To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \finiteFieldExtension{2m}^1$ given by $t \mapsto t^{1 - q^m}$.
@@
 Replacing the sum over $x \in \finiteFieldExtension{2m}^1$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
-	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
-	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
+	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
+	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
 \end{align*}
@@
 \begin{align*}
-	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(z\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
+	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
 \end{align*}
-Since $\chi \circ \FieldNorm{2m}{1} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
+Since $\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
 Hence, we may reduce the sum over $z$ to $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
@@
 	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
-	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
+	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
 \end{align*}
@@
 \begin{align*}
-	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\FieldNorm{2m}{1}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
+	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
 \end{align*}
@@
 $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(-x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
 	where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
@@
 $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\FieldNorm{2m}{1}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
 
@@
 	\begin{align*}
-		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
+		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
 	\end{align*}
@@
 \begin{proof}
-	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},$$
+	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor},$$
 	the facts \begin{equation*}
-		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor},
+		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor},
 	\end{equation*}
@@
 	Thus \begin{align*}
-		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
+		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
 	\end{align*}
@@
 \begin{enumerate}
-	\item For classical groups $G$ (as the ones we consider in this paper), the Lusztig series $\LusztigSeries{G}{s}$ contains at most one irreducible cuspidal representation.
-\calvin{False for $SL_2$?
-True for GSP though.
-Maybe true with connected center?}
-    \elad{No assumption on the center}\calvin{what about the two representations of $SL_2$ in anisotropic torus with the $-1$ character?}\elad{Maybe one of them is not cuspidal (has unipotent fixed vectors).
-See Lusztig's paper Irreducible Representations of Finite Classical Groups page 172}\calvin{I'm pretty sure neither has them.
-I haven't read this paper but my guess is the problem is that the centralizer of the $s$ in its Lusztig series is not connected: it is a seimdirect product of $\mathbb{G}_m$ and $\mathbb{Z}/2\mathbb{Z}$.}\elad{You are right, I checked Lusztig's paper and he takes $q$ to be a power of $2$ in the cases with disconnected center.
-I guess we have to switch to the similitude groups (for which Lusztig explains that we have unique cuspidals)}
-	\item The Lusztig series $\LusztigSeries{G}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $G$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
+	\item For the groups $\GroupExtension{G}$ as the ones we consider in this paper, the Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ contains at most one irreducible cuspidal representation.
+	\item The restriction of $R_{\GroupExtension{T},\GroupExtension{G}} \left(\GroupExtension{\theta}\right)$ to $G$ is $R_{T, G} \left(\tilde{\theta} \restriction_T\right)$ \cite[Page 140]{DigneMichel2020}.
+TODO: Write more.
+	\item The Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $\GroupExtension{G}$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
 \end{enumerate}
@@
 \begin{proof}
-	The proof is by induction on $\dim \hermitianSpace$.
+	The proof is by induction on $\dim_{\quadraticExtension} \hermitianSpace$.
 
@@
 	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
 	$$c_{\pi} \cdot \dblVirtualGaussSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
-	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblGaussSumScalar{\pi}{\chi}$, the result follows.

### 2025-03-01 paper.tex
More quadratic field notations

@@
 \newcommand{\RealPart}{\mathrm{Re}}
+\newcommand{\detQuadratic}{{\det}_{\quadraticExtension}}
 \newcommand{\Hom}{\mathrm{Hom}}
@@
 \newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
+\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
 \newcommand{\FieldExtension}[2]{{#1} \slash {#2}}
@@
 \section{Notation}
-Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter_{\finiteField} \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
 
@@
 For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
-This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
+$$\GaussSum{\tau \times \chi}{\fieldCharacter_{\finiteField}} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter_{\finiteField}\left(\trace g\right).$$
+This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter_{\finiteField}} \in \cComplex$ such that
+$$\GaussSum{\tau \times \chi}{\fieldCharacter_{\finiteField}} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter_{\finiteField}} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
 
@@
 	For any singular matrix $X \in \squareMatrix_n\left(\finiteField\right)$ and any $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the sum
-	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter\left(\trace\left(Xh\right)\right)$$
+	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter_{\finiteField}\left(\trace\left(Xh\right)\right)$$
 	is zero.
@@
 	where $1 \le r \le n$ and $h_1, h_2 \in \GL_n\left(\finiteField\right)$. Then
-	$$\fieldCharacter\left(\trace Xh\right) = \fieldCharacter\left(\trace\left( \begin{pmatrix}
+	$$\fieldCharacter_{\finiteField}\left(\trace Xh\right) = \fieldCharacter_{\finiteField}\left(\trace\left( \begin{pmatrix}
 		\IdentityMatrix{n-r}\\
@@
 	we obtain the inner sum
-	$$\sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
+	$$\sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \begin{pmatrix}
 		\IdentityMatrix{n-r}\\
@@
 	which equals
-	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
+	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \begin{pmatrix}
 		\IdentityMatrix{n-r}\\
@@
 	We have the identity
-	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter_{\finiteField}} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+			y^{-1} x = -g}} \fieldCharacter_{\finiteField}\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter_{\finiteField}\left(\trace y\right).$$
 \end{proposition}
 \begin{proof}
-	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$.
-Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	Changing variables $h \mapsto X^{-1} h$, we get
-	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
+	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \left(Xg\right)\right) \fieldCharacter_{\finiteField}\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter_{\finiteField}\left(-\trace X\right).$$
 	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
-	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter_{\finiteField}} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+			y^{-1} x = -g}} \fieldCharacter_{\finiteField}\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter_{\finiteField}\left(\trace y\right).$$
 \end{proof}
@@
 We now use this to compute $\dblGaussSum{\tau}{\chi}$.
-We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
+We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter_{\finiteField}} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter_{\finiteField}\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
 The last equality implies the following result.
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter_{\finiteField}}^k \GaussSumScalar{\tau}{\fieldCharacter_{\finiteField}} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter_{\finiteField}}.$$
 \end{theorem}
@@
 Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.
+Let $\fieldCharacter \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
 
@@
 As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right) & \text{if }\det\left(g - \idmap_{\hermitianSpace}\right) \ne 0\\
+\chi\left(\detQuadratic\left(g - \idmap_{\hermitianSpace}\right)\right) & \text{if }\detQuadratic\left(g - \idmap_{\hermitianSpace}\right) \ne 0\\
 0 & \text{otherwise,}
@@
 	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\det h\right) \fieldCharacter\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
 	Hence, \begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace\left(Ah\right)\right) \\
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter\left(\trace\left(Ah\right)\right) \\
 		& \times \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
@@
 	\begin{align*}
-		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\det A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\det h\right)\fieldCharacter\left(\trace h\right) \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter\left(\trace h\right) \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 	\begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\det\left(xh\right)\right) \fieldCharacter\left(\trace h\right) \\
-		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\det p'\right) \fieldCharacter\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter\left(\trace h\right) \\
+		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
-				\det\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\det\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
 	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\det\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \det\left(a\right)^{-1}\det\left(a - I_k\right)^2 \det\left( g' - \idmap_{\hermitianSpace'}\right),$$
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \detQuadratic\left(a\right)^{-1}\detQuadratic\left(a - I_k\right)^2 \detQuadratic\left( g' - \idmap_{\hermitianSpace'}\right),$$
 	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
@@
 	\begin{equation}
-		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\det a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
 	\end{equation}
@@
 \begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$.
+Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
 Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then

### 2025-03-01 paper.tex
Epsilon no more

@@
 	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
 Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then

### 2025-03-01 paper.tex
Norm one group notation

@@
 \newcommand{\FieldExtension}[2]{{#1} \slash {#2}}
+\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
 \newcommand{\algebraicClosure}[1]{\overline{#1}}
@@
 If $m \ge 1$, we denote 
-$$\finiteFieldExtension{2m}^1 = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
+$$\NormOneGroup{2m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
 
@@
 \subsubsection{Elliptic torus computation}
-In this section we compute the doubling method Gauss sum for a torus of the form $\finiteFieldExtension{2m}^1$.
+In this section we compute the doubling method Gauss sum for a torus of the form $\NormOneGroup{2m}$.
 
-Let $\theta \colon \finiteFieldExtension{2m}^1 \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$.
+Let $\theta \colon \NormOneGroup{2m} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$.
 It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
-Our goal is to compute $$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
+Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
 		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right).$$
@@
 As usual, we rewrite this sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
 If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
-$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
-To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \finiteFieldExtension{2m}^1$ given by $t \mapsto t^{1 - q^m}$.
+$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
+To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \NormOneGroup{2m}$ given by $t \mapsto t^{1 - q^m}$.
 This map is surjective, and its kernel is $\multiplicativegroup{\finiteFieldExtension{m}}$.
 Define $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
-Replacing the sum over $x \in \finiteFieldExtension{2m}^1$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
-	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \finiteFieldExtension{2m}^1} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
+Replacing the sum over $x \in \NormOneGroup{2m}$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
+	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
 	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
@@
 To summarize, we have
-$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
+$$\sum_{\substack{x \in \NormOneGroup{2m}\\
 		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
@@
 Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
-$$\sum_{\substack{x \in \finiteFieldExtension{2m}^1\\
+$$\sum_{\substack{x \in \NormOneGroup{2m}\\
 		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
@@
 
-Using the Hilbert 90 isomorphism $\finiteFieldExtension{2m} \slash \finiteFieldExtension{m} \to \finiteFieldExtension{2m}^{1}$ given by $$x \mapsto \frac{x}{x^{q^m}} = x^{1 - q^m},$$ we see that characters of $\finiteFieldExtension{2m}^1$ are in bijection with characters of $\multiplicativegroup{\finiteFieldExtension{2m}}$ such that their restriction to $\multiplicativegroup{\finiteFieldExtension{m}}$ is trivial.
+Using the Hilbert 90 isomorphism $\finiteFieldExtension{2m} \slash \finiteFieldExtension{m} \to \finiteFieldExtension{2m}^{1}$ given by $$x \mapsto \frac{x}{x^{q^m}} = x^{1 - q^m},$$ we see that characters of $\NormOneGroup{2m}$ are in bijection with characters of $\multiplicativegroup{\finiteFieldExtension{2m}}$ such that their restriction to $\multiplicativegroup{\finiteFieldExtension{m}}$ is trivial.
 Using the surjective norm map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\finiteFieldExtension{m}}$, such characters are precisely characters $\theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ such that $\theta \circ \FieldNorm{2m}{m} = \theta^{1 + q^m} = 1$.
-By realizing the character group $\widehat{\finiteFieldExtension{2m}^1}$ as the subgroup of $\charactergroup{2m}$ given by $$\left\{ \theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex} \mid \theta^{1+q^m} = 1\right\},$$
-we have that $$\ToriDualToriIsomorphism_{2m}\left(\widehat{\finiteFieldExtension{2m}^1}\right) = \left\{\xi \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \xi^{1+q^m} = 1\right\} = \finiteFieldExtension{2m}^1.$$
-Let us denote the restriction of $\ToriDualToriIsomorphism_{2m}$ to $\widehat{\finiteFieldExtension{2m}^1}$ by $\ToriDualToriIsomorphism_{2m}^1 \colon \widehat{\finiteFieldExtension{2m}^1} \to \finiteFieldExtension{2m}^1$.
+By realizing the character group $\widehat{\NormOneGroup{2m}}$ as the subgroup of $\charactergroup{2m}$ given by $$\left\{ \theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex} \mid \theta^{1+q^m} = 1\right\},$$
+we have that $$\ToriDualToriIsomorphism_{2m}\left(\widehat{\NormOneGroup{2m}}\right) = \left\{\xi \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \xi^{1+q^m} = 1\right\} = \NormOneGroup{2m}.$$
+Let us denote the restriction of $\ToriDualToriIsomorphism_{2m}$ to $\widehat{\NormOneGroup{2m}}$ by $\ToriDualToriIsomorphism_{2m}^1 \colon \widehat{\NormOneGroup{2m}} \to \NormOneGroup{2m}$.
 
@@
 
-Suppose that $T \cong \finiteFieldExtension{2m}^1$, and let $t \in T$ be an element such that $t$ is contained only in the torus $T$. Then
+Suppose that $T \cong \NormOneGroup{2m}$, and let $t \in T$ be an element such that $t$ is contained only in the torus $T$. Then
 $$K\left(t\right) = \sum_{\theta} \theta\left(t\right) \innerproduct{K}{\DeligneLusztigInduction{T}{G}\left(\theta\right)},$$

### 2025-03-01 paper.tex
Calvin's text

@@
 
+\subsubsection{Geomtric Conjugacy and Lusztig Series}
+(following chapter 13 of Digne and Michel's Representations of Finite Groups of Lie Type)
+Let $\mathbb{G}$ be a reductive group over $\mathbb{F}$ and fix a torus $\mathbb{T}$ defined over $\mathbb{F}$.
+The \emph{dual group over $\mathbb{F}$} of $\mathbb{G}$ with respect to the torus $\mathbb{T}$ corresponds to the group $\mathbb{G}^*$ with a dual torus $\mathbb{T}^*$ and root datum
+\[
+    (X^*(\mathbb{T}^*),\Phi_{\mathbb{T}^*},X_*(\mathbb{T}^*),\Phi_{\mathbb{T}^*}^\vee) \cong (X_*(\mathbb{T}),\Phi_{\mathbb{T}}^\vee,X^*(\mathbb{T}),\Phi_{\mathbb{T}})
+\]
+such that the isomorphism respects the Frobenius action on $X^*$ and $X_*$.
+
+Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$. 
+We get an isomorphism
+\begin{align*}
+\label{eq:DL}
+0 \to X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to_{F-1} X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to \mathbb{T}(\overline{\mathbb{F}}) \to 0
+\end{align*}
+with the last map being $y \mapsto N_{T(\mathbb{F}^n):T(\mathbb{F})}(y(\zeta_n))$
+for the $\zeta_n=q^n-1$-root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\mathbb{T}$ is split).
+
+Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\mathbb{T}$ to a fixed torus $\mathbb{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $X^*(\mathbb{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+\[
+    exp(\langle x_{T,\theta},y\rangle) = \theta(N_{T(\mathbb{F}^n):T(\mathbb{F})}(y(\zeta_n)))
+\]
+for large enough $n$, where $N_{T(\mathbb{F}^n):T(\mathbb{F})}(t) = t\cdot F(t)\cdot F^2(t)\cdot  \hdots \cdot F^{n-1}(t)$ is the torus norm map.
+This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact there is a correspondence between $(T,\theta)$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Corollary 13.9].
+By composing with \ref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
+
+\begin{definition}
+    Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(T,\theta)$ by $(s_{T,\theta})$.
+Similarly denote the Frobenius stable Weyl group element of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta})$
+    \\
+    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta}), (s_{T,\theta'})$ are equal.\\
+    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
+\end{definition}
+
+\begin{center}
+\begin{tabular}{ c c c c c c}
+ Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
+ $Sp(2n)$ & $(\mathbb{F}^\times)^n$ & 1 & 1 &$SO(2n+1)$ & $(\mathbb{F}^\times)^n$\\  
+ $GSp(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\mathbb{F}^\times)^{n+1}$ \\
+ $SO(2n)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$SO(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
+ $GO(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\
+ $SO(2n+1)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
+ $GO(2n+1)$ & $(\mathbb{F}^\times)^{n+1}$ &1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\ 
+  $U(n)$ & $(\mathbb{F}_2^{Nm=1})^{n}$ & -1 & 1 & $U(n)$ &  $(\mathbb{F}_2^{Nm=1})^{n}$ 
+\end{tabular}
+\end{center}
+
+For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\mathbb{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to  GL_n$.
+Fix a Frobenius stable maximal torus $\mathbb{T}^* \subset G^*$ and a Frobenius stable maximal torus $\mathbb{T} \subset GL_n$ which contains $\rho(\mathbb{T}^*)$.
+Let $\tilde{T}$ be the torus of $GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\mathbb{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$.
+Define
+\[
+    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
+    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(det(t))\psi(tr(t)).
+\]
+\calivn{check $\epsilon$ factors and Hasse-Davenport} The following lemma shows that this is well defined.
+\begin{lemma}
+\label{lemma:gl_invariance}
+\begin{enumerate}[(i)]
+	\item In the case $G = GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
+	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
+\end{enumerate}
+\end{lemma}
+\begin{proof}
+(i) In this case when $T = \Pi_{i} \mathbb{F}^{n_i}$ and $\theta = \Pi_{i} \alpha_i$, we recover the Gauss sum
+\[
+	g_{T,\rho}(\theta,\psi,\chi)  = \varepsilon_{\algebraicGroup{T}} \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi) .
+\]
+By by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
+\\
+(ii) For a Frobenius stable semisimple conjugacy class $(s)$ in $GL_n$ in $GL_n$, we define
+\[
+	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
+\]
+By (i) this is well defined. Then
+\[
+	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
+\]
+which is independent of of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
+\end{proof}
+
+\begin{corollary}
+\label{cor:geoconj}
+Suppose that $(T,\theta)(T',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$.
+\end{corollary}
+\begin{proof}
+Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
+\end{proof}
+
+\subsubsection{Invariance under geometric conjugacy in Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}}
+The main result of this subsection is 
+\begin{theorem}
+\label{thm:indep_geo_conj}
+	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+\end{theorem}
+
+The idea of the proof is that the formula from Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for an appropriate $\rho$.
+We will need the following computation:
+\begin{lemma}
+\label{lem:cochar_computation}
+    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
+We will consider two different Frobeinus actions on these characters:
+    \begin{enumerate}
+        \item When $F$ acts by trivially on both, $x_{\mathbb{F}_n^\times \times \mathbb{F}_n^\times,\alpha \times \alpha^{-1}} = \phi(x_{\mathbb{F}_n,\alpha})$
+        \item When $F$ acts by $-1$ on the domain and by $\begin{pmatrix}
+            0 & 1 \\
+            1 & 0\end{pmatrix}$ on the codomain, $x_{\mathbb{F}_{2n}^\times,\theta'}=\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
+    \end{enumerate}
+\end{lemma}
+\begin{proof}
+Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
+\[
+    exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\mathbb{F}_m):T(\mathbb{F})}(y(\zeta_m))).
+\]
+Thus the result follows from the computations:\\
+(i)
+\begin{align*}
+    exp(\langle\phi(x_{\mathbb{F}_n,\alpha}),(y_1,y_2)\rangle) &= exp(\langle x_{\mathbb{F}_n,\alpha},\phi^*(y_1,y_2)\rangle) \\
+    &= \alpha\left(Nm_{mn:n}(y_1(\zeta_{mn})\right) \alpha\left(Nm_{mn:n}(y_2(\zeta_{mn})\right)^{-1} \\
+    &= \left(\alpha\times\alpha^{-1}\right)\left(Nm_{mn:n}((y_1,y_2)(\zeta_{mn}))\right)
+\end{align*}
+(ii)
+\begin{align*}
+    exp(\langle\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta}),(y_1,y_2)\rangle) &= exp(\langle x_{(\mathbb{F}_{2n})^{Nm=1},\theta},\phi^*(y_1,y_2)\rangle) \\
+    &= \theta\left(\frac{Nm_{2mn:2n}(y_1(\zeta_{2mn})}{Nm_{2mn:2n}(y_1(\zeta_{2mn})^{q^n}}\right) \theta\left(\frac{Nm_{2mn:2n}(y_2(\zeta_{2mn})}{Nm_{2mn:2n}(y_2(\zeta_{2mn})^{q^n}}\right)^{-1} \\
+    &= \theta'\left(Nm_{2mn:2n}((y_1,y_2)(\zeta_{mn}))\right)
+\end{align*}
+\end{proof}
+
+Now we fix representations $\rho$ of the dual groups:
+\begin{center}
+\begin{tabular}{ c c}
+ Group & Dual group representations $\rho$ \\ 
+ $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
+ $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
+ $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
+ $GO(2n)$ & ? \\
+ $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
+ $GO(2n+1)$ & ? \\ 
+  $U(n)$  & $U(n) \to GL(2n)$  
+\end{tabular}
+\end{center}
+Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
+In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
+In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
+In all these cases we can apply lemma \ref{lem:cochar_computation}:
+
+\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] Let $T$ be a torus in $G$ and suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
+We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\mathbb{T}^*$ in $G^*$ including into the split torus $\mathbb{T}'$ in $GL$ in the non unitary case and in the unitary case we use the tori $\mathbb{T}^*$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus $\mathbb{T}'$ in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$.
+We then define $\tilde{T}$ as the $\mathbb{F}$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\mathbb{T}')$ where $(w)$ inside $W(\mathbb{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
+Lemma \ref{lem:cochar_computation} above implies that
+\[
+g_{T,\rho}(\theta,\psi,\chi)= \varepsilon_{\algebraicGroup{T}}\varepsilon_{\algebraicGroup{\tilde{T}}}g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
+        1  & G \neq Sp, GSp\\
+        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
+    \end{cases}
+\]
+where $g_T(\theta,\psi,\chi)$ is the expression from theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
+\calvin{how does $\epsilon$ depend on $w$?
+Is the product always one?}.
+Corollary \ref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.
+Now the formula for $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}$ in theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} finishes the proof.
+\begin{comment}
+We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
+
+Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ with $k_1 \geq k_2 \hdots \geq k_r$ and $m_1 \geq m_2 \hdots \geq m_r$ and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
+Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by $((k_1,k_2, \hdots, k_r), (m_1,m_2 \hdots m_s))$.
+The map $\rho$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
+Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
+Then by theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
+\[
+    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = \begin{cases}
+        g_T(\theta,\psi)  & G \neq Sp \textnormal{ or } GSp\\
+        g_T(\theta,\psi) \cdot g(1,\psi_1) & G = Sp \textnormal{ or } GSp
+    \end{cases}.
+\]
+Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$. \\
+Now for the unitary case: \calvin{this needs to be checked... I used engineers induction to guess at how the Weyl group conjugacy classes match the torus}
+Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s (\finiteFieldExtension{2m_i}^1)^2$ with $k_i$'s even and $m_i$'s odd \calvin{this is what I need to check...
+what tori you can get here} and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
+Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by having even cycles of lengths $k_1,k_2 \hdots k_r$ and odd cycles of lengths $m_1,m_1,m_2,m_2, \hdots, m_s,m_s$.
+The map $\Phi$ sends this conjugacy class to the conjugacy class with even cycles $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and odd cycles $m_1,m_1,m_1,m_1,m_2,m_2,m_2,m_2, \hdots, m_s,m_s,m_s,m_s$.
+Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class with all even cycles of lengths $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and $2m_1,2m_1,2m_2,2m_2, \hdots, 2m_s,2m_s$.
+Then $\Phi(s)$ is in this torus \calvin{write out what that means} giving a character $\tilde{\theta}$ on it and
+\[
+    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = g_T(\theta,\psi).
+\]
+Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
+\end{comment}
+\end{proof}
+
 \subsection{Computation for Lusztig series}

### 2025-03-03 paper.tex
Typo
Calvin stuff

@@
 If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter_{\finiteField} \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
 If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
@@
 
+\subsubsection{Invariance under geometric conjugacy}
+\calvin{todo:type in some motivation for class functions whose product doesn't depend on geometric conjugacy, gamma functions whatever}.
+
+\begin{definition}
+	A \emph{stable function} on $G(\mathbb{F})$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
+\calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
+COMPLEXES has this definition}
+\end{definition}
+
+A basic example of a class function which doesn't depend of geometric conjugacy 
+\begin{proposition}[FIND SOMEWHERE TO CITE or put in appendix]
+\label{prop:central_char}
+    Any function supported on the center of $G(\mathbb{F})$ is a stable function. \calvin{maybe add in connected group} 
+\end{proposition}
+\begin{proof}
+\calvin{todo.
+Here is a sketch.
+Use the definition of RTtheta to show for all torus theta pairs $(T,\theta)$, central element $x$ acts by scalar (in fact the scalar $\theta(x)$).
+This can also be showed using the character formula plus the ``only one cuspidal'' trick but it is probably overkill.
+Then if two pairs are conjugate, their hom dimesnion is nonzero, hence $x$ the scalar in both RTThetas}
+\end{proof}
+
+The main result of this subsection is 
+\begin{theorem}
+\label{thm:indep_geo_conj}
+	$\Phi_{\chi}(g)$ is a stable function.
+	%Equivalently	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+\end{theorem}
+
+In the $GL_n$ case this follows from theorem \ref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
+
 For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\mathbb{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to  GL_n$.
@@
 \]
-\calivn{check $\epsilon$ factors and Hasse-Davenport} The following lemma shows that this is well defined.
+The following lemma shows that this is well defined.
+
 \begin{lemma}
@@
 \[
-	g_{T,\rho}(\theta,\psi,\chi)  = \varepsilon_{\algebraicGroup{T}} \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi) .
+	g_{T,\rho}(\theta,\psi,\chi)  = \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi).
 \]
-By by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
+By the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
 \\
@@
 
-\subsubsection{Invariance under geometric conjugacy in Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}}
-The main result of this subsection is 
-\begin{theorem}
-\label{thm:indep_geo_conj}
-	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
-\end{theorem}
+The idea behind the proof of this theorem \ref{thm:indep_geo_conj} is that the formula from Theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
+\begin{center}
+\begin{tabular}{ c c}
+ Group & Dual group representations $\rho$ \\ 
+ $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
+ $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
+ $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
+ $GO(2n)$ & ? \\
+ $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
+ $GO(2n+1)$ & ? \\ 
+  $U(n)$  & $U(n) \to GL(2n)$  
+\end{tabular}
+\end{center}
+Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
+In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
+In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
 
-The idea of the proof is that the formula from Theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for an appropriate $\rho$.
-We will need the following computation:
+In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
+%The following computation in the proof of theorem \ref{thm:indep_geo_conj}.
+
 \begin{lemma}
@@
 
-Now we fix representations $\rho$ of the dual groups:
-\begin{center}
-\begin{tabular}{ c c}
- Group & Dual group representations $\rho$ \\ 
- $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
- $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
- $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
- $GO(2n)$ & ? \\
- $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
- $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to GL(2n)$  
-\end{tabular}
-\end{center}
-Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
-In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
-In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
-In all these cases we can apply lemma \ref{lem:cochar_computation}:
+\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] 
+By theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, it is enough to show that $g_{T}(\chi,\theta,\psi)$ and $\omega_{\pi}(-1) = \theta(-1)$ only depend of the geometric conjugacy of $(T,\theta)$.
+The latter only depends on geometric conjugacy by proposition \ref{prop:central_char}.\\
 
-\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] Let $T$ be a torus in $G$ and suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
+Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
 We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\mathbb{T}^*$ in $G^*$ including into the split torus $\mathbb{T}'$ in $GL$ in the non unitary case and in the unitary case we use the tori $\mathbb{T}^*$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus $\mathbb{T}'$ in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$.
@@
 \[
-g_{T,\rho}(\theta,\psi,\chi)= \varepsilon_{\algebraicGroup{T}}\varepsilon_{\algebraicGroup{\tilde{T}}}g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
+g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
         1  & G \neq Sp, GSp\\
         \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
-    \end{cases}
+    \end{cases}.
 \]
-where $g_T(\theta,\psi,\chi)$ is the expression from theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
-\calvin{how does $\epsilon$ depend on $w$?
-Is the product always one?}.
 Corollary \ref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$. 
-Now the formula for $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}$ in theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} finishes the proof.
 \begin{comment}

### 2025-03-03 paper.tex
Adding notations

@@
 Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter_{\finiteField} \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+Fix an algebraic closure $\algebraicClosure{\finiteField}$ of $\finiteField$.
+For any $k \ge 1$, let $\finiteFieldExtension{k} \slash \finiteField$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
 
@@
 
-Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$.
+Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$ contained in $\algebraicClosure{\finiteField}$.
+For any $k \ge 1$, let $\quadraticFieldExtension{k} \slash \quadraticExtension$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
 Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.

### 2025-03-03 paper.tex
Using LaTeX macros

@@
 
-\subsubsection{Geomtric Conjugacy and Lusztig Series}
-(following chapter 13 of Digne and Michel's Representations of Finite Groups of Lie Type)
-Let $\mathbb{G}$ be a reductive group over $\mathbb{F}$ and fix a torus $\mathbb{T}$ defined over $\mathbb{F}$.
-The \emph{dual group over $\mathbb{F}$} of $\mathbb{G}$ with respect to the torus $\mathbb{T}$ corresponds to the group $\mathbb{G}^*$ with a dual torus $\mathbb{T}^*$ and root datum
+\subsubsection{Geometric Conjugacy and Lusztig Series}
+(Following chapter 13 of \cite{DigneMichel2020})
+Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a torus $\algebraicGroup{T}$ defined over $\finiteField$.
+The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
 \[
-    (X^*(\mathbb{T}^*),\Phi_{\mathbb{T}^*},X_*(\mathbb{T}^*),\Phi_{\mathbb{T}^*}^\vee) \cong (X_*(\mathbb{T}),\Phi_{\mathbb{T}}^\vee,X^*(\mathbb{T}),\Phi_{\mathbb{T}})
+    (X^*(\algebraicGroup{T}^*),\Phi_{\algebraicGroup{T}^*},X_*(\algebraicGroup{T}^*),\Phi_{\algebraicGroup{T}^*}^\vee) \cong (X_*(\algebraicGroup{T}),\Phi_{\algebraicGroup{T}}^\vee,X^*(\algebraicGroup{T}),\Phi_{\algebraicGroup{T}})
 \]
@@
 
-Fix an isomorphism $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$. 
+Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
 We get an isomorphism
-\begin{align*}
+\begin{equation}
 \label{eq:DL}
-0 \to X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to_{F-1} X_*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \to \mathbb{T}(\overline{\mathbb{F}}) \to 0
-\end{align*}
-with the last map being $y \mapsto N_{T(\mathbb{F}^n):T(\mathbb{F})}(y(\zeta_n))$
-for the $\zeta_n=q^n-1$-root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\mathbb{T}$ is split).
+\xymatrix{0 \ar[r] & X_*(\algebraicGroup{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & X_*(\algebraicGroup{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T}(\algebraicClosure{\finiteField}) \ar[r] & 0}
+\end{equation}
+with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(y(\zeta_n))$
+for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
 
-Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\mathbb{T}$ to a fixed torus $\mathbb{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $X^*(\mathbb{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
 \[
-    exp(\langle x_{T,\theta},y\rangle) = \theta(N_{T(\mathbb{F}^n):T(\mathbb{F})}(y(\zeta_n)))
+    \exp(\langle x_{T,\theta},y\rangle) = \theta(\aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(y(\zeta_n)))
 \]
-for large enough $n$, where $N_{T(\mathbb{F}^n):T(\mathbb{F})}(t) = t\cdot F(t)\cdot F^2(t)\cdot  \hdots \cdot F^{n-1}(t)$ is the torus norm map.
-This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact there is a correspondence between $(T,\theta)$ pairs and $F$-stable Weyl group orbits in $X^*(\mathbb{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ [Corollary 13.9].
-By composing with \ref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
+for large enough $n$, where $\aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$ is the torus norm map.
+This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ \cite[Corollary 13.9]{DigneMichel2020}.
+By composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
 
@@
     Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(T,\theta)$ by $(s_{T,\theta})$.
-Similarly denote the Frobenius stable Weyl group element of $X^*(\mathbb{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta})$
-    \\
-    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta}), (s_{T,\theta'})$ are equal.\\
-    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \mathbb{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with nonzero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
+Similarly denote the Frobenius stable Weyl group element of $X^*(\algebraicGroup{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta}).$
+
+    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta}), (s_{T,\theta'})$ are equal.
+
+    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
 \end{definition}
@@
  Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
- $Sp(2n)$ & $(\mathbb{F}^\times)^n$ & 1 & 1 &$SO(2n+1)$ & $(\mathbb{F}^\times)^n$\\  
- $GSp(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\mathbb{F}^\times)^{n+1}$ \\
- $SO(2n)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$SO(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
- $GO(2n)$ & $(\mathbb{F}^\times)^{n+1}$ & 1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\
- $SO(2n+1)$ & $(\mathbb{F}^\times)^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\mathbb{F}^\times)^{n}$ \\
- $GO(2n+1)$ & $(\mathbb{F}^\times)^{n+1}$ &1 & 1 &? &  $(\mathbb{F}^\times)^{n+1}$ \\ 
-  $U(n)$ & $(\mathbb{F}_2^{Nm=1})^{n}$ & -1 & 1 & $U(n)$ &  $(\mathbb{F}_2^{Nm=1})^{n}$ 
+ $Sp(2n)$ & $(\multiplicativegroup{\finiteField})^n$ & 1 & 1 &$SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^n$\\  
+ $GSp(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
+ $SO(2n)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$SO(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
+ $GO(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
+ $SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
+ $GO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ 
+  $U(n)$ & $(\NormOneGroup{\finiteFieldExtension{2}})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{\finiteFieldExtension{2}})^{n}$ 
 \end{tabular}
@@
 \begin{definition}
-	A \emph{stable function} on $G(\mathbb{F})$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
+	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
 \calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
@@
 \label{prop:central_char}
-    Any function supported on the center of $G(\mathbb{F})$ is a stable function. \calvin{maybe add in connected group} 
+    Any function supported on the center of $\algebraicGroup{G}(\finiteField)$ is a stable function. \calvin{maybe add in connected group} 
 \end{proposition}
@@
 
-In the $GL_n$ case this follows from theorem \ref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
+In the $\GL_n$ case this follows from \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
 
-For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\mathbb{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to  GL_n$.
-Fix a Frobenius stable maximal torus $\mathbb{T}^* \subset G^*$ and a Frobenius stable maximal torus $\mathbb{T} \subset GL_n$ which contains $\rho(\mathbb{T}^*)$.
-Let $\tilde{T}$ be the torus of $GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\mathbb{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$.
+For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to \GL_n$.
+Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset G^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \GL_n$ which contains $\rho(\algebraicGroup{T}^*)$.
+Let $\tilde{T}$ be the torus of $\GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$.
 Define
@@
     g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
-    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(det(t))\psi(tr(t)).
+    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
 \]
@@
 \begin{enumerate}[(i)]
-	\item In the case $G = GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
-	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
+	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
+	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
 \end{enumerate}
@@
 \begin{proof}
-(i) In this case when $T = \Pi_{i} \mathbb{F}^{n_i}$ and $\theta = \Pi_{i} \alpha_i$, we recover the Gauss sum
+\begin{enumerate}[(i)]
+	\item In this case when $T = \prod_{i} \finiteFieldExtension{n_i}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
 	\[
-	g_{T,\rho}(\theta,\psi,\chi)  = \Pi_i \tau(\alpha_i \times (\chi\circ Nm),\psi).
+	g_{T,\rho}(\theta,\psi,\chi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
 	\]
-By the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
-\\
-(ii) For a Frobenius stable semisimple conjugacy class $(s)$ in $GL_n$ in $GL_n$, we define
+	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
+	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
 	\[
@@
 	\]
-By (i) this is well defined. Then
+	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
 	\[
@@
 	\]
-which is independent of of choice of $\mathbb{T}^* \subset G^*$ and $\mathbb{T} \subset GL_n$.
+	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
+\end{enumerate}
 \end{proof}
@@
 \label{cor:geoconj}
-Suppose that $(T,\theta)(T',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$.
+Suppose that $(T,\theta)$ and $(T',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$.
 \end{corollary}
@@
 
-The idea behind the proof of this theorem \ref{thm:indep_geo_conj} is that the formula from Theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
+The idea behind the proof of \Cref{thm:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
 \begin{center}
@@
  Group & Dual group representations $\rho$ \\ 
- $Sp(2n)$ &$SO(2n+1) \to GL(2n+1)$\\  
- $GSp(2n)$  &$GSpin(2n+1) \to GL(2n+1)$ \\
- $SO(2n)$ &$SO(2n) \to GL(2n)$ \\
+ $Sp(2n)$ &$SO(2n+1) \to \GL(2n+1)$\\  
+ $GSp(2n)$  &$GSpin(2n+1) \to \GL(2n+1)$ \\
+ $SO(2n)$ &$SO(2n) \to \GL(2n)$ \\
  $GO(2n)$ & ? \\
- $SO(2n+1)$ &$Sp(2n) \to GL(2n)$ \\
+ $SO(2n+1)$ &$Sp(2n) \to \GL(2n)$ \\
  $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to GL(2n)$  
+  $U(n)$  & $U(n) \to \GL(2n)$  
 \end{tabular}
 \end{center}
-Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
+Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
 In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
-In the unitary case, the torus whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
+In the unitary case, the torus whose $\finiteField$ points are $(\NormOneGroup{\finiteFieldExtension{2}})^n \subset G^*(\finiteField)$ includes into the torus in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
 
-In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
+In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
 %The following computation in the proof of theorem \ref{thm:indep_geo_conj}.
@@
 \label{lem:cochar_computation}
-    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
+    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
 We will consider two different Frobeinus actions on these characters:
     \begin{enumerate}
-        \item When $F$ acts by trivially on both, $x_{\mathbb{F}_n^\times \times \mathbb{F}_n^\times,\alpha \times \alpha^{-1}} = \phi(x_{\mathbb{F}_n,\alpha})$
-        \item When $F$ acts by $-1$ on the domain and by $\begin{pmatrix}
+        \item When $\Frobenius$ acts by trivially on both, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
+        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
             0 & 1 \\
-            1 & 0\end{pmatrix}$ on the codomain, $x_{\mathbb{F}_{2n}^\times,\theta'}=\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
+            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{\finiteFieldExtension{2n}},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
     \end{enumerate}
@@
 \begin{proof}
-Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\overline{\mathbb{F}}^\times \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
+Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
 \[
-    exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\mathbb{F}_m):T(\mathbb{F})}(y(\zeta_m))).
+    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
 \]
-Thus the result follows from the computations:\\
-(i)
-\begin{align*}
-    exp(\langle\phi(x_{\mathbb{F}_n,\alpha}),(y_1,y_2)\rangle) &= exp(\langle x_{\mathbb{F}_n,\alpha},\phi^*(y_1,y_2)\rangle) \\
-    &= \alpha\left(Nm_{mn:n}(y_1(\zeta_{mn})\right) \alpha\left(Nm_{mn:n}(y_2(\zeta_{mn})\right)^{-1} \\
-    &= \left(\alpha\times\alpha^{-1}\right)\left(Nm_{mn:n}((y_1,y_2)(\zeta_{mn}))\right)
+Thus the result follows from the computations:
+\begin{enumerate}
+	\item \begin{align*}
+		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
+		&= \alpha\left(\FieldNorm{mn}{n}(y_1(\zeta_{mn})\right) \alpha\left(\FieldNorm{mn}{n}(y_2(\zeta_{mn})\right)^{-1} \\
+		&= \left(\alpha\times\alpha^{-1}\right)\left(\FieldNorm{mn}{n}((y_1,y_2)(\zeta_{mn}))\right)
 	\end{align*}
-(ii)
-\begin{align*}
-    exp(\langle\phi(x_{(\mathbb{F}_{2n})^{Nm=1},\theta}),(y_1,y_2)\rangle) &= exp(\langle x_{(\mathbb{F}_{2n})^{Nm=1},\theta},\phi^*(y_1,y_2)\rangle) \\
-    &= \theta\left(\frac{Nm_{2mn:2n}(y_1(\zeta_{2mn})}{Nm_{2mn:2n}(y_1(\zeta_{2mn})^{q^n}}\right) \theta\left(\frac{Nm_{2mn:2n}(y_2(\zeta_{2mn})}{Nm_{2mn:2n}(y_2(\zeta_{2mn})^{q^n}}\right)^{-1} \\
-    &= \theta'\left(Nm_{2mn:2n}((y_1,y_2)(\zeta_{mn}))\right)
+	\item \begin{align*}
+		\exp(\langle\phi(x_{\NormOneGroup{\finiteFieldExtension{2n}},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{\finiteFieldExtension{2n}},\theta},\phi^*(y_1,y_2)\rangle) \\
+		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
+		&= \theta'\left(\FieldNorm{2mn}{2n}((y_1,y_2)(\zeta_{mn}))\right)
 	\end{align*}
+\end{enumerate}
 \end{proof}
 
-\begin{proof}[Proof of theorem \ref{thm:indep_geo_conj}] 
-By theorem \ref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, it is enough to show that $g_{T}(\chi,\theta,\psi)$ and $\omega_{\pi}(-1) = \theta(-1)$ only depend of the geometric conjugacy of $(T,\theta)$.
-The latter only depends on geometric conjugacy by proposition \ref{prop:central_char}.\\
+\begin{proof}[Proof of \Cref{thm:indep_geo_conj}] 
+By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, it is enough to show that $g_{T}(\chi,\theta,\psi)$ and $\omega_{\pi}(-1) = \theta(-1)$ only depend of the geometric conjugacy of $(T,\theta)$.
+The latter only depends on geometric conjugacy by \Cref{prop:central_char}.
 
 Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
-We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\mathbb{T}^*$ in $G^*$ including into the split torus $\mathbb{T}'$ in $GL$ in the non unitary case and in the unitary case we use the tori $\mathbb{T}^*$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^{Nm=1})^n \subset G^*(\mathbb{F})$ includes into the torus $\mathbb{T}'$ in $GL(2n)$ whose $\mathbb{F}$ points are $(\mathbb{F}_2^\times)^n$.
-We then define $\tilde{T}$ as the $\mathbb{F}$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\mathbb{T}')$ where $(w)$ inside $W(\mathbb{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
-Lemma \ref{lem:cochar_computation} above implies that
+We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{\finiteFieldExtension{2}})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$.
+We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
+\Cref{lem:cochar_computation} above implies that
 \[
@@
 \]
-Corollary \ref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$. 
+\Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
 \begin{comment}
@@
 The map $\rho$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
-Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
+Let $\tilde{T}$ be the torus in $\GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
 Then by theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
@@
 \]
-Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$. \\
+Since the sum above is a Gauss sum for $\GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$. \\
 Now for the unitary case: \calvin{this needs to be checked... I used engineers induction to guess at how the Weyl group conjugacy classes match the torus}
@@
 The map $\Phi$ sends this conjugacy class to the conjugacy class with even cycles $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and odd cycles $m_1,m_1,m_1,m_1,m_2,m_2,m_2,m_2, \hdots, m_s,m_s,m_s,m_s$.
-Let $\tilde{T}$ be the torus in $GL$ corresponding to the conjugacy class with all even cycles of lengths $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and $2m_1,2m_1,2m_2,2m_2, \hdots, 2m_s,2m_s$.
+Let $\tilde{T}$ be the torus in $\GL$ corresponding to the conjugacy class with all even cycles of lengths $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and $2m_1,2m_1,2m_2,2m_2, \hdots, 2m_s,2m_s$.
 Then $\Phi(s)$ is in this torus \calvin{write out what that means} giving a character $\tilde{\theta}$ on it and
@@
 \]
-Since the sum above is a Gauss sum for $GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
+Since the sum above is a Gauss sum for $\GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
 \end{comment}

### 2025-03-03 paper.tex
Some corrections

@@
 \subsubsection{Geometric Conjugacy and Lusztig Series}
-(Following chapter 13 of \cite{DigneMichel2020})
+(Following Chapter 13 of \cite{DigneMichel2020})
 Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a torus $\algebraicGroup{T}$ defined over $\finiteField$.
@@
 \begin{proof}
+The representation $R_T^G(\theta)$ is equal to $M \otimes_{}$
 \calvin{todo.
@@
 \begin{enumerate}[(i)]
-	\item In this case when $T = \prod_{i} \finiteFieldExtension{n_i}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
+	\item In this case when $T = \prod_{i} \multiplicativegroup{\finiteFieldExtension{n_i}}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
 	\[

### 2025-03-03 paper.tex
Calvin update

@@
 \label{prop:central_char}
-    Any function supported on the center of $\algebraicGroup{G}(\finiteField)$ is a stable function. \calvin{maybe add in connected group} 
+    Any function supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$ is a stable function. \calvin{maybe add in connected group} 
 \end{proposition}
 \begin{proof}
-The representation $R_T^G(\theta)$ is equal to $M \otimes_{}$
+\calvin{can probably delete this first part or put in appendix}
+The representation $R_T^G(\theta)$ is equal to $M \otimes_{\mathbb{C}[T]} \theta$ where $M$ is the virtual module corresponding to the Euler characteristic of cohomology on $X$ which as a variety is a subvariety of $\algebraicGroup{G}$ with the $G \times T$ action via $(g,\ell).x = gx\ell$.
+The center $\algebraicGroup{Z}$ then commutes across $X$ so the action of $(z,1)$ equals the action of $(1,z)$.
+The result is on the $\theta$ component of $M$, $z$ acts by $\theta(z)$.\\
+
 \calvin{todo.

### 2025-03-03 paper.tex
Writing about the different cases

@@
 \newcommand{\GL}{\mathrm{GL}}
+\newcommand{\SO}{\mathrm{SO}}
+\newcommand{\GSO}{\mathrm{GSO}}
+\newcommand{\Sp}{\mathrm{Sp}}
+\newcommand{\GSp}{\mathrm{GSp}}
+\newcommand{\UnitaryGroup}{\mathrm{U}}
 \newcommand{\UnipotentSubgroup}{U}
@@
 We denote by $G$ the identity component of $\IsometryGroup\left(\hermitianSpace\right)$.
-Let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+If $\quadraticExtension = \finiteField$, let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
 Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
-If $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace = 2n$ is even, then $\GroupExtension{G}$ consists of all elements in $\GroupExtension{\IsometryGroup\left(G\right)}$ satisfying $\similitudeCharacter\left(g\right) = \left(\det g\right)^n$.
-Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
+If $\quadraticExtension \ne \finiteField$, let $\GroupExtension{G} = G$.
 
 We will assume that $\dim_{\finiteField} \hermitianSpace$ is even.
-This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$, in which case we will only consider even special orthogonal groups.
+This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$.
+The group $\GroupExtension{G}$ has connected center and contains $G$.
+
+Let us summarize all possible cases for $G$ and $\GroupExtension{G}$. Let $$w_n = \begin{pmatrix}
+	& & & 1\\
+	& & 1\\
+	& \iddots\\
+	1
+\end{pmatrix} \in \GL_n\left(\finiteField\right)$$ be the longest Weyl element.
+\begin{enumerate}
+	\item (Even special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon = 1$.
+Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
+In this case, we have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
+There are two cases here.
+	\begin{enumerate}
+		\item Split case: in this case, we can write $\hermitianSpace = \xIsotropic \oplus \yIsotropic$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
+In this case, we have that $G$ is isomorphic to the subgroup $\SO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of elements $g$ satisfying $$g \cdot w_{2n} \cdot \transpose{g} = w_{2n}$$ and $\det g = 1$.
+		The group $\tilde{G}$ is isomorphic to the subgroup $\GSO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that $$g \cdot w_{2n} \cdot \transpose{g} = \similitudeCharacter\left(g\right) w_{2n},$$
+		and such that $\det g = \similitudeCharacter\left(g\right)^n$, where $\similitudeCharacter\left(g\right)$ is a non-zero scalar.
+		\item Non-split case:
+	\end{enumerate}
+	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon = -1$.
+In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to subgroup $\Sp_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of all elements $g$ satisfying $$g \cdot \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix} \cdot \transpose{g} = \begin{pmatrix}
+	& w_n\\
+	-w_n
+	\end{pmatrix}.$$ The group $\GroupExtension{G}$ is is isomorphic to the subgroup $\GSp_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of all elements $g$ such that $$g \cdot \begin{pmatrix}
+	& w_n\\
+	-w_n
+	\end{pmatrix} \cdot \transpose{g} = \similitudeCharacter\left(g\right) \begin{pmatrix}
+	& w_n\\
+	-w_n
+	\end{pmatrix},$$
+	where $\similitudeCharacter\left(g\right)$ is a non-zero scalar.
+	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
+Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
+In this case, the group $G = \GroupExtension{G}$ is isomorphic to the subgroup $\UnitaryGroup_n\left(\finiteField\right)$ of $\GL_{n}\left(\quadraticExtension\right)$ consisting of all elements $g$ such that $$g \cdot w_n \cdot \involution{\left(\transpose{g}\right)} = w_n.$$
+\end{enumerate}
+
+Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
 
@@
 
-Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$ if $\quadraticExtension = \finiteField$ and $H = G$ if $\quadraticExtension \ne \finiteField$.
+Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
 Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$

### 2025-03-03 paper.tex
Calvin changes

@@
 \label{prop:central_char}
-    Any function supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$ is a stable function. \calvin{maybe add in connected group} 
+    Any function $f$ supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$ is a stable function. 
 \end{proposition}
 \begin{proof}
-\calvin{can probably delete this first part or put in appendix}
-The representation $R_T^G(\theta)$ is equal to $M \otimes_{\mathbb{C}[T]} \theta$ where $M$ is the virtual module corresponding to the Euler characteristic of cohomology on $X$ which as a variety is a subvariety of $\algebraicGroup{G}$ with the $G \times T$ action via $(g,\ell).x = gx\ell$.
+\calvin{can probably put this proof in an appendix}
+Note it is enough to prove the statement for $f = 1_z$ an indicator function of an element $z \in \algebraicGroup{Z}(\mathbb{F})$. The he proof follows from the two claims:\\
+Claim 1: $z$ acts by the scalar $\theta(z)$ in the virtual representation $R_{T,\theta}$.\\
+Claim 2: If $(T,\theta),(T',\theta')$ are geometrically conjugate then $\theta|_{\algebraicGroup{Z}(\mathbb{F})} = \theta'_{\algebraicGroup{Z}(\mathbb{F})}$.\\
+Proof of claim 1: The representation $R_T^G(\theta)$ is equal to $M \otimes_{\mathbb{C}[T]} \theta$ where $M$ is the virtual module corresponding to the Euler characteristic of cohomology on $X$ which as a variety is a subvariety of $\algebraicGroup{G}$ with the $G \times T$ action via $(g,\ell).x = gx\ell$.
 The center $\algebraicGroup{Z}$ then commutes across $X$ so the action of $(z,1)$ equals the action of $(1,z)$.
 The result is on the $\theta$ component of $M$, $z$ acts by $\theta(z)$.\\
-
-\calvin{todo.
-Here is a sketch.
-Use the definition of RTtheta to show for all torus theta pairs $(T,\theta)$, central element $x$ acts by scalar (in fact the scalar $\theta(x)$).
-This can also be showed using the character formula plus the ``only one cuspidal'' trick but it is probably overkill.
-Then if two pairs are conjugate, their hom dimesnion is nonzero, hence $x$ the scalar in both RTThetas}
+Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}^n)$ such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
+So when restricted to the center, $\theta \circ Nm = \theta' \circ Nm$.
+Since $Nm$ is surjective onto the $\mathbb{F}$-points, $\theta|_{\algebraicGroup{Z}(\mathbb{F})} = \theta'|_{\algebraicGroup{Z}(\mathbb{F})}$.
 \end{proof}

### 2025-03-03 paper.tex
TODO list

@@
 \maketitle
+
+\subsection{TODO list}
+
+\begin{enumerate}
+	\item (Minor) Change terminology of Gauss sums $\dblGaussSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums
+	$$J\left(\alpha, \beta\right) = \sum_{\substack{x,y \in \multiplicativegroup{\finiteField}\\
+	x+y = 1}} \alpha\left(x\right) \beta\left(y\right),$$
+	compare with $$\dblGaussSumScalar{\pi}{\chi} = \sum_{\substack{g \in G\\
+			h \in \GL\left(\hermitianSpace\right)\\
+	g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det\left(-h\right)\right).$$
+	Consider replacing $\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right)$ with $\chi\left(\det\left(\idmap_{\hermitianSpace} - g\right)\right)$ for aesthetics (probably not worth it).
+	\item Maybe define the algebraic group versions $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$ in Section 3.2. For instance for $\algebraicGroup{\Sp}_{2n}$ we can define
+	$$\algebraicGroup{\tilde{G}} = \left\{ \left(g,\lambda\right) \in \algebraicGroup{\GL}\left(\hermitianSpace\right) \times \multiplcativeScheme \mid \involution{\transpose{g}} J g = \lambda J,\ \right\}$$ for suitable $J$ and then define the torus $\algebraicGroup{S}$ that appears in \cite[Page 140]{DigneMichel2020} as $$\algebraicGroup{S} = \left\{\left(\begin{pmatrix}
+		t \IdentityMatrix{n}\\
+		& \IdentityMatrix{n}
+	\end{pmatrix}, t\right) \mid t \in \multiplcativeScheme \right\} \subset \GroupExtension{\algebraicGroup{G}}.$$
+	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
+	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified.
+We should first use $\GroupExtension{G}$.
+For this group we have the ``at most one cuspidal'' property.
+Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
+	where we need to explain the notation.
+	\item \Cref{subsec:tori-isomorphism} should be removed and replaced with Calvin's arguments.
+\end{enumerate}
 
@@
 The result is on the $\theta$ component of $M$, $z$ acts by $\theta(z)$.\\
-Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}^n)$ such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
+Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}^n)$ \elad{Here you mean $\algebraicGroup{G}\left(\finiteFieldExtension{n}\right)$?} such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
 So when restricted to the center, $\theta \circ Nm = \theta' \circ Nm$.
@@
 
-\subsubsection{Tori isomorphism}
+\subsubsection{Tori isomorphism}\label{subsec:tori-isomorphism}
 
@@
 Our theorem is equivalent to the following statement.
-\begin{proposition}
+\begin{proposition}\label{prop:gamma-factor-is-constant-on-lusztig-series}
 	Keep the notations as above.

### 2025-03-03 paper.tex
Two sections should be removed

@@
 	where we need to explain the notation.
-	\item \Cref{subsec:tori-isomorphism} should be removed and replaced with Calvin's arguments.
+	\item \Cref{subsec:tori-isomorphism} and \Cref{subsec:gauss-sums-attached-to-semi-simple} should be removed and replaced with Calvin's arguments.
 \end{enumerate}
@@
 
-\subsubsection{Gauss sums attached to semisimple elements}
+\subsubsection{Gauss sums attached to semisimple elements}\label{subsec:gauss-sums-attached-to-semi-simple}
 

### 2025-03-03 paper.tex
Overleaf update

@@
 \subsection{TODO list}
-
+\calvin{I mentioned this to Charlotte and will meet with her sometime after Arizona to discuss specifically the DL stuff to make sure that it ok. So we could try to have a draft }
 \begin{enumerate}
@@
 \begin{lemma}\label{lem:sum-vanishes-for-singular-matrices}
-	For any singular matrix $X \in \squareMatrix_n\left(\finiteField\right)$ and any $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the sum
+	For any singular matrix $X \in \squareMatrix_n\left(\finiteField\right)$ and any $1 \ne \chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the sum
 	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter_{\finiteField}\left(\trace\left(Xh\right)\right)$$
@@
 The result is on the $\theta$ component of $M$, $z$ acts by $\theta(z)$.\\
-Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}^n)$ \elad{Here you mean $\algebraicGroup{G}\left(\finiteFieldExtension{n}\right)$?} such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
+Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}_n)$ \elad{Here you mean $\algebraicGroup{G}\left(\finiteFieldExtension{n}\right)$?}\calvin{oops yes} such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
 So when restricted to the center, $\theta \circ Nm = \theta' \circ Nm$.

### 2025-03-04 paper.tex
Explaining notation

@@
 As usual, we rewrite this sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right),$$
+where $\fieldCharacter_{2m} = \fieldCharacter \circ \trace_{\finiteFieldExtension{2m} \slash \quadraticExtension}$
+
 If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
@@
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
+Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}},$$ where $\fieldCharacter_{2m_i} = \fieldCharacter \circ \trace_{\finiteFieldExtension{2m_i} \slash \quadraticExtension}$.
+Then
 	\begin{align*}

### 2025-03-04 paper.tex
Adding the involution for unitary groups

@@
 \newcommand{\involution}[1]{#1^{c}}
+\newcommand{\minusInvolution}[1]{#1^{-c}}
+\newcommand{\involutionPlusOne}[1]{#1^{1+c}}
 \newcommand{\IdentityMatrix}[1]{I_{#1}}
@@
 
+Given a multiplicative character $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$, let $\involutionPlusOne{\chi} \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be the character given by
+$$\involutionPlusOne{\chi}\left(x\right) = \chi\left(x \cdot \involution{x}\right).$$ Similarly, let $\minusInvolution{\chi} \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be the character given by
+$$\minusInvolution{\chi}\left(x\right) = \chi^{-1}\left(\involution{x}\right).$$
+
 \begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
 	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$.
-Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\chi^2 \ne 1$, we have
-	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^k \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
+Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
+	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \detQuadratic\left(a\right)^{-1}\detQuadratic\left(a - I_k\right)^2 \detQuadratic\left( g' - \idmap_{\hermitianSpace'}\right),$$
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(a - \IdentityMatrix{k}\right) \det\left(\involution{\left(a - \IdentityMatrix{k}\right)}\right) \detQuadratic\left( g' - \idmap_{\hermitianSpace'}\right),$$
 	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
@@
 	\begin{equation}
-		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\chi^2}\left(a\right) \chi^{-1}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
 	\end{equation}
@@
 	\begin{align*}
-		&\chi\left(-1\right)^k \dblGaussSum{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}\\
-		=& \chi\left(-1\right)^k\dblGaussSumScalar{\tau \otimes \chi_{\GL_k}^{-1}}{\chi^2} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+		&\chi\left(-1\right)^k \dblGaussSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}\\
+		=& \chi\left(-1\right)^k\dblGaussSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
 	\end{align*}
@@
 Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
-For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi^{-1}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor}}.$$
+For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor}}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

### 2025-03-04 paper.tex
Correcting first computation

@@
 We use the results from the previous section to compute the doubling method Gauss sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
-Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\chi^2 \ne 1$.
+Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
 Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(x^{-1} - 1\right)\right).$$
+		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(\minusInvolution{x} - 1\right)\right).$$
 This can be rewritten as
 $$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(x\right)\right) \chi^2\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
+		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
 By the previous section, this equals
 \begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \GaussSumCharacter{\alpha}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\chi^2, \fieldCharacter\right)^k.
+	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_k} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)^k.
 \end{equation}
@@
 Notice that if $k = md$ and $\alpha = \beta \circ \FieldNorm{k}{m}$ where $\beta \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ is a character, then \eqref{eq:identity-for-multiplicative-group-of-f-k-gauss-sum} equals
-$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_m} \GaussSumCharacter{\beta}{\chi^{-1}}{\fieldCharacter_m} \tau\left(\chi^2, \fieldCharacter\right)^m\right)^{d}.$$
+$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_m} \GaussSumCharacter{\beta}{\minusInvolution{\chi}}{\fieldCharacter_m} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)^m\right)^{d}.$$
 

### 2025-03-04 paper.tex
Unitary group computations

@@
 \subsubsection{Elliptic torus computation}
-In this section we compute the doubling method Gauss sum for a torus of the form $\NormOneGroup{2m}$.
+In the next two sections we compute the doubling method Gauss sum for a torus of the form $\NormOneGroup{2m}$.
 
@@
 
-As usual, we rewrite this sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right),$$
-where $\fieldCharacter_{2m} = \fieldCharacter \circ \trace_{\finiteFieldExtension{2m} \slash \quadraticExtension}$
+We separate two cases: the case $\quadraticExtension = \finiteField$ and the case $\quadraticExtension \ne \finiteField$.
+
+\subsubsection{Elliptic torus computation: the case $\quadraticExtension = \finiteField$}
+In this section, we compute the above exponential sum for the case $\quadraticExtension = \finiteField$.
+
+As usual, we rewrite the sum as follows
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right),$$
+where $\fieldCharacter_{2m} = \fieldCharacter \circ \trace_{\finiteFieldExtension{2m} \slash \finiteField}$.
 
 If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
-$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
+$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
 To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \NormOneGroup{2m}$ given by $t \mapsto t^{1 - q^m}$.
@@
 Replacing the sum over $x \in \NormOneGroup{2m}$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
-	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
-	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
+	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
+	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
 \end{align*}
@@
 \begin{align*}
-	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(z\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
-\end{align*}
-Since $\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
+	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
+\end{align*}
+Since $\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
 Hence, we may reduce the sum over $z$ to $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
@@
 	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
-	\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
+			\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
 \end{align*}
@@
 \begin{align*}
-	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
+	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
 \end{align*}
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
 where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+
+\subsubsection{Elliptic torus computation: the case $\quadraticExtension \ne \finiteField$}
+In this section, we compute the above exponential sum for the case $\quadraticExtension = \finiteFieldExtension{2}$.
+Let $\chi \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$.
+We wish to compute the following sum.
+$$\sum_{\substack{x \in \NormOneGroup{2m}\\
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(x - 1\right)\right).$$
+By the appendix, this equals
+$$\theta\left(-1\right) q^{\frac{m}{2}} \GaussSumCharacter{\theta'}{\minusInvolution{\chi}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
+which equals
+$$\theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\minusInvolution{\chi}}{\fieldCharacter_{2m}}.$$
 
@@
  $GO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ 
-  $U(n)$ & $(\NormOneGroup{\finiteFieldExtension{2}})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{\finiteFieldExtension{2}})^{n}$ 
+  $U(n)$ & $(\NormOneGroup{2})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{2})^{n}$ 
 \end{tabular}
@@
 In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
-In the unitary case, the torus whose $\finiteField$ points are $(\NormOneGroup{\finiteFieldExtension{2}})^n \subset G^*(\finiteField)$ includes into the torus in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
+In the unitary case, the torus whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
 
@@
             0 & 1 \\
-            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{\finiteFieldExtension{2n}},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
+            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
     \end{enumerate}
@@
 	\item \begin{align*}
-		\exp(\langle\phi(x_{\NormOneGroup{\finiteFieldExtension{2n}},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{\finiteFieldExtension{2n}},\theta},\phi^*(y_1,y_2)\rangle) \\
+		\exp(\langle\phi(x_{\NormOneGroup{2n},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{2n},\theta},\phi^*(y_1,y_2)\rangle) \\
 		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
@@
 Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
-We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{\finiteFieldExtension{2}})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$.
+We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$.
 We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
@@
 \appendix
-\section{Evaluation of an exponential sum}
-
-In this appendix, we evaluate the following exponential sum.
-Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-We compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
+\section{Evaluation of norm one exponential sums}
+
+In this appendix, we evaluate several exponential sums.
+
+\subsection{The case $\quadraticExtension = \finiteField$}
+Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character. We compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
 	\trace_{\finiteFieldExtension{2} \slash \finiteField}\left(x\right) \ne 0}} \chi\left(\FieldNorm{2}{1}\left(\frac{x}{\trace_{\finiteFieldExtension{2} \slash \finiteField} x}\right) \right).$$
@@
 $$q^{\frac{1}{2}} \left(q-1\right) \tau\left(\chi, \fieldCharacter\right)^2 \tau\left(\chi^{-2}, \fieldCharacter\right).$$
+
+\subsection{The case $\quadraticExtension \ne \finiteField$}
+Let $\chi \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ be a non-trivial character and let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\cComplex}$ be a character.
+Our goal is to compute $$\sum_{1 \ne x \in \NormOneGroup{2}} \theta\left(x\right) \chi\left(x-1\right).$$
+Using the Hilbert 90 map this is equivalent to
+$$\frac{1}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
+x \notin \multiplicativegroup{\finiteField}}} \theta\left(\frac{x}{x^q}\right) \chi\left(\frac{x}{x^q}-1\right).$$
+Let $0 \ne \delta \in \multiplicativegroup{\finiteFieldExtension{2}}$ be a trace-zero element. Replacing $x$ with $\delta x$, we arrive at the sum
+$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
+		x \notin \delta^{-1} \multiplicativegroup{\finiteField}}} \theta'\left(x\right) \minusInvolution{\chi}\left(x\right) \chi\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right),$$
+	where $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ is given by $\theta'\left(x\right) = \theta\left(\frac{x}{x^q}\right)$ and $\minusInvolution{\chi}\left(x\right) = \chi^{-1}\left(x^{q}\right)$.
+
+	As usual, we may rewrite the last sum as
+	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \minusInvolution{\chi}\left(x\right) \chi\left(y\right) \fieldCharacter_{\finiteField}\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
+	Since $\chi \ne 1$, the inner sum vanishes when $z = 0$, and therefore we can reduce the sum over $z$ to $z \in \multiplicativegroup{\finiteField}$.
+Changing variables $x \mapsto -z^{-1} x$ and $y \mapsto z^{-1} y$, and using the fact that $z^q = z$, we arrive at the sum
+	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \minusInvolution{\chi}\left(x\right) \fieldCharacter_{\finiteField}\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter_\finiteField\left(y\right),$$
+	which equals
+	$$q^{\frac{1}{2}} \theta\left(-1\right) \GaussSumCharacter{\theta'}{\minusInvolution{\chi}}{\fieldCharacter_2} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
+
 \bibliographystyle{abbrv}

### 2025-03-04 paper.tex
Adding a comment

@@
 \begin{enumerate}
+	\item It seems like the unitary group case adds factors of the form $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)$ and $\tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)$, which are related ($\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right) = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)^2$).
+The character $\fieldCharacter$ should be of $\finiteField$ and not of $\quadraticExtension$.
+Should clean up and try to write in a uniform way.
 	\item (Minor) Change terminology of Gauss sums $\dblGaussSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums

### 2025-03-04 paper.tex
Trying to correct characters etc

@@
 \section{Notation}
-Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter_{\finiteField} \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
 Fix an algebraic closure $\algebraicClosure{\finiteField}$ of $\finiteField$.
@@
 For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
-$$\GaussSum{\tau \times \chi}{\fieldCharacter_{\finiteField}} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter_{\finiteField}\left(\trace g\right).$$
-This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter_{\finiteField}} \in \cComplex$ such that
-$$\GaussSum{\tau \times \chi}{\fieldCharacter_{\finiteField}} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter_{\finiteField}} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
+This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
 
@@
 	For any singular matrix $X \in \squareMatrix_n\left(\finiteField\right)$ and any $1 \ne \chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the sum
-	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter_{\finiteField}\left(\trace\left(Xh\right)\right)$$
+	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter\left(\trace\left(Xh\right)\right)$$
 	is zero.
@@
 	where $1 \le r \le n$ and $h_1, h_2 \in \GL_n\left(\finiteField\right)$. Then
-	$$\fieldCharacter_{\finiteField}\left(\trace Xh\right) = \fieldCharacter_{\finiteField}\left(\trace\left( \begin{pmatrix}
+	$$\fieldCharacter\left(\trace Xh\right) = \fieldCharacter\left(\trace\left( \begin{pmatrix}
 		\IdentityMatrix{n-r}\\
@@
 	we obtain the inner sum
-	$$\sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \begin{pmatrix}
+	$$\sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
 		\IdentityMatrix{n-r}\\
@@
 	which equals
-	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \begin{pmatrix}
+	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
 		\IdentityMatrix{n-r}\\
@@
 	We have the identity
-	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter_{\finiteField}} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter_{\finiteField}\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter_{\finiteField}\left(\trace y\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
 \end{proposition}
 \begin{proof}
-	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$.
-Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	Changing variables $h \mapsto X^{-1} h$, we get
-	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace \left(Xg\right)\right) \fieldCharacter_{\finiteField}\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter_{\finiteField}\left(-\trace X\right).$$
+	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
 	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
-	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter_{\finiteField}} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter_{\finiteField}\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter_{\finiteField}\left(\trace y\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
 \end{proof}
@@
 We now use this to compute $\dblGaussSum{\tau}{\chi}$.
-We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter_{\finiteField}} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter_{\finiteField}\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter_{\finiteField}\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
+We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
 The last equality implies the following result.
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter_{\finiteField}}^k \GaussSumScalar{\tau}{\fieldCharacter_{\finiteField}} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter_{\finiteField}}.$$
+	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
 \end{theorem}
@@
 Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.
-Let $\fieldCharacter \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
 
@@
 
+Let $\fieldCharacter_{\quadraticExtension} \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be the character  $\fieldCharacter_{\quadraticExtension} = \fieldCharacter \circ \trace_{\quadraticExtension \slash \finiteField}$.
 Given a multiplicative character $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$, let $\involutionPlusOne{\chi} \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be the character given by
@@
 Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
-	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter} \dblGaussSumScalar{\pi'}{\chi}.$$
+	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblGaussSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
 	Hence, \begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter\left(\trace\left(Ah\right)\right) \\
-		& \times \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 	\begin{align*}
-		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter\left(\trace h\right) \sum_{p \in P} \fieldCharacter\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
+		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
 	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
 	\begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter\left(\trace h\right) \\
-		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
+		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
+
+We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
+	\tau\left(\chi^2, \fieldCharacter\right)^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor} & \quadraticExtension = \finiteField\\
+	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField
+\end{dcases}.$$
+Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.
+
 For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{\GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor}}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \finiteField\right)}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter_{\finiteField} \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
 If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
@@
 As usual, we rewrite the sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right),$$
-where $\fieldCharacter_{2m} = \fieldCharacter \circ \trace_{\finiteFieldExtension{2m} \slash \finiteField}$.
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
 
@@
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}},$$ where $\fieldCharacter_{2m_i} = \fieldCharacter \circ \trace_{\finiteFieldExtension{2m_i} \slash \quadraticExtension}$.
-Then
+Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\minusInvolution{\chi}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\minusInvolution{\chi}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
 	\begin{align*}
@@
 	As usual, we may rewrite the last sum as
-	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \minusInvolution{\chi}\left(x\right) \chi\left(y\right) \fieldCharacter_{\finiteField}\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
+	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \minusInvolution{\chi}\left(x\right) \chi\left(y\right) \fieldCharacter\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
 	Since $\chi \ne 1$, the inner sum vanishes when $z = 0$, and therefore we can reduce the sum over $z$ to $z \in \multiplicativegroup{\finiteField}$.
 Changing variables $x \mapsto -z^{-1} x$ and $y \mapsto z^{-1} y$, and using the fact that $z^q = z$, we arrive at the sum
-	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \minusInvolution{\chi}\left(x\right) \fieldCharacter_{\finiteField}\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter_\finiteField\left(y\right),$$
+	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \minusInvolution{\chi}\left(x\right) \fieldCharacter\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter\left(y\right),$$
 	which equals

### 2025-03-04 paper.tex
Trying to correct field character again.

@@
 \begin{enumerate}
-	\item It seems like the unitary group case adds factors of the form $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)$ and $\tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)$, which are related ($\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right) = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)^2$).
-The character $\fieldCharacter$ should be of $\finiteField$ and not of $\quadraticExtension$.
-Should clean up and try to write in a uniform way.
 	\item (Minor) Change terminology of Gauss sums $\dblGaussSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums
@@
 Let $\fieldCharacter_{\quadraticExtension} \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be the character  $\fieldCharacter_{\quadraticExtension} = \fieldCharacter \circ \trace_{\quadraticExtension \slash \finiteField}$.
+Similarly, for any $k \ge 1$, let $\fieldCharacter_{\quadraticFieldExtension{k}} \colon \quadraticFieldExtension{k} \to \multiplicativegroup{\cComplex}$ be the character $\fieldCharacter_{\quadraticFieldExtension{k}} = \fieldCharacter \circ \trace_{\quadraticFieldExtension{k} \slash \finiteField}$.
+
 Given a multiplicative character $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$, let $\involutionPlusOne{\chi} \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be the character given by
@@
 For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \finiteField\right)}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 \begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_k} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)^k.
+	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
 \end{equation}
@@
 Notice that if $k = md$ and $\alpha = \beta \circ \FieldNorm{k}{m}$ where $\beta \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ is a character, then \eqref{eq:identity-for-multiplicative-group-of-f-k-gauss-sum} equals
-$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_m} \GaussSumCharacter{\beta}{\minusInvolution{\chi}}{\fieldCharacter_m} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter\right)^m\right)^{d}.$$
+$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \GaussSumCharacter{\beta}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^m\right)^{d}.$$
 
@@
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\minusInvolution{\chi}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\minusInvolution{\chi}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$ Then
+Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\minusInvolution{\chi}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.$$ Then
 	\begin{align*}

### 2025-03-04 paper.tex
Gauss sums are now Jacobi sums

@@
 \documentclass[12pt, reqno]{amsart}
+\usepackage[normalem]{ulem}
 
@@
 \newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
-\newcommand{\dblGaussSum}[2]{\mathcal{G}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblJacobiSum}[2]{\mathcal{J}^{\mathrm{dbl}}\left(#1, #2\right)}
 \newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
-\newcommand{\dblGaussSumScalar}[2]{\mathrm{G}^{\mathrm{dbl}}\left(#1, #2\right)}
-\newcommand{\dblVirtualGaussSumScalar}[2]{\mathrm{g}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}^{\mathrm{dbl}}\left(#1, #2\right)}
 \newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
@@
 	pdfsubject={Number theory, Representation theory},
-	pdfkeywords={Kloosterman sums, Gauss sums}}
+	pdfkeywords={Kloosterman sums, Exponential sums}}
 
@@
 \begin{enumerate}
-	\item (Minor) Change terminology of Gauss sums $\dblGaussSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums
+	\item (Minor) \sout{Change terminology of Gauss sums $\dblJacobiSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums}
 	$$J\left(\alpha, \beta\right) = \sum_{\substack{x,y \in \multiplicativegroup{\finiteField}\\
 	x+y = 1}} \alpha\left(x\right) \beta\left(y\right),$$
-	compare with $$\dblGaussSumScalar{\pi}{\chi} = \sum_{\substack{g \in G\\
+	compare with $$\dblJacobiSumScalar{\pi}{\chi} = \sum_{\substack{g \in G\\
 			h \in \GL\left(\hermitianSpace\right)\\
@@
 
-\section{Doubling method Gauss sums}
+\section{Doubling method Jacobi sums}
 
@@
 
-Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Gauss sum}:
-$$\dblGaussSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
-Then $\dblGaussSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$.
-Therefore, by Schur's lemma there exists a complex number $\dblGaussSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblGaussSum{\tau}{\chi} = \dblGaussSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
-
-The goal of this section is to express $\dblGaussSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.
+Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Jacobi sum}:
+$$\dblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
+Then $\dblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$.
+Therefore, by Schur's lemma there exists a complex number $\dblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblJacobiSum{\tau}{\chi} = \dblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
+
+The goal of this section is to express $\dblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.
 
@@
 
-We now use this to compute $\dblGaussSum{\tau}{\chi}$.
-We have that $$\dblGaussSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
+We now use this to compute $\dblJacobiSum{\tau}{\chi}$.
+We have that $$\dblJacobiSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
 The last equality implies the following result.
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\dblGaussSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+	$$\dblJacobiSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
 \end{theorem}
@@
 Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
-Denote $$\dblGaussSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
+Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
 Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$.
-Since $G$ is a normal subgroup of $H$, we have that $\dblGaussSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
-By Schur's lemma, there exists a constant $\dblGaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblGaussSum{\pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
-We call $\dblGaussSumScalar{\pi}{\chi}$ the \emph{doubling method Gauss sum}.
+Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
+By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
+We call $\dblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sum}.
 
 \subsubsection{Multiplicativity property}
-Our next goal is to understand how the doubling method Gauss sum behaves under parabolic induction.
+Our next goal is to understand how the doubling method Jacobi sum behaves under parabolic induction.
 
@@
 Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
-	$$\dblGaussSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblGaussSumScalar{\pi'}{\chi}.$$
+	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
-We compute $\dblGaussSum{\rho}{\chi} f$.
-
-	Notice that for $x \in G$, $$\left(\dblGaussSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
+We compute $\dblJacobiSum{\rho}{\chi} f$.
+
+	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
 	which can be rewritten as
-	$$\left(\dblGaussSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
+	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
 	As before, we may write
@@
 
-	Hence, we have that $\dblGaussSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblGaussSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
+	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
 	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
@@
 	\begin{align*}
-		&\chi\left(-1\right)^k \dblGaussSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblGaussSum{\pi'}{\chi} v_{\pi'}\\
-		=& \chi\left(-1\right)^k\dblGaussSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblGaussSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
+		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
 	\end{align*}
@@
 For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblGaussSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 
-The goal of the next two sections is to compute $\dblGaussSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
-
-In this section, we focus on the computing the analogous character sum corresponding to $\dblGaussSumScalar{\pi}{\fieldCharacter}$ for the virtual character $R_{T,\theta}$.
+The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
+
+In this section, we focus on the computing the analogous character sum corresponding to $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for the virtual character $R_{T,\theta}$.
 
@@
 
-Given a class function $F \colon G \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualGaussSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
-
-It is clear that if $\pi$ is an irreducible representation of $G$ then $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dblGaussSumScalar{\pi}{\chi} \cdot \dim \pi.$$
+Given a class function $F \colon G \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
+
+It is clear that if $\pi$ is an irreducible representation of $G$ then $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \dim \pi.$$
 Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in G$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
@@
 	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{G}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{G}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{G}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
 \end{proposition}
 In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $G$ and we have that for this $\pi$,
-$$\dblGaussSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{G}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{G}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
 Here $\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{G}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{G}_p$ is the size of the $p$-Sylow group of $G$, where $p$ is the characteristic of $\finiteField$.
@@
 \subsubsection{Split torus computation II}
-We use the results from the previous section to compute the doubling method Gauss sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
+We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
 Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
@@
 \subsubsection{Elliptic torus computation}
-In the next two sections we compute the doubling method Gauss sum for a torus of the form $\NormOneGroup{2m}$.
+In the next two sections we compute the doubling method Jacobi sum for a torus of the form $\NormOneGroup{2m}$.
 
@@
 	\begin{align*}
-		 \dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
+		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
 	\end{align*}
@@
 	Thus \begin{align*}
-		\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
+		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
 	\end{align*}
@@
 	$\Phi_{\chi}(g)$ is a stable function.
-	%Equivalently	$\frac{\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+	%Equivalently	$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
 \end{theorem}
@@
 
-The idea behind the proof of \Cref{thm:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualGaussSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
+The idea behind the proof of \Cref{thm:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
 \begin{center}
@@
 
-The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblGaussSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
+The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
 
@@
 	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualGaussSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualGaussSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualJacobiSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualJacobiSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
-	$$c_{\pi} \cdot \dblVirtualGaussSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
+	$$c_{\pi} \cdot \dblVirtualJacobiSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
 	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $\dblVirtualGaussSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblGaussSumScalar{\pi}{\chi}$, the result follows.
+	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	Since $\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblJacobiSumScalar{\pi}{\chi}$, the result follows.
 \end{proof}
@@
 	 \innerproduct{K}{\conjugate{\trace \pi}} &= \frac{1}{\sizeof{G}}\trace \left(\sum_{g_1,\dots,g_k \in G} \Phi_{\chi_1}\left(g_1\right) \dots \Phi_{\chi_k}\left(g_k\right) \pi\left(g_1 \dots g_k\right) \right) \\
-	 &= \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}}}{\sizeof{G}} \trace\left( \dblGaussSum{\pi}{\chi_1} \circ \dots \dblGaussSum{\pi}{\chi_k} \right).
-\end{align*}
-Thus $$\innerproduct{K}{\conjugate{\trace \pi}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \dim \pi}{\sizeof{G}} \cdot \prod_{j=1}^k \dblGaussSumScalar{\pi}{\chi_j}.$$
+	 &= \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}}}{\sizeof{G}} \trace\left( \dblJacobiSum{\pi}{\chi_1} \circ \dots \dblJacobiSum{\pi}{\chi_k} \right).
+\end{align*}
+Thus $$\innerproduct{K}{\conjugate{\trace \pi}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \dim \pi}{\sizeof{G}} \cdot \prod_{j=1}^k \dblJacobiSumScalar{\pi}{\chi_j}.$$
 It follows that if
 $$\DeligneLusztigInduction{T}{G}\theta = \sum_{\pi} c_{\pi} \cdot \trace \pi,$$
-then $$\innerproduct{K}{\conjugate{\DeligneLusztigInduction{T}{G}\theta}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblGaussSumScalar{\pi}{\chi_j}}{\sizeof{G}} \sum_{\pi} c_{\pi} \dim \pi = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblGaussSumScalar{\pi}{\chi_j}}{\sizeof{G}} \left(\DeligneLusztigInduction{T}{G}\theta\right)\left(1\right),$$
+then $$\innerproduct{K}{\conjugate{\DeligneLusztigInduction{T}{G}\theta}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblJacobiSumScalar{\pi}{\chi_j}}{\sizeof{G}} \sum_{\pi} c_{\pi} \dim \pi = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblJacobiSumScalar{\pi}{\chi_j}}{\sizeof{G}} \left(\DeligneLusztigInduction{T}{G}\theta\right)\left(1\right),$$
 where $\pi$ is any irreducible representation of $G$ such that $c_{\pi} \ne 0$.
@@
 where the sum is over all the characters of $T$.
-Using the formula $$\dblGaussSumScalar{\pi}{\chi} = \tau\left( \theta' \times \chi^{-1}, \fieldCharacter_{2m} \right) \theta\left(-1\right) \tau\left(\chi^2, \fieldCharacter\right)^m,$$
+Using the formula $$\dblJacobiSumScalar{\pi}{\chi} = \tau\left( \theta' \times \chi^{-1}, \fieldCharacter_{2m} \right) \theta\left(-1\right) \tau\left(\chi^2, \fieldCharacter\right)^m,$$
 we get

### 2025-03-04 paper.tex
Correcting factor
Removing dimension over 2

@@
 We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\tau\left(\chi^2, \fieldCharacter\right)^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor} & \quadraticExtension = \finiteField\\
+	\tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField\\
 	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField
@@
 Hence, we have the identity
-$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi_{\GL_k}, \fieldCharacter_k\right).$$
+$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
 
@@
 
-Let $\theta \colon \NormOneGroup{2m} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\chi^2 \ne 1$.
-It follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
+Let $\theta \colon \NormOneGroup{2m} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\involutionPlusOne{\chi} \ne 1$.
 Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
@@
 In this section, we compute the above exponential sum for the case $\quadraticExtension = \finiteField$.
+Since $\chi^2 \ne 1$, it follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
 
@@
 	\begin{align*}
-		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
+		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
 	\end{align*}
@@
 \begin{proof}
-	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor},$$
-	the facts \begin{equation*}
-		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor},
+	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
+	and the facts \begin{equation*}
+		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.
 	\end{equation*}
-	and finally from $$\GaussSumScalar{\chi^2}{\fieldCharacter} = -\tau\left(\chi^2, \fieldCharacter\right).$$
 \end{proof}
@@
 	Thus \begin{align*}
-		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
+		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
 	\end{align*}
@@
 	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualJacobiSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualJacobiSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualJacobiSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualJacobiSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
 	$$c_{\pi} \cdot \dblVirtualJacobiSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
-	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot \GaussSumScalar{\chi^2}{\fieldCharacter}^{\left\lfloor\frac{\dim_{\quadraticExtension} \hermitianSpace}{2}\right\rfloor} \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
 	Since $\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblJacobiSumScalar{\pi}{\chi}$, the result follows.

### 2025-03-04 paper.tex
Correction

@@
 We now use this to compute $\dblJacobiSum{\tau}{\chi}$.
-We have that $$\dblJacobiSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
+We have that $$\dblJacobiSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(-y^{-1} x\right).$$
 The last equality implies the following result.

### 2025-03-04 paper.tex
g-1 => 1-g

--- 2025-03-04 paper.tex
@@
 $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-	\chi\left(\det\left(g-\IdentityMatrix{k}\right)\right) & \text{if }\det\left(g-\IdentityMatrix{k}\right) \ne 0,\\
+	\chi\left(\det\left(\IdentityMatrix{k}-g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}-g\right) \ne 0,\\
 	0 & \text{otherwise.}
@@
 	We have the identity
-	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
 			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
@@
 \begin{proof}
-	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det\left(-h\right)\right).$$
 	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$.
-Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+Thus	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	Changing variables $h \mapsto X^{-1} h$, we get
-	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
+	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
 	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
-	$$\Phi_{\chi}\left(g\right) = q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
 			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
@@
 We now use this to compute $\dblJacobiSum{\tau}{\chi}$.
-We have that $$\dblJacobiSum{\tau}{\chi} = q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \pi\left(-y^{-1} x\right).$$
+We have that $$\dblJacobiSum{\tau}{\chi} = \chi\left(-1\right)^k q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(-y^{-1} x\right).$$
 The last equality implies the following result.
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\dblJacobiSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+	$$\dblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
 \end{theorem}
@@
 As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-\chi\left(\detQuadratic\left(g - \idmap_{\hermitianSpace}\right)\right) & \text{if }\detQuadratic\left(g - \idmap_{\hermitianSpace}\right) \ne 0\\
+\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} - g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} - g\right) \ne 0\\
 0 & \text{otherwise,}
@@
 	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h^{-1}\right)\right)\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(-\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
 	Hence, \begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
+		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
 		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
@@
 	\begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
+		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
 		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
@@
 		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
-				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(p - \idmap_{\hermitianSpace}\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
 	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(a - \IdentityMatrix{k}\right) \det\left(\involution{\left(a - \IdentityMatrix{k}\right)}\right) \detQuadratic\left( g' - \idmap_{\hermitianSpace'}\right),$$
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} - p\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} - a\right) \det\left(\involution{\left(\IdentityMatrix{k} - a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} - g'\right),$$
 	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
@@
 
-The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right).$$
+The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1-x\right)\right).$$
 Let us rewrite this as
-$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
+$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\left(-1\right)^k\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
 Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
@@
 Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$, this becomes
-$$q^{-k} \alpha\left(-1\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
+$$q^{-k} \alpha\left(-1\right) \chi\left(-1\right)^k \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
 Hence, we have the identity
-$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
+$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \chi\left(-1\right)^k \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
 
@@
 Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(x - 1\right)\right) \chi\left(\FieldNorm{k}{1}\left(\minusInvolution{x} - 1\right)\right).$$
+		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 - x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 - \minusInvolution{x}\right)\right).$$
 This can be rewritten as
 $$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(x - 1\right)\right).$$
+		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(1 - x\right)\right).$$
 By the previous section, this equals
@@
 Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x - 1\right)\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(1 - x\right)\right).$$
 
@@
 As usual, we rewrite the sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(-y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
 
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(x - 1\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
 where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(x - 1\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
 
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(x - 1\right)\right).$$
+		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 - x\right)\right).$$
 By the appendix, this equals
@@
 Let $\chi \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ be a non-trivial character and let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\cComplex}$ be a character.
-Our goal is to compute $$\sum_{1 \ne x \in \NormOneGroup{2}} \theta\left(x\right) \chi\left(x-1\right).$$
+Our goal is to compute $$\sum_{1 \ne x \in \NormOneGroup{2}} \theta\left(x\right) \chi\left(1-x\right).$$
 Using the Hilbert 90 map this is equivalent to
 $$\frac{1}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-x \notin \multiplicativegroup{\finiteField}}} \theta\left(\frac{x}{x^q}\right) \chi\left(\frac{x}{x^q}-1\right).$$
+x \notin \multiplicativegroup{\finiteField}}} \theta\left(\frac{x}{x^q}\right) \chi\left(1-\frac{x}{x^q}\right).$$
 Let $0 \ne \delta \in \multiplicativegroup{\finiteFieldExtension{2}}$ be a trace-zero element. Replacing $x$ with $\delta x$, we arrive at the sum

### 2025-03-04 paper.tex
Correction

@@
 	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(-\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
+	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
 	Hence, \begin{align*}

### 2025-03-04 paper.tex
TODO list

@@
 	g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det\left(-h\right)\right).$$
-	Consider replacing $\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right)$ with $\chi\left(\det\left(\idmap_{\hermitianSpace} - g\right)\right)$ for aesthetics (probably not worth it).
+	\sout{Consider replacing $\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right)$ with $\chi\left(\det\left(\idmap_{\hermitianSpace} - g\right)\right)$ for aesthetics (probably not worth it).}
 	\item Maybe define the algebraic group versions $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$ in Section 3.2. For instance for $\algebraicGroup{\Sp}_{2n}$ we can define
@@
 	\end{pmatrix}, t\right) \mid t \in \multiplcativeScheme \right\} \subset \GroupExtension{\algebraicGroup{G}}.$$
+	Actually it appears to me that we are not in the same situation as in \cite[Page 140]{DigneMichel2020}.
 	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.

### 2025-03-05 paper.tex
Some minor corrections

@@
 \newcommand{\dblGammaFactorSpace}[4]{\Gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
+\newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
 \newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
@@
 
+\begin{remark}
+	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \begin{dcases}
+				\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon = -1 \\
+				\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} & \text{otherwise}
+	\end{dcases}.$$
+	However, we will not need this version for our purposes.
+\end{remark}
+
 \subsection{Computation of character sums attached to Deligne--Lusztig data}
@@
 By the previous section, this equals
+\begin{equation*}
+	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+\end{equation*}
+which equals
 \begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation}
@@
 Notice that if $k = md$ and $\alpha = \beta \circ \FieldNorm{k}{m}$ where $\beta \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ is a character, then \eqref{eq:identity-for-multiplicative-group-of-f-k-gauss-sum} equals
-$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \GaussSumCharacter{\beta}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^m\right)^{d}.$$
+$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \GaussSumCharacter{\involution{\beta}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^m\right)^{d}.$$
 
@@
 By the appendix, this equals
-$$\theta\left(-1\right) q^{\frac{m}{2}} \GaussSumCharacter{\theta'}{\minusInvolution{\chi}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
+$$\theta\left(-1\right) q^{\frac{m}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
 which equals
-$$\theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\minusInvolution{\chi}}{\fieldCharacter_{2m}}.$$
+$$\theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}.$$
 
@@
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\minusInvolution{\chi}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.$$ Then
+Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.$$ Then
 	\begin{align*}
@@
 	which equals
-	$$q^{\frac{1}{2}} \theta\left(-1\right) \GaussSumCharacter{\theta'}{\minusInvolution{\chi}}{\fieldCharacter_2} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
+	$$q^{\frac{1}{2}} \theta\left(-1\right) \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_2} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
 

### 2025-03-06 paper.tex
Removing my writing about Characteristic Polynomials

@@
 
-Let $\hermitianSpace$ be a vector space of dimension $n$ over $\quadraticExtension$, equipped with a non-degenerate sesquilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \quadraticExtension$ which is $\epsilon$-symmetric for $\epsilon \in \left\{\pm 1\right\}$.
+Let $\hermitianSpace$ be a vector space of dimension $n$ over $\quadraticExtension$, equipped with a non-degenerate sesquilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \quadraticExtension$ which is $\epsilon_{\hermitianSpace}$-symmetric for $\epsilon_{\hermitianSpace} \in \left\{\pm 1\right\}$.
 By this we mean that:
@@
 	\item For every $x,y \in \hermitianSpace$ and $t \in \quadraticExtension$, $$\innerproduct{tx}{y} = t\innerproduct{x}{y}.$$
-	\item ($\epsilon$-symmetric) For every $x,y \in \hermitianSpace$, $$\innerproduct{x}{y} = \epsilon \involution{\innerproduct{y}{x}}.$$
+	\item ($\epsilon_{\hermitianSpace}$-symmetric) For every $x,y \in \hermitianSpace$, $$\innerproduct{x}{y} = \epsilon_{\hermitianSpace} \involution{\innerproduct{y}{x}}.$$
 	\item (non-degenerate) For every $0 \ne x \in \hermitianSpace$ there exists $y \in \hermitianSpace$ such that $$\innerproduct{x}{y} \ne 0.$$
@@
 We will assume that $\dim_{\finiteField} \hermitianSpace$ is even.
-This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon = 1$.
+This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
 The group $\GroupExtension{G}$ has connected center and contains $G$.
@@
 \begin{enumerate}
-	\item (Even special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon = 1$.
+	\item (Even special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
 Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
@@
 	\end{enumerate}
-	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon = -1$.
+	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
 In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to subgroup $\Sp_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of all elements $g$ satisfying $$g \cdot \begin{pmatrix}
@@
 	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \begin{dcases}
-				\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon = -1 \\
+				-\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
 				\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} & \text{otherwise}
@@
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote $$g_T\left(\chi, \theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.$$ Then
+Denote \begin{align*}
+		g_T\left(\chi, \theta, \fieldCharacter\right)
+		= & \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \\
+		& \times \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
+	\end{align*} Then
 	\begin{align*}
@@
 \end{theorem}
-In order to prove this theorem, we will use the theory of Lusztig series.
-
-\subsubsection{Tori isomorphism}\label{subsec:tori-isomorphism}
-
-For any finite abelian group $G$, let $\widehat{G}$ be the character group of $G$, consisting of characters $\theta \colon G \to \multiplicativegroup{\cComplex}$.
-
-Let $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ be a family of isomorphisms $\ToriDualToriIsomorphism_k \colon \charactergroup{k} \to \multiplicativegroup{\finiteFieldExtension{k}}$ such that if $k' \mid k$ then $\ToriDualToriIsomorphism_k^{-1}\left(\xi_{k'}\right) = \ToriDualToriIsomorphism_{k'}^{-1}\left(\xi_{k'}\right) \circ \FieldNorm{k}{k'}$ for any $\xi_{k'} \in \multiplicativegroup{\finiteFieldExtension{k'}}$.
-
-Using the Hilbert 90 isomorphism $\finiteFieldExtension{2m} \slash \finiteFieldExtension{m} \to \finiteFieldExtension{2m}^{1}$ given by $$x \mapsto \frac{x}{x^{q^m}} = x^{1 - q^m},$$ we see that characters of $\NormOneGroup{2m}$ are in bijection with characters of $\multiplicativegroup{\finiteFieldExtension{2m}}$ such that their restriction to $\multiplicativegroup{\finiteFieldExtension{m}}$ is trivial.
-Using the surjective norm map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\finiteFieldExtension{m}}$, such characters are precisely characters $\theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ such that $\theta \circ \FieldNorm{2m}{m} = \theta^{1 + q^m} = 1$.
-By realizing the character group $\widehat{\NormOneGroup{2m}}$ as the subgroup of $\charactergroup{2m}$ given by $$\left\{ \theta \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex} \mid \theta^{1+q^m} = 1\right\},$$
-we have that $$\ToriDualToriIsomorphism_{2m}\left(\widehat{\NormOneGroup{2m}}\right) = \left\{\xi \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \xi^{1+q^m} = 1\right\} = \NormOneGroup{2m}.$$
-Let us denote the restriction of $\ToriDualToriIsomorphism_{2m}$ to $\widehat{\NormOneGroup{2m}}$ by $\ToriDualToriIsomorphism_{2m}^1 \colon \widehat{\NormOneGroup{2m}} \to \NormOneGroup{2m}$.
-
-The family $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ allows us to define $\ToriDualToriIsomorphism_T \colon \widehat{T} \to T$ for any maximal torus $T$ of $G$.
-Recall that for a maximal torus $T$ of $G$ there exists an isomorphism of groups $$e_T \colon T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1,$$
-satisfying that if the image of $t \in T$ in $\GL\left(\hermitianSpace\right)$ has an $\finiteField$-characteristic polynomial $\characteristicPolynomial_{t}\left(X\right)$ and $$e_T\left(t\right) = \left(t_1,\dots,t_r,u_1,\dots,u_s\right)$$ then $$\characteristicPolynomial_{t}\left(X\right) = \prod_{j=1}^r \characteristicPolynomial_{t_j, \finiteFieldExtension{k_j}}\left(X\right) \characteristicPolynomial_{t_j^{-1}, \finiteFieldExtension{k_j}}\left(X\right) \cdot \prod_{i=1}^s \characteristicPolynomial_{u_i, \finiteFieldExtension{2 m_i}}\left(X\right),$$
-where for $\xi \in \multiplicativegroup{\finiteFieldExtension{k}}$, $\characteristicPolynomial_{\xi, \finiteFieldExtension{k}}\left(X\right)$ is the $\finiteField$-characteristic polynomial of the multiplication by $\xi$ map $\finiteFieldExtension{k} \to \finiteFieldExtension{k}$.
-
-The isomorphism $e_T$ induces an isomorphism for the character group $$e_{\widehat{T}} \colon \widehat{T} \to \prod_{j=1}^r \charactergroup{k_j} \times \prod_{i=1}^s \widehat{\finiteFieldExtension{2m_i}^1},$$
-given by
-$$e_{\widehat{T}}\left(\theta\right) = \theta \circ e_T^{-1}.$$
-Using the isomorphisms $\ToriDualToriIsomorphism_{k_j} \colon \charactergroup{k_j} \to \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $\ToriDualToriIsomorphism_{2m_i} \colon \widehat{\finiteFieldExtension{2m_i}^1} \to \finiteFieldExtension{2m_i}^1$ and using $e_T$ and $e_{\widehat{T}}$, we obtain an isomorphism $\ToriDualToriIsomorphism_{T} \colon \widehat{T} \to T$.
-Note that this construction depends on the family $\left(\ToriDualToriIsomorphism_k\right)_{k=1}^{\infty}$ and on the isomorphism $e_T$.
-
-%I just sent you an email about a similar idea which I think makes the writeup a little easier and you don't need the isomorphism between T and Tdual.
-I have to prepare for a seminar talk tomoro but later this week or early next we can talk
-
-%% Okay cool! good luck with your talk
-
-\subsubsection{Gauss sums attached to semisimple elements}\label{subsec:gauss-sums-attached-to-semi-simple}
-
-Let $T$ be as in the previous section.
-Let $t \in T$ and suppose that $\ToriDualToriIsomorphism_{T}^{-1}\left(t\right) = \theta$ is given by $$\theta = \left(\alpha_1,\dots,\alpha_r,\theta_1,\dots,\theta_s\right) \circ e_T,$$ where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-We define $$g_T\left(t, \fieldCharacter\right) = g_T\left(\theta, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot  \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi^{-1}}{\fieldCharacter_{k_j}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{k_j}}.$$
-We claim that this definition only depends on $t$ and not on the maximal torus $T$ containing it.
-
-To see this, suppose that $\deg \alpha_1 = d_1$, $\dots$, $\deg \alpha_k = d_k$, $\deg \theta'_1 = d'_1$, $\dots$, $\deg \theta'_s = d'_s$ and that $k_1 = b_1 d_1$, $\dots$, $k_r = b_r d_r$, $2m_1 = b'_1 d'_1$, $\dots$, $2m_s = b'_s d'_s$.
-Then for every $j$,
-$\alpha_j = \beta_j \circ \FieldNorm{b_j d_j}{d_j}$ for some regular character $\beta_j \colon \multiplicativegroup{\finiteFieldExtension{d_j}} \to \multiplicativegroup{\cComplex}$, and similarly for every $i$, $\theta'_i = \vartheta_i \circ \FieldNorm{b'_i d'_i}{d'_i}$ for some regular character $\vartheta_i \colon \multiplicativegroup{\finiteFieldExtension{d'_i}} \to \multiplicativegroup{\cComplex}$.
-By the Hasse--Davenport relation we have \begin{equation}\label{eq:hasse-davenport-for-semisimple-elements}
-	g_T\left(t, \fieldCharacter\right) = \prod_{i=1}^s \GaussSumCharacter{\vartheta_i}{\chi^{-1}}{\fieldCharacter_{d'_i}}^{b'_i} \cdot  \prod_{j=1}^r \GaussSumCharacter{\beta_j}{\chi^{-1}}{\fieldCharacter_{d_j}}^{b_j} \GaussSumCharacter{\beta_j^{-1}}{\chi^{-1}}{\fieldCharacter_{d_j}}^{b_j}.
-\end{equation}
-On the other hand, let $$e_T\left(t\right) = \left(t_1,\dots,t_r,u_1,\dots,u_s\right),$$
-where $t_j \in \multiplicativegroup{\finiteFieldExtension{k_j}}$ and $u_i \in \finiteFieldExtension{2m_i}^1$ for every $i$ and $j$.
-Then we have that $t_j \in \multiplicativegroup{\finiteFieldExtension{d_j}}$ and $u_i \in \multiplicativegroup{\finiteFieldExtension{d'_i}}$ for every $i$ and $j$ (and these elements do not belong to smaller field extensions).
-Thus
-\begin{equation}\label{eq:characteristic-polynomial-equality-for-semisimple-elements}
-	\characteristicPolynomial_{t}\left(X\right) = \prod_{i=1}^s \characteristicPolynomial_{u_i, \finiteFieldExtension{d'_i}}\left(X\right)^{b'_i} \cdot \prod_{j=1}^r \characteristicPolynomial_{t_j, \finiteFieldExtension{d_j}}\left(X\right)^{b_j}\characteristicPolynomial_{t_j^{-1}, \finiteFieldExtension{d_j}}\left(X\right)^{b_j}.
-\end{equation}
-The equalities \eqref{eq:hasse-davenport-for-semisimple-elements} and \eqref{eq:characteristic-polynomial-equality-for-semisimple-elements} imply that may define $g_T\left(t,\fieldCharacter\right)$ using the $\finiteField$-characteristic polynomial of $t$ (viewed as an element of $\GL\left(\hermitianSpace\right)$) by defining a fully multiplicative function $\tau_{\chi, \fieldCharacter} \colon \finiteField\left[X\right]_{\mathrm{monic}} \to \cComplex$, sending $1$ to $1$ and any monic irreducible polynomial $p\left(X\right)$ of degree $d \ge 1$ to $\GaussSumCharacter{\ToriDualToriIsomorphism_{d}^{-1}\left(\xi\right)}{\chi^{-1}}{\fieldCharacter_d}$, where $\xi \in \multiplicativegroup{\finiteFieldExtension{d}}$ is any root of the polynomial $P\left(X\right)$.
-This map is well defined because Gauss sums are constant on Frobenius orbits of characters.
-
-If $s \in \GL_n\left(\finiteField\right)$ is semisimple, we denote $$\tau_{\GL_n\left(\finiteField\right), \chi, \fieldCharacter}\left(s\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_s\left(X\right)\right).$$
-
-Since the $\finiteField$-characteristic polynomial of $t$ does not depend on the maximal torus $T$ containing $t$, we conclude that the map $t \mapsto g_T\left(t, \fieldCharacter\right)$ does not depend on $t$ and we denote for any semisimple element $s \in G$, $$\tau_{G, \chi, \fieldCharacter}\left(s, \fieldCharacter\right) = g_T\left(s, \fieldCharacter\right) = \tau_{\chi, \fieldCharacter}\left(\characteristicPolynomial_{s}\left(X\right)\right),$$
-where $T$ is any maximal torus containing $s$ and $\characteristicPolynomial_{s}$ is the $\finiteField$-characteristic polynomial of $s$, viewed as an element of $\GL\left(\hermitianSpace\right)$.
 
@@
 
-\begin{comment}
-\calvin{here is the geometric idea:}
-\begin{lemma}
-    Let $\mathcal{F} := \mathcal{L}(\theta) \otimes tr^{*}\mathcal{L}(\psi)$. Then
-    \[
-        dim H_c^i(T,\mathcal{F}) = \begin{cases}
-        0    & i \neq dim(T) \\
-        1    & i = dim(T)
-        \end{cases}
-    \]
-\end{lemma}
-\calvin{Might exist in literature somewhere otherwise is a little bit of a pain. It should be analogous to the fact that the Guass sum on a field of size $p^d$ is of magnitude $\sqrt{p^d}$.}
-Combining this with Grothendieck-Lefschetz we get
-\begin{corollary}
-	$g_T(\theta,\psi)^k = g_T(\theta \circ Nm_{k:1},tr_{k:1} \circ \psi)$.
-\end{corollary}
-\calvin{there might be a simple non-geometric way to do this corollary not sure.}
-\calvin{The corollary plus the definition of geometric conjugacy imply $g_T(\theta,\psi) = \mu_kg_{T'}(\theta',\psi)$ for some $k$-th root of unity $\mu_k$. Not sure how to finish from here.}
-\end{comment}
-Let $\ToriDualToriIsomorphism_T \colon \widehat{T} \to T$ be as in the previous sections.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that $\ToriDualToriIsomorphism_T\left(\theta\right) = s$.
+\elad{Merge with Calvin's stuff}
 The \emph{Lusztig series} $\LusztigSeries{G}{s}$ consists of (equivalence classes of) the irreducible representations $\pi$ of $R_{T, \theta}$ with $c_{\pi} \ne 0$ as in the theorem.
@@
 $$\LusztigSeries{L}{s} = \left(\bigotimes_{j=1}^{\ell} \LusztigSeries{\GL_{t_j}\left(\finiteField\right)}{s_j}\right) \otimes \LusztigSeries{G'}{s_0}.$$
-It is clear that $$\tau_{G, \chi, \fieldCharacter}\left(s\right) = \tau_{G', \chi, \fieldCharacter}\left(s_0\right) \cdot \prod_{j=1}^r \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j\right) \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j^{-1}\right).$$
 
@@
 	\item For the groups $\GroupExtension{G}$ as the ones we consider in this paper, the Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ contains at most one irreducible cuspidal representation.
-	\item The restriction of $R_{\GroupExtension{T},\GroupExtension{G}} \left(\GroupExtension{\theta}\right)$ to $G$ is $R_{T, G} \left(\tilde{\theta} \restriction_T\right)$ \cite[Page 140]{DigneMichel2020}.
-TODO: Write more.
 	\item The Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $\GroupExtension{G}$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
+	\item \elad{TODO} The correspondence between the Lusztig series $\LusztigSeries{\GroupExtension{G}}{\tilde{s}}$ and $\LusztigSeries{G}{s}$, where $\tilde{s} = i^{\ast}\left(s\right)$ (\cite[Proof of Theorem 1]{Li2023}, \cite[Proof of Theorem 3.2]{Li2019}, \cite[Proof of Lemma 4.8]{SchaefferFryTaylorVinroot2025}).
 \end{enumerate}

### 2025-03-06 paper.tex
Changes

@@
 \begin{remark}
-	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \begin{dcases}
-				-\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
-				\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} & \text{otherwise}
+	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
+				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
+				\left(-1\right)^{n+1} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
+				1 & \text{otherwise.}
 	\end{dcases}.$$
@@
 
-Let us realize $G$ as the fixed points of the Frobenius map $\Frobenius$ acting on a connected reductive algebraic group $\algebraicGroup{G}$.
-
-Given a class function $F \colon G \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
-
-It is clear that if $\pi$ is an irreducible representation of $G$ then $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \dim \pi.$$
-Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in G$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
+Let us realize $H$ as the fixed points of the Frobenius map $\Frobenius$ acting on a connected reductive algebraic group $\algebraicGroup{H}$.
+
+Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
+
+It is clear that if $\pi$ is an irreducible representation of $H$ then $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \dim \pi.$$
+Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in H$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
-	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{G}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{G}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{H}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
+	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
 \end{proposition}
-In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $G$ and we have that for this $\pi$,
-$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{G}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
-Here $\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{G}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{G}_p$ is the size of the $p$-Sylow group of $G$, where $p$ is the characteristic of $\finiteField$.
+In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
+$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+Here $\varepsilon_{\algebraicGroup{H}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{H}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{H}_p$ is the size of the $p$-Sylow group of $H$, where $p$ is the characteristic of $\finiteField$.
 
@@
 \begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$.
+	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$.
 Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
@@
 		g_T\left(\chi, \theta, \fieldCharacter\right)
-		= & \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \\
-		& \times \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
+		= & \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
 	\end{align*} Then
 	\begin{align*}
-		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
+		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
 	\end{align*}
@@
 \begin{proof}
-	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{G}{T}}{\sizeof{G}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{G}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
-	and the facts \begin{equation*}
-		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r \text{\,\,\,\,\,\, and \,\,\,\,\,\,}  \varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.
+	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
+	and the fact \begin{equation*}
+		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r.
 	\end{equation*}
@@
 \begin{remark}
-	Suppose that $\pi$ is any irreducible representation of $G$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
+	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.$$ If $\finiteField = \quadraticExtension$ then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
+\end{remark}
+\begin{remark}
+	Suppose that $\pi$ is any irreducible representation of $H$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
 	\begin{align*}
@@
 	Thus \begin{align*}
-		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\theta, \fieldCharacter\right).
+		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
 	\end{align*}
@@
 $$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-		x \notin \delta^{-1} \multiplicativegroup{\finiteField}}} \theta'\left(x\right) \minusInvolution{\chi}\left(x\right) \chi\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right),$$
-	where $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ is given by $\theta'\left(x\right) = \theta\left(\frac{x}{x^q}\right)$ and $\minusInvolution{\chi}\left(x\right) = \chi^{-1}\left(x^{q}\right)$.
+		x \notin \delta^{-1} \multiplicativegroup{\finiteField}}} \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right),$$
+	where $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ is given by $\theta'\left(x\right) = \theta\left(\frac{x}{x^q}\right)$.
 
 	As usual, we may rewrite the last sum as
-	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \minusInvolution{\chi}\left(x\right) \chi\left(y\right) \fieldCharacter\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
+	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(y\right) \fieldCharacter\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
 	Since $\chi \ne 1$, the inner sum vanishes when $z = 0$, and therefore we can reduce the sum over $z$ to $z \in \multiplicativegroup{\finiteField}$.
 Changing variables $x \mapsto -z^{-1} x$ and $y \mapsto z^{-1} y$, and using the fact that $z^q = z$, we arrive at the sum
-	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \minusInvolution{\chi}\left(x\right) \fieldCharacter\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter\left(y\right),$$
-	which equals
+	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \chi^{-q}\left(x\right) \fieldCharacter\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter\left(y\right),$$
+	which by changing variables $x \mapsto x^q$ equals
 	$$q^{\frac{1}{2}} \theta\left(-1\right) \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_2} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$

### 2025-03-06 paper.tex
G => H

@@
 \begin{theorem}
-	Let $T \subset G$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
-	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
+	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
+	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$.
 Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.

### 2025-03-07 paper.tex
Fact collection

@@
 \newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
+\newcommand{\DualFrobeniusFixedPoints}[2][\Frobenius^{\ast}]{\algebraicGroup{#2}^{\ast #1}}
+\newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
 
@@
 In this case, we have that $G$ is isomorphic to the subgroup $\SO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of elements $g$ satisfying $$g \cdot w_{2n} \cdot \transpose{g} = w_{2n}$$ and $\det g = 1$.
-		The group $\tilde{G}$ is isomorphic to the subgroup $\GSO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that $$g \cdot w_{2n} \cdot \transpose{g} = \similitudeCharacter\left(g\right) w_{2n},$$
+		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that $$g \cdot w_{2n} \cdot \transpose{g} = \similitudeCharacter\left(g\right) w_{2n},$$
 		and such that $\det g = \similitudeCharacter\left(g\right)^n$, where $\similitudeCharacter\left(g\right)$ is a non-zero scalar.
@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
 	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
@@
 
-We will need the following two facts:
+We collect some facts that will be used for proving \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}.
+
+The following proposition allows us to make use of the multiplicativity property (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}) for non-cuspidal elements in a given Lusztig series.
+\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]
+	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
+\end{proposition}
+
+The following Proposition shows that is suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the group $\GroupExtension{G}$.
+\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
+	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
 	\begin{enumerate}
-	\item For the groups $\GroupExtension{G}$ as the ones we consider in this paper, the Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ contains at most one irreducible cuspidal representation.
-	\item The Lusztig series $\LusztigSeries{\GroupExtension{G}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(P,\sigma\right)$ where $P$ is a parabolic subgroup of $\GroupExtension{G}$ with Levi part $L$ and $\sigma \in \LusztigSeries{L}{s}$ is an irreducible cuspidal representation.
-	\item \elad{TODO} The correspondence between the Lusztig series $\LusztigSeries{\GroupExtension{G}}{\tilde{s}}$ and $\LusztigSeries{G}{s}$, where $\tilde{s} = i^{\ast}\left(s\right)$ (\cite[Proof of Theorem 1]{Li2023}, \cite[Proof of Theorem 3.2]{Li2019}, \cite[Proof of Lemma 4.8]{SchaefferFryTaylorVinroot2025}).
+		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
 	\end{enumerate}
-Our theorem is equivalent to the following statement.
+\end{proposition}
+
+Finally, the following proposition shows that the multiplicativity property takes care of all but at most one element in a given Lusztig series.
+\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
+	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
+\end{proposition}
+
+\Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is now equivalent to the following statement.
 \begin{proposition}\label{prop:gamma-factor-is-constant-on-lusztig-series}
 	Keep the notations as above.
-Suppose that $P$ is a parabolic subgroup of $G$ with Levi part $L$.
-Then for any irreducible cuspidal $\sigma \in \LusztigSeries{L}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{P}{G}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
+Suppose that $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$.
+Then for any irreducible cuspidal $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{\FrobeniusFixedPoints{P}}{\FrobeniusFixedPoints{\GroupExtension{G}}}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{\GroupExtension{G}, \chi, \fieldCharacter}\left(s\right).$$
+	\elad{Many things are not defined anymore. Need to define $\tau_{\GroupExtension{G}, \chi, \fieldCharacter}\left(s\right)$, etc.}
 \end{proposition}

### 2025-03-14 paper.tex
Removing unused macros
Calvin changes

@@
 \newcommand{\UnipotentSubgroup}{U}
-\newcommand{\UnipotentRadicalForWss}[2]{N_{\left(#2^{#1}\right)}}
-\newcommand{\UnipotentRadicalForWssRecursion}[2]{\mathcal{Y}_{c,k}}
 \newcommand{\UnipotentRadical}{N}
@@
 \newcommand{\aFieldNorm}{\mathrm{N}}
-\newcommand{\FieldTrace}{\mathrm{Tr}}
 \newcommand{\finiteField}{\mathbb{F}}
@@
 \newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
-\newcommand{\FieldExtension}[2]{{#1} \slash {#2}}
 \newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
 \newcommand{\algebraicClosure}[1]{\overline{#1}}
-\newcommand{\charactergroup}[1]{\widehat{\multiplicativegroup{\finiteFieldExtension{#1}}}}
-\newcommand{\limitcharactergroup}{\Gamma}
 \newcommand{\Galois}{\operatorname{Gal}}
@@
 \newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
-\newcommand{\frobeniusDegree}{\operatorname{deg}}
-\newcommand{\Steinberg}{\operatorname{St}}
-\newcommand{\ProjectionOperator}{\operatorname{pr}}
-\newcommand{\SymmetricGroup}{\mathfrak{S}}
-\newcommand{\whittakerVector}[1]{v_{#1, \fieldCharacter}}
-\newcommand{\gwhittakerVector}[2]{v_{#1, #2}}
-\newcommand{\WhittakerProjection}{\ProjectionOperator_{\mathrm{Wh}}}
-\newcommand{\ParabolicForSpeh}[2]{P_{\left({#1}^{#2}\right)}}
-\newcommand{\UnipotentForSpeh}[2]{N_{\left({#1}^{#2}\right)}}
-\newcommand{\PoincarePolynomial}[2]{P_{#2}}
-
-%Partition macros
-\newcommand{\localField}{F}
-\newcommand{\ringOfIntegers}{\mathfrak{o}}
-\newcommand{\residueField}{\mathfrak{f}}
-\newcommand{\maximalIdeal}{\mathfrak{p}}
-\newcommand{\depthZeroRepresentation}{\mathcal{T}}
-\newcommand{\differential}{\mathrm{d}}
-\newcommand{\mdifferential}{\differential^{\times}}
-\newcommand{\quotientMap}{\nu}
-\newcommand{\Lift}{\mathcal{L}}
-\newcommand{\uniformizer}{\varpi}
-\newcommand{\VolumeOf}{\operatorname{Vol}}
-
-\newcommand{\Erdelyi}{Erd{\'e}lyi}
-\newcommand{\Toth}{T{\'o}th}
-
-\newcommand{\parabolicSection}{\Phi^{\left(z_1, \dots, z_c\right)}}
-\newcommand{\intertwiningOperator}{M^{\left(z_1, \dots, z_c\right)}}
-\newcommand{\holomorphicRepresentation}{\depthZeroRepresentation^{\left(z_1, \dots, z_c\right)}}
-\newcommand{\WhittakerFunctional}[1]{\ell_{#1, \fieldCharacter}}
-\newcommand{\gWhittakerFunctional}[2]{\ell_{#1, #2}}
-\newcommand{\gSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}, \fieldCharacter_{\UnipotentRadicalForWss{#2}{#3}}}}
-\newcommand{\gShortSpehWhittakerFunctional}[3]{\ell_{\SpehRepresentation{#1}{#3}}}
 \newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
@@
 \newcommand{\dblLanglandsGammaFactorSpace}[4]{\gamma^{\mathrm{dbl}}_{#1}\left(#2 \times #3, #4\right)}
-\newcommand{\GKGaussSum}[3]{\mathcal{G}\left(#1 \times #2, #3\right)}
-\newcommand{\GKGaussSumScalar}[3]{\mathrm{G}\left(#1 \times #2, #3\right)}
-\newcommand{\fieldCharacterkc}[2]{\fieldCharacter_{\left({#2}^{#1}\right)}}
-\newcommand{\ExoticKloosterman}{\mathrm{Kl}}
 \newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
-\newcommand{\IrrCusp}{\Irr_{\mathrm{cusp}}}
-\newcommand{\convolutionWithCompactSupport}{\boldsymbol{\mathrm{R}}}
 \newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
-\newcommand{\artinScrier}{\operatorname{AS}}
-\newcommand{\KloostermanSumClassFunction}{\mathcal{K}}
 \newcommand{\IsometryGroup}{\mathrm{Isom}}
@@
 \newcommand{\LusztigSeries}[2]{\mathcal{E}\left(#1, (#2)\right)}
-\newcommand{\ToriDualToriIsomorphism}{\kappa}
 \newcommand{\characteristicPolynomial}{\operatorname{CharPoly}}
@@
 	\item \Cref{subsec:tori-isomorphism} and \Cref{subsec:gauss-sums-attached-to-semi-simple} should be removed and replaced with Calvin's arguments.
+    \item We might be able to include $SO_{odd}$ with $\Phi(g)$ the symmetric function in the eigenvalues of $g$ given by $\sum_{i=1}^{dim(V)} \chi(\Pi_{j \neq i}(\lambda_j-1))$.
 \end{enumerate}
@@
 Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
-In this case, we have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
+In this case, we have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$ \calvin{not sure I get what this $\Tilde{G}$ is.
+I thought it would just be $\widetilde{Isom(V)}$-or maybe its identity component.
+As it reads it sounds like you are supposed to fix sim and then define $\tilde{G}$.}.
 There are two cases here.
@@
 		and such that $\det g = \similitudeCharacter\left(g\right)^n$, where $\similitudeCharacter\left(g\right)$ is a non-zero scalar.
-		\item Non-split case:
+		\item Non-split case: \calvin{do we want to do even characteristic?
+Not sure what the classification of quadratic forms over even char are} for odd characteristic there is one non-split case when $V = X \oplus \mathbb{E} \oplus Y$ where $\mathbb{E}$ is the unique degree two extension of $\mathbb{F}$ with quadratic form $Nm_{\mathbb{E}:\mathbb{F}}$ \calvin{find someone to cite}
 	\end{enumerate}
@@
 
+\calvin{non split form of $SO(even)$, is the dual group itself?.
+The torus I think is $(\mathbb{F}_2)^{Nm=1} \times (\mathbb{F}^\times)^{dim -1}$.
+The Frobenius action on the characters is $(-1,1,1,1\hdots 1)$ and on $W$ its trivial}
+
 \subsubsection{Invariance under geometric conjugacy}
@@
 \begin{definition}
-	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
+	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
 \calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
@@
 
-The main result of this subsection is 
+The main result of this paper is 
 \begin{theorem}
-\label{thm:indep_geo_conj}
-	$\Phi_{\chi}(g)$ is a stable function.
+\label{thm:Phi_stable}
+	$\Phi_{\chi}(g)$ is a stable function. In other words $\dblVirtualJacobiSumScalar{\pi}{\chi}$ only depends on the Lusztig packet of $\pi$.
 	%Equivalently	$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
 \end{theorem}
+
+In this section we prove a slightly weaker result:
+\begin{lemma}
+\label{lem:indep_geo_conj}
+    $\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+\end{lemma}
 
@@
 
-The idea behind the proof of \Cref{thm:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
+The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
 \begin{center}
@@
 In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
-%The following computation in the proof of theorem \ref{thm:indep_geo_conj}.
+%The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
 
@@
 
-\begin{proof}[Proof of \Cref{thm:indep_geo_conj}] 
+\begin{proof}[Proof of \Cref{lem:indep_geo_conj}] 
 By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, it is enough to show that $g_{T}(\chi,\theta,\psi)$ and $\omega_{\pi}(-1) = \theta(-1)$ only depend of the geometric conjugacy of $(T,\theta)$.
@@
 
-\subsubsection{Proof of the main result}
+\calvin{start alternate writeup of section 3.4/3.4.1:}
+\subsection{Computation for Lusztig Series}
+The goal of this section is to prove \Cref{thm:Phi_stable} in particular that if $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
+\begin{theorem}
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
+\end{theorem}
+\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
+\subsubsection{Proof of \Cref{thm:Phi_stable}}
+Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
+First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
+\\
+
+\begin{proof}
+\calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
+\end{proof}
+
+By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
+$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_T\left(\theta, \fieldCharacter\right)$$
+is independent of geometric conjugacy class of $(T,\theta)$. Since we know the relevant equality for non cupsidal $\pi$, we get that
+$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_T\left(\theta, \fieldCharacter\right)$$.
+
+To finish we will show that all cuspidal $\pi$ in a Lusztig packet $\LusztigSeries{G}{s}$ have the same $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
+This will follow from
+
+\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
+	Let $\GroupExtension{G}$ have connected center.
+For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
+\end{proposition}
+
+While our groups $G$ may not have connected center, the function $\Phi(g)$ extends by zero to a class function on $\tilde{G}$ (see section 3.2) which does have connected center.
+Hence if a representation $\pi$ of $\tilde{G}$ deposes intorepresentations $\pi_1 \oplus \pi_2 \hdots \oplus \pi_r$ of $G$, $\dblGammaFactorSpace{\hermitianSpace}{\pi_1}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi_2}{\chi}{\fieldCharacter} =\hdots =\dblGammaFactorSpace{\hermitianSpace}{\pi_r}{\chi}{\fieldCharacter}$.
+
+\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
+	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
+	\begin{enumerate}
+		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
+	\end{enumerate}
+\end{proposition}
+\calvin{maybe say that cuspidal breaks into cuspidal pieces}
+So all the cuspidal $\pi$ in a Lusztig packet $\LusztigSeries{G}{s}$ are irreducible pieces in the restriction from $\GroupExtension{G}$ to $G$ of a single cuspidal representation $\tilde{\pi}$ of $\GroupExtension{G}$.
+
+\calvin{end alternate writeup}
+\subsubsection{Proof of the main result \calvin{\Cref{thm:Phi_stable}}}
 

### 2025-03-14 paper.tex
Adding comments

@@
 I thought it would just be $\widetilde{Isom(V)}$-or maybe its identity component.
-As it reads it sounds like you are supposed to fix sim and then define $\tilde{G}$.}.
-There are two cases here.
+As it reads it sounds like you are supposed to fix sim and then define $\tilde{G}$.} \elad{This is the definition used is Lusztig's paper for example.
+It is the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
+Generally speaking, we have the equality $\det g^2 = \similitudeCharacter\left(g\right)^{2n}$ (you can see this by taking the determinant of both sides).
+So the identity component is the matrices for which the ``square root'' of this equality holds, i.e.
+$\det g = \similitudeCharacter\left(g\right)^n$ and not $\det g = -\similitudeCharacter\left(g\right)^n$} There are two cases here.
 	\begin{enumerate}
@@
 		\item Non-split case: \calvin{do we want to do even characteristic?
-Not sure what the classification of quadratic forms over even char are} for odd characteristic there is one non-split case when $V = X \oplus \mathbb{E} \oplus Y$ where $\mathbb{E}$ is the unique degree two extension of $\mathbb{F}$ with quadratic form $Nm_{\mathbb{E}:\mathbb{F}}$ \calvin{find someone to cite}
+Not sure what the classification of quadratic forms over even char are} \elad{Let's not do characteristic two} for odd characteristic there is one non-split case when $V = X \oplus \mathbb{E} \oplus Y$ where $\mathbb{E}$ is the unique degree two extension of $\mathbb{F}$ with quadratic form $Nm_{\mathbb{E}:\mathbb{F}}$ \calvin{find someone to cite}
 	\end{enumerate}

### 2025-03-14 paper.tex
Trying to prove that the function after intertwining operator vanishes outside of the parabolic

@@
 \newcommand{\GroupExtension}[1]{\widetilde{#1}}
+\newcommand{\Center}{\mathrm{Z}}
 
@@
 where $\hermitianSpace' \subset \hermitianSpace$ is a non-degenerate subspace, orthogonal to $\xIsotropic$ and $\yIsotropic$.
-Let $P$ be the parabolic subgroup of $H$, consisting of all elements stabilizing the flag $$0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.$$
+Let $P = P_{H}\left(\mathcal{F}\right)$ be the parabolic subgroup of $H$, consisting of all elements stabilizing the flag \begin{equation}\label{eq:definition-of-flag-for-parabolic-subgroup}
+	\mathcal{F} \colon 0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.
+\end{equation}
 Let $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
@@
 	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
-	Hence, \begin{align*}
-		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
+	Hence, \begin{equation}
+		\begin{split}\label{eq:gamma-factor-multiplicativity-support-expression}
+			& \chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) \\
+			= & \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1}p - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		\end{split}
+	\end{equation}
 	Assume that $\chi \ne 1$.
@@
 	\begin{align*}
-		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
-	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
+		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} p - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Replace the sum over $p \in P$ by a sum over $l \in L$ and $u \in N$ where $p = lu$ and change variables $u \mapsto u^{-1}$ and $A \mapsto A u$. We arrive at the sum
 	\begin{align*}
-		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
-		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.
+		\sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{l \in L} \sum_{u \in U} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} l - u\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).
+	\end{align*}
+	Using the appendix, we arrive at the sum
+	\eqref{eq:gamma-factor-multiplicativity-support-expression} is given by
+	\begin{align*}
+		& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
+		& \times \sum_{A \in P_{\GL_{\quadraticExtension}\left(\mathcal{F}\right)}} \sum_{p \in P} \chi^{-1}\left(\detQuadratic A\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} p - \idmap_{\hermitianSpace} \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right),
+	\end{align*}
+	Where $P_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ is the parabolic subgroup of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ stabilizing the flag $\mathcal{F}$ from \eqref{eq:definition-of-flag-for-parabolic-subgroup}.
+By decomposing the sum over $A$ into a sum over its Levi part and its unipotent radical, we see that the inner sum over the unipotent radical will vanish unless $x^{-1} p - \idmap_{\hermitianSpace}$ is an upper triangular matrix, which implies that $x \in P \cap G$.
 
@@
 \end{proof}
+\begin{remark}
+	A proof similar to the second part of our proof is given in \cite{Chang1997}. However, the proof in \cite{Chang1997} only works if the parabolically induced representation is irreducible.
+\end{remark}
 
@@
 \appendix
+\section{Unipotent averaging}
+
+Choose bases $e_1,\dots,e_k$ for $\xIsotropic$ and $f_1,\dots,f_k$ for $\yIsotropic$ that are dual, i.e., $\innerproduct{e_i}{f_j} = \delta_{ij}$, where $\delta_{ij}$ is Kronecker's delta function, and choose a basis $v'_1, \dots, v'_{r}$ for $\hermitianSpace'$.
+Then with respect to the basis $e_1,\dots,e_k,v_1',\dots,v_r',f_k,f_{k-1},\dots,f_1$, elements in $N$ can be represented in matrix form $$\begin{pmatrix}
+	\IdentityMatrix{k} & X & Z\\
+	& \IdentityMatrix{r} & Y\\
+	& & \IdentityMatrix{k}
+\end{pmatrix},$$
+where $X,Y$ and $Z$ are matrices satisfying certain relations.
+Under this realization, the center $\Center\left(N\right)$ of $N$ corresponds to matrices of the form \begin{equation}\label{eq:center-matrix-representation}
+	\begin{pmatrix}
+		\IdentityMatrix{k} & 0 & Z\\
+		& \IdentityMatrix{r} & 0\\
+		& & \IdentityMatrix{k}
+	\end{pmatrix},
+\end{equation}
+where $Z$ is a certain type of matrix: it is ``-$\epsilon$ symmetric'', that is, it satisfies $$Z = -\epsilon w_k \involution{\left(\transpose{Z}\right)} w_k,$$
+where $$w_k = \begin{pmatrix}
+	& & & 1\\
+	& & 1\\
+	& \iddots\\
+	1
+\end{pmatrix} \in \GL_k\left(\finiteField\right)$$ is the long Weyl element.
+
+The following sum appears as an inner sum in \eqref{TODO}:
+\begin{equation}\label{eq:sum-that-vanishes-unless-A-is-upper-triangular}
+	\sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Au\right)\right) = \sum_{u \in N \slash \Center\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Au\right)\right) \sum_{z \in \Center\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Az\right)\right).
+\end{equation}
+Consider the inner sum 
+\begin{equation*}
+	\sum_{u \in Z\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(-Az\right)\right).
+\end{equation*}
+This sum vanishes unless the matrix representation of $A$ is of the form $$\begin{pmatrix}
+	a_{k \times k} & a'_{k \times r} & a''_{k \times k} \\
+	b_{r \times k} & b'_{r \times r} & b''_{r \times k}\\
+	c_{k \times k} & c'_{k \times r} & c''_{k \times k}
+\end{pmatrix},$$
+where $c_{k \times k}$ is ``$\epsilon$-symmetric'', that is, it satisfies \begin{equation}\label{eq:epsilon-symmetric-relation}
+	c_{k \times k} = \epsilon w_k \involution{\left(\transpose{c_{k \times k}}\right)} w_k.
+\end{equation}
+Let us denote by $R$ the subset of $\EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ consisting of elements such that their matrix representation satisfies the relation \eqref{eq:epsilon-symmetric-relation}.
+Then we may replace the sum
+$$\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} l - u\right)\right)\right)$$ with
+$$\sizeof{\Center\left(N\right)} \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R} \chi^{-1}\left(\detQuadratic A\right) \sum_{u \in N \slash \Center\left(N\right)} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(x^{-1} l - u\right)\right)\right).$$
+Let $N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ be the unipotent radical of the parabolic subgroup $P_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ stabilizing the flag $\mathcal{F}$.
+Its center $\Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$ consists of linear maps whose matrix representation is of the form \eqref{eq:center-matrix-representation}, where $Z$ is an arbitrary matrix.
+
+We notice the following observation: if $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R$, then for any $z \in \Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$, we have $zA \in \GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R$.
+This is because the left action of $\Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$ does not change the last $k$ rows of $A$.
+It follows that $\GL_{\quadraticExtension}\left(\hermitianSpace\right) \cap R$ is a union of left (or right) cosets of $\Center\left(N_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)\right)$.
+
+$P_{\GL_{\quadraticExtension}\left(\hermitianSpace\right)}\left(\mathcal{F}\right)$ is the parabolic subgroup of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ that stabilizes the flag $\mathcal{F}$ from \eqref{eq:definition-of-flag-for-parabolic-subgroup}.
+
 \section{Evaluation of norm one exponential sums}

### 2025-03-14 paper.tex
Calvin update

--- 2025-03-14 paper.tex
@@
 	\item \Cref{subsec:tori-isomorphism} and \Cref{subsec:gauss-sums-attached-to-semi-simple} should be removed and replaced with Calvin's arguments.
+    \item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}
     \item We might be able to include $SO_{odd}$ with $\Phi(g)$ the symmetric function in the eigenvalues of $g$ given by $\sum_{i=1}^{dim(V)} \chi(\Pi_{j \neq i}(\lambda_j-1))$.
+
 \end{enumerate}
@@
 \begin{definition}
-	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
+	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
 \calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
@@
 \end{theorem}
-
+In the $\GL_n$ case this follows from \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
 In this section we prove a slightly weaker result:
+
 \begin{lemma}
@@
 \end{lemma}
-
-In the $\GL_n$ case this follows from \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
 
@@
 \subsection{Computation for Lusztig Series}
-The goal of this section is to prove \Cref{thm:Phi_stable} in particular that if $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
+The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
 \begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
 $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
@@
 \calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
-\subsubsection{Proof of \Cref{thm:Phi_stable}}
+\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
 Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
@@
 \calvin{end alternate writeup}
+\calvin{start alternate writeup 2 of section 3.4/3.4.1}
+\subsection{Computation for Lusztig Series}
+The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
+\begin{theorem}
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
+\end{theorem}
+\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
+\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
+We instead prove a version of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$ (see section 3.2) of $G$:
+\begin{theorem}
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} Extend $\Phi_{\chi}$ by zero to $\GroupExtension{G}$.
+If $c_{\pi}$ is nonzero in the virtual representation $R_{T}(\theta) = \sum c_{\pi} \pi$ of $\GroupExtension{G}$ then
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
+where the doubling factor is defined by
+\[
+\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} := \omega_{\pi}(-1)\frac{\sum_{g \in \GroupExtension{G}}\pi(g)\Phi_{\chi}(g)}{\sqrt{|g|}c_V(\chi,\pi)}
+\]
+\end{theorem}
+Any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
+\[
+    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
+\]
+
+The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only dependeing on $s$.
+Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions}.
+
+\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
+	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
+	\begin{enumerate}
+		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
+	\end{enumerate}
+\end{proposition}
+
+Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
+First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for all Levi factors.
+\\
+
+\begin{proof}
+\calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
+\end{proof}
+
+By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
+$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
+is independent of geometric conjugacy class of $(T \cap G,\theta|_{T \cap G})$ he. Since we know the relevant equality for non cupsidal $\pi$, we get that
+$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
+
+But in fact there is only one cuspidal $\pi$, hence the above equation determines 
+\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
+	Let $\GroupExtension{G}$ have connected center.
+For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
+\end{proposition}
+
+While our groups $G$ may not have connected center, the function $\Phi(g)$ extends by zero to a class function on $\tilde{G}$ (see section 3.2) which does have connected center.
+Hence if a representation $\pi$ of $\tilde{G}$ deposes intorepresentations $\pi_1 \oplus \pi_2 \hdots \oplus \pi_r$ of $G$, $\dblGammaFactorSpace{\hermitianSpace}{\pi_1}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi_2}{\chi}{\fieldCharacter} =\hdots =\dblGammaFactorSpace{\hermitianSpace}{\pi_r}{\chi}{\fieldCharacter}$.
+
+\calvin{maybe say that cuspidal breaks into cuspidal pieces}
+So all the cuspidal $\pi$ in a Lusztig packet $\LusztigSeries{G}{s}$ are irreducible pieces in the restriction from $\GroupExtension{G}$ to $G$ of a single cuspidal representation $\tilde{\pi}$ of $\GroupExtension{G}$.
+
+\calvin{end alternate writeup 2}
+
 \subsubsection{Proof of the main result \calvin{\Cref{thm:Phi_stable}}}

### 2025-03-19 paper.tex
Sync with overleaf

@@
 \]
+\elad{Note that on page 6 we already defined $\dblJacobiSum{\pi}{\chi}$ by only summing on the $G$ points. Same for $\dblJacobiSumScalar{F}{\chi}$ on page 9.}
 \end{theorem}
@@
 By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
-$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
-is independent of geometric conjugacy class of $(T \cap G,\theta|_{T \cap G})$ he. Since we know the relevant equality for non cupsidal $\pi$, we get that
+$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
+Since we know the relevant equality for non cupsidal $\pi$, we get that
 $$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
 
-But in fact there is only one cuspidal $\pi$, hence the above equation determines 
+But it is well known that there is only one cuspidal $\pi$:
 \begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
@@
 
-While our groups $G$ may not have connected center, the function $\Phi(g)$ extends by zero to a class function on $\tilde{G}$ (see section 3.2) which does have connected center.
-Hence if a representation $\pi$ of $\tilde{G}$ deposes intorepresentations $\pi_1 \oplus \pi_2 \hdots \oplus \pi_r$ of $G$, $\dblGammaFactorSpace{\hermitianSpace}{\pi_1}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi_2}{\chi}{\fieldCharacter} =\hdots =\dblGammaFactorSpace{\hermitianSpace}{\pi_r}{\chi}{\fieldCharacter}$.
-
-\calvin{maybe say that cuspidal breaks into cuspidal pieces}
-So all the cuspidal $\pi$ in a Lusztig packet $\LusztigSeries{G}{s}$ are irreducible pieces in the restriction from $\GroupExtension{G}$ to $G$ of a single cuspidal representation $\tilde{\pi}$ of $\GroupExtension{G}$.
+So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} is complete.
 

### 2025-03-19 paper.tex
Some modifications

@@
 
-\calvin{I kinda prefer the normalization where we divide by $|G|$. I guess both for little and upper $G$. That way it is the honest product of characters in the representation ring.}
-
 Let us realize $H$ as the fixed points of the Frobenius map $\Frobenius$ acting on a connected reductive algebraic group $\algebraicGroup{H}$.
@@
 \subsubsection{Geometric Conjugacy and Lusztig Series}
-(Following Chapter 13 of \cite{DigneMichel2020})
 Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a torus $\algebraicGroup{T}$ defined over $\finiteField$.
@@
 for large enough $n$, where $\aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$ is the torus norm map.
-This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ \cite[Corollary 13.9]{DigneMichel2020}.
+This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
 By composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
@@
 
-    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta}), (s_{T,\theta'})$ are equal.
-
-    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of (equivalence classes of) the irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
+    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta})$ and $(s_{T,\theta'})$ are equal.
+
+    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of the (equivalence classes of the) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
 \end{definition}

### 2025-03-19 cleanup.tex
Trying to cleanup Calvin's stuff

--- 2025-03-19 paper.tex
@@
 \newcommand{\GSp}{\mathrm{GSp}}
+\newcommand{\GSpin}{\mathrm{GSpin}}
 \newcommand{\UnitaryGroup}{\mathrm{U}}
@@
  Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
- $Sp(2n)$ & $(\multiplicativegroup{\finiteField})^n$ & 1 & 1 &$SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^n$\\  
- $GSp(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
- $SO(2n)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$SO(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
- $GO(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
- $SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
- $GO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ 
-  $U(n)$ & $(\NormOneGroup{2})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{2})^{n}$ 
+ $\algebraicGroup{\GSp}_{2n}$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &$\algebraicGroup{\GSpin}_{2n+1}$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
+ $\algebraicGroup{\GSO}^{\pm}_{2n}$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 & $\algebraicGroup{\GSpin}^{\pm}_{2n}$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ $\algebraicGroup{\SO}_{2n+1}$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &$\algebraicGroup{\Sp}_{2n}$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
+  $\algebraicGroup{\UnitaryGroup}_n$ & $(\NormOneGroup{2})^{n}$ & -1 & 1 & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\NormOneGroup{2})^{n}$ 
 \end{tabular}
@@
 
-\calvin{non split form of $SO(even)$, is the dual group itself?.
-The torus I think is $(\mathbb{F}_2)^{Nm=1} \times (\mathbb{F}^\times)^{dim -1}$.
-The Frobenius action on the characters is $(-1,1,1,1\hdots 1)$ and on $W$ its trivial}
-
 \subsubsection{Invariance under geometric conjugacy}
-\calvin{todo:type in some motivation for class functions whose product doesn't depend on geometric conjugacy, gamma functions whatever}.
-
-\begin{definition}
-	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
-\calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
-COMPLEXES has this definition}
-\end{definition}
-
-A basic example of a class function which doesn't depend of geometric conjugacy 
-\begin{proposition}[FIND SOMEWHERE TO CITE or put in appendix]
-\label{prop:central_char}
-    Any function $f$ supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$ is a stable function. 
-\end{proposition}
-\begin{proof}
-\calvin{can probably put this proof in an appendix}
-Note it is enough to prove the statement for $f = 1_z$ an indicator function of an element $z \in \algebraicGroup{Z}(\mathbb{F})$. The he proof follows from the two claims:\\
-Claim 1: $z$ acts by the scalar $\theta(z)$ in the virtual representation $R_{T,\theta}$.\\
-Claim 2: If $(T,\theta),(T',\theta')$ are geometrically conjugate then $\theta|_{\algebraicGroup{Z}(\mathbb{F})} = \theta'_{\algebraicGroup{Z}(\mathbb{F})}$.\\
-Proof of claim 1: The representation $R_T^G(\theta)$ is equal to $M \otimes_{\mathbb{C}[T]} \theta$ where $M$ is the virtual module corresponding to the Euler characteristic of cohomology on $X$ which as a variety is a subvariety of $\algebraicGroup{G}$ with the $G \times T$ action via $(g,\ell).x = gx\ell$.
-The center $\algebraicGroup{Z}$ then commutes across $X$ so the action of $(z,1)$ equals the action of $(1,z)$.
-The result is on the $\theta$ component of $M$, $z$ acts by $\theta(z)$.\\
-Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}_n)$ \elad{Here you mean $\algebraicGroup{G}\left(\finiteFieldExtension{n}\right)$?}\calvin{oops yes} such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
-So when restricted to the center, $\theta \circ Nm = \theta' \circ Nm$.
-Since $Nm$ is surjective onto the $\mathbb{F}$-points, $\theta|_{\algebraicGroup{Z}(\mathbb{F})} = \theta'|_{\algebraicGroup{Z}(\mathbb{F})}$.
-\end{proof}
-
-The main result of this paper is 
-\begin{theorem}
-\label{thm:Phi_stable}
-	$\Phi_{\chi}(g)$ is a stable function. In other words $\dblVirtualJacobiSumScalar{\pi}{\chi}$ only depends on the Lusztig packet of $\pi$.
-	%Equivalently	$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
-\end{theorem}
-In the $\GL_n$ case this follows from \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
-In this section we prove a slightly weaker result:
-
-\begin{lemma}
-\label{lem:indep_geo_conj}
-    $\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+The goal of this section is to prove the following result.
+
+\begin{lemma}\label{lem:indep_geo_conj}If $\left(T, \theta\right)$ and $\left(T',\theta'\right)$ are geometrically conjugate, then
+    $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T, \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
 \end{lemma}
@@
 	\]
-	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
+	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$.
 	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
@@
  Group & Dual group representations $\rho$ \\ 
- $Sp(2n)$ &$SO(2n+1) \to \GL(2n+1)$\\  
- $GSp(2n)$  &$GSpin(2n+1) \to \GL(2n+1)$ \\
- $SO(2n)$ &$SO(2n) \to \GL(2n)$ \\
- $GO(2n)$ & ? \\
- $SO(2n+1)$ &$Sp(2n) \to \GL(2n)$ \\
- $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to \GL(2n)$  
+ $\GSp_{2n}$  & $\GSpin_{2n+1} \to \GL_{2n+1}$ \\
+ $\GSO^{\pm}_{2n}$ & $\GSpin_{2n}^{\pm} \to \GL_{2n}$ \\
+ $\SO_{2n+1}$ &$\Sp_{2n} \to \GL_{2n}$ \\
+ $\UnitaryGroup_n$  & $\UnitaryGroup_n \to \GL_{2n}$  
 \end{tabular}

### 2025-03-20 cleanup.tex
Some improvements

@@
 
-    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta})$ and $(s_{T,\theta'})$ are equal.
+    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{T,\theta})$ and $(s_{T,\theta'})$ are equal.
 
@@
  $\SO_{2n+1}$ &$\Sp_{2n} \to \GL_{2n}$ \\
- $\UnitaryGroup_n$  & $\UnitaryGroup_n \to \GL_{2n}$  
+ $\UnitaryGroup_n$  & $\UnitaryGroup_n \to \GL_{n}$  
 \end{tabular}
@@
 
-In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
+In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus-character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
@@
 \label{lem:cochar_computation}
-    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
-We will consider two different Frobeinus actions on these characters:
+    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\tilde{\algebraicGroup{T}}_{\GL_{2n}})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$. 
     \begin{enumerate}
-        \item When $\Frobenius$ acts by trivially on both, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
-        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
+        \item Suppose that $\Frobenius$ acts by trivially on both the domain and the range.
+Then $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
+        \item Suppose that $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
             0 & 1 \\
-            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
+            1 & 0\end{pmatrix}$ on the codomain. Then $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ for $\theta'(t) = \theta(t^{1-q^n})$.
     \end{enumerate}
@@
 \begin{proof}
-Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
-\[
-    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
-\]
-Thus the result follows from the computations:
+Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the prescribed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ by the formula.\[
+    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(\aFieldNorm_{\algebraicGroup{T}(\finiteField_m):\algebraicGroup{T}(\finiteField)}(y(\zeta_m))),
+\]
+for all $y \in X_{\ast}\left(\algebraicGroup{T}\right)$.
+
+Thus the result follows from the following computations.
 \begin{enumerate}
-	\item \begin{align*}
+	\item Let $\left(y_1, y_2\right) \in X_{\ast}\left(\GL_n\right) \times X_{\ast}\left(\GL_n\right)$. Then  \begin{align*}
 		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\

### 2025-03-20 paper.tex
Adding the 1+ case

@@
 
+\begin{remark}
+	Changing variables $x \mapsto \to x$, we have that \begin{align*}
+		& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+				x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
+			=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+	\end{align*}
+\end{remark}
+
 \subsubsection{Elliptic torus computation}
@@
 To summarize, we have
-$$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),$$
+\begin{align*}
+	& \sum_{\substack{x \in \NormOneGroup{2m}\\
+			x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) \\
+		=& q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),
+\end{align*}
 where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
@@
 		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+\begin{remark}
+	Changing variables $x \mapsto -x$, we have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
+			x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+\end{remark}
 

### 2025-03-20 paper.tex
Some cleanup

@@
 \[
-    \exp(\langle x_{T,\theta},y\rangle) = \theta(\aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(y(\zeta_n)))
+    \exp(\langle x_{T,\theta},y\rangle) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
 \]
-for large enough $n$, where $\aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$ is the torus norm map.
+for large enough $n$, where $\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$ is the torus norm map.
 This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
@@
 
-\begin{definition}
     Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(T,\theta)$ by $(s_{T,\theta})$.
@@
 
-    The pairs $(T',\theta'),(T,\theta)$ are said to be \emph{geometrically conjugate} is the geometric conjugacy classes $(s_{T,\theta})$ and $(s_{T,\theta'})$ are equal.
-
-    The \emph{Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of the (equivalence classes of the) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
-\end{definition}
+We say that the pairs $(T,\theta)$ and $(T',\theta')$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{T,\theta})$ and $(s_{T',\theta'})$ are equal.
+This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
+
+The \emph{geometric Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
 
@@
 
+Let $f \colon \algebraicGroup{G}\left(\finiteField\right) \to \cComplex$ be a class function.
+Then by Schur's lemma for any irreducible representation $\pi$, there exists $\gamma_{f} \in \cComplex$ such that $$\sum_{g \in G} f(g)\pi(g) = \gamma_{f}\left(\pi\right) \cdot \idmap_{\pi}.$$
+
 \begin{definition}
-	A \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ is a class function $f$ such that $\sum_{g \in G} f(g)\pi(g)$ is a scalar which only depends on the Lusztig packet for $\pi$.
-\calvin{FUNCTORIAL TRANSFER FOR REDUCTIVE GROUPS AND CENTRAL
-COMPLEXES has this definition}
+	We say that  $f \colon \algebraicGroup{G}\left(\finiteField\right) \to \cComplex$ is a \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ if it satisfies the following property: if $\pi$ and $\pi'$ are irreducible representations of $\algebraicGroup{G}(\finiteField)$ such that lie in the same geometric Lusztig series, then $$\gamma_{f}\left(\pi\right) = \gamma_{f}\left(\pi'\right).$$
+(See also \cite[Section 4]{LaumonLetellier2023} and \cite[Section 4.1]{ChenBhattacharya2024})
 	\end{definition}
 
-A basic example of a class function which doesn't depend of geometric conjugacy 
-\begin{proposition}[FIND SOMEWHERE TO CITE or put in appendix]
+Here is a basic example of a stable class function.
+\begin{proposition}
 \label{prop:central_char}
-    Any function $f$ supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$ is a stable function. 
+    If $f \colon \algebraicGroup{G}\left(\finiteField\right) \to \cComplex$ is supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$, then $f$ is a stable function.
 \end{proposition}
 \begin{proof}
-\calvin{can probably put this proof in an appendix}
-Note it is enough to prove the statement for $f = 1_z$ an indicator function of an element $z \in \algebraicGroup{Z}(\mathbb{F})$. The he proof follows from the two claims:\\
-Claim 1: $z$ acts by the scalar $\theta(z)$ in the virtual representation $R_{T,\theta}$.\\
-Claim 2: If $(T,\theta),(T',\theta')$ are geometrically conjugate then $\theta|_{\algebraicGroup{Z}(\mathbb{F})} = \theta'_{\algebraicGroup{Z}(\mathbb{F})}$.\\
-Proof of claim 1: The representation $R_T^G(\theta)$ is equal to $M \otimes_{\mathbb{C}[T]} \theta$ where $M$ is the virtual module corresponding to the Euler characteristic of cohomology on $X$ which as a variety is a subvariety of $\algebraicGroup{G}$ with the $G \times T$ action via $(g,\ell).x = gx\ell$.
-The center $\algebraicGroup{Z}$ then commutes across $X$ so the action of $(z,1)$ equals the action of $(1,z)$.
-The result is on the $\theta$ component of $M$, $z$ acts by $\theta(z)$.\\
-Proof of claim 2: Geometric conjugacy is equivalent to for large enough $n$, there exists $g \in \algebraicGroup{G}(\mathbb{F}_n)$ \elad{Here you mean $\algebraicGroup{G}\left(\finiteFieldExtension{n}\right)$?}\calvin{oops yes} such that $g\algebraicGroup{T}g^{-1} = \algebraicGroup{T}'$ and $g(\theta \circ Nm) g^{-1} = (\theta' \circ Nm)$.
-So when restricted to the center, $\theta \circ Nm = \theta' \circ Nm$.
-Since $Nm$ is surjective onto the $\mathbb{F}$-points, $\theta|_{\algebraicGroup{Z}(\mathbb{F})} = \theta'|_{\algebraicGroup{Z}(\mathbb{F})}$.
+By \cite[Lemma 2.2]{Malle2007}, if $\pi$ and $\pi'$ lie in the same geometric Lusztig series, then they have the same central character. The result now immediately follows.
 \end{proof}
@@
 \label{thm:Phi_stable}
-	$\Phi_{\chi}(g)$ is a stable function. In other words $\dblVirtualJacobiSumScalar{\pi}{\chi}$ only depends on the Lusztig packet of $\pi$.
-	%Equivalently	$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+	The assignment $H \to \cComplex$ given by $$h \mapsto \begin{dcases}
+		\chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - h\right)\right) & h \in G \text{ and } \detQuadratic\left(\idmap_{\hermitianSpace} - h\right) \ne 0,\\
+		0 & \text{otherwise.}
+	\end{dcases}$$ is a stable function. Equivalently, the assignment $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ is constant on geometric Lusztig series.
 \end{theorem}
@@
 \label{lem:indep_geo_conj}
-    $\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)}$ only depends on the geometric conjugacy class of $(T,\theta)$.
+    If $(T,\theta)$ and $(T', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T,\theta}(1)}.$$
 \end{lemma}
@@
 
-\subsection{Computation for Lusztig series}
+\subsection{Computation for geometric Lusztig series}
 

### 2025-03-20 paper.tex
Typo

@@
 \begin{remark}
-	Changing variables $x \mapsto \to x$, we have that \begin{align*}
+	Changing variables $x \mapsto -x$, we have that \begin{align*}
 		& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\

### 2025-03-20 paper.tex
Typo

@@
 \label{lem:indep_geo_conj}
-    If $(T,\theta)$ and $(T', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T,\theta}(1)}.$$
+    If $(T,\theta)$ and $(T', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
 \end{lemma}

### 2025-03-20 paper.tex
Torus character

@@
 
-For a torus theta pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to \GL_n$.
+For a torus character pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to \GL_n$.
 Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset G^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \GL_n$ which contains $\rho(\algebraicGroup{T}^*)$.
@@
 
-In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus theta pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
+In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.

### 2025-03-20 paper.tex
Rearrange

@@
 \end{equation}
-with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}(\finiteFieldExtension{n}):\algebraicGroup{T}(\finiteField)}(y(\zeta_n))$
+with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n))$
 for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
+Here, $$\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$$ is the torus norm map.
 
@@
 \]
-for large enough $n$, where $\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$ is the torus norm map.
+for large enough $n$.
 This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.

### 2025-03-20 paper.tex
Macros

@@
 \newcommand{\FrobeniusFixedPoints}[2][\Frobenius]{\algebraicGroup{#2}^{#1}}
+\newcommand{\CharacterLattice}[1]{X^{\ast}\left(#1\right)}
+\newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}
 
@@
 \[
-    (X^*(\algebraicGroup{T}^*),\Phi_{\algebraicGroup{T}^*},X_*(\algebraicGroup{T}^*),\Phi_{\algebraicGroup{T}^*}^\vee) \cong (X_*(\algebraicGroup{T}),\Phi_{\algebraicGroup{T}}^\vee,X^*(\algebraicGroup{T}),\Phi_{\algebraicGroup{T}})
+    (\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
 \]
-such that the isomorphism respects the Frobenius action on $X^*$ and $X_*$.
+such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.
 
 Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
-We get an isomorphism
+By \cite[Proposition 13.7 (ii)]{DigneMichel2020}, we have an exact sequence
 \begin{equation}
 \label{eq:DL}
-\xymatrix{0 \ar[r] & X_*(\algebraicGroup{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & X_*(\algebraicGroup{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T}(\algebraicClosure{\finiteField}) \ar[r] & 0}
+\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T}(\algebraicClosure{\finiteField}) \ar[r] & 0}
 \end{equation}
@@
 
-Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
 \[
@@
 for large enough $n$.
-This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $X^*(\algebraicGroup{T}')_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
+This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
 By composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
@@
     Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(T,\theta)$ by $(s_{T,\theta})$.
-Similarly denote the Frobenius stable Weyl group element of $X^*(\algebraicGroup{T})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta}).$
+Similarly, denote the Frobenius stable Weyl group element of $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta}).$
 

### 2025-03-20 paper.tex
Making all groups algebraic

@@
 
-\title{On exponential sums arising from the classical doubling method}
+\title[Doubling method exponential sums]{On exponential sums arising from the classical doubling method}
 
@@
 \subsubsection{Geometric Conjugacy and Lusztig Series}
-Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a torus $\algebraicGroup{T}$ defined over $\finiteField$.
+Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal torus $\algebraicGroup{T}$ defined over $\finiteField$.
 The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
@@
 
-Hence for a torus character pair $(T,\theta)$ for $G$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W$ in the twisted Weyl group conjugacy class corresponding to $T$) stable element $x_{T,\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character.
+By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{T,\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
 \[
@@
 This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
-By composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $G^*$.
-
-    Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(T,\theta)$ by $(s_{T,\theta})$.
-Similarly, denote the Frobenius stable Weyl group element of $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(T,\theta)$ by $(x_{T,\theta}).$
-
-We say that the pairs $(T,\theta)$ and $(T',\theta')$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{T,\theta})$ and $(s_{T',\theta'})$ are equal.
+By composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
+
+    Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
+Similarly, denote the Frobenius stable Weyl group element of $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
+
+We say that the torus character pairs $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ for $\algebraicGroup{G}$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{\algebraicGroup{T},\theta})$ and $(s_{\algebraicGroup{T}',\theta'})$ are equal.
 This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
 
-The \emph{geometric Lusztig series} $\LusztigSeries{G}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
+The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
 
@@
 
-Let $f \colon \algebraicGroup{G}\left(\finiteField\right) \to \cComplex$ be a class function.
-Then by Schur's lemma for any irreducible representation $\pi$, there exists $\gamma_{f} \in \cComplex$ such that $$\sum_{g \in G} f(g)\pi(g) = \gamma_{f}\left(\pi\right) \cdot \idmap_{\pi}.$$
+Let $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ be a class function.
+Then by Schur's lemma for any irreducible representation $\pi$, there exists $\gamma_{f}\left(\pi\right) \in \cComplex$ such that $$\sum_{g \in G} f(g)\pi(g) = \gamma_{f}\left(\pi\right) \cdot \idmap_{\pi}.$$
 
 \begin{definition}
-	We say that  $f \colon \algebraicGroup{G}\left(\finiteField\right) \to \cComplex$ is a \emph{stable function} on $\algebraicGroup{G}(\finiteField)$ if it satisfies the following property: if $\pi$ and $\pi'$ are irreducible representations of $\algebraicGroup{G}(\finiteField)$ such that lie in the same geometric Lusztig series, then $$\gamma_{f}\left(\pi\right) = \gamma_{f}\left(\pi'\right).$$
+	We say that  $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ is a \emph{stable function} on $\algebraicGroup{G}^{\Frobenius}$ if it satisfies the following property: if $\pi$ and $\pi'$ are irreducible representations of $\algebraicGroup{G}^{\Frobenius}$ such that lie in the same geometric Lusztig series, then $$\gamma_{f}\left(\pi\right) = \gamma_{f}\left(\pi'\right).$$
 (See also \cite[Section 4]{LaumonLetellier2023} and \cite[Section 4.1]{ChenBhattacharya2024})
@@
 \label{prop:central_char}
-    If $f \colon \algebraicGroup{G}\left(\finiteField\right) \to \cComplex$ is supported on the center $\algebraicGroup{Z}(\mathbb{F})$ of $\algebraicGroup{G}(\finiteField)$, then $f$ is a stable function.
+    If $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ is supported on the center $\algebraicGroup{Z}^{\Frobenius}$ of $\algebraicGroup{G}^{\Frobenius}$, then $f$ is a stable function.
 \end{proposition}
@@
 \label{lem:indep_geo_conj}
-    If $(T,\theta)$ and $(T', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
+    If $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
 \end{lemma}
 
-For a torus character pair $(T,\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset G^*$ and an embedding $\rho:G^* \to \GL_n$.
-Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset G^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \GL_n$ which contains $\rho(\algebraicGroup{T}^*)$.
-Let $\tilde{T}$ be the torus of $\GL_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{T},\tilde{\theta}})$.
+For a torus character pair $(\algebraicGroup{T},\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset \algebraicGroup{G}^*$ and an embedding $\rho:\algebraicGroup{G}^* \to \algebraicGroup{\GL}_n$.
+Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$ which contains $\rho(\algebraicGroup{T}^*)$.
+Let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 Define
 \[
-    g_{T,\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
-    \tilde{T}}}\sum_{t\in \tilde{T}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
+    g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
+    \tilde{\algebraicGroup{T}}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
 \]
@@
 \label{cor:geoconj}
-Suppose that $(T,\theta)$ and $(T',\theta')$ are geometrically conjugate torus character pairs in $G$. Then $g_{T,\rho}(\theta,\psi,\chi) = g_{T',\rho}(\theta',\psi,\chi)$.
+Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$.
+Then $g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
 \end{corollary}

### 2025-03-20 paper.tex
Typo

@@
 	Changing variables $x \mapsto -x$, we have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
 \end{remark}

### 2025-03-20 paper.tex
Writing about the different groups

@@
 \section{Notation}
-Let $\finiteField$ be a finite field with $q$ elements, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+Let $\finiteField$ be a finite field with $q$ elements, where $2 \nmid q$, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
 Fix an algebraic closure $\algebraicClosure{\finiteField}$ of $\finiteField$.
@@
 \begin{enumerate}
-	\item (Even special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
+	\item (Special even orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
 Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
-In this case, we have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$ \calvin{not sure I get what this $\Tilde{G}$ is.
-I thought it would just be $\widetilde{Isom(V)}$-or maybe its identity component.
-As it reads it sounds like you are supposed to fix sim and then define $\tilde{G}$.} \elad{This is the definition used is Lusztig's paper for example.
-It is the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
-Generally speaking, we have the equality $\det g^2 = \similitudeCharacter\left(g\right)^{2n}$ (you can see this by taking the determinant of both sides).
-So the identity component is the matrices for which the ``square root'' of this equality holds, i.e.
-$\det g = \similitudeCharacter\left(g\right)^n$ and not $\det g = -\similitudeCharacter\left(g\right)^n$} There are two cases here.
+It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$.
+Similarly, every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$.
+In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
+There are two cases here.
 	\begin{enumerate}
 		\item Split case: in this case, we can write $\hermitianSpace = \xIsotropic \oplus \yIsotropic$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
-In this case, we have that $G$ is isomorphic to the subgroup $\SO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of elements $g$ satisfying $$g \cdot w_{2n} \cdot \transpose{g} = w_{2n}$$ and $\det g = 1$.
-		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that $$g \cdot w_{2n} \cdot \transpose{g} = \similitudeCharacter\left(g\right) w_{2n},$$
-		and such that $\det g = \similitudeCharacter\left(g\right)^n$, where $\similitudeCharacter\left(g\right)$ is a non-zero scalar.
-		\item Non-split case: \calvin{do we want to do even characteristic?
-Not sure what the classification of quadratic forms over even char are} \elad{Let's not do characteristic two} for odd characteristic there is one non-split case when $V = X \oplus \mathbb{E} \oplus Y$ where $\mathbb{E}$ is the unique degree two extension of $\mathbb{F}$ with quadratic form $Nm_{\mathbb{E}:\mathbb{F}}$ \calvin{find someone to cite}
+In this case, we have that $G$ is isomorphic to $\SO^{+}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid g \cdot w_{2n} \cdot \transpose{g} = w_{2n},\,\, \det g = 1\right\}.$$
+		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{+}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid g \cdot w_{2n} \cdot \transpose{g} = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
+		\item Non-split case: In this case, there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
+		where $\xIsotropic$ and $\yIsotropic$ are totally isotropic spaces in duality and $\hermitianSpace'$ is an antisotropic space (that is, for any $0 \ne v' \in \hermitianSpace'$, we have $\innerproduct{v'}{v'} \ne 0$) of dimension 2.
+Let $d$ be an element of $\multiplicativegroup{\finiteField}$ that is not a square.
+Denote $$B_{n,d} = \begin{pmatrix}
+			\IdentityMatrix{n-1}\\
+			& & 1 &\\
+			& -d & &\\
+			& & & \IdentityMatrix{n-1}
+		\end{pmatrix} \cdot w_{2n}.$$
+		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid g \cdot B_{n,d} \cdot \transpose{g} = B_{n,d},\,\, \det g = 1\right\}.$$
+		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{-}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid g \cdot B_{n,d} \cdot \transpose{g} = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
 	\end{enumerate}
 	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
-In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to subgroup $\Sp_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of all elements $g$ satisfying $$g \cdot \begin{pmatrix}
+In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid g \cdot \begin{pmatrix}
 		& w_n\\
@@
 		-w_n
-	\end{pmatrix}.$$ The group $\GroupExtension{G}$ is is isomorphic to the subgroup $\GSp_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$ consisting of all elements $g$ such that $$g \cdot \begin{pmatrix}
+	\end{pmatrix}\right\}.$$ The group $\GroupExtension{G}$ is isomorphic to the group $\GSp_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSp}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid g \cdot \begin{pmatrix}
 	& w_n\\
 	-w_n
-	\end{pmatrix} \cdot \transpose{g} = \similitudeCharacter\left(g\right) \begin{pmatrix}
+	\end{pmatrix} \cdot \transpose{g} = \lambda \begin{pmatrix}
 	& w_n\\
 	-w_n
-	\end{pmatrix},$$
-	where $\similitudeCharacter\left(g\right)$ is a non-zero scalar.
+	\end{pmatrix}\right\}.$$
 	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
 Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
-In this case, the group $G = \GroupExtension{G}$ is isomorphic to the subgroup $\UnitaryGroup_n\left(\finiteField\right)$ of $\GL_{n}\left(\quadraticExtension\right)$ consisting of all elements $g$ such that $$g \cdot w_n \cdot \involution{\left(\transpose{g}\right)} = w_n.$$
+In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid g \cdot w_n \cdot \involution{\left(\transpose{g}\right)} = w_n \right\}.$$
 \end{enumerate}

### 2025-03-20 paper.tex
Slightly nicer

@@
 \subsection{TODO list}
-\calvin{I mentioned this to Charlotte and will meet with her sometime after Arizona to discuss specifically the DL stuff to make sure that it ok. So we could try to have a draft }
 \begin{enumerate}
-	\item (Minor) \sout{Change terminology of Gauss sums $\dblJacobiSumScalar{\pi}{\chi}$ to Jacobi sums and the notation to $J^{\mathrm{dbl}}\left(\pi, \chi\right)$ as they are similar to the Jacobi sums}
-	$$J\left(\alpha, \beta\right) = \sum_{\substack{x,y \in \multiplicativegroup{\finiteField}\\
-			x+y = 1}} \alpha\left(x\right) \beta\left(y\right),$$
-	compare with $$\dblJacobiSumScalar{\pi}{\chi} = \sum_{\substack{g \in G\\
-			h \in \GL\left(\hermitianSpace\right)\\
-			g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det\left(-h\right)\right).$$
-	\sout{Consider replacing $\chi\left(\det\left(g - \idmap_{\hermitianSpace}\right)\right)$ with $\chi\left(\det\left(\idmap_{\hermitianSpace} - g\right)\right)$ for aesthetics (probably not worth it).}
-	\item Maybe define the algebraic group versions $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$ in Section 3.2. For instance for $\algebraicGroup{\Sp}_{2n}$ we can define
-	$$\algebraicGroup{\tilde{G}} = \left\{ \left(g,\lambda\right) \in \algebraicGroup{\GL}\left(\hermitianSpace\right) \times \multiplcativeScheme \mid \involution{\transpose{g}} J g = \lambda J,\ \right\}$$ for suitable $J$ and then define the torus $\algebraicGroup{S}$ that appears in \cite[Page 140]{DigneMichel2020} as $$\algebraicGroup{S} = \left\{\left(\begin{pmatrix}
-		t \IdentityMatrix{n}\\
-		& \IdentityMatrix{n}
-	\end{pmatrix}, t\right) \mid t \in \multiplcativeScheme \right\} \subset \GroupExtension{\algebraicGroup{G}}.$$
-	Actually it appears to me that we are not in the same situation as in \cite[Page 140]{DigneMichel2020}.
 	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
@@
 	where we need to explain the notation.
-	\item \Cref{subsec:tori-isomorphism} and \Cref{subsec:gauss-sums-attached-to-semi-simple} should be removed and replaced with Calvin's arguments.
 	\item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}
@@
 		\item Split case: in this case, we can write $\hermitianSpace = \xIsotropic \oplus \yIsotropic$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
-In this case, we have that $G$ is isomorphic to $\SO^{+}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid g \cdot w_{2n} \cdot \transpose{g} = w_{2n},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{+}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid g \cdot w_{2n} \cdot \transpose{g} = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
+In this case, we have that $G$ is isomorphic to $\SO^{+}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} w_{2n} g  = w_{2n},\,\, \det g = 1\right\}.$$
+		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{+}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
 		\item Non-split case: In this case, there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
@@
 		\end{pmatrix} \cdot w_{2n}.$$
-		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid g \cdot B_{n,d} \cdot \transpose{g} = B_{n,d},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{-}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid g \cdot B_{n,d} \cdot \transpose{g} = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
+		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
+		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{-}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
 	\end{enumerate}
 	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
-In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid g \cdot \begin{pmatrix}
+In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} \begin{pmatrix}
 		& w_n\\
 		-w_n
-	\end{pmatrix} \cdot \transpose{g} = \begin{pmatrix}
+	\end{pmatrix} g = \begin{pmatrix}
 		& w_n\\
 		-w_n
-	\end{pmatrix}\right\}.$$ The group $\GroupExtension{G}$ is isomorphic to the group $\GSp_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSp}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid g \cdot \begin{pmatrix}
+	\end{pmatrix}\right\}.$$ The group $\GroupExtension{G}$ is isomorphic to the group $\GSp_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSp}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} \begin{pmatrix}
 	& w_n\\
 	-w_n
-	\end{pmatrix} \cdot \transpose{g} = \lambda \begin{pmatrix}
+	\end{pmatrix} g = \lambda \begin{pmatrix}
 	& w_n\\
@@
 Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
-In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid g \cdot w_n \cdot \involution{\left(\transpose{g}\right)} = w_n \right\}.$$
+In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
 \end{enumerate}

### 2025-03-20 paper.tex
Cleanup

@@
 In this case, we have that $G$ is isomorphic to $\SO^{+}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} w_{2n} g  = w_{2n},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{+}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
+		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{+}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
 		\item Non-split case: In this case, there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
@@
 		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{-}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
+		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{-}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
 	\end{enumerate}

### 2025-03-20 paper.tex
Writing a bit about cocharacters and characters

@@
 \subsubsection{Geometric Conjugacy and Lusztig Series}
-Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal torus $\algebraicGroup{T}$ defined over $\finiteField$.
+Let $\ell$ be a prime number not equal to the characteristic of $\finiteField$. Fix an isomorphism $\ladicnumbers \cong \cComplex$.
+
+Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal $\Frobenius$-stable torus $\algebraicGroup{T} \subset \algebraicGroup{G}$ defined over $\finiteField$.
+We denote by $$\CharacterLattice{\algebraicGroup{T}} = \Hom_{\finiteField}\left(\algebraicGroup{T}, \multiplcativeScheme\right)$$ the \emph{character lattice} of $\algebraicGroup{T}$ and by $$\CocharacterLattice{\algebraicGroup{T}} = \Hom_{\finiteField}\left(\multiplcativeScheme, \algebraicGroup{T}\right)$$ the \emph{cocharacter lattice} of $\algebraicGroup{T}$, where we regard $\algebraicGroup{T}$ and $\multiplcativeScheme$ as algebraic groups over $\finiteField$.
+Recall that $\CharacterLattice{\algebraicGroup{T}}$ and $\CocharacterLattice{\algebraicGroup{T}}$ are free $\zIntegers$-modules of the same finite rank.
+The assignment $\CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \Hom_{\finiteField}\left(\multiplcativeScheme, \multiplcativeScheme\right)$ given by composition $\left(x,y\right) \mapsto x\left(y\left(z\right)\right)$ for any $z \in \multiplcativeScheme$ defines a pairing $\innerproduct{\cdot}{\cdot} \colon \CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \zIntegers$ by the rule $$x\left(y\left(z\right)\right) = z^{\innerproduct{x}{y}}.$$
+
 The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum

### 2025-03-20 paper.tex
Explaining the notation a bit

--- 2025-03-20 paper.tex
@@
 \newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
-\newcommand{\multiplcativeScheme}{\mathbb{G}_m}
+\newcommand{\multiplcativeScheme}{\algebraicGroup{G}_m}
 \newcommand{\affineLine}{\mathbb{A}^1}
@@
 \subsubsection{Geometric Conjugacy and Lusztig Series}
-Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal torus $\algebraicGroup{T}$ defined over $\finiteField$.
+Let $\ell$ be a prime number not equal to the characteristic of $\finiteField$. Fix an isomorphism $\ladicnumbers \cong \cComplex$.
+
+Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal $\Frobenius$-stable torus $\algebraicGroup{T} \subset \algebraicGroup{G}$ defined over $\finiteField$.
+We denote by $$\CharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\algebraicGroup{T}, \multiplcativeScheme\right)$$ the \emph{character lattice} of $\algebraicGroup{T}$ and by $$\CocharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\multiplcativeScheme, \algebraicGroup{T}\right)$$ the \emph{cocharacter lattice} of $\algebraicGroup{T}$, where we regard $\algebraicGroup{T}$ and $\multiplcativeScheme$ as algebraic groups over $\finiteField$.
+Recall that $\CharacterLattice{\algebraicGroup{T}}$ and $\CocharacterLattice{\algebraicGroup{T}}$ are free $\zIntegers$-modules of the same finite rank.
+The assignment $\CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \Hom_{\finiteField}\left(\multiplcativeScheme, \multiplcativeScheme\right)$ given by composition $\left(x,y\right) \mapsto \left(z \mapsto x\left(y\left(z\right)\right)\right)$ defines a pairing $\innerproduct{\cdot}{\cdot} \colon \CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \zIntegers$ by the rule $$x\left(y\left(z\right)\right) = z^{\innerproduct{x}{y}}.$$
+
 The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum

### 2025-03-21 paper.tex
Making things more clear to me

@@
 We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character.
-By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{T,\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
 \[
@@
 This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
-By composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
+Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
 
     Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
-Similarly, denote the Frobenius stable Weyl group element of $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
+Similarly, denote the $\Frobenius$-stable Weyl group orbit in $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
 

### 2025-03-21 paper.tex
Minor

@@
 
-The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{T, \theta}$ for some $(T,\theta)$ such that $(s_{T,\theta}) = (s)$.
+The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
 

### 2025-03-21 paper.tex
Minors

@@
 \[
-    \exp(\langle x_{T,\theta},y\rangle) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
+    \exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
 \]
 for large enough $n$.
-This $x_{T,\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between $(T,\theta)$ pairs and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
+This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
 Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.

### 2025-03-21 paper.tex
More clarification

@@
 \label{eq:DL}
-\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T}(\algebraicClosure{\finiteField}) \ar[r] & 0}
+\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T} \ar[r] & 0}
 \end{equation}
@@
 This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
-Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
+Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
 

### 2025-03-21 paper.tex
Writing an example

@@
 
-We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character.
+We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\ladicnumbers}$ is a character.
 By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
@@
 This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
+
+\begin{example}
+	Take $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
+	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
+Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
+	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.
+Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$.
+The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$.
+We thus have
+	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
+\end{example}
 

### 2025-03-21 detailedExample.tex
Detailed example

--- 2025-03-21 paper.tex
@@
 
-\subsection{TODO list}
-\begin{enumerate}
-	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
-	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified.
-We should first use $\GroupExtension{G}$.
-For this group we have the ``at most one cuspidal'' property.
-Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
-	where we need to explain the notation.
-	\item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}
-	\item We might be able to include $SO_{odd}$ with $\Phi(g)$ the symmetric function in the eigenvalues of $g$ given by $\sum_{i=1}^{dim(V)} \chi(\Pi_{j \neq i}(\lambda_j-1))$.
+\begin{example}
+	Take $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
+	We can make this explicit.
+Choose $d \in \multiplicativegroup{\finiteField}$ that is not a square.
+Then $$\algebraicGroup{T}'_2 = \left\{a + b\sqrt{d} \mid \left(a,b,n\right) \in \affineLine \times \affineLine \times \multiplcativeScheme , \,\, a^2-db^2 = n \right\},$$
+	and 
+	$$\algebraicGroup{T}_2 = \left\{a + b\sqrt{d} \mid \left(a,b\right) \in \affineLine \times \affineLine, \,\, a^2-db^2 = 1 \right\}.$$
+	The arithmetic Frobenius action is given by raising $a$ and $b$ and $n$ (in the case of $\algebraicGroup{T}'_2$) to the $q$-th power.
+The rational Frobenius action is given by replacing $b$ with $-b$.
 
-\end{enumerate}
+	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
+Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
+	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.
+Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ by the map $$a + b\sqrt{d} \mapsto \left(a + b\sqrt{d}, a - b \sqrt{d}\right),$$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$ by the map $$a + b\sqrt{d} \mapsto a + b\sqrt{d}.$$ The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $$\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)^q,$$ while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $$\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}.$$ Indeed, using the composition $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius^{2}} \to \algebraicGroup{T}_2^{\Frobenius}$, it suffices to compute this for $m=2$, in which case we have that the norm map $\algebraicGroup{T}_2^{\Frobenius^{2}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\left(a + b\sqrt{d}\right) \mapsto \left(a + b\sqrt{d}\right)\left(a^q + b^q\sqrt{d}\right)$, and we have that $$a^q + b^q \sqrt{d} = \left(a-b\sqrt{d}\right)^q = \left(a+b\sqrt{d}\right)^{-q}.$$
+	Similarly, for $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^2} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$, the norm map is given by $$a + b\sqrt{d} \mapsto \left(a + b\sqrt{d}\right)\left(a^q + b^q \sqrt{d}\right) = \left(a+b\sqrt{d}\right)\left(a-b\sqrt{d}\right)^q.$$
 
-\section{Notation}
-Let $\finiteField$ be a finite field with $q$ elements, where $2 \nmid q$, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-Fix an algebraic closure $\algebraicClosure{\finiteField}$ of $\finiteField$.
-For any $k \ge 1$, let $\finiteFieldExtension{k} \slash \finiteField$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
-
-\section{Kondo Gauss sums}
-Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. 
-For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
-This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
-
-\begin{lemma}\label{lem:sum-vanishes-for-singular-matrices}
-	For any singular matrix $X \in \squareMatrix_n\left(\finiteField\right)$ and any $1 \ne \chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the sum
-	$$\sum_{h \in \GL_n\left(\finiteField\right)} \chi\left(\det h\right) \fieldCharacter\left(\trace\left(Xh\right)\right)$$
-	is zero.
-\end{lemma}
-\begin{proof}
-	Write $$X = h_1 \begin{pmatrix}
-		\IdentityMatrix{n-r}\\
-		& 0_r
-	\end{pmatrix} h_2,$$
-	where $1 \le r \le n$ and $h_1, h_2 \in \GL_n\left(\finiteField\right)$. Then
-	$$\fieldCharacter\left(\trace Xh\right) = \fieldCharacter\left(\trace\left( \begin{pmatrix}
-		\IdentityMatrix{n-r}\\
-		& 0_r
-	\end{pmatrix} h_2 h h_1\right)\right).$$
-	Changing variables $h \mapsto h_2^{-1} h h_1^{-1},$
-	we obtain the inner sum
-	$$\sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
-		\IdentityMatrix{n-r}\\
-		& 0_r
-	\end{pmatrix} h \right) \chi\left(\det h\right),$$
-	which equals
-	$$\frac{1}{\sizeof{\multiplicativegroup{\finiteField}}} \sum_{a \in \multiplicativegroup{\finiteField}} \sum_{h \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace \begin{pmatrix}
-		\IdentityMatrix{n-r}\\
-		& 0_r
-	\end{pmatrix} \begin{pmatrix}
-		\IdentityMatrix{n-1}\\
-		& a
-	\end{pmatrix} h \right) \chi\left(\det h\right).$$
-	Changing variables $h \mapsto \left(\begin{smallmatrix}
-		\IdentityMatrix{n-1}\\
-		& a^{-1}
-	\end{smallmatrix}\right) h$, we get the inner sum $$\sum_{a \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(a\right),$$
-	which vanishes because $\chi \ne 1$.
-\end{proof}
-
-\section{Doubling method Jacobi sums}
-
-\subsection{The case of general linear groups}
-
-Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-
-Consider the following assignment $\GL_k\left(\finiteField\right) \to \cComplex$
-$$\Phi_{\chi}\left(g\right) = \begin{dcases}
-	\chi\left(\det\left(\IdentityMatrix{k}-g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}-g\right) \ne 0,\\
-	0 & \text{otherwise.}
-\end{dcases}$$
-It is clear that $\Phi_{\chi}$ is a class function of $\GL_k\left(\finiteField\right)$.
-
-Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Jacobi sum}:
-$$\dblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
-Then $\dblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$.
-Therefore, by Schur's lemma there exists a complex number $\dblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblJacobiSum{\tau}{\chi} = \dblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
-
-The goal of this section is to express $\dblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.
-
-\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
-	We have the identity
-	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
-\end{proposition}
-\begin{proof}
-	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det\left(-h\right)\right).$$
-	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$.
-Thus	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
-	Changing variables $h \mapsto X^{-1} h$, we get
-	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
-	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
-	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
-\end{proof}
-
-We now use this to compute $\dblJacobiSum{\tau}{\chi}$.
-We have that $$\dblJacobiSum{\tau}{\chi} = \chi\left(-1\right)^k q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(-y^{-1} x\right).$$
-The last equality implies the following result.
-\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\dblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
-\end{theorem}
-
-\subsection{The case of classical groups}
-
-Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$ contained in $\algebraicClosure{\finiteField}$.
-For any $k \ge 1$, let $\quadraticFieldExtension{k} \slash \quadraticExtension$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
-Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.
-
-Let $\hermitianSpace$ be a vector space of dimension $n$ over $\quadraticExtension$, equipped with a non-degenerate sesquilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \quadraticExtension$ which is $\epsilon_{\hermitianSpace}$-symmetric for $\epsilon_{\hermitianSpace} \in \left\{\pm 1\right\}$.
-By this we mean that:
-\begin{enumerate}
-	\item For every $x_1,x_2,y \in \hermitianSpace$, $$\innerproduct{x_1 + x_2}{y} = \innerproduct{x_1}{y} + \innerproduct{x_2}{y}.$$
-	\item For every $x,y \in \hermitianSpace$ and $t \in \quadraticExtension$, $$\innerproduct{tx}{y} = t\innerproduct{x}{y}.$$
-	\item ($\epsilon_{\hermitianSpace}$-symmetric) For every $x,y \in \hermitianSpace$, $$\innerproduct{x}{y} = \epsilon_{\hermitianSpace} \involution{\innerproduct{y}{x}}.$$
-	\item (non-degenerate) For every $0 \ne x \in \hermitianSpace$ there exists $y \in \hermitianSpace$ such that $$\innerproduct{x}{y} \ne 0.$$
-\end{enumerate}
-Let $\IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
-We denote by $G$ the identity component of $\IsometryGroup\left(\hermitianSpace\right)$.
-If $\quadraticExtension = \finiteField$, let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
-Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
-If $\quadraticExtension \ne \finiteField$, let $\GroupExtension{G} = G$.
-
-We will assume that $\dim_{\finiteField} \hermitianSpace$ is even.
-This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
-The group $\GroupExtension{G}$ has connected center and contains $G$.
-
-Let us summarize all possible cases for $G$ and $\GroupExtension{G}$. Let $$w_n = \begin{pmatrix}
-	& & & 1\\
-	& & 1\\
-	& \iddots\\
-	1
-\end{pmatrix} \in \GL_n\left(\finiteField\right)$$ be the longest Weyl element.
-\begin{enumerate}
-	\item (Special even orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
-Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
-It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$.
-Similarly, every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$.
-In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
-There are two cases here.
-	\begin{enumerate}
-		\item Split case: in this case, we can write $\hermitianSpace = \xIsotropic \oplus \yIsotropic$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
-In this case, we have that $G$ is isomorphic to $\SO^{+}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} w_{2n} g  = w_{2n},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{+}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
-		\item Non-split case: In this case, there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
-		where $\xIsotropic$ and $\yIsotropic$ are totally isotropic spaces in duality and $\hermitianSpace'$ is an antisotropic space (that is, for any $0 \ne v' \in \hermitianSpace'$, we have $\innerproduct{v'}{v'} \ne 0$) of dimension 2.
-Let $d$ be an element of $\multiplicativegroup{\finiteField}$ that is not a square.
-Denote $$B_{n,d} = \begin{pmatrix}
-			\IdentityMatrix{n-1}\\
-			& & 1 &\\
-			& -d & &\\
-			& & & \IdentityMatrix{n-1}
-		\end{pmatrix} \cdot w_{2n}.$$
-		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{-}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
-	\end{enumerate}
-	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
-In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} \begin{pmatrix}
-		& w_n\\
-		-w_n
-	\end{pmatrix} g = \begin{pmatrix}
-		& w_n\\
-		-w_n
-	\end{pmatrix}\right\}.$$ The group $\GroupExtension{G}$ is isomorphic to the group $\GSp_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSp}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} \begin{pmatrix}
-	& w_n\\
-	-w_n
-	\end{pmatrix} g = \lambda \begin{pmatrix}
-	& w_n\\
-	-w_n
-	\end{pmatrix}\right\}.$$
-	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
-Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
-In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
-\end{enumerate}
-
-Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
-
-Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
-As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} - g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} - g\right) \ne 0\\
-0 & \text{otherwise,}
-\end{dcases}$$
-is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
-
-Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
-Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
-Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$.
-Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
-By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
-We call $\dblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sum}.
-
-\subsubsection{Multiplicativity property}
-Our next goal is to understand how the doubling method Jacobi sum behaves under parabolic induction.
-
-Let $\xIsotropic$ and $\yIsotropic$ be isotropic spaces of $\hermitianSpace$ of dimension $k$, such that $\xIsotropic$ and $\yIsotropic$ are in duality with respect to form $\innerproduct{\cdot}{\cdot}$.
-Let us write $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
-where $\hermitianSpace' \subset \hermitianSpace$ is a non-degenerate subspace, orthogonal to $\xIsotropic$ and $\yIsotropic$.
-Let $P$ be the parabolic subgroup of $H$, consisting of all elements stabilizing the flag $$0 \subset \xIsotropic \subset \xIsotropic \oplus \hermitianSpace' \subset \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic = \hermitianSpace.$$
-Let $G' = \IsometryGroup\left(\hermitianSpace'\right)$.
-Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$.
-Then $L$ is isomorphic to $H' \times \GL_k\left(\quadraticExtension\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.
-
-Let $\fieldCharacter_{\quadraticExtension} \colon \quadraticExtension \to \multiplicativegroup{\cComplex}$ be the character  $\fieldCharacter_{\quadraticExtension} = \fieldCharacter \circ \trace_{\quadraticExtension \slash \finiteField}$.
-Similarly, for any $k \ge 1$, let $\fieldCharacter_{\quadraticFieldExtension{k}} \colon \quadraticFieldExtension{k} \to \multiplicativegroup{\cComplex}$ be the character $\fieldCharacter_{\quadraticFieldExtension{k}} = \fieldCharacter \circ \trace_{\quadraticFieldExtension{k} \slash \finiteField}$.
-
-Given a multiplicative character $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$, let $\involutionPlusOne{\chi} \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be the character given by
-$$\involutionPlusOne{\chi}\left(x\right) = \chi\left(x \cdot \involution{x}\right).$$ Similarly, let $\minusInvolution{\chi} \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be the character given by
-$$\minusInvolution{\chi}\left(x\right) = \chi^{-1}\left(\involution{x}\right).$$
-
-\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
-	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$.
-Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
-	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
-\end{theorem}
-\begin{proof}
-	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$.
-Consider $f \in \rho$ defined as follows.
-The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$.
-The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
-We compute $\dblJacobiSum{\rho}{\chi} f$.
-
-	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
-	which can be rewritten as
-	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
-	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
-	Hence, \begin{align*}
-		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Assume that $\chi \ne 1$.
-By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
-Let us replace $h$ with $A^{-1} h$.
-We get the sum
-	\begin{align*}
-		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
-	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
-	\begin{align*}
-		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
-		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.
-
-	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
-	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
-		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
-				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
-	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} - p\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} - a\right) \det\left(\involution{\left(\IdentityMatrix{k} - a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} - g'\right),$$
-	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
-	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
-	\begin{equation}
-		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
-	\end{equation}
-	which in turn is
-	\begin{align*}
-		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
-		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
-	\end{align*}
-	The result now follows.
-\end{proof}
-
-\subsubsection{Gamma factors}
-In order to make the computations more tolerable, it is beneficial to work with fully multiplicative functions. We introduce the doubling method gamma factors.
-
-Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
-
-We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField\\
-	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField
-\end{dcases}.$$
-Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.
-
-For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
-Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
-
-\begin{theorem}\label{thm:multiplicativity-in-terms-of-gamma-factors}
-	\begin{enumerate}
-		\item If $\tau_1$ and $\tau_2$ are irreducible representations of $\GL_{k_1}\left(\finiteField\right)$ and $\GL_{k_2}\left(\finiteField\right)$, respectively, then for any irreducible subrepresentation $\tau$ of the parabolic induction $\tau_1 \circ \tau_2$, we have
-		$$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \dblGammaFactor{\tau_1}{\chi}{\fieldCharacter} \dblGammaFactor{\tau_2}{\chi}{\fieldCharacter}.$$
-		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\chi \ne 1$, then
-		$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \dblGammaFactor{\tau}{\chi}{\fieldCharacter}.$$
-	\end{enumerate}
-\end{theorem}
-
-\begin{remark}
-	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
-				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
-				\left(-1\right)^{n+1} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
-				1 & \text{otherwise.}
-	\end{dcases}.$$
-	However, we will not need this version for our purposes.
-\end{remark}
-
-\subsection{Computation of character sums attached to Deligne--Lusztig data}
-
-The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
-
-In this section, we focus on the computing the analogous character sum corresponding to $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for the virtual character $R_{T,\theta}$.
-
-Let us realize $H$ as the fixed points of the Frobenius map $\Frobenius$ acting on a connected reductive algebraic group $\algebraicGroup{H}$.
-
-Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
-
-It is clear that if $\pi$ is an irreducible representation of $H$ then $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \dim \pi.$$
-Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in H$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
-\begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
-	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{H}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
-\end{proposition}
-In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
-$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
-Here $\varepsilon_{\algebraicGroup{H}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{H}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{H}_p$ is the size of the $p$-Sylow group of $H$, where $p$ is the characteristic of $\finiteField$.
-
-\subsubsection{Gauss sum notations}
-If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
-If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
-$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
-
-If $m \ge 1$, we denote 
-$$\NormOneGroup{2m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
-
-\subsubsection{Split torus computation I}
-Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ be a character and let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-
-The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1-x\right)\right).$$
-Let us rewrite this as
-$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\left(-1\right)^k\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
-Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
-$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
-Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$, this becomes
-$$q^{-k} \alpha\left(-1\right) \chi\left(-1\right)^k \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
-Hence, we have the identity
-$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \chi\left(-1\right)^k \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
-
-\subsubsection{Split torus computation II}
-We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
-Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
-Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 - x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 - \minusInvolution{x}\right)\right).$$
-This can be rewritten as
-$$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(1 - x\right)\right).$$
-By the previous section, this equals
-\begin{equation*}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
-\end{equation*}
-which equals
-\begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
-\end{equation}
-
-Notice that if $k = md$ and $\alpha = \beta \circ \FieldNorm{k}{m}$ where $\beta \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ is a character, then \eqref{eq:identity-for-multiplicative-group-of-f-k-gauss-sum} equals
-$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \GaussSumCharacter{\involution{\beta}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^m\right)^{d}.$$
-
-\begin{remark}
-	Changing variables $x \mapsto -x$, we have that \begin{align*}
-		& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-				x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
-			=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
-	\end{align*}
-\end{remark}
-
-\subsubsection{Elliptic torus computation}
-In the next two sections we compute the doubling method Jacobi sum for a torus of the form $\NormOneGroup{2m}$.
-
-Let $\theta \colon \NormOneGroup{2m} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be non-trivial characters, such that $\involutionPlusOne{\chi} \ne 1$.
-Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(1 - x\right)\right).$$
-
-We separate two cases: the case $\quadraticExtension = \finiteField$ and the case $\quadraticExtension \ne \finiteField$.
-
-\subsubsection{Elliptic torus computation: the case $\quadraticExtension = \finiteField$}
-In this section, we compute the above exponential sum for the case $\quadraticExtension = \finiteField$.
-Since $\chi^2 \ne 1$, it follows that $\theta\left(x^{1-q^m}\right) \ne \chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(x\right)$ for some $x \in \multiplicativegroup{\finiteFieldExtension{2m}}$.
-
-As usual, we rewrite the sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(-y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
-
-If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
-$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
-To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \NormOneGroup{2m}$ given by $t \mapsto t^{1 - q^m}$.
-This map is surjective, and its kernel is $\multiplicativegroup{\finiteFieldExtension{m}}$.
-Define $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ by $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
-Replacing the sum over $x \in \NormOneGroup{2m}$ with a sum over $t \in \multiplicativegroup{\finiteFieldExtension{2m}}$, we get \begin{align*}
-	& \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right) \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right) \\
-	= & \frac{1}{q^m-1}\sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z^{q^m}\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t^{1-q^m} z\right).
-\end{align*}
-Replacing $z$ with $t^{q^m} z$, this becomes
-\begin{align*}
-	\frac{1}{q^m-1}\sum_{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) t\right).
-\end{align*}
-Since $\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField} \ne \theta'$, if $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) = 0$, we have that the inner sum over $t$ is zero.
-Hence, we may reduce the sum over $z$ to $z$ such that $\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0$.
-Using the fact that $\theta'$ is trivial on $\multiplicativegroup{\finiteFieldExtension{m}}$, we have after replacing variables $t \mapsto \frac{t}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right)}$,
-\begin{align*}
-	\frac{1}{q^m-1}\sum_{\substack{t,z \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
-			\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) \ne 0}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(\frac{z}{\trace_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{m}}\left(z\right) }\right)\right) \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right).
-\end{align*}
-By the appendix, this equals
-\begin{align*}
-	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
-\end{align*}
-
-To summarize, we have
-\begin{align*}
-	& \sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) \\
-		=& q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),
-\end{align*}
-where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
-Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
-$$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
-\begin{remark}
-	Changing variables $x \mapsto -x$, we have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
-\end{remark}
-
-\subsubsection{Elliptic torus computation: the case $\quadraticExtension \ne \finiteField$}
-In this section, we compute the above exponential sum for the case $\quadraticExtension = \finiteFieldExtension{2}$.
-Let $\chi \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$.
-We wish to compute the following sum.
-$$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 - x\right)\right).$$
-By the appendix, this equals
-$$\theta\left(-1\right) q^{\frac{m}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
-which equals
-$$\theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}.$$
-
-\subsubsection{Computation for Deligne--Lusztig characters}
-Combining the results of the previous sections with \Cref{prop:reduction-of-gauss-sum-to-torus}, we arrive at the following result.
-
-\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote \begin{align*}
-		g_T\left(\chi, \theta, \fieldCharacter\right)
-		= & \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
-	\end{align*} Then
-	\begin{align*}
-		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
-	\end{align*}
-\end{theorem}
-\begin{proof}
-	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
-	and the fact \begin{equation*}
-		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r.
-	\end{equation*}
-\end{proof}
-\begin{remark}
-	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.$$ If $\finiteField = \quadraticExtension$ then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
-\end{remark}
-\begin{remark}
-	Suppose that $\pi$ is any irreducible representation of $H$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
-	\begin{align*}
-		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
-	\end{align*}
-	Thus \begin{align*}
-		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
-	\end{align*}
-\end{remark}
-
-\subsubsection{Geometric Conjugacy and Lusztig Series}
-Let $\ell$ be a prime number not equal to the characteristic of $\finiteField$. Fix an isomorphism $\ladicnumbers \cong \cComplex$.
-
-Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal $\Frobenius$-stable torus $\algebraicGroup{T} \subset \algebraicGroup{G}$ defined over $\finiteField$.
-We denote by $$\CharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\algebraicGroup{T}, \multiplcativeScheme\right)$$ the \emph{character lattice} of $\algebraicGroup{T}$ and by $$\CocharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\multiplcativeScheme, \algebraicGroup{T}\right)$$ the \emph{cocharacter lattice} of $\algebraicGroup{T}$, where we regard $\algebraicGroup{T}$ and $\multiplcativeScheme$ as algebraic groups over $\finiteField$.
-Recall that $\CharacterLattice{\algebraicGroup{T}}$ and $\CocharacterLattice{\algebraicGroup{T}}$ are free $\zIntegers$-modules of the same finite rank.
-The assignment $\CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \Hom_{\finiteField}\left(\multiplcativeScheme, \multiplcativeScheme\right)$ given by composition $\left(x,y\right) \mapsto \left(z \mapsto x\left(y\left(z\right)\right)\right)$ defines a pairing $\innerproduct{\cdot}{\cdot} \colon \CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \zIntegers$ by the rule $$x\left(y\left(z\right)\right) = z^{\innerproduct{x}{y}}.$$
-
-The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
-\[
-(\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
-\]
-such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.
-
-Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
-By \cite[Proposition 13.7 (ii)]{DigneMichel2020}, we have an exact sequence
-\begin{equation}
-\label{eq:DL}
-\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T}(\algebraicClosure{\finiteField}) \ar[r] & 0}
-\end{equation}
-with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n))$
-for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
-Here, $$\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$$ is the torus norm map.
-
-We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character.
-By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
-\[
-    \exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
-\]
-for large enough $n$.
-This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
-Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL}, we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
-
-    Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
-Similarly, denote the $\Frobenius$-stable Weyl group orbit in $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
-
-We say that the torus character pairs $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ for $\algebraicGroup{G}$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{\algebraicGroup{T},\theta})$ and $(s_{\algebraicGroup{T}',\theta'})$ are equal.
-This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
-
-The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
-
-\begin{center}
-\begin{tabular}{ c c c c c c}
- Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
- $Sp(2n)$ & $(\multiplicativegroup{\finiteField})^n$ & 1 & 1 &$SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^n$\\  
- $GSp(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
- $SO(2n)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$SO(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
- $GO(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
- $SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
- $GO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ 
-  $U(n)$ & $(\NormOneGroup{2})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{2})^{n}$ 
-\end{tabular}
-\end{center}
-
-\calvin{non split form of $SO(even)$, is the dual group itself?.
-The torus I think is $(\mathbb{F}_2)^{Nm=1} \times (\mathbb{F}^\times)^{dim -1}$.
-The Frobenius action on the characters is $(-1,1,1,1\hdots 1)$ and on $W$ its trivial}
-
-\subsubsection{Invariance under geometric conjugacy}
-\calvin{todo:type in some motivation for class functions whose product doesn't depend on geometric conjugacy, gamma functions whatever}.
-
-Let $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ be a class function.
-Then by Schur's lemma for any irreducible representation $\pi$, there exists $\gamma_{f}\left(\pi\right) \in \cComplex$ such that $$\sum_{g \in G} f(g)\pi(g) = \gamma_{f}\left(\pi\right) \cdot \idmap_{\pi}.$$
-
-\begin{definition}
-	We say that  $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ is a \emph{stable function} on $\algebraicGroup{G}^{\Frobenius}$ if it satisfies the following property: if $\pi$ and $\pi'$ are irreducible representations of $\algebraicGroup{G}^{\Frobenius}$ such that lie in the same geometric Lusztig series, then $$\gamma_{f}\left(\pi\right) = \gamma_{f}\left(\pi'\right).$$
-(See also \cite[Section 4]{LaumonLetellier2023} and \cite[Section 4.1]{ChenBhattacharya2024})
-	\end{definition}
-
-Here is a basic example of a stable class function.
-\begin{proposition}
-\label{prop:central_char}
-    If $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ is supported on the center $\algebraicGroup{Z}^{\Frobenius}$ of $\algebraicGroup{G}^{\Frobenius}$, then $f$ is a stable function.
-\end{proposition}
-\begin{proof}
-By \cite[Lemma 2.2]{Malle2007}, if $\pi$ and $\pi'$ lie in the same geometric Lusztig series, then they have the same central character. The result now immediately follows.
-\end{proof}
-
-The main result of this paper is 
-\begin{theorem}
-\label{thm:Phi_stable}
-	The assignment $H \to \cComplex$ given by $$h \mapsto \begin{dcases}
-		\chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - h\right)\right) & h \in G \text{ and } \detQuadratic\left(\idmap_{\hermitianSpace} - h\right) \ne 0,\\
-		0 & \text{otherwise.}
-	\end{dcases}$$ is a stable function. Equivalently, the assignment $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ is constant on geometric Lusztig series.
-\end{theorem}
-In the $\GL_n$ case this follows from \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
-In this section we prove a slightly weaker result:
-
-\begin{lemma}
-\label{lem:indep_geo_conj}
-    If $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
-\end{lemma}
-
-For a torus character pair $(\algebraicGroup{T},\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset \algebraicGroup{G}^*$ and an embedding $\rho:\algebraicGroup{G}^* \to \algebraicGroup{\GL}_n$.
-Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$ which contains $\rho(\algebraicGroup{T}^*)$.
-Let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
-Define
-\[
-    g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
-    \tilde{\algebraicGroup{T}}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
-\]
-The following lemma shows that this is well defined.
-
-\begin{lemma}
-\label{lemma:gl_invariance}
-\begin{enumerate}[(i)]
-	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
-	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
-\end{enumerate}
-\end{lemma}
-\begin{proof}
-\begin{enumerate}[(i)]
-	\item In this case when $T = \prod_{i} \multiplicativegroup{\finiteFieldExtension{n_i}}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
-	\[
-	g_{T,\rho}(\theta,\psi,\chi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
-	\]
-	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
-	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
-	\[
-	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
-	\]
-	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
-	\[
-	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
-	\]
-	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
-\end{enumerate}
-\end{proof}
-
-\begin{corollary}
-\label{cor:geoconj}
-Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$.
-Then $g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
-\end{corollary}
-\begin{proof}
-Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
-\end{proof}
-
-The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
-\begin{center}
-\begin{tabular}{ c c}
- Group & Dual group representations $\rho$ \\ 
- $Sp(2n)$ &$SO(2n+1) \to \GL(2n+1)$\\  
- $GSp(2n)$  &$GSpin(2n+1) \to \GL(2n+1)$ \\
- $SO(2n)$ &$SO(2n) \to \GL(2n)$ \\
- $GO(2n)$ & ? \\
- $SO(2n+1)$ &$Sp(2n) \to \GL(2n)$ \\
- $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to \GL(2n)$  
-\end{tabular}
-\end{center}
-Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
-In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
-In the unitary case, the torus whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$ and the induced map of cocharacters is $(x_1,x_2, \hdots, x_n) \mapsto (x_1,-x_1,x_2,-x_2, \hdots ,x_n,-x_n)$.
-
-In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
-%The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
-
-\begin{lemma}
-\label{lem:cochar_computation}
-    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
-We will consider two different Frobeinus actions on these characters:
-    \begin{enumerate}
-        \item When $\Frobenius$ acts by trivially on both, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
-        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
-            0 & 1 \\
-            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
-    \end{enumerate}
-\end{lemma}
-\begin{proof}
-Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
-\[
-    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
-\]
-Thus the result follows from the computations:
-\begin{enumerate}
-	\item \begin{align*}
-		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
-		&= \alpha\left(\FieldNorm{mn}{n}(y_1(\zeta_{mn})\right) \alpha\left(\FieldNorm{mn}{n}(y_2(\zeta_{mn})\right)^{-1} \\
-		&= \left(\alpha\times\alpha^{-1}\right)\left(\FieldNorm{mn}{n}((y_1,y_2)(\zeta_{mn}))\right)
-	\end{align*}
-	\item \begin{align*}
-		\exp(\langle\phi(x_{\NormOneGroup{2n},\theta}),(y_1,y_2)\rangle) &= \exp(\langle x_{\NormOneGroup{2n},\theta},\phi^*(y_1,y_2)\rangle) \\
-		&= \theta\left(\frac{\FieldNorm{2mn}{2n}(y_1(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_1(\zeta_{2mn})^{q^n}\right)}\right) \theta\left(\frac{\FieldNorm{2mn}{2n}(y_2(\zeta_{2mn})}{\FieldNorm{2mn}{2n}\left(y_2(\zeta_{2mn})^{q^n}\right)}\right)^{-1} \\
-		&= \theta'\left(\FieldNorm{2mn}{2n}((y_1,y_2)(\zeta_{mn}))\right)
-	\end{align*}
-\end{enumerate}
-\end{proof}
-
-\begin{proof}[Proof of \Cref{lem:indep_geo_conj}] 
-By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, it is enough to show that $g_{T}(\chi,\theta,\psi)$ and $\omega_{\pi}(-1) = \theta(-1)$ only depend of the geometric conjugacy of $(T,\theta)$.
-The latter only depends on geometric conjugacy by \Cref{prop:central_char}.
-
-Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
-We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$.
-We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
-\Cref{lem:cochar_computation} above implies that
-\[
-g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
-        1  & G \neq Sp, GSp\\
-        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
-    \end{cases}.
-\]
-\Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
-\begin{comment}
-We will have to treat the unitary group case seperatedly. First for the non-unitary group case:\\
-
-Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1 \left[\times \{\pm 1\}\right]$ with $k_1 \geq k_2 \hdots \geq k_r$ and $m_1 \geq m_2 \hdots \geq m_r$ and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
-Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by $((k_1,k_2, \hdots, k_r), (m_1,m_2 \hdots m_s))$.
-The map $\rho$ sends this conjugacy class (or union of two conjugacy classes) to the conjugacy class with cycle decomposition the union of cycles of lengths $k_1,k_1,k_2,k_2 \hdots, k_r,k_r, 2m_1,2m_2 \hdots 2m_r$ along with a cycle of length $1$ in the $Sp$ and $GSp$ case.
-Let $\tilde{T}$ be the torus in $\GL$ corresponding to the conjugacy class above and let $\tilde{\theta}$ be the character of $\tilde{T}$ corresponding to $\Phi(s)$.
-Then by theorem \ref{thm:thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-\[
-    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = \begin{cases}
-        g_T(\theta,\psi)  & G \neq Sp \textnormal{ or } GSp\\
-        g_T(\theta,\psi) \cdot g(1,\psi_1) & G = Sp \textnormal{ or } GSp
-    \end{cases}.
-\]
-Since the sum above is a Gauss sum for $\GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$. \\
-Now for the unitary case: \calvin{this needs to be checked... I used engineers induction to guess at how the Weyl group conjugacy classes match the torus}
-Write $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s (\finiteFieldExtension{2m_i}^1)^2$ with $k_i$'s even and $m_i$'s odd \calvin{this is what I need to check...
-what tori you can get here} and under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s \times \epsilon$, where  $\left[\epsilon \colon \left\{\pm 1\right\} \to \multiplicativegroup{\cComplex},\right]$ $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$.
-Then the Frobenius conjugacy class of the Weyl group corresponding to $T$ is represented by having even cycles of lengths $k_1,k_2 \hdots k_r$ and odd cycles of lengths $m_1,m_1,m_2,m_2, \hdots, m_s,m_s$.
-The map $\Phi$ sends this conjugacy class to the conjugacy class with even cycles $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and odd cycles $m_1,m_1,m_1,m_1,m_2,m_2,m_2,m_2, \hdots, m_s,m_s,m_s,m_s$.
-Let $\tilde{T}$ be the torus in $\GL$ corresponding to the conjugacy class with all even cycles of lengths $k_1,k_1,k_2,k_2 \hdots k_r,k_r$ and $2m_1,2m_1,2m_2,2m_2, \hdots, 2m_s,2m_s$.
-Then $\Phi(s)$ is in this torus \calvin{write out what that means} giving a character $\tilde{\theta}$ on it and
-\[
-    \sum_{t \in \tilde{T}} \tilde{\theta}(t) \chi(det(t-1)) = g_T(\theta,\psi).
-\]
-Since the sum above is a Gauss sum for $\GL$ it is equal to the Gauss sum attatched to the semisimple element $\Phi(s)$.
-\end{comment}
-\end{proof}
-
-\subsection{Computation for geometric Lusztig series}
-
-The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
-
-\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
-	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
-	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$.
-Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.
-Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
-\end{theorem}
-
-\calvin{start alternate writeup of section 3.4/3.4.1:}
-\subsection{Computation for Lusztig Series}
-The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
-\begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
-\end{theorem}
-\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
-\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
-Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
-First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
-\\
-
-\begin{proof}
-\calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
-\end{proof}
-
-By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
-$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_T\left(\theta, \fieldCharacter\right)$$
-is independent of geometric conjugacy class of $(T,\theta)$. Since we know the relevant equality for non cupsidal $\pi$, we get that
-$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_T\left(\theta, \fieldCharacter\right)$$.
-
-To finish we will show that all cuspidal $\pi$ in a Lusztig packet $\LusztigSeries{G}{s}$ have the same $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
-This will follow from
-
-\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
-	Let $\GroupExtension{G}$ have connected center.
-For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
-\end{proposition}
-
-While our groups $G$ may not have connected center, the function $\Phi(g)$ extends by zero to a class function on $\tilde{G}$ (see section 3.2) which does have connected center.
-Hence if a representation $\pi$ of $\tilde{G}$ deposes intorepresentations $\pi_1 \oplus \pi_2 \hdots \oplus \pi_r$ of $G$, $\dblGammaFactorSpace{\hermitianSpace}{\pi_1}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi_2}{\chi}{\fieldCharacter} =\hdots =\dblGammaFactorSpace{\hermitianSpace}{\pi_r}{\chi}{\fieldCharacter}$.
-
-\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
-	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
-	\begin{enumerate}
-		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
-	\end{enumerate}
-\end{proposition}
-\calvin{maybe say that cuspidal breaks into cuspidal pieces}
-So all the cuspidal $\pi$ in a Lusztig packet $\LusztigSeries{G}{s}$ are irreducible pieces in the restriction from $\GroupExtension{G}$ to $G$ of a single cuspidal representation $\tilde{\pi}$ of $\GroupExtension{G}$.
-
-\calvin{end alternate writeup}
-\calvin{start alternate writeup 2 of section 3.4/3.4.1}
-\subsection{Computation for Lusztig Series}
-The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
-\begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
-\end{theorem}
-\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
-\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
-We instead prove a version of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$ (see section 3.2) of $G$:
-\begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} Extend $\Phi_{\chi}$ by zero to $\GroupExtension{G}$.
-If $c_{\pi}$ is nonzero in the virtual representation $R_{T}(\theta) = \sum c_{\pi} \pi$ of $\GroupExtension{G}$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
-where the doubling factor is defined by
-\[
-\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} := \omega_{\pi}(-1)\frac{\sum_{g \in \GroupExtension{G}}\pi(g)\Phi_{\chi}(g)}{\sqrt{|g|}c_V(\chi,\pi)}
-\]
-\elad{Note that on page 6 we already defined $\dblJacobiSum{\pi}{\chi}$ by only summing on the $G$ points. Same for $\dblJacobiSumScalar{F}{\chi}$ on page 9.}
-\end{theorem}
-Any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
-\[
-    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
-\]
-
-The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only dependeing on $s$.
-Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions}.
-
-\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
-	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
-	\begin{enumerate}
-		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
-	\end{enumerate}
-\end{proposition}
-
-Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
-First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for all Levi factors.
-\\
-
-\begin{proof}
-\calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
-\end{proof}
-
-By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
-$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
-Since we know the relevant equality for non cupsidal $\pi$, we get that
-$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
-
-But it is well known that there is only one cuspidal $\pi$:
-\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
-	Let $\GroupExtension{G}$ have connected center.
-For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
-\end{proposition}
-
-So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} is complete.
-
-\calvin{end alternate writeup 2}
-
-\subsubsection{Proof of the main result \calvin{\Cref{thm:Phi_stable}}}
-
-\elad{Merge with Calvin's stuff}
-The \emph{Lusztig series} $\LusztigSeries{G}{s}$ consists of (equivalence classes of) the irreducible representations $\pi$ of $R_{T, \theta}$ with $c_{\pi} \ne 0$ as in the theorem.
-
-Let $L \subset G$ be a Levi subgroup of $G$, and suppose that $L \cong \prod_{j=1}^\ell \GL_{t_j}\left(\finiteField\right) \times G'$ where $G' = \IsometryGroup\left(\hermitianSpace'\right)$ where $\hermitianSpace'$ is a non-degenerate hermitian subspace and $\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic$, where $\xIsotropic$ and $\yIsotropic$ are totally isotropic subspace in duality.
-Suppose that $s \in L$, and denote by $s_i$ the projection of $s$ to $\GL_{t_i}\left(\finiteField\right)$ for $1 \le i \le \ell$ and by $s_0$ the projection of $s$ to $G'$.
-We denote
-$$\LusztigSeries{L}{s} = \left(\bigotimes_{j=1}^{\ell} \LusztigSeries{\GL_{t_j}\left(\finiteField\right)}{s_j}\right) \otimes \LusztigSeries{G'}{s_0}.$$
-
-We collect some facts that will be used for proving \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}.
-
-The following proposition allows us to make use of the multiplicativity property (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}) for non-cuspidal elements in a given Lusztig series.
-\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]
-	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
-\end{proposition}
-
-The following Proposition shows that is suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the group $\GroupExtension{G}$.
-\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
-	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
-	\begin{enumerate}
-		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
-	\end{enumerate}
-\end{proposition}
-
-Finally, the following proposition shows that the multiplicativity property takes care of all but at most one element in a given Lusztig series.
-\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
-	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
-\end{proposition}
-
-\Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is now equivalent to the following statement.
-\begin{proposition}\label{prop:gamma-factor-is-constant-on-lusztig-series}
-	Keep the notations as above.
-Suppose that $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$.
-Then for any irreducible cuspidal $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{\FrobeniusFixedPoints{P}}{\FrobeniusFixedPoints{\GroupExtension{G}}}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{\GroupExtension{G}, \chi, \fieldCharacter}\left(s\right).$$
-	\elad{Many things are not defined anymore. Need to define $\tau_{\GroupExtension{G}, \chi, \fieldCharacter}\left(s\right)$, etc.}
-\end{proposition}
-\begin{proof}
-	The proof is by induction on $\dim_{\quadraticExtension} \hermitianSpace$.
-
-	Suppose first that $L \ne G$.
-Then by using the multiplicativity property repeatedly (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}), we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \cdot \prod_{j=1}^r \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j\right) \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j^{-1}\right),$$
-	where $\pi'$ is an irreducible cuspidal representation of $G'$ that lies in the Lusztig series $\LusztigSeries{\pi'}{s_0}$.
-By the induction hypothesis, we have $$\dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} = \tau_{G', \chi, \fieldCharacter}\left(s_0\right),$$
-	which implies the result.
-
-	Next, suppose that $L = G$ and that $\pi = \sigma$ is an irreducible cuspidal representation. Let us write $$R_{T, \theta} = \sum_{\Pi} c_\Pi \trace \Pi,$$
-	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualJacobiSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualJacobiSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
-	$$c_{\pi} \cdot \dblVirtualJacobiSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
-	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblJacobiSumScalar{\pi}{\chi}$, the result follows.
-\end{proof}
-
-\subsection{Kloosterman type sums}
-
-Let $\chi_1, \dots, \chi_k \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\chi_i^2 \ne 1$ for any $i$.
-Consider the assignment $K \colon G \to \cComplex$ given by $$K\left(x\right) = K_{\chi_1,\dots,\chi_k}\left(x\right) = \sum_{\substack{g_1, \dots, g_k \in G\\
-g_1 \dots g_k = x}} \Phi_{\chi_1}\left(g_1\right) \dots \Phi_{\chi_k}\left(g_k\right).$$
-It is clear that $K$ is a class function of $G$. Let $\pi$ be an irreducible representation of $G$. Then \begin{align*}
-	 \innerproduct{K}{\conjugate{\trace \pi}} &= \frac{1}{\sizeof{G}}\trace \left(\sum_{g_1,\dots,g_k \in G} \Phi_{\chi_1}\left(g_1\right) \dots \Phi_{\chi_k}\left(g_k\right) \pi\left(g_1 \dots g_k\right) \right) \\
-	 &= \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}}}{\sizeof{G}} \trace\left( \dblJacobiSum{\pi}{\chi_1} \circ \dots \dblJacobiSum{\pi}{\chi_k} \right).
-\end{align*}
-Thus $$\innerproduct{K}{\conjugate{\trace \pi}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \dim \pi}{\sizeof{G}} \cdot \prod_{j=1}^k \dblJacobiSumScalar{\pi}{\chi_j}.$$
-It follows that if
-$$\DeligneLusztigInduction{T}{G}\theta = \sum_{\pi} c_{\pi} \cdot \trace \pi,$$
-then $$\innerproduct{K}{\conjugate{\DeligneLusztigInduction{T}{G}\theta}} = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblJacobiSumScalar{\pi}{\chi_j}}{\sizeof{G}} \sum_{\pi} c_{\pi} \dim \pi = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \prod_{j=1}^k \dblJacobiSumScalar{\pi}{\chi_j}}{\sizeof{G}} \left(\DeligneLusztigInduction{T}{G}\theta\right)\left(1\right),$$
-where $\pi$ is any irreducible representation of $G$ such that $c_{\pi} \ne 0$.
-
-Suppose that $T \cong \NormOneGroup{2m}$, and let $t \in T$ be an element such that $t$ is contained only in the torus $T$. Then
-$$K\left(t\right) = \sum_{\theta} \theta\left(t\right) \innerproduct{K}{\DeligneLusztigInduction{T}{G}\left(\theta\right)},$$
-where the sum is over all the characters of $T$.
-Using the formula $$\dblJacobiSumScalar{\pi}{\chi} = \tau\left( \theta' \times \chi^{-1}, \fieldCharacter_{2m} \right) \theta\left(-1\right) \tau\left(\chi^2, \fieldCharacter\right)^m,$$
-we get
-$$K\left(t\right) = \frac{\sizeof{\lieAlgebra}^{\frac{k}{2}} \cdot \DeligneLusztigInduction{T}{G}\left(\theta\right)\left(1\right)}{\sizeof{G}} \sum_{\theta} \theta\left( \left(-1\right)^k t\right) \prod_{j=1}^k \tau\left(\theta' \times \chi_j^{-1}, \fieldCharacter_{2m}\right) \tau\left(\chi_j^2, \fieldCharacter\right)^m.$$
-
-Expanding the last sum, we have
-\begin{align*}
-	K\left(t\right) = & \frac{\left(-1\right)^k q^{-km}  \sizeof{\lieAlgebra}^{\frac{k}{2}} \DeligneLusztigInduction{T}{G}\left(\theta\right)\left(1\right)}{\sizeof{G}} \cdot \prod_{j=1}^k \tau\left(\chi_j^2, \fieldCharacter\right)^m \\
-	 & \times \sum_{\theta} \sum_{\xi_1,\dots,\xi_k \in \multiplicativegroup{\finiteFieldExtension{2m}}} \theta\left( \left(-1\right)^k t \xi_1^{1-q^m} \dots \xi_k^{1-q^m} \right) \fieldCharacter_{2m}\left(\sum_{j=1}^k \xi_j\right) \prod_{j=1}^k \chi_j\left(\FieldNorm{2m}{1}\left(\xi_1^{-1} \right)\right).
-\end{align*}
-The sum on the second row becomes
-$$\sum_{\substack{\xi_1,\dots,\xi_k \in \multiplicativegroup{\finiteFieldExtension{2m}}\\
-\prod_{j=1}^k \xi_j^{1-q^m} = \left(-1\right)^k t^{-1}}} \left(\prod_{j=1}^k \chi_j^{-1}\left(\FieldNorm{2m}{1}\left(\xi_j \right)\right)\right) \fieldCharacter_{2m}\left(\sum_{j=1}^k \xi_j\right).$$
-
-\appendix
-\section{Evaluation of norm one exponential sums}
-
-In this appendix, we evaluate several exponential sums.
-
-\subsection{The case $\quadraticExtension = \finiteField$}
-Let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character. We compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-	\trace_{\finiteFieldExtension{2} \slash \finiteField}\left(x\right) \ne 0}} \chi\left(\FieldNorm{2}{1}\left(\frac{x}{\trace_{\finiteFieldExtension{2} \slash \finiteField} x}\right) \right).$$
-As usual, we rewrite this sum as
-$$\frac{1}{q} \sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}} \chi\left(\FieldNorm{2}{1}\left(xy\right)\right) \fieldCharacter\left(z\left(y \trace_{\finiteFieldExtension{2} \slash \finiteField} x - 1\right)\right).$$
-It is clear that if $z = 0$, then the sum over $x$ will vanish.
-Hence, we may reduce the sum to a sum over $z \in \multiplicativegroup{\finiteField}$.
-By replacing $y$ with $z^{-1} y$ and then replacing $z$ with $-z$, we arrive at the sum
-$$\frac{1}{q} \sum_{y \in \multiplicativegroup{\finiteField}} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}} \chi\left(\FieldNorm{2}{1}\left(xy\right)\right) \fieldCharacter\left(y \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{z \in \multiplicativegroup{\finiteField}} \chi^{-2}\left(z\right)\fieldCharacter\left(z\right).$$
-Replacing $x$ with $y^{-1}x$, and using the Hasse--Davenport relation, we arrive at the sum
-$$q^{\frac{1}{2}} \left(q-1\right) \tau\left(\chi, \fieldCharacter\right)^2 \tau\left(\chi^{-2}, \fieldCharacter\right).$$
-
-\subsection{The case $\quadraticExtension \ne \finiteField$}
-Let $\chi \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ be a non-trivial character and let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\cComplex}$ be a character.
-Our goal is to compute $$\sum_{1 \ne x \in \NormOneGroup{2}} \theta\left(x\right) \chi\left(1-x\right).$$
-Using the Hilbert 90 map this is equivalent to
-$$\frac{1}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-x \notin \multiplicativegroup{\finiteField}}} \theta\left(\frac{x}{x^q}\right) \chi\left(1-\frac{x}{x^q}\right).$$
-Let $0 \ne \delta \in \multiplicativegroup{\finiteFieldExtension{2}}$ be a trace-zero element. Replacing $x$ with $\delta x$, we arrive at the sum
-$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-		x \notin \delta^{-1} \multiplicativegroup{\finiteField}}} \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right),$$
-	where $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ is given by $\theta'\left(x\right) = \theta\left(\frac{x}{x^q}\right)$.
-
-	As usual, we may rewrite the last sum as
-	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(y\right) \fieldCharacter\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
-	Since $\chi \ne 1$, the inner sum vanishes when $z = 0$, and therefore we can reduce the sum over $z$ to $z \in \multiplicativegroup{\finiteField}$.
-Changing variables $x \mapsto -z^{-1} x$ and $y \mapsto z^{-1} y$, and using the fact that $z^q = z$, we arrive at the sum
-	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \chi^{-q}\left(x\right) \fieldCharacter\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter\left(y\right),$$
-	which by changing variables $x \mapsto x^q$ equals
-	$$q^{\frac{1}{2}} \theta\left(-1\right) \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_2} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
+	We thus have
+	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
+\end{example}
 

### 2025-03-21 paper.tex
Changes with Calvin

@@
 Similarly, every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$.
-In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det \hermitianSpace = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
+In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det g = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
 There are two cases here.
@@
 \begin{example}
-	Take $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
+	Take $\algebraicGroup{G}' = \algebraicGroup{\GL}_2$.
+Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
 	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
@@
 	\begin{tabular}{ c c c c c c}
- Group & Fixed Torus & Frobenius on $X(T)$ & Frobenius on $W$ &Dual Group & Dual Torus \\ 
- $Sp(2n)$ & $(\multiplicativegroup{\finiteField})^n$ & 1 & 1 &$SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^n$\\  
- $GSp(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &$GSpin(2n+1)$ &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
- $SO(2n)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$SO(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
- $GO(2n)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ & 1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\
- $SO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n}$ & 1 & 1 &$Sp(2n)$ &  $(\multiplicativegroup{\finiteField})^{n}$ \\
- $GO(2n+1)$ & $(\multiplicativegroup{\finiteField})^{n+1}$ &1 & 1 &? &  $(\multiplicativegroup{\finiteField})^{n+1}$ \\ 
-  $U(n)$ & $(\NormOneGroup{2})^{n}$ & -1 & 1 & $U(n)$ &  $(\NormOneGroup{2})^{n}$ 
+		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$  \\
+		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \\		 
+		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \\	
+		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$\\  			 
+		$\algebraicGroup{\SO}^{+}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}^{+}_{2n}$ &  $\multiplcativeScheme^n$ \\
+		$\algebraicGroup{\SO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \left(-1\right)$ &$\algebraicGroup{\SO}^{-}_{2n}$ &  $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ \\
+		 $\algebraicGroup{\GSp}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 &$\algebraicGroup{GSpin}_{2n+1}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
+		 $\algebraicGroup{\GSO}^{+}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 & $\algebraicGroup{GSpin}_{2n}^{+}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
+		 $\algebraicGroup{\GSO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \sigma^{\ast}$ & $\algebraicGroup{GSpin}_{2n}^{-}$ &  $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$
 \end{tabular}
 \end{center}
-
-\calvin{non split form of $SO(even)$, is the dual group itself?.
-The torus I think is $(\mathbb{F}_2)^{Nm=1} \times (\mathbb{F}^\times)^{dim -1}$.
-The Frobenius action on the characters is $(-1,1,1,1\hdots 1)$ and on $W$ its trivial}
+For all the pairs $\algebraicGroup{T} \subset \algebraicGroup{G}$ in this list, the Frobenius root $\Frobenius$ of $\algebraicGroup{G}$ acts trivially on the Weyl group $W\left(\algebraicGroup{T}\right)$.
+In the last row, $\sigma \colon \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \to \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ is the automorphism $a + b\sqrt{d} \mapsto a - b\sqrt{d}$ where $d \in \multiplicativegroup{\finiteField}$ is a non-square.
 
@@
 \]
+\calvin{check if we need a $\chi$ in the $\tau$ factor}
 \Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
@@
 \end{theorem}
-
+\begin{comment}
 \calvin{start alternate writeup of section 3.4/3.4.1:}
@@
 \calvin{end alternate writeup}
+\end{comment}
 \calvin{start alternate writeup 2 of section 3.4/3.4.1}
@@
 \begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right)$$
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its group extension $\GroupExtension{G}$.
+If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
 \end{theorem}
@@
 \subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
-We instead prove a version of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$ (see section 3.2) of $G$:
-\begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} Extend $\Phi_{\chi}$ by zero to $\GroupExtension{G}$.
-If $c_{\pi}$ is nonzero in the virtual representation $R_{T}(\theta) = \sum c_{\pi} \pi$ of $\GroupExtension{G}$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
-where the doubling factor is defined by
-\[
-\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} := \omega_{\pi}(-1)\frac{\sum_{g \in \GroupExtension{G}}\pi(g)\Phi_{\chi}(g)}{\sqrt{|g|}c_V(\chi,\pi)}
-\]
-\elad{Note that on page 6 we already defined $\dblJacobiSum{\pi}{\chi}$ by only summing on the $G$ points. Same for $\dblJacobiSumScalar{F}{\chi}$ on page 9.}
-\end{theorem}
-Any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
+We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center.
+For any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
 \[
@@
 
-The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only dependeing on $s$.
-Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions}.
+The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only depending on $s$.
+Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$ (see section 3.2).
 
@@
 
+We now prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$.
+
 Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
-First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} for all Levi factors.
+First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
 \\
@@
 
-But it is well known that there is only one cuspidal $\pi$:
+But it is well known that there is only one cuspidal $\pi$ appearing in our sum:
 \begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
@@
 
-So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig-extensions} is complete.
+So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is complete.
 

### 2025-03-21 paper.tex
Calvin update
Adding signed Jacobi sums

@@
 \newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
-\newcommand{\dblJacobiSum}[2]{\mathcal{J}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblJacobiSum}[2]{\mathcal{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\posDblJacobiSum}[2]{\mathcal{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\negDblJacobiSum}[2]{\mathcal{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\JacobiKernel}[1]{\Phi_{#1}}
+\newcommand{\posJacobiKernel}[1]{\Phi^{+}_{#1}}
+\newcommand{\negJacobiKernel}[1]{\Phi^{-}_{#1}}
+\newcommand{\genJacobiKernel}[1]{\Phi^{\pm}_{#1}}
+
 \newcommand{\GaussSumScalar}[2]{\mathrm{G}\left(#1, #2\right)}
-\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}^{\mathrm{dbl}}\left(#1, #2\right)}
-\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblJacobiSumScalar}[2]{\mathrm{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\posDblJacobiSumScalar}[2]{\mathrm{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\negDblJacobiSumScalar}[2]{\mathrm{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
 \newcommand{\dblGammaFactor}[3]{\Gamma^{\mathrm{dbl}}\left(#1 \times #2, #3\right)}
@@
 $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-	\chi\left(\det\left(\IdentityMatrix{k}-g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}-g\right) \ne 0,\\
+	\chi\left(\det\left(\IdentityMatrix{k}+g\right)\right) & \text{if }\det\left(\IdentityMatrix{k}+g\right) \ne 0,\\
 	0 & \text{otherwise.}
@@
 Given an irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$, we consider the following \emph{doubling method Jacobi sum}:
-$$\dblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
-Then $\dblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$.
-Therefore, by Schur's lemma there exists a complex number $\dblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\dblJacobiSum{\tau}{\chi} = \dblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
-
-The goal of this section is to express $\dblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.
+$$\posDblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(g\right) \tau\left(g\right).$$
+Then $\posDblJacobiSum{\tau}{\chi}$ defines an element of $\Hom_{\GL_k\left(\finiteField\right)}\left(\tau, \tau\right)$.
+Therefore, by Schur's lemma there exists a complex number $\posDblJacobiSumScalar{\tau}{\chi} \in \cComplex$ such that $$\posDblJacobiSum{\tau}{\chi} = \posDblJacobiSumScalar{\tau}{\chi} \cdot \idmap_\tau.$$
+
+The goal of this section is to express $\posDblJacobiSumScalar{\tau}{\chi}$ in terms of Kondo's Gauss sum.
 
@@
 	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
+			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
 \end{proposition}
 \begin{proof}
-	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det\left(-h\right)\right).$$
+	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$.
-Thus	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g-\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
+Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
 	Changing variables $h \mapsto X^{-1} h$, we get
-	$$\Phi_{\chi}\left(g\right) = \frac{\chi\left(-1\right)^k}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(-\trace X\right).$$
-	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $-X = y$, we get  
+	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(\trace X\right).$$
+	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $X = y$, we get  
 	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
-			y^{-1} x = -g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
+			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
 \end{proof}
 
-We now use this to compute $\dblJacobiSum{\tau}{\chi}$.
-We have that $$\dblJacobiSum{\tau}{\chi} = \chi\left(-1\right)^k q^{-k^2} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(-y^{-1} x\right).$$
+We now use this to compute $\posDblJacobiSum{\tau}{\chi}$.
+We have that $$\posDblJacobiSum{\tau}{\chi} = q^{-k^2} \chi\left(-1\right)^k \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(y^{-1} x\right).$$
 The last equality implies the following result.
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\dblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
 \end{theorem}
+
+We can define analogous sums $\negDblJacobiSum{\tau}{\chi}$ and $\negDblJacobiSumScalar{\tau}{\chi}$ by the formulas
+$$\negDblJacobiSum{\tau}{\chi} = q^{-\frac{k^2}{2}} \sum_{g \in \GL_k\left(\finiteField\right)} \Phi_{\chi}\left(-g\right) \tau\left(g\right) = \negDblJacobiSumScalar{\tau}{\chi} \cdot \idmap_{\tau}.$$
+Then we have the simple relation
+$$\negDblJacobiSumScalar{\tau}{\chi} = \centralCharacter{\tau}\left(-1\right) \posDblJacobiSumScalar{\tau}{\chi}.$$
 
@@
 Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
-As before, the assignment $\Phi_{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\Phi_{\chi}\left(g\right) = \begin{dcases}
-\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} - g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} - g\right) \ne 0\\
+As before, the assignment $\JacobiKernel{\chi} \colon \GL_{\quadraticExtension}\left(\hermitianSpace\right) \to \cComplex$ given by $$\JacobiKernel{\chi}\left(g\right) = \begin{dcases}
+\chi\left(\detQuadratic\left( \idmap_{\hermitianSpace} + g\right)\right) & \text{if }\detQuadratic\left( \idmap_{\hermitianSpace} + g\right) \ne 0\\
 0 & \text{otherwise,}
@@
 is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
+Denote for $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$, $\posJacobiKernel{\chi}\left(g\right) = \JacobiKernel{\chi}\left(g\right)$ and $\negJacobiKernel{\chi}\left(g\right) = \JacobiKernel{\chi}\left(-g\right)$.
 
 Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
-Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \Phi_{\chi}\left(g\right).$$
-Since $\Phi_{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$.
+Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \genJacobiKernel{\chi}\left(g\right).$$
+Since $\genJacobiKernel{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$.
 Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
 By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
-We call $\dblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sum}.
+We call $\posDblJacobiSumScalar{\pi}{\chi}$ and $\negDblJacobiSumScalar{\pi}{\chi}$ the \emph{doubling method Jacobi sums}.
 
@@
 Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
-	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(-1\right) \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
+	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(\pm 1\right) \chi\left(\pm 1\right)^k \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 
-	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \Phi_{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \Phi_{\chi}\left(x^{-1} p\right),$$
+	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
 	which can be rewritten as
-	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \Phi_{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
+	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
 	As before, we may write
-	$$\Phi_{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic \left(-h\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(g - \idmap_{\hermitianSpace} - h\right)\right)\right).$$
+	$$\genJacobiKernel{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm g - h \right)\right)\right).$$
 	Hence, \begin{align*}
-		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(Ah\right)\right) \\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		q^{k^2} \sum_{p \in P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
-Let us replace $h$ with $A^{-1} h$.
+Let us replace $h$ with $-A^{-1} h$.
 We get the sum
 	\begin{align*}
-		\sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right) \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(xp - \idmap_{\hermitianSpace}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A x l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
-	The inner sum over $N$ will vanish unless $Ax \in P$. Thus we have
+		& \chi\left(-1\right)^k \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right)\\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1}p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(\pm A x^{-1} l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
+	The inner sum over $N$ will vanish unless $\pm Ax^{-1} \in P$ \elad{This is not true in general}. Thus we have
 	\begin{align*}
-		\chi\left(-1\right)^k q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
-		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left(p - x^{-1}\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p - x^{-1} \in P$, which implies that $x \in P \cap G$.
+		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
+		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left( p \mp x  \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p \mp x \in P$, which implies that $x \in P \cap G$.
 
@@
 		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
-				\detQuadratic\left(p - \idmap_{\hermitianSpace}\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+				\detQuadratic\left(\idmap_{\hermitianSpace}\pm p\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
 	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} - p\right) = \left(-1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} - a\right) \det\left(\involution{\left(\IdentityMatrix{k} - a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} - g'\right),$$
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right) = \left(\mp 1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} \pm a\right) \det\left(\involution{\left(\IdentityMatrix{k} \pm a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} \pm g'\right),$$
 	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
@@
 	\begin{equation}
-		\chi\left(-1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \Phi_{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \Phi_{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+		\chi\left(\mp 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genJacobiKernel{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
 	\end{equation}
@@
 	\begin{align*}
-		&\chi\left(-1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
-		=& \chi\left(-1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+		&\chi\left(\mp 1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
+		=& \chi\left(\mp 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
 	\end{align*}
@@
 
-Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \Phi_{\chi}\left(g\right).$$
+Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genJacobiKernel{\chi}\left(g\right).$$
 
@@
 	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{H}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genJacobiKernel{\chi}\left(t\right).$$
 \end{proposition}
 In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
-$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \Phi_{\chi}\left(t\right).$$
+$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genJacobiKernel{\chi}\left(t\right).$$
 Here $\varepsilon_{\algebraicGroup{H}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{H}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{H}_p$ is the size of the $p$-Sylow group of $H$, where $p$ is the characteristic of $\finiteField$.
@@
 
-The goal of this section is to compute $$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1-x\right)\right).$$
+The goal of this section is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+x \ne -1}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1+x\right)\right).$$
 Let us rewrite this as
-$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\left(-1\right)^k\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
+$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
 Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
-$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x - 1\right)\right)z\right).$$
-Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$, this becomes
-$$q^{-k} \alpha\left(-1\right) \chi\left(-1\right)^k \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
+$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
+Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$ and $z$ with $-z$, this becomes
+$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
 Hence, we have the identity
-$$\sum_{x \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x-1\right)\right) = -q^{\frac{k}{2}} \chi\left(-1\right)^k \alpha\left(-1\right) \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
+$$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+x \ne -1}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x+1\right)\right) = -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
 
@@
 Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 - x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 - \minusInvolution{x}\right)\right).$$
+		x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right).$$
 This can be rewritten as
-$$\chi\left(-1\right)^k \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne 1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(1 - x\right)\right).$$
+$$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+		x \ne -1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(1 + x\right)\right).$$
 By the previous section, this equals
 \begin{equation*}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation*}
@@
 \begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
-	-q^{\frac{k}{2}} \alpha\left(-1\right)  \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation}
 
-Notice that if $k = md$ and $\alpha = \beta \circ \FieldNorm{k}{m}$ where $\beta \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ is a character, then \eqref{eq:identity-for-multiplicative-group-of-f-k-gauss-sum} equals
-$$-\left(q^{\frac{m}{2}} \GaussSumCharacter{\beta^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \GaussSumCharacter{\involution{\beta}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{m}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^m\right)^{d}.$$
-
-\begin{remark}
-	Changing variables $x \mapsto -x$, we have that \begin{align*}
+Changing variables $x \mapsto \pm x$, we obtain the following.
+
+\begin{theorem}We have the following identity:
+\begin{align*}
 	& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-				x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
-			=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
-	\end{align*}
-\end{remark}
+			x \ne \mp 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 \pm x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 \pm \minusInvolution{x}\right)\right) \\
+	=& -\alpha\left(\pm 1\right) q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+\end{align*}
+\end{theorem}
 
@@
 Our goal is to compute $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(1 - x\right)\right).$$
+		x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \quadraticExtension}\left(1 + x\right)\right).$$
 
@@
 As usual, we rewrite the sum as follows
-$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(-y\right)\right) \fieldCharacter_{2m}\left(z\left(y-x+1\right)\right).$$
-
-If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ we get the sum
-$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(-x\right) \fieldCharacter_{2m}\left(xz\right).$$
+$$q^{-2m} \sum_{z \in \finiteFieldExtension{2m}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{2m}}} \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(y\right)\right) \fieldCharacter_{2m}\left(z\left(y-\left(1+x\right)\right)\right).$$
+
+If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ and $z$ with $-z$, we get the sum
+$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right).$$
 To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \NormOneGroup{2m}$ given by $t \mapsto t^{1 - q^m}$.
@@
 	& \sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne 1}} \theta \left(-x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) \\
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) \\
 		=& q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 - x\right)\right) = \theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
-\begin{remark}
-	Changing variables $x \mapsto -x$, we have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
 		x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
-\end{remark}
+Changing variables $x \mapsto \pm x$, we obtain the following. \begin{theorem}
+	We have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
+			x \ne \mp 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 \pm x\right)\right) = \theta\left(\pm 1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+\end{theorem}
 
@@
 $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-		x \ne 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 - x\right)\right).$$
+		x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right).$$
 By the appendix, this equals
-$$\theta\left(-1\right) q^{\frac{m}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
+$$q^{\frac{m}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
 which equals
-$$\theta\left(-1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}.$$
+$$q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}.$$
+
+Changing variables $x \mapsto \pm x$, we obtain the following.
+\begin{theorem}
+	We have the following identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = \theta\left(\pm 1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}$$
+\end{theorem}
 
@@
             1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
+    \end{enumerate}
+    \calvin{new cases:}
+    \begin{enumerate}
+        \item When $\Frobenius$ acts by an $n$-cycle $(12 \hdots n)$ on the preimage and the cycle $(12 \hdots n),(n+1,n+2 \hdots 2n)$ on the image, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
+        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
+            0 & 1 \\
+            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
+        \item When 
     \end{enumerate}
@@
 Let $\chi \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ be a non-trivial character and let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\cComplex}$ be a character.
-Our goal is to compute $$\sum_{1 \ne x \in \NormOneGroup{2}} \theta\left(x\right) \chi\left(1-x\right).$$
+Our goal is to compute $$\sum_{-1 \ne x \in \NormOneGroup{2}} \theta\left(x\right) \chi\left(1+x\right).$$
 Using the Hilbert 90 map this is equivalent to
 $$\frac{1}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-x \notin \multiplicativegroup{\finiteField}}} \theta\left(\frac{x}{x^q}\right) \chi\left(1-\frac{x}{x^q}\right).$$
-Let $0 \ne \delta \in \multiplicativegroup{\finiteFieldExtension{2}}$ be a trace-zero element. Replacing $x$ with $\delta x$, we arrive at the sum
-$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
-		x \notin \delta^{-1} \multiplicativegroup{\finiteField}}} \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right),$$
+x \notin \delta \multiplicativegroup{\finiteField}}} \theta\left(\frac{x}{x^q}\right) \chi\left(1+\frac{x}{x^q}\right),$$
+Where $\delta \in \multiplicativegroup{\finiteFieldExtension{2}}$ is a trace zero element. 
+We arrive at the sum
+$$\frac{1}{q-1} \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{2}}\\
+		x \notin \delta \multiplicativegroup{\finiteField}}} \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right),$$
 	where $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\cComplex}$ is given by $\theta'\left(x\right) = \theta\left(\frac{x}{x^q}\right)$.
 
-	As usual, we may rewrite the last sum as
-	$$\frac{\theta\left(-1\right) \chi\left(-1\right)}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(y\right) \fieldCharacter\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} x\right)\right).$$
+	We have that $x \in \multiplicativegroup{\finiteFieldExtension{2}}$ satisfies $x \notin \delta \multiplicativegroup{\finiteField}$ if and only if $\trace_{\finiteFieldExtension{2} \slash \finiteField}\left(x\right) \ne 0$.
+As usual, we may use this last condition to rewrite the sum as
+	$$\frac{1}{q\left(q-1\right)} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\sum_{z \in \finiteField} \sum_{y \in \multiplicativegroup{\finiteField}}  \theta'\left(x\right) \chi^{-q}\left(x\right) \chi\left(y\right) \fieldCharacter\left(z\left(y - \trace_{\finiteFieldExtension{2} \slash \finiteField} \left(x\right)\right)\right).$$
 	Since $\chi \ne 1$, the inner sum vanishes when $z = 0$, and therefore we can reduce the sum over $z$ to $z \in \multiplicativegroup{\finiteField}$.
 Changing variables $x \mapsto -z^{-1} x$ and $y \mapsto z^{-1} y$, and using the fact that $z^q = z$, we arrive at the sum
-	$$\frac{\theta\left(-1\right)}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \chi^{-q}\left(x\right) \fieldCharacter\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} x\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter\left(y\right),$$
+	$$\frac{1}{q} \sum_{x \in \multiplicativegroup{\finiteFieldExtension{2}}}\theta'\left(x\right)  \chi^{-q}\left(x\right) \fieldCharacter\left(\trace_{\finiteFieldExtension{2} \slash \finiteField} \left(x\right)\right) \sum_{y \in \multiplicativegroup{\finiteField}}   \chi\left(y\right) \fieldCharacter\left(y\right),$$
 	which by changing variables $x \mapsto x^q$ equals
-	$$q^{\frac{1}{2}} \theta\left(-1\right) \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_2} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
+	$$q^{\frac{1}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
 

### 2025-03-24 paper.tex
Comment
Calvin changes

@@
 	\item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}
-	\item We might be able to include $SO_{odd}$ with $\Phi(g)$ the symmetric function in the eigenvalues of $g$ given by $\sum_{i=1}^{dim(V)} \chi(\Pi_{j \neq i}(\lambda_j-1))$.
 
@@
 	\begin{align*}
-		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right).
-	\end{align*}
+		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(\pm 1\right) \cdot \prod_{j=1}^r \alpha_j\left(\pm 1\right).
+	\end{align*}
+	\elad{Modify this so it is also true in the odd special orthogonal group case: it is zero for $-$ and there are factors $\theta\left(2\right)$ for $+$}
 \end{theorem}
@@
     \calvin{new cases:}
+    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-x)$.
+Then we have the following cases corresponding to conjugacy classes in the Weyl group
     \begin{enumerate}
-        \item When $\Frobenius$ acts by an $n$-cycle $(12 \hdots n)$ on the preimage and the cycle $(12 \hdots n),(n+1,n+2 \hdots 2n)$ on the image, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
-        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
-            0 & 1 \\
-            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
-        \item When 
+        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
+        \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
+ In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
+    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} w & 0 \\
+        0 & w
+        \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
+        \end{pmatrix}$  on the image, and 
+        \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} w & 0 \\
+        0 & w
+        \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
+        \end{pmatrix}$ on the image , and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
     \end{enumerate}
@@
 \begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its group extension $\GroupExtension{G}$.
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its extension $\GroupExtension{G}$.
 If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
@@
 \end{theorem}
-\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$.
-\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:Phi_stable}}
+\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$, implying \Cref{thm:Phi_stable}.
+\subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}}
 We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center.
@@
 
+Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
 By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
 $$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
-Since we know the relevant equality for non cupsidal $\pi$, we get that
+Subtracting our the equality for non-cupsidal $\pi$ we are left with:
 $$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
@@
 \begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
-	Let $\GroupExtension{G}$ have connected center.
+	Let $\GroupExtension{G}$ be a classical group with connected center.
 For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.

### 2025-03-24 paper.tex
Jacobi sums modification

@@
 \newcommand{\dblVirtualJacobiSumScalar}[2]{\mathrm{j}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblPosVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
+\newcommand{\dblNegVirtualJacobiSumScalar}[2]{\mathrm{j}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
 \newcommand{\posDblVirtualJacobiSumScalar}[2]{\mathrm{j}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
@@
 We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField\\
-	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField
-\end{dcases}.$$
+	\tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
+	\chi\left(2\right) \tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
+	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
+\end{dcases}$$
 Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.
@@
 For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \centralCharacter{\pi}\left(-1\right) \frac{\dblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
+For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 	However, we will not need this version for our purposes.
+\elad{Check odd orthogonal case.
+Probably needs a sign modification (the formula needs to be $\left(-1\right)^{\text{dual group dimension}} \times \text{product of Gauss sums}$).
+$\varepsilon_{\algebraicGroup{G}}$ contributes half of the dimension so that's why we add another half here.}
 \end{remark}
@@
 It is clear that if $\pi$ is an irreducible representation of $H$ then $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \dim \pi.$$
-Notice that the assignment $g \mapsto \Phi_{\chi}\left(g\right)$ only depends on the semisimple part of $g \in H$. By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
+Notice that the assignments $g \mapsto \posJacobiKernel{\chi}\left(g\right)$ and $g \mapsto \negJacobiKernel{\chi}\left(g\right)$ only depends on the semisimple part of $g \in H$.
+By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
@@
 which equals
-\begin{equation}\label{eq:identity-for-multiplicative-group-of-f-k-gauss-sum}
+\begin{equation*}
 	-q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
-\end{equation}
-
-Changing variables $x \mapsto \pm x$, we obtain the following.
-
-\begin{theorem}We have the following identity:
+\end{equation*}
+Thus we obtained the following.
+\begin{theorem}We have the identity
 \begin{align*}
 	& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-			x \ne \mp 1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 \pm x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 \pm \minusInvolution{x}\right)\right) \\
-	=& -\alpha\left(\pm 1\right) q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+			x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
+	=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
 \end{align*}
@@
 where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
-Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the identity
-$$\sum_{\substack{x \in \NormOneGroup{2m}\\
+Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the following. \begin{theorem}
+	We have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
 			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
-Changing variables $x \mapsto \pm x$, we obtain the following. \begin{theorem}
-	We have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne \mp 1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 \pm x\right)\right) = \theta\left(\pm 1\right) q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
 \end{theorem}
@@
 
-Changing variables $x \mapsto \pm x$, we obtain the following.
+Thus, we obtained the following.
 \begin{theorem}
 	We have the following identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = \theta\left(\pm 1\right) q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}$$
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}$$
 \end{theorem}
@@
 	\begin{align*}
-		 \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) \prod_{i=1}^s \theta_i\left(\pm 1\right) \cdot \prod_{j=1}^r \alpha_j\left(\pm 1\right).
-	\end{align*}
-	\elad{Modify this so it is also true in the odd special orthogonal group case: it is zero for $-$ and there are factors $\theta\left(2\right)$ for $+$}
+		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),
+	\end{align*}
+	and \begin{align*}
+		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \begin{dcases}
+			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd.}\\
+			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right) & \text{ otherwise.}
+		\end{dcases}
+	\end{align*}
 \end{theorem}
 \begin{proof}
-	This follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
+	Notice that if $\dim_{\finiteField} \hermitianSpace$ is odd then $\negJacobiKernel{\chi}\left(t\right) = 0$ for any $t \in T$, as $\idmap_{\hermitianSpace} - t$ always has determinant zero.
+
+	We have that if $t$ corresponds to $\left(a_1,\dots,a_r,t_1,\dots,t_s\right) \in \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \NormOneGroup{2m_i}$ such that $\idmap_{\hermitianSpace} + t$ is invertible then \begin{align*}
+		\posJacobiKernel{\chi}\left(t\right) =& \prod_{i=1}^s \chi\left(\FieldNorm{2m_i}{1}\left(1 + t_i\right)\right) \cdot \prod_{j=1}^r \chi\left(\aFieldNorm_{\quadraticFieldExtension{k_j} / \quadraticExtension}\left(1 + a_j\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k_j} / \quadraticExtension}\left(1 + \minusInvolution{a_j}\right)\right) \\
+		& \times  \begin{dcases}
+			\chi\left(2\right) & \dim_{\finiteField} \hermitianSpace \text{ is odd},\\
+			1 & \text{otherwise}
+		\end{dcases}.
+	\end{align*}
+	If $t$ corresponds to $\left(a_1,\dots,a_r,t_1,\dots,t_s\right) \in \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \NormOneGroup{2m_i}$ such that $\idmap_{\hermitianSpace} - t$ is invertible then \begin{align*}
+		\negJacobiKernel{\chi}\left(t\right) =& \begin{dcases}
+			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd},\\
+			\posJacobiKernel{\chi}\left(-t\right) & \text{otherwise.}
+		\end{dcases}
+	\end{align*}
+
+	Hence our theorem follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
 	and the fact \begin{equation*}
@@
 \begin{remark}
-	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}}.$$ If $\finiteField = \quadraticExtension$ then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
+	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}.$$ If $\finiteField = \quadraticExtension$ and $\dim_{\finiteField} \hermitianSpace$ is even then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
 \end{remark}
@@
 	Thus \begin{align*}
-		\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
+		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
 	\end{align*}
@@
 \label{thm:Phi_stable}
-	The assignment $H \to \cComplex$ given by $$h \mapsto \begin{dcases}
-		\chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} - h\right)\right) & h \in G \text{ and } \detQuadratic\left(\idmap_{\hermitianSpace} - h\right) \ne 0,\\
+	The assignments $H \to \cComplex$ given by $$h \mapsto \begin{dcases}
+		\chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm h\right)\right) & h \in G \text{ and } \detQuadratic\left(\idmap_{\hermitianSpace} \pm h\right) \ne 0,\\
 		0 & \text{otherwise.}
-	\end{dcases}$$ is a stable function. Equivalently, the assignment $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ is constant on geometric Lusztig series.
+	\end{dcases}$$ are stable functions. Equivalently, the assignments $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ are constant on geometric Lusztig series.
 \end{theorem}

### 2025-03-24 reorganization.tex
Reorganizing the document

--- 2025-03-24 paper.tex
@@
 \newcommand{\genJacobiKernel}[1]{\Phi^{\pm}_{#1}}
+\newcommand{\genHermitianJacobiKernel}[2]{\Phi^{\pm}_{#1,#2}}
 
@@
 
-\subsection{TODO list}
-\begin{enumerate}
-	\item In the computations of $\dblGammaFactor{\pi}{\chi}{\fieldCharacter}$ in terms of Deligne--Lusztig we should say that when we take a torus of $\GroupExtension{G}$ and intersect it with $G$ we get a torus of $G$ and hence it suffices to compute whatever we are computing.
-	\item The proof of \Cref{prop:gamma-factor-is-constant-on-lusztig-series} should be modified.
-We should first use $\GroupExtension{G}$.
-For this group we have the ``at most one cuspidal'' property.
-Then we should use \cite[Page 140]{DigneMichel2020} $$R_{\GroupExtension{T}}^{\GroupExtension{G}}\left(\tilde{\theta}\right) \restriction_{G} = R_{T}^G \left(\tilde{\theta}\restriction_{T}\right),$$
-	where we need to explain the notation.
-	\item Find what the root data + F action for the non-split quadratic form is. Find the dual gorup and add the appropriate representation to \Cref{lem:indep_geo_conj}
-
-\end{enumerate}
-
-\section{Notation}
+\section{Introduction}
+
+\section{Preliminaries}
 Let $\finiteField$ be a finite field with $q$ elements, where $2 \nmid q$, and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
@@
 For any $k \ge 1$, let $\finiteFieldExtension{k} \slash \finiteField$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
-
-\section{Kondo Gauss sums}
+If $k' \mid k$, let $\FieldNorm{k}{k'} \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\finiteFieldExtension{k'}}$ be the norm map.
+
+\subsection{Representation theory of $\GL_n\left(\finiteField\right)$}
+
+\subsection{Gauss sums}
+
+\subsubsection{Gauss sum notations}
+If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
+where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
+$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
+
+\subsubsection{Kondo Gauss sums}
+
 Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. 
@@
 This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo.
-
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo \cite{Kondo1963}.
+
+\begin{theorem}
+	Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\theta_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$.
+Then
+	$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\theta_j}{\chi}{\fieldCharacter_{n_j}}.$$
+\end{theorem}
+
+We will need the following lemma that allows us to determine that a degenerate Kondo Gauss sum vanishes.
 \begin{lemma}\label{lem:sum-vanishes-for-singular-matrices}
@@
 
+\subsection{Classical groups}
+
+In this section, we recall the notion of classical groups and their corresponding similitude groups. These are the main groups which we will study in this paper.
+
+\subsubsection{$\epsilon$-sesquilinear spaces}
+Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$ contained in $\algebraicClosure{\finiteField}$.
+For any $k \ge 1$, let $\quadraticFieldExtension{k} \slash \quadraticExtension$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
+Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.
+
+Let $\hermitianSpace$ be a vector space of dimension $n$ over $\quadraticExtension$, equipped with a non-degenerate sesquilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \quadraticExtension$ which is $\epsilon_{\hermitianSpace}$-symmetric for $\epsilon_{\hermitianSpace} \in \left\{\pm 1\right\}$.
+By this we mean that:
+\begin{enumerate}
+	\item For every $x_1,x_2,y \in \hermitianSpace$, $$\innerproduct{x_1 + x_2}{y} = \innerproduct{x_1}{y} + \innerproduct{x_2}{y}.$$
+	\item For every $x,y \in \hermitianSpace$ and $t \in \quadraticExtension$, $$\innerproduct{tx}{y} = t\innerproduct{x}{y}.$$
+	\item ($\epsilon_{\hermitianSpace}$-symmetric) For every $x,y \in \hermitianSpace$, $$\innerproduct{x}{y} = \epsilon_{\hermitianSpace} \involution{\innerproduct{y}{x}}.$$
+	\item (non-degenerate) For every $0 \ne x \in \hermitianSpace$ there exists $y \in \hermitianSpace$ such that $$\innerproduct{x}{y} \ne 0.$$
+\end{enumerate}
+
+\subsubsection{Isometry groups}\label{subsec:isometry-groups}
+Let $\IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+We denote by $G$ the identity component of $\IsometryGroup\left(\hermitianSpace\right)$.
+For the purposes of later sections, it would be useful to realize $G$ as the $\finiteField$ points of an algebraic group $\algebraicGroup{G}$.
+We explain how the possible options for $G$ and the corresponding group $\algebraicGroup{G}$ in the following list.
+
+Let $$w_n = \begin{pmatrix}
+	& & & 1\\
+	& & 1\\
+	& \iddots\\
+	1
+\end{pmatrix} \in \GL_n\left(\finiteField\right)$$ be the longest Weyl element.
+\begin{enumerate}
+	\item (Special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
+It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$.
+In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det g = 1$.
+There are two cases here.
+	\begin{enumerate}
+		\item Split case: in this case, we can write $$\hermitianSpace = \begin{dcases}
+		\xIsotropic \oplus \yIsotropic & \dim_{\finiteField} \hermitianSpace = 2n\\
+		\xIsotropic \oplus \finiteField v \oplus \yIsotropic & \dim_{\finiteField}\hermitianSpace = 2n + 1
+		\end{dcases}$$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
+In the odd dimensional case, $v \in \hermitianSpace$ is an element orthogonal to $\xIsotropic$ and $\yIsotropic$ that satisfies $\innerproduct{v}{v} \ne 0$.
+
+		In either case, denote $d = \dim_{\finiteField} \hermitianSpace$.
+We have that $G$ is isomorphic to $\SO^{+}_{d}\left(\finiteField\right) \subset  \GL_{d}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{d} = \left\{g \in \algebraicGroup{\GL}_{d} \mid \transpose{g} w_{d} g  = w_{d},\,\, \det g = 1\right\}.$$
+
+		In the odd-dimensional case $d = 2n+1$, we are always in this situation, and we simply denote $\SO_{2n+1}\left(\finiteField\right) = \SO_{2n+1}^{+}\left(\finiteField\right)$ and $\algebraicGroup{\SO}_{2n+1} = \algebraicGroup{\SO}_{2n+1}^{+}$.
+		\item Non-split case: In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ and there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
+		where $\xIsotropic$ and $\yIsotropic$ are totally isotropic spaces in duality and $\hermitianSpace'$ is an antisotropic space (that is, for any $0 \ne v' \in \hermitianSpace'$, we have $\innerproduct{v'}{v'} \ne 0$) of dimension 2.
+Let $d$ be an element of $\multiplicativegroup{\finiteField}$ that is not a square.
+Denote $$B_{n,d} = \begin{pmatrix}
+			\IdentityMatrix{n-1}\\
+			& & 1 &\\
+			& -d & &\\
+			& & & \IdentityMatrix{n-1}
+		\end{pmatrix} \cdot w_{2n}.$$
+		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
+	\end{enumerate}
+	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
+In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix} g = \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix}\right\}.$$
+	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
+Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
+In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
+\end{enumerate}
+
+Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
+
+\subsubsection{The group $\tilde{G}$ and similitude groups}\label{subsec:similitute-groups}
+In this section, we will introduce a group $\tilde{\algebraicGroup{G}}$ containing $\algebraicGroup{G}$ that has connected center.
+This will be important for later, as the Deligne--Lusztig theory  is easier  for $\tilde{\algebraicGroup{G}}$.
+
+If special odd orthogonal group case (that is, $\epsilon_{\hermitianSpace} = 1$, $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace$ is odd) and in the unitary case (that is, $\quadraticExtension \ne \finiteField$), we have that $\algebraicGroup{G}$ has connected center and we denote $\tilde{\algebraicGroup{G}} = \algebraicGroup{G}$.
+
+Let us assume that $\quadraticExtension = \finiteField$ and that $\dim_{\finiteField} \hermitianSpace$ is even.
+In this case, $\algebraicGroup{G}$ does not have a connected center.
+We extend $\algebraicGroup{G}$ to a group $\tilde{\algebraicGroup{G}}$ with connected center by considering the similitude group corresponding to $\hermitianSpace$.
+
+First, let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
+Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
+The group $\GroupExtension{G}$ has connected center and contains $G$.
+
+We write a more explicit description of $\tilde{G}$ and $\tilde{\algebraicGroup{G}}$.
+\begin{enumerate}
+	\item (Even special orthogonal groups): Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
+Every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$.
+Similarly to before, we obtain the connected components of the identity by adding a restriction on the determinant.
+The group $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
+We have the two cases from before here:
+	\begin{enumerate}
+		\item (Split case): The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{+}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
+		\item (Non-split case): The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{-}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
+	\end{enumerate}
+	\item The group $\GroupExtension{G}$ is isomorphic to the group $\GSp_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSp}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix} g = \lambda \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix}\right\}.$$
+\end{enumerate}
+
+\subsubsection{Tori}
+
+\elad{Under construction}
+If $m \ge 1$, we denote 
+$$\NormOneGroup{2m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
+
+\subsection{Deligne--Lusztig theory}
+\elad{Write a 101-intro to Deligne--Lusztig but not too detailed}
+
+\subsubsection{Geometric Conjugacy and Lusztig Series}
+Let $\ell$ be a prime number not equal to the characteristic of $\finiteField$. Fix an isomorphism $\ladicnumbers \cong \cComplex$.
+
+Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal $\Frobenius$-stable torus $\algebraicGroup{T} \subset \algebraicGroup{G}$ defined over $\finiteField$.
+We denote by $$\CharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\algebraicGroup{T}, \multiplcativeScheme\right)$$ the \emph{character lattice} of $\algebraicGroup{T}$ and by $$\CocharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\multiplcativeScheme, \algebraicGroup{T}\right)$$ the \emph{cocharacter lattice} of $\algebraicGroup{T}$, where we regard $\algebraicGroup{T}$ and $\multiplcativeScheme$ as algebraic groups over $\finiteField$.
+Recall that $\CharacterLattice{\algebraicGroup{T}}$ and $\CocharacterLattice{\algebraicGroup{T}}$ are free $\zIntegers$-modules of the same finite rank.
+The assignment $\CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \Hom_{\finiteField}\left(\multiplcativeScheme, \multiplcativeScheme\right)$ given by composition $\left(x,y\right) \mapsto \left(z \mapsto x\left(y\left(z\right)\right)\right)$ defines a pairing $\innerproduct{\cdot}{\cdot} \colon \CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \zIntegers$ by the rule $$x\left(y\left(z\right)\right) = z^{\innerproduct{x}{y}}.$$
+
+The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
+\[
+(\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
+\]
+such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.
+
+Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
+By \cite[Proposition 13.7 (ii)]{DigneMichel2020}, we have an exact sequence
+\begin{equation}
+	\label{eq:DL}
+	\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T} \ar[r] & 0}
+\end{equation}
+with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n))$
+for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
+Here, $$\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$$ is the torus norm map.
+
+We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\ladicnumbers}$ is a character.
+By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+\[
+\exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
+\]
+for large enough $n$.
+This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
+Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
+
+Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
+Similarly, denote the $\Frobenius$-stable Weyl group orbit in $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
+
+We say that the torus character pairs $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ for $\algebraicGroup{G}$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{\algebraicGroup{T},\theta})$ and $(s_{\algebraicGroup{T}',\theta'})$ are equal.
+This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
+
+\begin{example}
+	\elad{Correct example or remove it}
+	Take $\algebraicGroup{G}' = \algebraicGroup{\GL}_2$.
+Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
+	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
+Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
+	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.
+Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$.
+The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$.
+We thus have
+	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
+\end{example}
+
+The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
+
+\begin{center}
+	\begin{tabular}{ c c c c c c}
+		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$  \\
+		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \\		 
+		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \\	
+		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$\\  			 
+		$\algebraicGroup{\SO}^{+}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}^{+}_{2n}$ &  $\multiplcativeScheme^n$ \\
+		$\algebraicGroup{\SO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \left(-1\right)$ &$\algebraicGroup{\SO}^{-}_{2n}$ &  $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ \\
+		$\algebraicGroup{\GSp}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 &$\algebraicGroup{GSpin}_{2n+1}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
+		$\algebraicGroup{\GSO}^{+}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 & $\algebraicGroup{GSpin}_{2n}^{+}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
+		$\algebraicGroup{\GSO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \sigma^{\ast}$ & $\algebraicGroup{GSpin}_{2n}^{-}$ &  $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$
+	\end{tabular}
+\end{center}
+For all the pairs $\algebraicGroup{T} \subset \algebraicGroup{G}$ in this list, the Frobenius root $\Frobenius$ of $\algebraicGroup{G}$ acts trivially on the Weyl group $W\left(\algebraicGroup{T}\right)$.
+In the last row, $\sigma \colon \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \to \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ is the automorphism $a + b\sqrt{d} \mapsto a - b\sqrt{d}$ where $d \in \multiplicativegroup{\finiteField}$ is a non-square.
+
 \section{Doubling method Jacobi sums}
 
-\subsection{The case of general linear groups}
+\subsection{Definition}
+
+\subsubsection{The case of general linear groups}
 
@@
 
-\subsection{The case of classical groups}
-
-Let $\quadraticExtension \slash \finiteField$ be a field extension of degree $1$ or $2$ contained in $\algebraicClosure{\finiteField}$.
-For any $k \ge 1$, let $\quadraticFieldExtension{k} \slash \quadraticExtension$ be the unique field extension of degree $k$ contained in $\algebraicClosure{\finiteField}$.
-Let $x \mapsto \involution{x}$ be the generator of $\Galois\left(\quadraticExtension \slash \finiteField\right)$.
-
-Let $\hermitianSpace$ be a vector space of dimension $n$ over $\quadraticExtension$, equipped with a non-degenerate sesquilinear form $\innerproduct{\cdot}{\cdot} \colon \hermitianSpace \times \hermitianSpace \to \quadraticExtension$ which is $\epsilon_{\hermitianSpace}$-symmetric for $\epsilon_{\hermitianSpace} \in \left\{\pm 1\right\}$.
-By this we mean that:
-\begin{enumerate}
-	\item For every $x_1,x_2,y \in \hermitianSpace$, $$\innerproduct{x_1 + x_2}{y} = \innerproduct{x_1}{y} + \innerproduct{x_2}{y}.$$
-	\item For every $x,y \in \hermitianSpace$ and $t \in \quadraticExtension$, $$\innerproduct{tx}{y} = t\innerproduct{x}{y}.$$
-	\item ($\epsilon_{\hermitianSpace}$-symmetric) For every $x,y \in \hermitianSpace$, $$\innerproduct{x}{y} = \epsilon_{\hermitianSpace} \involution{\innerproduct{y}{x}}.$$
-	\item (non-degenerate) For every $0 \ne x \in \hermitianSpace$ there exists $y \in \hermitianSpace$ such that $$\innerproduct{x}{y} \ne 0.$$
-\end{enumerate}
-Let $\IsometryGroup \left(\hermitianSpace\right)$ be the isometry group of $\hermitianSpace$, consisting of all the elements of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$ that satisfy $\innerproduct{gx}{gy} = \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
-We denote by $G$ the identity component of $\IsometryGroup\left(\hermitianSpace\right)$.
-If $\quadraticExtension = \finiteField$, let $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ be the similitude group version of $\IsometryGroup\left(\hermitianSpace\right)$, consisting of the elements $g \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$ with the property that there exists a constant $\similitudeCharacter\left(g\right) \in \multiplicativegroup{\quadraticExtension}$ such that for every $\innerproduct{gx}{gy} = \similitudeCharacter\left(g\right) \innerproduct{x}{y}$ for every $x,y \in \hermitianSpace$.
-Let $\GroupExtension{G}$ be the identity component of $\GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$.
-If $\quadraticExtension \ne \finiteField$, let $\GroupExtension{G} = G$.
-
-We will assume that $\dim_{\finiteField} \hermitianSpace$ is even.
-This is automatic in all cases, expect for when $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
-The group $\GroupExtension{G}$ has connected center and contains $G$.
-
-Let us summarize all possible cases for $G$ and $\GroupExtension{G}$. Let $$w_n = \begin{pmatrix}
-	& & & 1\\
-	& & 1\\
-	& \iddots\\
-	1
-\end{pmatrix} \in \GL_n\left(\finiteField\right)$$ be the longest Weyl element.
-\begin{enumerate}
-	\item (Special even orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
-Denote $\dim_{\finiteField} \hermitianSpace = 2n$.
-It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$.
-Similarly, every element $g \in \widetilde{\IsometryGroup\left(\hermitianSpace\right)}$ satisfies $\left(\det g\right)^2 = \similitudeCharacter\left(g\right)^{2n}$.
-In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det g = 1$, and that $\GroupExtension{G}$ consists of all elements $g \in \GroupExtension{\IsometryGroup\left(\hermitianSpace\right)}$ such that $\det g = \similitudeCharacter\left(g\right)^n$.
-There are two cases here.
-	\begin{enumerate}
-		\item Split case: in this case, we can write $\hermitianSpace = \xIsotropic \oplus \yIsotropic$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
-In this case, we have that $G$ is isomorphic to $\SO^{+}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} w_{2n} g  = w_{2n},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{+}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$
-		\item Non-split case: In this case, there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
-		where $\xIsotropic$ and $\yIsotropic$ are totally isotropic spaces in duality and $\hermitianSpace'$ is an antisotropic space (that is, for any $0 \ne v' \in \hermitianSpace'$, we have $\innerproduct{v'}{v'} \ne 0$) of dimension 2.
-Let $d$ be an element of $\multiplicativegroup{\finiteField}$ that is not a square.
-Denote $$B_{n,d} = \begin{pmatrix}
-			\IdentityMatrix{n-1}\\
-			& & 1 &\\
-			& -d & &\\
-			& & & \IdentityMatrix{n-1}
-		\end{pmatrix} \cdot w_{2n}.$$
-		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
-		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{-}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
-	\end{enumerate}
-	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
-In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} \begin{pmatrix}
-		& w_n\\
-		-w_n
-	\end{pmatrix} g = \begin{pmatrix}
-		& w_n\\
-		-w_n
-	\end{pmatrix}\right\}.$$ The group $\GroupExtension{G}$ is isomorphic to the group $\GSp_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSp}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} \begin{pmatrix}
-	& w_n\\
-	-w_n
-	\end{pmatrix} g = \lambda \begin{pmatrix}
-	& w_n\\
-	-w_n
-	\end{pmatrix}\right\}.$$
-	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
-Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
-In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
-\end{enumerate}
-
-Let $\lieAlgebra$ be the Lie algebra of $G$, consisting of all elements $A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)$ satisfying $\innerproduct{Ax}{y} + \involution{\innerproduct{x}{AY}} = 0$ for every $x, y \in \hermitianSpace$.
+\subsubsection{The case of classical groups}
+
+Let $\left(\hermitianSpace, \innerproduct{\cdot}{\cdot}\right)$ be a non-degenerate $\epsilon_{\hermitianSpace}$-sesquilinear hermitian space.
+Let $G$ and $\tilde{G}$ be as in Sections \ref{subsec:isometry-groups} and \ref{subsec:similitute-groups}.
 
@@
 
+We define $\genHermitianJacobiKernel{\hermitianSpace}{\chi} \colon \tilde{G} \to \cComplex$ by $$\genHermitianJacobiKernel{\hermitianSpace}{\chi} =
+	\begin{dcases}
+		\genJacobiKernel{\chi}\left(g\right) & g \in G,\\
+		0 & \text{otherwise.}
+	\end{dcases}$$
 Let $\pi$ be an irreducible representation of $H$ where $H \in \{G, \GroupExtension{G}\}$.
-Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \genJacobiKernel{\chi}\left(g\right).$$
-Since $\genJacobiKernel{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, it is also a class function of $G$.
-Since $G$ is a normal subgroup of $H$, we have that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
+Denote $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in H} \pi\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} \pi\left(g\right) \genJacobiKernel{\chi}\left(g\right).$$
+Since $\genJacobiKernel{\chi}$ is a class function of $\GL_{\quadraticExtension}\left(\hermitianSpace\right)$, and since $G$ is a normal subgroup of $H$, we have that $\genHermitianJacobiKernel{\hermitianSpace}{\chi}$ is a class function of $H$.
+It follows that $\dblJacobiSum{\pi}{\chi} \in \Hom_{H}\left(\pi, \pi\right)$.
 By Schur's lemma, there exists a constant $\dblJacobiSumScalar{\pi}{\fieldCharacter} \in \cComplex$, such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_\pi.$$
@@
 
-\subsubsection{Multiplicativity property}
-Our next goal is to understand how the doubling method Jacobi sum behaves under parabolic induction.
+\subsection{Multiplicativity property}
+The goal of this section is to understand how the doubling method Jacobi sums behave under parabolic induction.
+
+\elad{TODO: work on section}
 
@@
 Write $P = L \ltimes N$, where $L$ is the Levi part of $P$ and $N$ is the unipotent radical of $P$.
-Then $L$ is isomorphic to $H' \times \GL_k\left(\quadraticExtension\right)$, where $H' \in \left\{G',\GroupExtension{G'}\right\}$ is of the same type as $H$.
+Then $L$ is isomorphic to $H' \times \GL_k\left(\quadraticExtension\right)$, where $H' \in \{G',\GroupExtension{G'}\}$ is of the same type as $H$.
 
@@
 
-	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
+	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
 	which can be rewritten as
-	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
+	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
 	As before, we may write
@@
 	Hence, \begin{align*}
-		q^{k^2} \sum_{p \in P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
+		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
 		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
@@
 	\begin{align*}
-		q^{k^2} \sum_{p \in P} \Phi_{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
-		& \times \sum_{p' \in P} \sum_{p \in P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left( p \mp x  \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
+		& \times \sum_{p' \in G \cap P} \sum_{p \in G \cap P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left( p \mp x  \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
 	\end{align*}
@@
 	\begin{equation}
-		\chi\left(\mp 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genJacobiKernel{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+		\chi\left(\mp 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
 	\end{equation}
@@
 				1 & \text{otherwise.}
-	\end{dcases}.$$
+	\end{dcases},$$
+	where $n = \left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2} \right\rfloor$.
 	However, we will not need this version for our purposes.
@@
 
-Let us realize $H$ as the fixed points of the Frobenius map $\Frobenius$ acting on a connected reductive algebraic group $\algebraicGroup{H}$.
-
-Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genJacobiKernel{\chi}\left(g\right).$$
+Let us realize $H = \algebraicGroup{H}^{\Frobenius}$, that is, $H$ is the group consisting fixed points of the Frobenius map $\Frobenius$ acting on the connected reductive algebraic group $\algebraicGroup{H}$, where $\algebraicGroup{H} = \tilde{\algebraicGroup{G}}$ if $H = \tilde{G}$ and $\algebraicGroup{H} = \algebraicGroup{G}$ if $H = G$.
+
+Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right).$$
 
 It is clear that if $\pi$ is an irreducible representation of $H$ then $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \dim \pi.$$
-Notice that the assignments $g \mapsto \posJacobiKernel{\chi}\left(g\right)$ and $g \mapsto \negJacobiKernel{\chi}\left(g\right)$ only depends on the semisimple part of $g \in H$.
+Notice that the assignments $g \mapsto \posJacobiKernel{\chi}\left(g\right)$ and $g \mapsto \negJacobiKernel{\chi}\left(g\right)$ only depend on the semisimple part of $g \in H$.
 By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
@@
 	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{H}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genJacobiKernel{\chi}\left(t\right).$$
+	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
 \end{proposition}
 In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
-$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genJacobiKernel{\chi}\left(t\right).$$
+$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
 Here $\varepsilon_{\algebraicGroup{H}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{H}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{H}_p$ is the size of the $p$-Sylow group of $H$, where $p$ is the characteristic of $\finiteField$.
-
-\subsubsection{Gauss sum notations}
-If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
-If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
-$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
-
-If $m \ge 1$, we denote 
-$$\NormOneGroup{2m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
 
@@
 x \ne -1}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1+x\right)\right).$$
-Let us rewrite this as
+This computation will be useful for the next section, which in turn will be useful for invoking \Cref{prop:reduction-of-gauss-sum-to-torus}.
+
+Let us rewrite our sum as
 $$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
@@
 
-\subsubsection{Geometric Conjugacy and Lusztig Series}
-Let $\ell$ be a prime number not equal to the characteristic of $\finiteField$. Fix an isomorphism $\ladicnumbers \cong \cComplex$.
-
-Let $\algebraicGroup{G}$ be a reductive group over $\finiteField$ and fix a maximal $\Frobenius$-stable torus $\algebraicGroup{T} \subset \algebraicGroup{G}$ defined over $\finiteField$.
-We denote by $$\CharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\algebraicGroup{T}, \multiplcativeScheme\right)$$ the \emph{character lattice} of $\algebraicGroup{T}$ and by $$\CocharacterLattice{\algebraicGroup{T}} = \Hom_{\algebraicClosure{\finiteField}}\left(\multiplcativeScheme, \algebraicGroup{T}\right)$$ the \emph{cocharacter lattice} of $\algebraicGroup{T}$, where we regard $\algebraicGroup{T}$ and $\multiplcativeScheme$ as algebraic groups over $\finiteField$.
-Recall that $\CharacterLattice{\algebraicGroup{T}}$ and $\CocharacterLattice{\algebraicGroup{T}}$ are free $\zIntegers$-modules of the same finite rank.
-The assignment $\CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \Hom_{\finiteField}\left(\multiplcativeScheme, \multiplcativeScheme\right)$ given by composition $\left(x,y\right) \mapsto \left(z \mapsto x\left(y\left(z\right)\right)\right)$ defines a pairing $\innerproduct{\cdot}{\cdot} \colon \CharacterLattice{\algebraicGroup{T}} \times \CocharacterLattice{\algebraicGroup{T}} \to \zIntegers$ by the rule $$x\left(y\left(z\right)\right) = z^{\innerproduct{x}{y}}.$$
-
-The \emph{dual group over $\finiteField$} of $\algebraicGroup{G}$ with respect to the torus $\algebraicGroup{T}$ corresponds to the group $\algebraicGroup{G}^*$ with a dual torus $\algebraicGroup{T}^*$ and root datum
-\[
-(\CharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*},\CocharacterLattice{\algebraicGroup{T}^*},\Phi_{\algebraicGroup{T}^*}^\vee) \cong (\CocharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}}^\vee,\CharacterLattice{\algebraicGroup{T}},\Phi_{\algebraicGroup{T}})
-\]
-such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.
-
-Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
-By \cite[Proposition 13.7 (ii)]{DigneMichel2020}, we have an exact sequence
-\begin{equation}
-\label{eq:DL}
-\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T} \ar[r] & 0}
-\end{equation}
-with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n))$
-for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
-Here, $$\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$$ is the torus norm map.
-
-We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\ladicnumbers}$ is a character.
-By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
-\[
-    \exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
-\]
-for large enough $n$.
-This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
-Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
-
-    Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
-Similarly, denote the $\Frobenius$-stable Weyl group orbit in $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
-
-We say that the torus character pairs $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ for $\algebraicGroup{G}$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{\algebraicGroup{T},\theta})$ and $(s_{\algebraicGroup{T}',\theta'})$ are equal.
-This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
-
-\begin{example}
-	Take $\algebraicGroup{G}' = \algebraicGroup{\GL}_2$.
-Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
-	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
-Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
-	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.
-Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$.
-The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$.
-We thus have
-	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
-\end{example}
-
-The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
-
-\begin{center}
-	\begin{tabular}{ c c c c c c}
-		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$  \\
-		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \\		 
-		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \\	
-		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$\\  			 
-		$\algebraicGroup{\SO}^{+}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}^{+}_{2n}$ &  $\multiplcativeScheme^n$ \\
-		$\algebraicGroup{\SO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \left(-1\right)$ &$\algebraicGroup{\SO}^{-}_{2n}$ &  $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ \\
-		 $\algebraicGroup{\GSp}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 &$\algebraicGroup{GSpin}_{2n+1}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
-		 $\algebraicGroup{\GSO}^{+}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 & $\algebraicGroup{GSpin}_{2n}^{+}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
-		 $\algebraicGroup{\GSO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \sigma^{\ast}$ & $\algebraicGroup{GSpin}_{2n}^{-}$ &  $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$
-\end{tabular}
-\end{center}
-For all the pairs $\algebraicGroup{T} \subset \algebraicGroup{G}$ in this list, the Frobenius root $\Frobenius$ of $\algebraicGroup{G}$ acts trivially on the Weyl group $W\left(\algebraicGroup{T}\right)$.
-In the last row, $\sigma \colon \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \to \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ is the automorphism $a + b\sqrt{d} \mapsto a - b\sqrt{d}$ where $d \in \multiplicativegroup{\finiteField}$ is a non-square.
-
-\subsubsection{Invariance under geometric conjugacy}
+\subsection{Invariance under geometric conjugacy}
 \calvin{todo:type in some motivation for class functions whose product doesn't depend on geometric conjugacy, gamma functions whatever}.
@@
 \label{thm:Phi_stable}
-	The assignments $H \to \cComplex$ given by $$h \mapsto \begin{dcases}
-		\chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm h\right)\right) & h \in G \text{ and } \detQuadratic\left(\idmap_{\hermitianSpace} \pm h\right) \ne 0,\\
-		0 & \text{otherwise.}
-	\end{dcases}$$ are stable functions. Equivalently, the assignments $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ are constant on geometric Lusztig series.
+	The assignments $H \to \cComplex$ given by $$h \mapsto \genHermitianJacobiKernel{\hermitianSpace}{h}$$ are stable functions.
+Equivalently, the assignments $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ are constant on geometric Lusztig series.
 \end{theorem}

### 2025-03-24 reorganization.tex
Calvin changes

@@
 
-\subsubsection{Tori}
+\subsubsection{Rational Tori}
+A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\mathbb{F}$ is a torus defined over $\mathbb{F}$. 
+Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
+In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk}(\algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ [cite Roger Carter Finite Groups of Lie Type section 3.3].%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
+%could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
+Applying this theory to our groups $\algebraicGroup{G}$
+
+\begin{enumerate}
+	\item (Special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
+It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$.
+In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det g = 1$.
+There are two cases here.
+	\begin{enumerate}
+		\item Split case: in this case, we can write $$\hermitianSpace = \begin{dcases}
+		\xIsotropic \oplus \yIsotropic & \dim_{\finiteField} \hermitianSpace = 2n\\
+		\xIsotropic \oplus \finiteField v \oplus \yIsotropic & \dim_{\finiteField}\hermitianSpace = 2n + 1
+		\end{dcases}$$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
+In the odd dimensional case, $v \in \hermitianSpace$ is an element orthogonal to $\xIsotropic$ and $\yIsotropic$ that satisfies $\innerproduct{v}{v} \ne 0$.
+
+		In either case, denote $d = \dim_{\finiteField} \hermitianSpace$.
+We have that $G$ is isomorphic to $\SO^{+}_{d}\left(\finiteField\right) \subset  \GL_{d}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{d} = \left\{g \in \algebraicGroup{\GL}_{d} \mid \transpose{g} w_{d} g  = w_{d},\,\, \det g = 1\right\}.$$
+
+		In the odd-dimensional case $d = 2n+1$, we are always in this situation, and we simply denote $\SO_{2n+1}\left(\finiteField\right) = \SO_{2n+1}^{+}\left(\finiteField\right)$ and $\algebraicGroup{\SO}_{2n+1} = \algebraicGroup{\SO}_{2n+1}^{+}$.
+		\item Non-split case: In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ and there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
+		where $\xIsotropic$ and $\yIsotropic$ are totally isotropic spaces in duality and $\hermitianSpace'$ is an antisotropic space (that is, for any $0 \ne v' \in \hermitianSpace'$, we have $\innerproduct{v'}{v'} \ne 0$) of dimension 2.
+Let $d$ be an element of $\multiplicativegroup{\finiteField}$ that is not a square.
+Denote $$B_{n,d} = \begin{pmatrix}
+			\IdentityMatrix{n-1}\\
+			& & 1 &\\
+			& -d & &\\
+			& & & \IdentityMatrix{n-1}
+		\end{pmatrix} \cdot w_{2n}.$$
+		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
+	\end{enumerate}
+	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
+In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix} g = \begin{pmatrix}
+		& w_n\\
+		-w_n
+	\end{pmatrix}\right\}.$$
+	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
+Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
+In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
+\end{enumerate}
 
@@
 If $m \ge 1$, we denote 
-$$\NormOneGroup{2m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\}.$$
+$$\NormOneGroup{2m} := \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\} = \left(\mathrm{Res}_{\mathbb{F}_{m}:\mathbb{F}} \algebraicGroup{U}(1)\right)(\mathbb{F}).$$
 
@@
 \label{lem:cochar_computation}
-    Define $\phi:(\mathbb{Q}/\mathbb{Z})_{p'}^n \to (\mathbb{Q}/\mathbb{Z})_{p'}^{2n} = X_*(\GL_{2n})_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ by $\phi(x) = (x,-x)$.
-We will consider two different Frobeinus actions on these characters:
-    \begin{enumerate}
-        \item When $\Frobenius$ acts by trivially on both, $x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$
-        \item When $\Frobenius$ acts by $-1$ on the domain and by $\begin{pmatrix}
-            0 & 1 \\
-            1 & 0\end{pmatrix}$ on the codomain, $x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$ where $\theta'(t) = \theta(t^{1-q^n})$
-    \end{enumerate}
-    \calvin{new cases:}
     Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-x)$.
@@
     \begin{enumerate}
-        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
+        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases.
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
         \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:

### 2025-03-24 reorganization.tex
Gauss sums reorganization

@@
 
-\subsubsection{Gauss sum notations}
-If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$
-where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
-If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
-$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
-
-\subsubsection{Kondo Gauss sums}
-
 Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. 
@@
 
-\begin{theorem}
+In order to state Kondo's result, we need to introduce some Gauss sum notation which will be used throughout the paper.
+
+If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
+$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
+
+We are now ready to state Kondo's result.
+\begin{theorem}[Kondo {\cite{Kondo1963}}]
 	Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\theta_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$.
@@
 
-We will need the following lemma that allows us to determine that a degenerate Kondo Gauss sum vanishes.
+We will need the following lemma that allows us to determine whether a degenerate Kondo Gauss sum vanishes.
 \begin{lemma}\label{lem:sum-vanishes-for-singular-matrices}

### 2025-03-24 reorganization.tex
Adding reference to Carter

@@
 Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
-In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk}(\algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ [cite Roger Carter Finite Groups of Lie Type section 3.3].%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
+In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ \cite[Section 3.3]{Carter1985}.%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
 %could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field

### 2025-03-24 reorganization.tex
Writing the standard tori

@@
 
-		In either case, denote $d = \dim_{\finiteField} \hermitianSpace$.
-We have that $G$ is isomorphic to $\SO^{+}_{d}\left(\finiteField\right) \subset  \GL_{d}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{d} = \left\{g \in \algebraicGroup{\GL}_{d} \mid \transpose{g} w_{d} g  = w_{d},\,\, \det g = 1\right\}.$$
-
-		In the odd-dimensional case $d = 2n+1$, we are always in this situation, and we simply denote $\SO_{2n+1}\left(\finiteField\right) = \SO_{2n+1}^{+}\left(\finiteField\right)$ and $\algebraicGroup{\SO}_{2n+1} = \algebraicGroup{\SO}_{2n+1}^{+}$.
+		In either case, denote $N = \dim_{\finiteField} \hermitianSpace$.
+We have that $G$ is isomorphic to $\SO^{+}_{N}\left(\finiteField\right) \subset  \GL_{N}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{N} = \left\{g \in \algebraicGroup{\GL}_{N} \mid \transpose{g} w_{N} g  = w_{N},\,\, \det g = 1\right\}.$$
+
+		In the odd-dimensional case $N = 2n+1$, we are always in this situation, and we simply denote $\SO_{2n+1}\left(\finiteField\right) = \SO_{2n+1}^{+}\left(\finiteField\right)$ and $\algebraicGroup{\SO}_{2n+1} = \algebraicGroup{\SO}_{2n+1}^{+}$.
 		\item Non-split case: In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ and there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
@@
 \subsubsection{Rational Tori}
-A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\mathbb{F}$ is a torus defined over $\mathbb{F}$. 
-Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
-In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ \cite[Section 3.3]{Carter1985}.%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
+A \emph{rational torus} $\algebraicGroup{T} \subset \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
+Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
+In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\finiteField})$ \cite[Section 3.3]{Carter1985}.
+
+%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
 %could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
+
+Let $\algebraicGroup{A}_n \subset \algebraicGroup{\GL}_n$ be the diagonal torus.
+We denote for an element $g \in \algebraicGroup{\GL}_n$, $g^{\ast} = w_n \transpose{g}^{-1} w_n$, where $w_n$ is the long Weyl element (see \Cref{subsec:isometry-groups}).
+Using $\algebraicGroup{A}_n$ we define standard (mostly split) tori in our groups as follows.
+\begin{center}
+\begin{tabular}{|c|c|}
+	\hline 
+		$\algebraicGroup{G}$ & $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ \tabularnewline
+		\hline 
+		\hline 
+		$\algebraicGroup{\UnitaryGroup}_{2n}$ & $\left\{ \begin{pmatrix}
+			a\\
+			& \involution{\left(a^{\ast}\right)}
+		\end{pmatrix}  \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
+		\hline 
+		$\algebraicGroup{\UnitaryGroup}_{2n+1}$ & $\left\{ \begin{pmatrix}
+	a \\
+	& t\\
+	& & \involution{\left(a^{\ast}\right)}
+\end{pmatrix}  \mid a \in \algebraicGroup{A}_n,\,\, t \in \algebraicGroup{U}_1 \right\}$ \tabularnewline
+\hline 
+	$\algebraicGroup{\SO}_{2n+1}$ & $\left\{ \begin{pmatrix}
+		a\\
+		& 1\\
+		& & a^{\ast}
+	\end{pmatrix} \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
+	\hline 
+	$\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}^{+}_{2n}$ & $\left\{ \begin{pmatrix}
+		a\\
+		& a^{\ast}
+	\end{pmatrix} \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
+	\hline 
+	$\algebraicGroup{\SO}_{2n}^{-}$ & $\left\{ \begin{pmatrix}
+		a\\
+		& h\\
+		& & a^{\ast}
+	\end{pmatrix} \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \algebraicGroup{\SO}_2^{-} \right\}$ \tabularnewline
+	\hline		
+	\end{tabular}
+\end{center}
+Here $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$, is split for all rows except for the the last row. We also write down the standard tori for the relevant corresponding similitude groups.
+\begin{center}
+	\begin{tabular}{|c|c|}
+		\hline 
+		$\algebraicGroup{G}$ & $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ \tabularnewline
+		\hline 
+		\hline 
+		$\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}^{+}_{2n}$ & $\left\{\left(\lambda, \begin{pmatrix}
+			\lambda a\\
+			& a^{\ast}
+		\end{pmatrix}\right) \mid a \in \algebraicGroup{A}_n,\,\, \lambda \in \multiplcativeScheme \right\}$ \tabularnewline
+		\hline 
+		$\algebraicGroup{\GSO}_{2n}^{-}$ & $\left\{ \left(\algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right), \begin{pmatrix}
+			\algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right) a\\
+			& h\\
+			& & a^{\ast}
+		\end{pmatrix}\right) \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \right\}$ \tabularnewline
+		\hline		
+	\end{tabular}
+\end{center}
+Here we realize $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ as $$\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} = \left\{ \left(\lambda, \begin{pmatrix}
+	a & b\\
+	db & a
+\end{pmatrix}\right) \mid a^2 - db^2 = \lambda \in \multiplcativeScheme \right\},$$
+where $d$ is as in \Cref{subsec:isometry-groups}.
+
 Applying this theory to our groups $\algebraicGroup{G}$
-
 \begin{enumerate}

### 2025-03-24 reorganization.tex
Calvin update

@@
 \subsubsection{Rational Tori}
-A \emph{rational torus} $\algebraicGroup{T} \subset \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
-Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
-In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\finiteField})$ \cite[Section 3.3]{Carter1985}.
+A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\mathbb{F}$ is a torus defined over $\mathbb{F}$. 
+Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
+In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk}(\algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ [cite Roger Carter Finite Groups of Lie Type section 3.3].%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
+%could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
+Applying this theory to our groups $\algebraicGroup{G}$, for each group we find a nice rational torus $\algebraicGroup{T}$ and write out the Frobenius order action on the Weyl group and the
+
+\begin{enumerate}
+	\item(Special orthogonal groups) 
+	In each case let $\algebraicGroup{T}$ be the diagonal torus. Then $W(\algebraicGroup{T} )$ has representatives the type B or D permutation matrices which are fixed by the Frobenius order.
+	\begin{enumerate}[(a)]
+		\item (Split odd case $\algebraicGroup{SO}_{2n+1}$) $\algebraicGroup{T} = \algebraicGroup{G}_m^{n}$.
+In type B the Weyl group conjugacy classes are given by $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from.
+Given a representation $w$ of the conjugacy class we get:
+		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+		\item (Split even case $\algebraicGroup{SO}_{2n}^+$) $\algebraicGroup{T} = \algebraicGroup{G}_m^{n}$.
+Given $w \in W(\algebraicGroup{T})$ the rational structure of $^w\algebraicGroup{T}$ is determined by the conjugacy class of $w$ in the Type B Weyl group (a $\mathbb{Z}/2\mathbb{Z}$ extension of $W(\algebraicGroup{T})$.
+If $w$ is conjugate in the extension to $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from:
+		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+			\item (Non-split even case $\algebraicGroup{SO}_{2n}^-$) Set $\algebraicGroup{T} = \algebraicGroup{G}_m^{n-1} \times \algebraicGroup{U}(1)$ the diagonal torus.
+Given $w \in W(\algebraicGroup{T})$ the rational structure of $^w\algebraicGroup{T}$ is determined by the conjugacy class of $w$ in the Type B Weyl group (a $\mathbb{Z}/2\mathbb{Z}$ extension of $W(\algebraicGroup{T})$.
+If $w \circ (-1,1)$ is conjugate in the extension to $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from:
+		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+	\end{enumerate}
+	\item (Symplectic groups) In type B the Weyl group conjugacy classes are given by $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from.
+Given a representation $w$ of the conjugacy class we get:
+		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+	\item (Unitary groups) We let our torus be the diagonal torus for the unitary group with hermitian form $I_n$.
+Then $\algebraicGroup{T}=U(1)^n$ and the Frobenius action on the Weyl group is trivial.
+Note since all hermitian forms are equivalent over a finite field, $\algebraicGroup{T}$ is a torus in the group $\algebraicGroup{U}_n$ from the previous section.
+In type A the Weyl group conjugacy classes are given by $(\lambda)$, and
+	$$^w\algebraicGroup{T} = \Pi_{\lambda_i} \begin{cases}
+	\mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}} \algebraicGroup{G}_m& \lambda_i \textnormal{ is even} \\
+	\mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{U}(1) & \lambda_i \textnormal{ is odd}
+	\end{cases}$$
+	\item (Even special orthogonal similitude groups)
+	\item (Symplectic similitude groups)
+\end{enumerate}
 
@@
 \end{center}
+Here $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the the last row.
 Here $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$, is split for all rows except for the the last row. We also write down the standard tori for the relevant corresponding similitude groups.
@@
 
-Applying this theory to our groups $\algebraicGroup{G}$
-\begin{enumerate}
-	\item (Special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
-It follows by definition that every element $g \in \IsometryGroup\left(\hermitianSpace\right)$ satisfies $\left(\det g\right)^2 = 1$.
-In this case, we obtain the connected components of the identity by adding a restriction on the determinant: We have that $G$ consists of all elements $g \in \IsometryGroup\left(\hermitianSpace\right)$ with $\det g = 1$.
-There are two cases here.
-	\begin{enumerate}
-		\item Split case: in this case, we can write $$\hermitianSpace = \begin{dcases}
-		\xIsotropic \oplus \yIsotropic & \dim_{\finiteField} \hermitianSpace = 2n\\
-		\xIsotropic \oplus \finiteField v \oplus \yIsotropic & \dim_{\finiteField}\hermitianSpace = 2n + 1
-		\end{dcases}$$ where $\xIsotropic$ and $\yIsotropic$ are totally isotropic (that is, for every $x \in \xIsotropic$, $\innerproduct{x}{x} = 0$ and similarly for $\yIsotropic$) and these spaces are in duality with respect to $\innerproduct{\cdot}{\cdot}$, i.e., the map $\yIsotropic \to \Hom_{\finiteField}\left(\xIsotropic, \finiteField\right)$ given by $y \mapsto \left(x \mapsto \innerproduct{x}{y}\right)$ is an isomorphism.
-In the odd dimensional case, $v \in \hermitianSpace$ is an element orthogonal to $\xIsotropic$ and $\yIsotropic$ that satisfies $\innerproduct{v}{v} \ne 0$.
-
-		In either case, denote $d = \dim_{\finiteField} \hermitianSpace$.
-We have that $G$ is isomorphic to $\SO^{+}_{d}\left(\finiteField\right) \subset  \GL_{d}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{+}_{d} = \left\{g \in \algebraicGroup{\GL}_{d} \mid \transpose{g} w_{d} g  = w_{d},\,\, \det g = 1\right\}.$$
-
-		In the odd-dimensional case $d = 2n+1$, we are always in this situation, and we simply denote $\SO_{2n+1}\left(\finiteField\right) = \SO_{2n+1}^{+}\left(\finiteField\right)$ and $\algebraicGroup{\SO}_{2n+1} = \algebraicGroup{\SO}_{2n+1}^{+}$.
-		\item Non-split case: In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ and there exists a decomposition $$\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic,$$
-		where $\xIsotropic$ and $\yIsotropic$ are totally isotropic spaces in duality and $\hermitianSpace'$ is an antisotropic space (that is, for any $0 \ne v' \in \hermitianSpace'$, we have $\innerproduct{v'}{v'} \ne 0$) of dimension 2.
-Let $d$ be an element of $\multiplicativegroup{\finiteField}$ that is not a square.
-Denote $$B_{n,d} = \begin{pmatrix}
-			\IdentityMatrix{n-1}\\
-			& & 1 &\\
-			& -d & &\\
-			& & & \IdentityMatrix{n-1}
-		\end{pmatrix} \cdot w_{2n}.$$
-		In this case, we have that $G$ is isomorphic to $\SO^{-}_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\SO}^{-}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} B_{n,d} g = B_{n,d},\,\, \det g = 1\right\}.$$
-	\end{enumerate}
-	\item (Symplectic groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$.
-In this case, $\dim_{\finiteField} \hermitianSpace = 2n$ for some positive integer $n$ and $G$ is isomorphic to the group $\Sp_{2n}\left(\finiteField\right) \subset  \GL_{2n}\left(\finiteField\right)$, defined as the $\finiteField$-points of $$\algebraicGroup{\Sp}_{2n} = \left\{g \in \algebraicGroup{\GL}_{2n} \mid \transpose{g} \begin{pmatrix}
-		& w_n\\
-		-w_n
-	\end{pmatrix} g = \begin{pmatrix}
-		& w_n\\
-		-w_n
-	\end{pmatrix}\right\}.$$
-	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
-Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
-In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
-\end{enumerate}
-
 \elad{Under construction}

### 2025-03-24 reorganization.tex
Reformatting

@@
 \subsubsection{Rational Tori}
-A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\mathbb{F}$ is a torus defined over $\mathbb{F}$. 
-Over a finite field, $\algebraicGroup{G}(\mathbb{F})$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
-In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk}(\algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\mathbb{F}})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\mathbb{F})$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$ [cite Roger Carter Finite Groups of Lie Type section 3.3].%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
+A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
+Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
+In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.
+
+%since $\Frobenius(g\algebraicGroup{T}_0g^{-1}) = g\algebraicGroup{T}_0g^{-1}$
 %could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
@@
 Given a representation $w$ of the conjugacy class we get:
-		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
 		\item (Split even case $\algebraicGroup{SO}_{2n}^+$) $\algebraicGroup{T} = \algebraicGroup{G}_m^{n}$.
@@
 If $w$ is conjugate in the extension to $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from:
-		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
 			\item (Non-split even case $\algebraicGroup{SO}_{2n}^-$) Set $\algebraicGroup{T} = \algebraicGroup{G}_m^{n-1} \times \algebraicGroup{U}(1)$ the diagonal torus.
@@
 If $w \circ (-1,1)$ is conjugate in the extension to $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from:
-		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
 	\end{enumerate}
@@
 Given a representation $w$ of the conjugacy class we get:
-		$$^w\algebraicGroup{T} = \Pi_{\lambda^+_i} \mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{G}_m \times \Pi_{\lambda^-_i} \mathrm{Res}_{\mathbb{F}_{\lambda^-_i}:\mathbb{F}}\algebraicGroup{U}(1)$$
+		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
 	\item (Unitary groups) We let our torus be the diagonal torus for the unitary group with hermitian form $I_n$.
-Then $\algebraicGroup{T}=U(1)^n$ and the Frobenius action on the Weyl group is trivial.
+Then $\algebraicGroup{T}=\algebraicGroup{\UnitaryGroup}_1^n$ and the Frobenius action on the Weyl group is trivial.
 Note since all hermitian forms are equivalent over a finite field, $\algebraicGroup{T}$ is a torus in the group $\algebraicGroup{U}_n$ from the previous section.
 In type A the Weyl group conjugacy classes are given by $(\lambda)$, and
-	$$^w\algebraicGroup{T} = \Pi_{\lambda_i} \begin{cases}
-	\mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}} \algebraicGroup{G}_m& \lambda_i \textnormal{ is even} \\
-	\mathrm{Res}_{\mathbb{F}_{\lambda^+_i}:\mathbb{F}}\algebraicGroup{U}(1) & \lambda_i \textnormal{ is odd}
-	\end{cases}$$
+	$$^w\algebraicGroup{T} = \prod_{i} \begin{dcases}
+	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
+	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
+	\end{dcases}$$
 	\item (Even special orthogonal similitude groups)

### 2025-03-24 reorganization.tex
Adding borders to the table
Correction

@@
 		\hline 
-		$\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}^{+}_{2n}$ & $\left\{\left(\lambda, \begin{pmatrix}
+		$\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}^{+}_{2n}$ & $\left\{\left(\begin{pmatrix}
 			\lambda a\\
 			& a^{\ast}
-		\end{pmatrix}\right) \mid a \in \algebraicGroup{A}_n,\,\, \lambda \in \multiplcativeScheme \right\}$ \tabularnewline
+		\end{pmatrix}, \lambda\right) \mid a \in \algebraicGroup{A}_n,\,\, \lambda \in \multiplcativeScheme \right\}$ \tabularnewline
 		\hline 
-		$\algebraicGroup{\GSO}_{2n}^{-}$ & $\left\{ \left(\algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right), \begin{pmatrix}
+		$\algebraicGroup{\GSO}_{2n}^{-}$ & $\left\{ \left(\begin{pmatrix}
 			\algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right) a\\
@@
 			& & a^{\ast}
-		\end{pmatrix}\right) \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \right\}$ \tabularnewline
+		\end{pmatrix}, \algebraicGroup{\aFieldNorm}_{\finiteFieldExtension{2} \slash \finiteField}\left(h\right)\right) \mid a \in \algebraicGroup{A}_{n-1}\,\, h \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \right\}$ \tabularnewline
 		\hline		
@@
 \end{center}
-Here we realize $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ as $$\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} = \left\{ \left(\lambda, \begin{pmatrix}
+Here we realize $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ as $$\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} = \left\{ \left(\begin{pmatrix}
 	a & b\\
 	db & a
-\end{pmatrix}\right) \mid a^2 - db^2 = \lambda \in \multiplcativeScheme \right\},$$
+\end{pmatrix}, \lambda\right) \mid a^2 - db^2 = \lambda \in \multiplcativeScheme \right\},$$
 where $d$ is as in \Cref{subsec:isometry-groups}.
@@
 \begin{center}
-	\begin{tabular}{ c c c c c c}
-		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$  \\
-		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \\		 
-		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \\	
-		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$\\  			 
-		$\algebraicGroup{\SO}^{+}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}^{+}_{2n}$ &  $\multiplcativeScheme^n$ \\
-		$\algebraicGroup{\SO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \left(-1\right)$ &$\algebraicGroup{\SO}^{-}_{2n}$ &  $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ \\
-		$\algebraicGroup{\GSp}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 &$\algebraicGroup{GSpin}_{2n+1}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
-		$\algebraicGroup{\GSO}^{+}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 & $\algebraicGroup{GSpin}_{2n}^{+}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \\
-		$\algebraicGroup{\GSO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \sigma^{\ast}$ & $\algebraicGroup{GSpin}_{2n}^{-}$ &  $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$
+	\begin{tabular}{|c|c|c|c|c|c|} \hline
+		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$ \tabularnewline \hline \hline
+		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \tabularnewline \hline
+		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \tabularnewline \hline
+		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ \tabularnewline \hline		 
+		$\algebraicGroup{\SO}^{+}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}^{+}_{2n}$ &  $\multiplcativeScheme^n$ \tabularnewline \hline
+		$\algebraicGroup{\SO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \left(-1\right)$ &$\algebraicGroup{\SO}^{-}_{2n}$ &  $\multiplcativeScheme^{n-1} \times \algebraicGroup{\UnitaryGroup}_1$ \tabularnewline \hline
+		$\algebraicGroup{\GSp}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 &$\algebraicGroup{GSpin}_{2n+1}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \tabularnewline \hline
+		$\algebraicGroup{\GSO}^{+}_{2n}$ & $\multiplcativeScheme \times \multiplcativeScheme^{n}$ & 1 & $\algebraicGroup{GSpin}_{2n}^{+}$ &  $\multiplcativeScheme \times \multiplcativeScheme^{n}$ \tabularnewline \hline
+		$\algebraicGroup{\GSO}^{-}_{2n}$ & $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ & $\left(1\right)^{\times {\left(n-1\right)}} \times \sigma^{\ast}$ & $\algebraicGroup{GSpin}_{2n}^{-}$ &  $\multiplcativeScheme^{n-1} \times \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ \tabularnewline \hline
 	\end{tabular}

### 2025-03-25 reorganization.tex
Reorganizing proof of multiplicativity

@@
 \end{theorem}
-\begin{proof}
-	Let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$.
+
+This theorem was proved in \cite{GirschZelingher2025} under the assumption that $\pi' \subset \Ind{P}{H'}{\tau' \overline{\otimes} \pi''}$, where $\pi''$ is an irreducible cuspidal representation of $H''$ and $\tau'$ is an irreducible representation of $\GL_{k'}\left(\finiteField\right)$ such that $\chi$ nor $\minusInvolution{\chi}$ appear in the cuspidal support of $\tau''$.
+\elad{TODO: check the exact condition.
+The Gauss sums appearing here suggest that we should replace $\chi$ with $\involution{\chi}$ and $\minusInvolution{\chi}$ with $\chi^{-1}$}
+
+In order to prove a more general form of this theorem, let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$.
 Consider $f \in \rho$ defined as follows.
@@
 The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
-We compute $\dblJacobiSum{\rho}{\chi} f$.
-
+We claim the following.
+\begin{proposition}\label{prop:multiplicativity-of-jacobi-sum-given-support}
+	Suppose that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. Then \Cref{thm:multiplicativity-in-terms-of-gauss-sums} is true.
+\end{proposition}
+\begin{proof}
+	We compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
+	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
+		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
+				\detQuadratic\left(\idmap_{\hermitianSpace}\pm p\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+	\end{equation}
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right) = \left(\pm 1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} \pm a\right) \det\left(\involution{\left(\IdentityMatrix{k} \pm a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} \pm g'\right),$$
+	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
+	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
+	\begin{equation}
+		\chi\left(\pm 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+	\end{equation}
+	which in turn is
+	\begin{align*}
+		&\chi\left(\pm 1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
+		=& \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+	\end{align*}
+
+	It follows that $$\dblJacobiSum{\rho}{\chi} f = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f.$$
+
+	Write $\rho = \bigoplus_i \sigma_i$ where $\sigma_i$ are irreducible representations of $\sigma_i$ and the $\sigma_i$'s need not be non-isomorphic.
+By writing $f = \sum_{i} f_i$ where $0 \ne f_i \in \sigma_i$, we have that $$\sum_i \dblJacobiSum{\sigma_i}{\chi} f_i = \dblJacobiSum{\rho}{\chi} f,$$
+	and therefore $$\dblJacobiSum{\sigma_i}{\chi} f_i = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f_i,$$
+	for every $i$. The result now follows.
+\end{proof}
+The assumption in \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds in certain cases.
+For example, if $\rho$ is an irreducible representation, this assumption holds.
+It seems difficult to prove that this assumption holds in general.
+However, it is possible in a special case which suffices given the results of \cite{GirschZelingher2025}.
+
+\begin{proposition}
+	Suppose that $k=1$. Then the assumption of \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds.
+\end{proposition}
+\begin{proof}\elad{Work on this}
 	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
@@
 
-	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. We move to compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
-	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
-		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
-				\detQuadratic\left(\idmap_{\hermitianSpace}\pm p\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
-	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right) = \left(\mp 1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} \pm a\right) \det\left(\involution{\left(\IdentityMatrix{k} \pm a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} \pm g'\right),$$
-	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
-	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
-	\begin{equation}
-		\chi\left(\mp 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
-	\end{equation}
-	which in turn is
-	\begin{align*}
-		&\chi\left(\mp 1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
-		=& \chi\left(\mp 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
-	\end{align*}
-	The result now follows.
+	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. 
 \end{proof}

### 2025-03-25 reorganization.tex
Calvin changes

@@
 \subsubsection{Rational Tori}
-A \emph{rational torus} $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
+A \emph{rational torus} $\algebraicGroup{T} \subset \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
 Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
@@
 %could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
-Applying this theory to our groups $\algebraicGroup{G}$, for each group we find a nice rational torus $\algebraicGroup{T}$ and write out the Frobenius order action on the Weyl group and the
-
-\begin{enumerate}
-	\item(Special orthogonal groups) 
-	In each case let $\algebraicGroup{T}$ be the diagonal torus. Then $W(\algebraicGroup{T} )$ has representatives the type B or D permutation matrices which are fixed by the Frobenius order.
-	\begin{enumerate}[(a)]
-		\item (Split odd case $\algebraicGroup{SO}_{2n+1}$) $\algebraicGroup{T} = \algebraicGroup{G}_m^{n}$.
-In type B the Weyl group conjugacy classes are given by $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from.
-Given a representation $w$ of the conjugacy class we get:
-		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-		\item (Split even case $\algebraicGroup{SO}_{2n}^+$) $\algebraicGroup{T} = \algebraicGroup{G}_m^{n}$.
-Given $w \in W(\algebraicGroup{T})$ the rational structure of $^w\algebraicGroup{T}$ is determined by the conjugacy class of $w$ in the Type B Weyl group (a $\mathbb{Z}/2\mathbb{Z}$ extension of $W(\algebraicGroup{T})$.
-If $w$ is conjugate in the extension to $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from:
-		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-			\item (Non-split even case $\algebraicGroup{SO}_{2n}^-$) Set $\algebraicGroup{T} = \algebraicGroup{G}_m^{n-1} \times \algebraicGroup{U}(1)$ the diagonal torus.
-Given $w \in W(\algebraicGroup{T})$ the rational structure of $^w\algebraicGroup{T}$ is determined by the conjugacy class of $w$ in the Type B Weyl group (a $\mathbb{Z}/2\mathbb{Z}$ extension of $W(\algebraicGroup{T})$.
-If $w \circ (-1,1)$ is conjugate in the extension to $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from:
-		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-	\end{enumerate}
-	\item (Symplectic groups) In type B the Weyl group conjugacy classes are given by $(\lambda^+,\lambda^-)$ where $\lambda^+$ is the partition formed from and $\lambda^-$ is the partition formed from.
-Given a representation $w$ of the conjugacy class we get:
-		$$^w\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-	\item (Unitary groups) We let our torus be the diagonal torus for the unitary group with hermitian form $I_n$.
-Then $\algebraicGroup{T}=\algebraicGroup{\UnitaryGroup}_1^n$ and the Frobenius action on the Weyl group is trivial.
-Note since all hermitian forms are equivalent over a finite field, $\algebraicGroup{T}$ is a torus in the group $\algebraicGroup{U}_n$ from the previous section.
-In type A the Weyl group conjugacy classes are given by $(\lambda)$, and
-	$$^w\algebraicGroup{T} = \prod_{i} \begin{dcases}
-	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
-	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
-	\end{dcases}$$
-	\item (Even special orthogonal similitude groups)
-	\item (Symplectic similitude groups)
-\end{enumerate}
 
@@
 \end{center}
-Here $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the the last row.
-Here $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$, is split for all rows except for the the last row. We also write down the standard tori for the relevant corresponding similitude groups.
+Here, $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
 \begin{center}
@@
 where $d$ is as in \Cref{subsec:isometry-groups}.
+
+In the unitary case, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is conjugation by $w_n$.
+In the $\algebraicGroup{SO}^-_{2n}$ case, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is the outer automorphism on the Dynkin diagram of type D.
+In terms of signed permutations with an even number of negative signs this corresponds to conjugation by the transposition $(-1,1)$ \calvin{or the $(-n,n)$.
+Kinda depends on conventions.
+The most correct thing to say is it corresponds to conjugation by the matrix $\begin{pmatrix} I_{n-1} & 0 & 0&0 \\ 0 &0&1&0\\0&1&0&0\\0&0&0&I_{n-1}\end{pmatrix}$}.
+In all other cases, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is trivial.
+We now parameterize the Weyl group $\Frobenius$-twisted conjugacy classes and their corresponding tori:
+
+\begin{enumerate}
+    \item (Type A: Unitary groups) The map $w \mapsto w\cdot w_n$ sends a $w_n$-twisted $S_n$ conjugacy class to an $S_n$ conjugacy class.
+Thus twisted conjugacy classes are determined by the cycle partition $\lambda$ associated to $w\cdot w_n$.
+The corresponding algebraic torus is \calvin{$L$ is the lang map}
+	$$^{L^{-1}w}\algebraicGroup{T} =\prod_{i} \begin{dcases}
+	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
+	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
+	\end{dcases}$$
+    \item (Type B, C, D: Special orthogonal and symplectic groups)
+    Conjugacy classes in the type B Weyl (signed permutations) group are classified by pairs of partitions $(\lambda^+,\lambda^-)$.
+	\begin{enumerate}[(a)]
+        \item ($\algebraicGroup{SO}_{2n+1}$ or $\algebraicGroup{Sp}$) Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$. Then
+		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
+        \item ($\algebraicGroup{SO}_{2n}^+$) Viewing the type D Weyl (even signed permutations) group as a subgroup of signed permutations, we can associate to a $(\lambda^+,\lambda^-)$ pair via the conjugacy class of $w$.
+Then
+		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
+		\item ($\algebraicGroup{SO}_{2n}^-$) The map $w \mapsto w\circ (-1,1)$ sends a $(-1,1)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group.
+Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w\circ (-1,1)$.
+Then
+		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
+	\end{enumerate}
+	\item (Type C,D similitude groups)
+        \begin{enumerate}[(a)]
+        \item ($\algebraicGroup{GSp}$ or $\algebraicGroup{GSO}_{2n}^+$) Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w$.
+Then \calvin{probably should have an alternate description}
+        $$^{L^{-1}w}\algebraicGroup{T} = \{(\vec{x},\vec{y},\lambda) \in  \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme\} | \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = \lambda \textnormal{ for all }y_i\}$$
+		\item ($\algebraicGroup{SO}_{2n}^-$) Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w\circ (-1,1)$. Then
+		$$^{L^{-1}w}\algebraicGroup{T} = \{(\vec{x},\vec{y},\lambda) \in  \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme\} | \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = \lambda \textnormal{ for all }y_i\}$$
+        \end{enumerate}
+\end{enumerate}
+
+A summary of the types of tori are
+\begin{center}
+	\begin{tabular}{|c|c|c|}
+		\hline 
+		$\algebraicGroup{G}$ & $W(\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}})$ $\Frobenius$-conj. class& corresponding torus\tabularnewline
+		\hline 
+		\hline 
+		$\algebraicGroup{\UnitaryGroup}$ & $\lambda = [w]$ &$\prod_{i} \begin{dcases}
+	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
+	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
+	\end{dcases}$  
+    \tabularnewline 
+    \hline
+        $\begin{array}{c}
+\algebraicGroup{\SO}_{2n+1}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}^{+}_{2n}\\
+\algebraicGroup{\SO}^{-}_{2n}
+\end{array}$ &
+$(\lambda^+,\lambda^-) = \begin{cases}
+[w] \\
+[w\circ (-1,1)]
+\end{cases}$ & $\prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $\tabularnewline
+	\hline 
+		\hline
+        $\begin{array}{c}
+\algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}^{+}_{2n}\\
+\algebraicGroup{\GSO}^{-}_{2n}
+\end{array}$ &
+$(\lambda^+,\lambda^-) = \begin{cases}
+[w] \\
+[w\circ (-1,1)]
+\end{cases}$ & $\prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \left(\prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times_{\FieldNorm{2\lambda^-_i}{\lambda^-_i}} \multiplcativeScheme\right) $\tabularnewline
+		\hline		
+	\end{tabular}
+\end{center}
 

### 2025-03-26 main.tex
Rename file

--- 2025-03-25 reorganization.tex
@@
 
-If special odd orthogonal group case (that is, $\epsilon_{\hermitianSpace} = 1$, $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace$ is odd) and in the unitary case (that is, $\quadraticExtension \ne \finiteField$), we have that $\algebraicGroup{G}$ has connected center and we denote $\tilde{\algebraicGroup{G}} = \algebraicGroup{G}$.
+In the special odd orthogonal group case (that is, $\epsilon_{\hermitianSpace} = 1$, $\quadraticExtension = \finiteField$ and $\dim_{\finiteField} \hermitianSpace$ is odd) and in the unitary case (that is, $\quadraticExtension \ne \finiteField$), we have that $\algebraicGroup{G}$ has connected center and we denote $\tilde{\algebraicGroup{G}} = \algebraicGroup{G}$.
 
@@
 \begin{example}
-	\elad{Correct example or remove it}
+	\elad{Correct example or remove it}\calvin{They are geo conjugate in $\algebraicGroup{Sp}_4$}
 	Take $\algebraicGroup{G}' = \algebraicGroup{\GL}_2$.
@@
 \[
-    \exp(\langle x_{T,\theta},y\rangle) = \theta(y(N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
+    \exp(\langle x_{T,\theta},y\rangle) = \theta((N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
 \]
+\calvin{can cut this next part but for the sake of completeness in early drafts lets keep it:}
+For different tori with Frob action we get
+\begin{enumerate}
+    \item ($n$-cycle) $\algebraicGroup{T}(\finiteField) \cong \finiteField_n^\times$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{mn}) = (\zeta_n)^{y_1+qy_2+q^2y_3 \hdots +q^{n-1}y_n}$$
+    \item ($n$-cycle with one negative) $\algebraicGroup{T}(\finiteField) \cong \{x \in \finiteField_{2n}^\times: \FieldNorm{2n}{n}(x) = 1\}$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{2mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{2mn}) = (\beta_n)^{y_1+qy_2+q^2y_3 \hdots +q^{n-1}y_n}$$
+    where $\beta_n = \zeta_{2n}^{1-q^n}$.
+    \item ($(-1) \cdot n$-cycle, $n$ even) $\algebraicGroup{T}(\finiteField) \cong \finiteField_n^\times$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{mn}) = (\zeta_n)^{y_1-qy_2+q^2y_3-q^3y_4 \hdots -q^{n-1}y_n}$$
+    \item ($(-1) \cdot n$-cycle, $n$ odd) $\algebraicGroup{T}(\finiteField) \cong \{x \in \finiteField_{2n}^\times: \FieldNorm{2n}{n}(x) = 1\}$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{2mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{2mn}) = (\beta_n)^{y_1-qy_2+q^2y_3-q^3y_4 \hdots +q^{n-1}y_n}$$
+    where $\beta_n = \zeta_{2n}^{1-q^n}$.
+\end{enumerate}
+\calvin{end cut part}
+Now the results follow from checking that
+\[
+    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
+\]
+for $r$ divisible as above.
+\begin{comment}
 Thus the result follows from the computations:
 \begin{enumerate}
-	\item \begin{align*}
+	\item[B,C,D Case 1] \begin{align*}
 		\exp(\langle\phi(x_{\finiteFieldExtension{n},\alpha}),(y_1,y_2)\rangle) &= \exp(\langle x_{\finiteFieldExtension{n},\alpha},\phi^*(y_1,y_2)\rangle) \\
@@
 \end{enumerate}
+\end{comment}
 \end{proof}

### 2025-03-26 main.tex
Update main.tex
added basic DL 101. Can spruce up later, add more properties we need to use

@@
 \elad{Write a 101-intro to Deligne--Lusztig but not too detailed}
+For each maximal rational torus $\algebraicGroup{T}$ in $\algebraicGroup{G}$, Deligne and Lusztig contructed a geometric space with commuting actions of $\algebraicGroup{T}(\finiteField)$ and $\algebraicGroup{G}$.
+The $\ell$-adic \'etale Euler characteristic of this space is a $\algebraicGroup{T}(\finiteField) \times \algebraicGroup{G}(\finiteField)$ virtual representation, and taking the $\algebraicGroup{T}(\finiteField)$ $\theta$-invariants gives a $\algebraicGroup{G}(\finiteField)$ virtual representation $R_T^G(\theta)$.
+The $R_T^G(\theta)$ only depends on the $\algebraicGroup{G}(\finiteField)$-conjugacy class of $(\algebraicGroup{T},\theta)$ and
+the collection of virtual representations $\{R_T^G(\theta)\}$ contain every irreducible $\algebraicGroup{G}(\finiteField)$-representation as a sub-virtual representation.
+
+\begin{proposition}[cite Digne Michel Cor 12.7]
+Treating $R_T^G(\theta)$ as a class function of $\algebraicGroup{G}(\finiteField)$ via the character of $R_T^G(\theta)$, for any class function $f$ on $\algebraicGroup{G}(\finiteField)$ which satisfies $f(g) = f(s)$ when $g=su$ is the Jordan decompositoin of $g$, we have
+\[
+	\langle R_T^G(\theta),f \rangle_{\algebraicGroup{G}(\finiteField)} = \langle \theta, f|_{\algebraicGroup{T}(\finiteField)}\rangle_{\algebraicGroup{T}(\finiteField)}
+\]
+in other words:
+\[
+	\frac{1}{|\algebraicGroup{G}(\finiteField)|}\sum_{g \in \algebraicGroup{G}(\finiteField)}\left(R_T^G(\theta)\right)(g)f(g) = \frac{1}{|\algebraicGroup{T}(\finiteField)|}\sum_{t \in  \algebraicGroup{T}(\finiteField)} \theta(t)f(t)
+\]
+\end{proposition}
 
@@
 
-The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
+The virtual representations $R_T^G(\theta)$ and $R_{T'}^G(\theta')$ share an irreducible representation only if $(T,\theta),(T',\theta')$ are geometrically conjugate.
+This yields a natural partitioning of the irreducible representations of $\algebraicGroup{G}(\finiteField)$: the \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
 

### 2025-03-26 main.tex
Update main.tex
added commented out proof of functions on the center being stable just to have it somewhere

@@
 \end{proof}
+%adding in the commented out sketched proof just in case:
+\begin{comment}
+\begin{proof}
+The Deligne Lusztig variety is a subset of the group, for any $z \in \algebraicGroup{Z}(\finiteField)$ we can move the action of $z \in algebraicGroup{G}(\finiteField)$ to the action of $z \in \algebraicGroup{T}(\finiteField)$
+Thus it suffices to show that $\theta|_{\algebraicGroup{Z}(\finiteField))} = \theta'|_{\algebraicGroup{Z}(\finiteField)}$
+But this follows from geometric conjugacy: for large enough $n$, $\theta \circ \fieldNorm{n}{1}|_{\algebraicGroup{Z}(\finiteField))} = \theta'\circ \fieldNorm{n}{1}|_{\algebraicGroup{Z}(\finiteField)}$
+and the Norm map is surjective.
+\end{proof}
+\end{comment}
 

### 2025-03-27 main.tex
lemmas cochar_computation and indep_geo_conj proofs case by case now
updated lemmas cochar_computation and indep_geo_conj to be case by case proofs.

@@
 \[
-    g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) := \varepsilon_{\algebraicGroup{
+    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \varepsilon_{\algebraicGroup{
     \tilde{\algebraicGroup{T}}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
@@
 \begin{enumerate}[(i)]
-	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\theta,\psi,\chi)$ depends only on the semisimple conjugacy class of $(s)$.
-	\item $g_{T,\rho}(\theta,\psi,\chi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
+	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s)$.
+	\item $g_{T,\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
 \end{enumerate}
@@
 	\[
-	g_{T,\rho}(\theta,\psi,\chi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
+	g_{T,\rho}(\chi,\theta,\psi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
 	\]
@@
 	\[
-	g_{(s)}(\psi,\chi) := g_{T,\rho}(\theta,\psi,\chi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
+	g_{(s)}(\psi,\chi) := g_{T,\rho}(\chi,\theta,\psi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
 	\]
@@
 	\[
-	g_{T,\rho}(\theta,\psi,\chi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
+	g_{T,\rho}(\chi,\theta,\psi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
 	\]
@@
 Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$.
-Then $g_{\algebraicGroup{T},\rho}(\theta,\psi,\chi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
+Then $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
 \end{corollary}
@@
 
-The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\theta,\psi,\chi)$ for the appropriate $\rho$ in the table below.
+The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate $\rho$ in the table below.
 \begin{center}
@@
 
-In particular to analyze $g_{T,\rho}(\theta,\psi,\chi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
+In particular to analyze $g_{T,\rho}(\chi,\theta,\psi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
@@
         \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases.
-Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w_nww_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
         \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
@@
     \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} w & 0 \\
-        0 & w
+        0 & w_nwww_n
         \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
@@
 \]
-\calvin{can cut this next part but for the sake of completeness in early drafts lets keep it:}
 For different tori with Frob action we get
@@
 \end{enumerate}
-\calvin{end cut part}
-Now the results follow from checking that
-\[
-    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
-\]
-for $r$ divisible as above.
+Now the results follow from the equalities
+\begin{align*}
+	\alpha(\zeta^{((y_1-y_{n+1})+q(y_2-y_{n+2}) + \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\alpha(\zeta^{(y_1+qy_2 + \hdots +q^{n-1}y_{n})}) \alpha^{-1}(\zeta^{(y_{n+1}+qy_{n+2} + \hdots +q^{n-1}y_{2n})}) \\
+	\theta(\beta^{((y_1-y_{n+1})+q(y_2-y_{n+2}) + \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\theta(\beta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{n+1}+q^{n+1}y_{n+2} \hdots +q^{2n-1}y_{2n})}) \\
+	&=\theta'(\zeta^{(y_1+q(y_2) + \hdots +q^{2n-1}y_{2n})})\\
+	\alpha(\zeta^{((y_1-y_{n+1})-q(y_2-y_{n+2}) +q^2(y_3-y_{n+3}) \hdots -q^{n-1}(y_{n}-y_{2n}))})&= \alpha(\zeta^{(y_1+qy_{n+2}+q^2y_3 +q^3y_4 \hdots +q^{n-1}y_{2n})}) \alpha^{-1}(\zeta^{(y_{n+1}+q(y_{2}) + q^2y_{n+3}\hdots +q^{n-1}y_{n})}) \\
+	\theta(\beta^{((y_1-y_{n+1})-q(y_2-y_{n+2}) +q^2(y_3-y_{n+3}) \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\theta(\beta^{(y_1+qy_{n+2} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{n+1}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{2n})}) \\
+	&=\theta'(\zeta^{(y_1+qy_2 + \hdots +q^{2n-1}y_{2n})})
+\end{align*}
+%Now the results follow from checking that
+%\[
+%    (\theta_1 \times \theta_1^{-1}) \circ \FieldNorm{\algebraicGroup{T}_1(\finiteField_r)}{\algebraicGroup{T}_1(\finiteField)} (\vec{y})(\zeta_r) = \theta_2\circ \FieldNorm{\algebraicGroup{T}_2(\finiteField_r)}{\algebraicGroup{T}_2(\finiteField)}(\vec{y})(\zeta_r)
+%\]
+%for $r$ divisible as above.
 \begin{comment}
@@
 \end{proof}
+We let $\phi_{B,\lambda_i^+}, \phi_{B,\lambda_i^-}$ denote the $\phi$'s above in cases 1 and 2 respectivitly with $n = |\lambda_i|$. 
+Let $\phi_{U,\lambda_i}$ denote the $\phi$'s above in cases 3 and 4 with $n = |\lambda_i|$.
 
@@
 
-Suppose $T \cong \prod_{j=1}^r \multiplicativegroup{\finiteFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$.
-We compute $g_{T,\rho}(\theta,\psi,\chi)$ using the the split torus $\algebraicGroup{T}^*$ in $G^*$ including into the split torus $\algebraicGroup{T}'$ in $\GL$ in the non unitary case and in the unitary case we use the tori $\algebraicGroup{T}^*$ whose $\finiteField$ points are $(\NormOneGroup{2})^n \subset G^*(\finiteField)$ includes into the torus $\algebraicGroup{T}'$ in $\GL(2n)$ whose $\finiteField$ points are $(\finiteFieldExtension{2}^\times)^n$.
-We then define $\tilde{T}$ as the $\finiteField$-rational torus corresponding to the Frobenius stable Weyl group orbit of $\rho(w)$ inside $W(\algebraicGroup{T}')$ where $(w)$ inside $W(\algebraicGroup{T}^*)$ is the Frobenius stable Weyl group orbit associated to $T$.
-\Cref{lem:cochar_computation} above implies that
+For the former we will show
 \[
-g_{T,\rho}(\theta,\psi,\chi)= g_{T}(\theta,\psi,\chi) \cdot \begin{cases}
+g_{T,\rho}(\chi,\theta,\psi)= g_{T}(\chi,\theta,\psi) \cdot \begin{cases}
         1  & G \neq Sp, GSp\\
-        \tau(1,\psi_1) & G = Sp \textnormal{ or } GSp
+        \tau{\chi}{\psi} & G = Sp \textnormal{ or } GSp
     \end{cases}.
 \]
-\calvin{check if we need a $\chi$ in the $\tau$ factor}
-\Cref{cor:geoconj} then implies that $g_T(\theta,\psi,\chi)$ only depends on the geometric conjugacy class of $(T,\theta)$.   
+\calvin{$\chi$ or $\chi^{-1}$? Check throughout proof!}
+We will do this casewise, demonstrating in each case that the Frobeinus equivariant map $X_*(\algebraicGroup{T}) \to X_*(\algebraicGroup{G})$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}.
+Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ and geometric Frobeinus action on $X_*(\algebraicGroup{T})$.
+
+\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
+\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}}.
+\begin{enumerate}
+    \item[($\algebraicGroup{U}$)] Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$. Let $w \circ w_n$ have cycle decomposition $\lambda$ 
+	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. Then
+	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
+	and applying \Cref{lem:cochar_computation}
+	\begin{align*}
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i} \begin{cases}
+			\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} & \lambda_i \textnormal{ even} \\
+			\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i}} & \lambda_i \textnormal{ odd}
+		\end{cases}
+	\end{align*}
+	which is equal to $g_{T}(\chi,\theta,\psi)$.
+	\item[($\algebraicGroup{SO}_{2n+1}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
+	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} $$
+	and applying \Cref{lem:cochar_computation}
+	\begin{align*}
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \times \Pi_{\lambda_i^-}\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi,\theta,\psi)$.
+	\item[($\algebraicGroup{Sp}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
+	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} \oplus \left(0:X_*(\algebraicGroup{T}) \to \mathbb{Z}\right)$$
+	applying \Cref{lem:cochar_computation}
+	\begin{align*}
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
+		\times \tau{\chi}{\psi}
+	\end{align*}
+	which is equal to $g_{T}(\chi,\theta,\psi) \cdot \tau(\chi,\psi)$.
+	\item[($\algebraicGroup{SO}_{2n}^+$)] Let $T$ correspond to the signed permutation conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
+	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
+	applying \Cref{lem:cochar_computation}
+	\begin{align*}
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi,\theta,\psi)$.
+	\item[($\algebraicGroup{SO}_{2n}^-$)] Let $T$ correspond to the $(-n,n)$-twisted permutation conjugacy class $[w]$ with cycle decompositionof $[w \cdot (-n,n)]$ equal to $(\lambda^+,\lambda^-)$ 
+	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
+	applying \Cref{lem:cochar_computation}
+	\begin{align*}
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi,\theta,\psi)$.
+\end{enumerate}
+
 \begin{comment}

### 2025-03-28 main.tex
Update from Overleaf

--- 2025-03-26 main.tex
@@
 \newcommand{\isomorphic}{\cong}
-\newcommand{\lengthof}{\mathfrak{n}}
+\newcommand{\lengthof}{\ell}
 \newcommand{\abs}[1]{\left|#1\right|}
@@
 \newcommand{\CocharacterLattice}[1]{X_{\ast}\left(#1\right)}
+\newcommand{\SymmetricGroup}{\mathfrak{S}}
 
@@
 We are now ready to state Kondo's result.
+%test
 \begin{theorem}[Kondo {\cite{Kondo1963}}]
@@
 Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
-In particular if you fix a rational torus $\algebraicGroup{T}_0$ with rank $=\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and it's $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of $g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.
+In particular if we fix a rational torus $\algebraicGroup{T}_0$ with rank $\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and its $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of the Lang map $L \colon \algebraicGroup{G}\left(\algebraicClosure{\finiteField}\right) \to \algebraicGroup{G}\left(\algebraicClosure{\finiteField}\right)$ defined as $L\left(g\right) = g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.
 
@@
 %could really demonstrate this by stating Land map is surjective + that all maximal tori are conjugate over an algebraiclly closed field
+
+Let us denote $$\left(\quadraticExtension, x \mapsto \involution{x}\right) = \begin{dcases}
+	\left(\finiteFieldExtension{2}, x \mapsto x^q\right)  & \algebraicGroup{G} \text{ is a unitary group},\\
+	\left(\finiteField, x \mapsto x\right) & \text{otherwise.}
+\end{dcases}$$
 
@@
 	\hline 
-		$\algebraicGroup{G}$ & $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ \tabularnewline
+		$\algebraicGroup{G}$ & $\algebraicGroup{T}_0$ \tabularnewline
 		\hline 
@@
 		\hline 
-		$\algebraicGroup{G}$ & $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ \tabularnewline
+		$\algebraicGroup{G}$ & $\algebraicGroup{T}_0$ \tabularnewline
 		\hline 
@@
 
-In the unitary case, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is conjugation by $w_n$.
-In the $\algebraicGroup{SO}^-_{2n}$ case, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is the outer automorphism on the Dynkin diagram of type D.
-In terms of signed permutations with an even number of negative signs this corresponds to conjugation by the transposition $(-1,1)$ \calvin{or the $(-n,n)$.
-Kinda depends on conventions.
-The most correct thing to say is it corresponds to conjugation by the matrix $\begin{pmatrix} I_{n-1} & 0 & 0&0 \\ 0 &0&1&0\\0&1&0&0\\0&0&0&I_{n-1}\end{pmatrix}$}.
-In all other cases, the action of $\Frobenius$ on $W(\algebraicGroup{T}_{\algebraicGroup{U}}^{std})$ is trivial.
-We now parameterize the Weyl group $\Frobenius$-twisted conjugacy classes and their corresponding tori:
+In the unitary case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\UnitaryGroup}_n}^{\mathrm{std}}\right)$ is conjugation by $w_n$.
+In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\SO}^{-}_{2n}}^{\mathrm{std}}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
+In our matrix representation, $\Frobenius$ acts on the Weyl group by conjugation by the matrix $$\left(-n,n\right) \coloneq \begin{pmatrix}\IdentityMatrix{n-1} & 0 & 0 & 0\\
+	0 & 1 & 0 & 0\\
+	0 & 0 & -1 & 0\\
+	0 & 0 & 0 & \IdentityMatrix{n-1}
+\end{pmatrix}.$$ In all other cases, the action of $\Frobenius$ on $W(\algebraicGroup{T}_0)$ is trivial.
+We now parameterize the Weyl group $\Frobenius$-twisted conjugacy classes and their corresponding tori.
 
 \begin{enumerate}
-    \item (Type A: Unitary groups) The map $w \mapsto w\cdot w_n$ sends a $w_n$-twisted $S_n$ conjugacy class to an $S_n$ conjugacy class.
-Thus twisted conjugacy classes are determined by the cycle partition $\lambda$ associated to $w\cdot w_n$.
-The corresponding algebraic torus is \calvin{$L$ is the lang map}
-	$$^{L^{-1}w}\algebraicGroup{T} =\prod_{i} \begin{dcases}
-	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
-	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
-	\end{dcases}$$
-    \item (Type B, C, D: Special orthogonal and symplectic groups)
-    Conjugacy classes in the type B Weyl (signed permutations) group are classified by pairs of partitions $(\lambda^+,\lambda^-)$.
-	\begin{enumerate}[(a)]
-        \item ($\algebraicGroup{SO}_{2n+1}$ or $\algebraicGroup{Sp}$) Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$. Then
-		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-        \item ($\algebraicGroup{SO}_{2n}^+$) Viewing the type D Weyl (even signed permutations) group as a subgroup of signed permutations, we can associate to a $(\lambda^+,\lambda^-)$ pair via the conjugacy class of $w$.
+    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{\UnitaryGroup}_n\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
+If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{\UnitaryGroup}_n\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class.
+Thus twisted conjugacy classes are determined by the cycle partition $\lambda \vdash n$ associated to $\dot{w} \cdot w_n$.
+Let us denote by $\lambda^+$ the partition formed by taking the even parts of $\lambda$ and by $\lambda^{-}$ the partition formed by taking the odd parts of $\lambda$.
+The corresponding algebraic torus is
+	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{i} 	\restrictionOfScalars{\finiteFieldExtension{\lambda^{+}_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \\
+	\restrictionOfScalars{\finiteFieldExtension{\lambda_i^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+	% The embedding into the unitary group requires conjugation by \diag(1,1,1,\sqrt{d},\sqrt{d},\sqrt{d}). I would rather not write it.
+
+	%The embedding into $\algebraicGroup{\UnitaryGroup}_n$ is given by the map %\begin{equation}\label{eq:torus-embedding-unitary-group}
+	%	\left( \left(g_i\right)_{i=1}^{\lengthof\left(\lambda^+\right)}, \left(h_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto \diag(g_1,\dots, g_{\lengthof\left(\lambda^+\right)}, h_1^{\ast}, \dots, h_{\lengthof\left(\lambda^{-}\right)}^{\ast}, \involution{(g^{\ast}_{\lengthof\left(\lambda^+\right)})}, \dots, \involution{(g^{\ast}_1)}).
+	%\end{equation}
+	See also \cite[Section 2.3]{ThiemVinroot2009} and \cite[Section 2.2]{SaitoShinoda2000}.
+    \item (Odd special orthogonal and symplectic groups)
+    For $\algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{\SO}_{2n+1}$, the Weyl group is isomorphic to $$\left\{\pm 1\right\}^n \rtimes \SymmetricGroup_n,$$ which we can identify with the group signed permutations.
+The conjugacy classes of the Weyl group are classified by pairs of partitions $(\lambda^+,\lambda^-)$ with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$.
+See \cite[Section 2.2]{KonvalinkaMatjavPfeiffer2011} for more details.
+Let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w$ in the Weyl group.
 Then
-		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-		\item ($\algebraicGroup{SO}_{2n}^-$) The map $w \mapsto w\circ (-1,1)$ sends a $(-1,1)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group.
-Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w\circ (-1,1)$.
+		$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+		See also \cite[Section 3.2 Part (B)]{Zalesski2018}.
+        \item (Even special orthogonal groups) The Weyl group of $\algebraicGroup{SO}_{2n}^{\pm}$ is isomorphic to $$\left\{ \left(x_1,\dots,x_n\right) \in \left\{\pm 1\right\}^n \mid \prod_{i=1}^n x_i = 1\right\} \rtimes \SymmetricGroup_n,$$ which can be realized the subgroup of the group of signed permutations, consisting of all even signed permutations.
+Using this realization, we may attach to $w$ in the Weyl group a pair of partitions $\left(\lambda^+, \lambda^-\right)$ as before, with $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$.
+If $\lambda^{-}$ is not the empty partition, the pair $\left(\lambda^+, \lambda^-\right)$ determines the conjugacy class of $w$.
+Otherwise, there are two different conjugacy classes of the Weyl group corresponding to the same pair $\left(\lambda^{+}, \lambda^{-}\right)$.
+These two conjugacy class correspond to isomorphic tori, and these tori are not conjugate in $\algebraicGroup{\SO}_{2n}^{\pm}$.
+See \cite[Section 2.3]{KonvalinkaMatjavPfeiffer2011} for more details.
+        \begin{enumerate}
+        	\item (Split case): For $\algebraicGroup{\SO}_{2n}^+$ we have that
+        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+			See also \cite[Section 3.2 Parts (C) and (D)]{Zalesski2018}.        	
+        	\item (Non-split case): As in the unitary group case, for $\algebraicGroup{SO}_{2n}^-$, the map $w \mapsto \dot{w}\circ (-n,n)$ sends a $(-n,n)$-twisted conjugacy class in the even signed permutation group to a conjugacy class in the signed permutation group.
+Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $\dot{w} \circ (-n,n)$.
 Then
-		$$^{L^{-1}w}\algebraicGroup{T} = \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $$
-	\end{enumerate}
-	\item (Type C,D similitude groups)
-        \begin{enumerate}[(a)]
-        \item ($\algebraicGroup{GSp}$ or $\algebraicGroup{GSO}_{2n}^+$) Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w$.
-Then \calvin{probably should have an alternate description}
-        $$^{L^{-1}w}\algebraicGroup{T} = \{(\vec{x},\vec{y},\lambda) \in  \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme\} | \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = \lambda \textnormal{ for all }y_i\}$$
-		\item ($\algebraicGroup{SO}_{2n}^-$) Let $(\lambda^+,\lambda^-)$ correspond to the signed permutation group conjugacy class of $w\circ (-1,1)$. Then
-		$$^{L^{-1}w}\algebraicGroup{T} = \{(\vec{x},\vec{y},\lambda) \in  \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme\} | \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = \lambda \textnormal{ for all }y_i\}$$
-        \end{enumerate}
-\end{enumerate}
-
-A summary of the types of tori are
-\begin{center}
-	\begin{tabular}{|c|c|c|}
-		\hline 
-		$\algebraicGroup{G}$ & $W(\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}})$ $\Frobenius$-conj. class& corresponding torus\tabularnewline
-		\hline 
-		\hline 
-		$\algebraicGroup{\UnitaryGroup}$ & $\lambda = [w]$ &$\prod_{i} \begin{dcases}
-	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} & \lambda_i \textnormal{ is even} \\
-	\restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}  & \lambda_i \textnormal{ is odd}
-	\end{dcases}$  
-    \tabularnewline 
-    \hline
-        $\begin{array}{c}
-\algebraicGroup{\SO}_{2n+1}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}^{+}_{2n}\\
-\algebraicGroup{\SO}^{-}_{2n}
-\end{array}$ &
-$(\lambda^+,\lambda^-) = \begin{cases}
-[w] \\
-[w\circ (-1,1)]
-\end{cases}$ & $\prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1} $\tabularnewline
-	\hline 
-		\hline
-        $\begin{array}{c}
-\algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}^{+}_{2n}\\
-\algebraicGroup{\GSO}^{-}_{2n}
-\end{array}$ &
-$(\lambda^+,\lambda^-) = \begin{cases}
-[w] \\
-[w\circ (-1,1)]
-\end{cases}$ & $\prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \left(\prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times_{\FieldNorm{2\lambda^-_i}{\lambda^-_i}} \multiplcativeScheme\right) $\tabularnewline
-		\hline		
-	\end{tabular}
-\end{center}
-
-\elad{Under construction}
-If $m \ge 1$, we denote 
-$$\NormOneGroup{2m} := \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right)= 1\right\} = \left(\mathrm{Res}_{\mathbb{F}_{m}:\mathbb{F}} \algebraicGroup{U}(1)\right)(\mathbb{F}).$$
+        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+			See also \cite[Section 3.2 Part (D)]{Zalesski2018}. Notice that we differ from that \cite{Zalesski2018} since we do not incorporate the element $\left(-n, n\right)$ in the Frobenius root.
+        \end{enumerate}
+    \end{enumerate}
+	We summarize all these cases in the following theorem.
+
+	\begin{theorem}
+		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to $$\algebraicGroup{T} \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
+		where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$, where in the unitary group case we require that $\lambda^+$ consists only of even parts and that $\lambda^-$ consists only of odd parts.
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \NormOneGroup{2 \lambda_i^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto
+		\begin{pmatrix}
+			\iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
+			& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}
+			 \right) &\\
+			 & & \involution{\iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)}
+		\end{pmatrix},$$
+		where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \prod_{i} \NormOneGroup{2 \lambda_j^-} \to G'$ are embeddings.
+Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
+
+		In the odd special orthogonal case, the embedding $\iota_{-}$ can be chosen to fix the middle standard vector $e_{n+1}$.
+	\end{theorem}
+
+    In addition, we write the tori classification for the similitude groups we consider.
+	\begin{enumerate}
+		\item For $\algebraicGroup{\GSp}_{2n}$ or $\algebraicGroup{\GSO}_{2n}^+$, suppose that $(\lambda^+,\lambda^-)$ corresponds to the conjugacy class of $w$ as an element of the group of signed permutations.
+Then
+			\begin{align*}
+				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
+				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
+			\end{align*}
+			\item For $\algebraicGroup{\GSO}_{2n}^-$, let $(\lambda^+,\lambda^-)$ correspond to the conjugacy class of $w\circ (-n,n)$ viewed as an element of the group of signed permutations. Then
+			\begin{align*}
+				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
+				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
+			\end{align*}
+	\end{enumerate}
+
+	We summarize these cases in the following theorem.
+	\begin{theorem}
+	A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} =  \algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}_{2n}^{\pm}$ is isomorphic to \begin{align*}
+		\algebraicGroup{T} \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right)  \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
+		& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
+	\end{align*}
+	where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$.
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(\left(a_j\right)_{j = 1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i = 1}^{\lengthof\left(\lambda^-\right)}, z\right) \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \subset \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}} \times \multiplicativegroup{\finiteField}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right) \mapsto
+	\begin{pmatrix}
+		z \cdot \iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
+		& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z
+		\right) &\\
+		& & \iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)
+	\end{pmatrix},$$
+	where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(\left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right)\in \prod_{i} \finiteFieldExtension{2\lambda^{-}_i} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \to G'$$ are embeddings.
+Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
+\end{theorem}
 
@@
 \elad{Write a 101-intro to Deligne--Lusztig but not too detailed}
-For each maximal rational torus $\algebraicGroup{T}$ in $\algebraicGroup{G}$, Deligne and Lusztig contructed a geometric space with commuting actions of $\algebraicGroup{T}(\finiteField)$ and $\algebraicGroup{G}$.
-The $\ell$-adic \'etale Euler characteristic of this space is a $\algebraicGroup{T}(\finiteField) \times \algebraicGroup{G}(\finiteField)$ virtual representation, and taking the $\algebraicGroup{T}(\finiteField)$ $\theta$-invariants gives a $\algebraicGroup{G}(\finiteField)$ virtual representation $R_T^G(\theta)$.
-The $R_T^G(\theta)$ only depends on the $\algebraicGroup{G}(\finiteField)$-conjugacy class of $(\algebraicGroup{T},\theta)$ and
-the collection of virtual representations $\{R_T^G(\theta)\}$ contain every irreducible $\algebraicGroup{G}(\finiteField)$-representation as a sub-virtual representation.
-
-\begin{proposition}[cite Digne Michel Cor 12.7]
-Treating $R_T^G(\theta)$ as a class function of $\algebraicGroup{G}(\finiteField)$ via the character of $R_T^G(\theta)$, for any class function $f$ on $\algebraicGroup{G}(\finiteField)$ which satisfies $f(g) = f(s)$ when $g=su$ is the Jordan decompositoin of $g$, we have
-\[
-	\langle R_T^G(\theta),f \rangle_{\algebraicGroup{G}(\finiteField)} = \langle \theta, f|_{\algebraicGroup{T}(\finiteField)}\rangle_{\algebraicGroup{T}(\finiteField)}
-\]
-in other words:
-\[
-	\frac{1}{|\algebraicGroup{G}(\finiteField)|}\sum_{g \in \algebraicGroup{G}(\finiteField)}\left(R_T^G(\theta)\right)(g)f(g) = \frac{1}{|\algebraicGroup{T}(\finiteField)|}\sum_{t \in  \algebraicGroup{T}(\finiteField)} \theta(t)f(t)
-\]
-\end{proposition}
 
@@
 
-The virtual representations $R_T^G(\theta)$ and $R_{T'}^G(\theta')$ share an irreducible representation only if $(T,\theta),(T',\theta')$ are geometrically conjugate.
-This yields a natural partitioning of the irreducible representations of $\algebraicGroup{G}(\finiteField)$: the \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
+The \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
 

### 2025-03-28 main.tex
Adding a table of contents and minor chages
added one comment
Nicer notation

@@
 \newcommand{\similitudeCharacter}{\operatorname{sim}}
+\newcommand{\etale}{\'etale }
 
@@
 
+\tableofcontents
+
 \section{Introduction}
@@
 If $k' \mid k$, let $\FieldNorm{k}{k'} \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\finiteFieldExtension{k'}}$ be the norm map.
+
+Given a partition $\lambda = \left(\lambda_1, \dots, \lambda_\ell\right)$, we denote the \etale $\finiteField$-algebra $$\finiteFieldExtension{\lambda} = \prod_{i=1}^{\ell} \finiteFieldExtension{\lambda_i}$$ and define
+$$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$
 
@@
 The corresponding algebraic torus is
-	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{i} 	\restrictionOfScalars{\finiteFieldExtension{\lambda^{+}_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \\
-	\restrictionOfScalars{\finiteFieldExtension{\lambda_i^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 	% The embedding into the unitary group requires conjugation by \diag(1,1,1,\sqrt{d},\sqrt{d},\sqrt{d}). I would rather not write it.
@@
 Then
-		$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 		See also \cite[Section 3.2 Part (B)]{Zalesski2018}.
@@
         	\item (Split case): For $\algebraicGroup{\SO}_{2n}^+$ we have that
-        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+        	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
         	See also \cite[Section 3.2 Parts (C) and (D)]{Zalesski2018}.        	
@@
 Then
-        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+        	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 			See also \cite[Section 3.2 Part (D)]{Zalesski2018}. Notice that we differ from that \cite{Zalesski2018} since we do not incorporate the element $\left(-n, n\right)$ in the Frobenius root.
@@
 	\begin{theorem}
-		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to $$\algebraicGroup{T} \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
+		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to 	$$\algebraicGroup{T} \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
 		where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$, where in the unitary group case we require that $\lambda^+$ consists only of even parts and that $\lambda^-$ consists only of odd parts.
-We have that $$\algebraicGroup{T}^{\Frobenius} \cong \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \NormOneGroup{2 \lambda_i^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(a, t\right) \mapsto
 		\begin{pmatrix}
-			\iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
-			& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}
-			 \right) &\\
-			 & & \involution{\iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)}
+			\iota_+\left(a\right)\\
+			& \iota_{-}\left(t\right) &\\
+			 & & \involution{\iota_+^{\ast}\left(a\right)}
 		\end{pmatrix},$$
-		where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \prod_{i} \NormOneGroup{2 \lambda_j^-} \to G'$ are embeddings.
+		where $\iota_+ \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \NormOneGroup{2 \lambda^{-}} \to G'$ are embeddings.
 Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
@@
 			\begin{align*}
-				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
-				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
+				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
 			\end{align*}
@@
 	A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} =  \algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}_{2n}^{\pm}$ is isomorphic to \begin{align*}
-		\algebraicGroup{T} \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right)  \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
-		& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
+				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
 	\end{align*}
 	where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$.
-We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(\left(a_j\right)_{j = 1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i = 1}^{\lengthof\left(\lambda^-\right)}, z\right) \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \subset \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}} \times \multiplicativegroup{\finiteField}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right) \mapsto
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(x, y, z\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(t_i\right) = z \right\}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y, z\right) \mapsto
 	\begin{pmatrix}
-		z \cdot \iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
-		& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z
-		\right) &\\
-		& & \iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)
+		z \cdot \iota_+ \left(x\right)\\
+		& \iota_{-}\left(y\right) &\\
+		& & \iota_+^{\ast}\left(x\right)
 	\end{pmatrix},$$
-	where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(\left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right)\in \prod_{i} \finiteFieldExtension{2\lambda^{-}_i} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \to G'$$ are embeddings.
+	where $\iota_+ \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(y, z\right)\in \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(y\right) = z \text{ for all } i \right\} \to G'$$ are embeddings.
 Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
@@
     \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} w & 0 \\
-        0 & w
+        0 & w^{\ast}
         \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
@@
         1  & G \neq Sp, GSp\\
-        \tau{\chi}{\psi} & G = Sp \textnormal{ or } GSp
+        \tau\left(\chi, \fieldCharacter\right) & G = Sp \textnormal{ or } GSp
     \end{cases}.
@@
 
-\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}} 
-\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}}.
 \begin{enumerate}

### 2025-03-28 main.tex
Minors

@@
 $$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$
+
+\elad{Need to define $2 \lambda$ and $\FieldNorm{2\lambda}{\lambda}$ and $\NormOneGroup{2 \lambda}$}
 
@@
 \end{pmatrix} \in \GL_n\left(\finiteField\right)$$ be the longest Weyl element.
+\calvin{we should standardize an order between Unitary, Special Orthogonal Symplectic and try to kinda stick with it throughout.}
 \begin{enumerate}
@@
 		where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$, where in the unitary group case we require that $\lambda^+$ consists only of even parts and that $\lambda^-$ consists only of odd parts.
-We have that $$\algebraicGroup{T}^{\Frobenius} \cong \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(a, t\right) \mapsto
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y\right) \mapsto
 		\begin{pmatrix}
-			\iota_+\left(a\right)\\
-			& \iota_{-}\left(t\right) &\\
-			 & & \involution{\iota_+^{\ast}\left(a\right)}
+			\iota_+\left(x\right)\\
+			& \iota_{-}\left(y\right) &\\
+			 & & \involution{\iota_+^{\ast}\left(x\right)}
 		\end{pmatrix},$$
@@
 	where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$.
-We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(x, y, z\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(t_i\right) = z \right\}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y, z\right) \mapsto
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(x, y, z\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(y\right) = z \right\}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y, z\right) \mapsto
 	\begin{pmatrix}

### 2025-03-28 main.tex
Weyl group notations

@@
 \end{center}
-Here, $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
+Here, $\algebraicGroup{T}_{0}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
 \begin{center}
@@
 
-In the unitary case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\UnitaryGroup}_n}^{\mathrm{std}}\right)$ is conjugation by $w_n$.
-In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\SO}^{-}_{2n}}^{\mathrm{std}}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
+In the unitary group case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is conjugation by $w_n$.
+In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
 In our matrix representation, $\Frobenius$ acts on the Weyl group by conjugation by the matrix $$\left(-n,n\right) \coloneq \begin{pmatrix}\IdentityMatrix{n-1} & 0 & 0 & 0\\
@@
 \begin{enumerate}
-    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{\UnitaryGroup}_n\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
-If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{\UnitaryGroup}_n\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class.
+    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
+If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{T}_{0}\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class.
 Thus twisted conjugacy classes are determined by the cycle partition $\lambda \vdash n$ associated to $\dot{w} \cdot w_n$.
@@
     \end{enumerate}
-	We summarize all these cases in the following theorem.
+	The following theorem summarizes these cases.
 
@@
 
-	We summarize these cases in the following theorem.
+	The following theorem summarizes these cases.
 	\begin{theorem}

### 2025-03-28 main.tex
Started working on Introduction

@@
 \newcommand{\etale}{\'etale }
+\newcommand{\Erdelyi}{Erd{\'e}lyi}
+\newcommand{\Toth}{T{\'o}th}
 
@@
 \section{Introduction}
+
+Gauss sums are prominent objects in number theory...
+
+Let $\finiteField$ be a finite field with $q$ elements and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+Given a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ the normalized Gauss sum corresponding to the data $\left(\chi, \fieldCharacter\right)$ is defined by the formula
+$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \fieldCharacter\left(x\right).$$
+
+In the 1960s, Kondo \cite{Kondo1963} introduced an interesting exponential sum, which can be thought of as a higher dimensional version of the Gauss sum defined above.
+Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$.
+Then the sum $$\GaussSum{\pi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace g\right) \pi\left(g\right)$$
+defines an operator in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$.
+Since $\pi$ is irreducible, by Schur's lemma there exists a scalar $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$ such that $$\GaussSum{\pi}{\fieldCharacter} = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_{\pi}.$$
+
+In \cite{Kondo1963}, Kondo explicitly computed $\GaussSumScalar{\pi}{\fieldCharacter}$.
+His result shows that $\GaussSumScalar{\pi}{\fieldCharacter}$ can be expressed as a product of Gauss sums as above associated to the multiplicative characters that correspond to $\pi$ in the Deligne--Lusztig parameterization.
+
+In \cite{Zelingher2024}, the second author utilized Kondo's result to explicitly express twisted matrix Kloosterman sums in terms of Hall--Littlewood polynomials evaluated at the eigenvalues of the Frobenius action on the corresponding twisted Kloosterman sheaf.
+As a result, he resolved a conjecture of \Erdelyi{}--\Toth{} \cite{ErdelyiToth2024}.
+
+It is natural to ask whether the results of Kondo in \cite{Kondo1963} and the results of the second author in \cite{Zelingher2024} mentioned above have generalizations to other groups besides $\GL_n\left(\finiteField\right)$.
+An attempt to generalize Kondo's result was given by Saito--Shinoda in \cite{SaitoShinoda2000}.
+Given a classical group $G$, embedded naturally as a subgroup of a general linear group, and an irreducible representation $\pi$ of $G$, they considered the analogous Gauss sum
+$$\sum_{g \in G} \pi\left(g\right) \fieldCharacter\left(\trace g\right).$$
+
+As before, by Schur's lemma, this sum is scalar multiple of $\idmap_{\pi}$.
+However, the computations of Saito--Shinoda show that this scalar is not well behaved, even for the case $\Sp_{4}\left(\finiteField\right)$.
+The main issue with this naive Gauss sum is that it is \emph{not constant on Lusztig series}.
+
+An alternative approach for defining an analog of Kondo's Gauss sum comes from the theory of automorphic representations.
+Not long after Kondo's result was published, Godement and Jacquet \cite{GodementJacquet1972} defined a theory for standard $L$-functions for $\GL_n$.
+Nowadays it is known that the finite field analog of the Godemenet--Jacquet gamma factor corresponding to an irreducible representation $\pi$ of $\GL_n\left(\finiteField\right)$ coincides with Kondo's Gauss sum of $\pi$, see \cite[Section 2]{Macdonald80}.
+
+Since Godement--Jacquet developed their theory for the standard $L$-functions, many other constructions for $L$-functions attached to different representations have appeared in the literature.
+Unlike the construction of Godement--Jacquet, most of these constructions require the representations in question to satisfy certain genericity conditions.
+In the 1980s, Piatetski-Shapiro and Rallis \cite{PiatetskiShapiroRallis1986, GelbartPiatetskiShapiroRallis1987} discovered a new construction of (twisted) standard $L$-functions for classical groups.
+Their construction, known as ``the doubling method'', does not require the representations in question to satisfy any genericity condition, and it is similar to the construction of Godement--Jacquet in some sense.
+In fact, it is closely related to the construction of Godement--Jacquet, which shows up as certain inner integrals when considering parabolically induced representations of the classical group.
+
+Thus, a promising way to obtain a well behaved exponential sum for classical groups is to consider the finite field analog of the ``doubling method'' construction of Piatetski-Shapiro--Rallis and analyzing the formula for the gamma factor that this theory yields.
+This was done for $\Sp_{2n}\left(\finiteField\right)$ by Jun Chang \cite{Chang1997} in her doctoral thesis.
+In the upcoming work of Girsch and the second author \cite{GirschZelingher2025}, the finite field theory analog of the doubling method is developed for all classical groups.
+
+The computations of \cite{Chang1997} and \cite{GirschZelingher2025} show that, generically speaking, the finite field doubling method gamma factor for classical groups is given by exponential sums that resemble Jacobi sums.
+Let $G \subset \GL\left(\hermitianSpace\right)$ be a classical group, corresponding to the space $\left(\hermitianSpace, \innerproduct{\cdot}{\cdot}\right)$, and let $\lieAlgebra \subset \EndomorphismRing\left(\hermitianSpace\right)$ be the Lie algebra of $G$.
+Given an irreducible representation $\pi$ of $G$ and a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ such that $\chi^2 \ne 1$, the exponential sums arising from the finite field doubling method gamma factor of $\pi$ are given by the formula
+$$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sizeof{\lieAlgebra}^{1 \slash 2}} \sum_{\substack{g \in G\\
+\det\left(g \pm \idmap_{\hermitianSpace}\right) \ne 0}} \pi\left(g\right) \chi\left(\det\left(\idmap_{\hermitianSpace} \pm g\right)\right).$$
+
+Notice that $$\negDblJacobiSum{\pi}{\chi} = \frac{1}{\sizeof{\lieAlgebra}^{1/2}}\sum_{\substack{g \in G, h \in \GL\left(\hermitianSpace\right)\\
+g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\detQuadratic\left(h\right)\right),$$
+which resembles a classical Jacobi sum attached to characters $\chi_1, \chi_2 \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$:
+$$\sum_{\substack{x_1,x_2 \in \multiplicativegroup{\finiteField}\\
+		x_1 + x_2 = 1}} \chi_1\left(x\right) \chi_2\left(x_2\right).$$
+
+As before, we have that $\posDblJacobiSum{\pi}{\chi}$ and $\negDblJacobiSum{\pi}{\chi}$ lie in $\Hom_G\left(\pi, \pi\right)$.
+Since $\pi$ is irreducible, by Schur's lemma there exists scalars $\dblJacobiSumScalar{\pi}{\chi} \in \multiplicativegroup{\cComplex}$ such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_{\pi}.$$
+
+In this paper, we study the doubling method Jacobi sums $\dblJacobiSum{\pi}{\chi}$.
+We compute the scalars $\dblJacobiSumScalar{\pi}{\chi}$ in terms of the Deligne--Lusztig data corresponding to $\pi$ and show that, up to some well understood factors, it matches the Kondo Gauss sum of the conjectural functorial transfer of $\pi$ to a general linear group.
+This is done by combining a couple of ingredients.
+The first ingredient is a lemma of Saito--Shinoda \cite{SaitoShinoda2000} that allows us to explicitly compute the analogous character sums for Deligne--Lusztig virtual representations $R_{T, \theta}$.
+The second ingredient, which is a key ingredient for this computation, is that these Jacobi sums are well behaved, in the sense that they are constant on Lusztig series.
+To show this, we utilize a multiplicativity property of these Jacobi sums from \cite{GirschZelingher2025} and combine it with a careful analysis of the Deligne--Lusztig data corresponding to $\pi$ after functorial transfer.
+
+\elad{Write about the Braverman--Kazhdan proposal that generalizes Godement--Jacquet to all groups and all representations, but is not explicit.}
 

### 2025-03-28 main.tex
Two scalars

@@
 In this paper, we study the doubling method Jacobi sums $\dblJacobiSum{\pi}{\chi}$.
-We compute the scalars $\dblJacobiSumScalar{\pi}{\chi}$ in terms of the Deligne--Lusztig data corresponding to $\pi$ and show that, up to some well understood factors, it matches the Kondo Gauss sum of the conjectural functorial transfer of $\pi$ to a general linear group.
+We compute the scalars $\dblJacobiSumScalar{\pi}{\chi}$ in terms of the Deligne--Lusztig data corresponding to $\pi$ and show that, up to some well understood factors, they match the Kondo Gauss sum of the conjectural functorial transfer of $\pi$ to a general linear group.
 This is done by combining a couple of ingredients.

### 2025-03-28 main.tex
Just det here

@@
 Notice that $$\negDblJacobiSum{\pi}{\chi} = \frac{1}{\sizeof{\lieAlgebra}^{1/2}}\sum_{\substack{g \in G, h \in \GL\left(\hermitianSpace\right)\\
-g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\detQuadratic\left(h\right)\right),$$
+g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det h\right),$$
 which resembles a classical Jacobi sum attached to characters $\chi_1, \chi_2 \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$:

### 2025-03-29 main.tex
typo
changed section titles to be more descriptive/exciting

@@
 \newcommand{\similitudeCharacter}{\operatorname{sim}}
-\newcommand{\etale}{\'etale }
-\newcommand{\Erdelyi}{Erd{\'e}lyi}
-\newcommand{\Toth}{T{\'o}th}
 
@@
 
-Gauss sums are prominent objects in number theory...
-
-Let $\finiteField$ be a finite field with $q$ elements and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-Given a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ the normalized Gauss sum corresponding to the data $\left(\chi, \fieldCharacter\right)$ is defined by the formula
-$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \fieldCharacter\left(x\right).$$
-
-In the 1960s, Kondo \cite{Kondo1963} introduced an interesting exponential sum, which can be thought of as a higher dimensional version of the Gauss sum defined above.
-Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$.
-Then the sum $$\GaussSum{\pi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace g\right) \pi\left(g\right)$$
-defines an operator in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$.
-Since $\pi$ is irreducible, by Schur's lemma there exists a scalar $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$ such that $$\GaussSum{\pi}{\fieldCharacter} = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_{\pi}.$$
-
-In \cite{Kondo1963}, Kondo explicitly computed $\GaussSumScalar{\pi}{\fieldCharacter}$.
-His result shows that $\GaussSumScalar{\pi}{\fieldCharacter}$ can be expressed as a product of Gauss sums as above associated to the multiplicative characters that correspond to $\pi$ in the Deligne--Lusztig parameterization.
-
-In \cite{Zelingher2024}, the second author utilized Kondo's result to explicitly express twisted matrix Kloosterman sums in terms of Hall--Littlewood polynomials evaluated at the eigenvalues of the Frobenius action on the corresponding twisted Kloosterman sheaf.
-As a result, he resolved a conjecture of \Erdelyi{}--\Toth{} \cite{ErdelyiToth2024}.
-
-It is natural to ask whether the results of Kondo in \cite{Kondo1963} and the results of the second author in \cite{Zelingher2024} mentioned above have generalizations to other groups besides $\GL_n\left(\finiteField\right)$.
-An attempt to generalize Kondo's result was given by Saito--Shinoda in \cite{SaitoShinoda2000}.
-Given a classical group $G$, embedded naturally as a subgroup of a general linear group, and an irreducible representation $\pi$ of $G$, they considered the analogous Gauss sum
-$$\sum_{g \in G} \pi\left(g\right) \fieldCharacter\left(\trace g\right).$$
-
-As before, by Schur's lemma, this sum is scalar multiple of $\idmap_{\pi}$.
-However, the computations of Saito--Shinoda show that this scalar is not well behaved, even for the case $\Sp_{4}\left(\finiteField\right)$.
-The main issue with this naive Gauss sum is that it is \emph{not constant on Lusztig series}.
-
-An alternative approach for defining an analog of Kondo's Gauss sum comes from the theory of automorphic representations.
-Not long after Kondo's result was published, Godement and Jacquet \cite{GodementJacquet1972} defined a theory for standard $L$-functions for $\GL_n$.
-Nowadays it is known that the finite field analog of the Godemenet--Jacquet gamma factor corresponding to an irreducible representation $\pi$ of $\GL_n\left(\finiteField\right)$ coincides with Kondo's Gauss sum of $\pi$, see \cite[Section 2]{Macdonald80}.
-
-Since Godement--Jacquet developed their theory for the standard $L$-functions, many other constructions for $L$-functions attached to different representations have appeared in the literature.
-Unlike the construction of Godement--Jacquet, most of these constructions require the representations in question to satisfy certain genericity conditions.
-In the 1980s, Piatetski-Shapiro and Rallis \cite{PiatetskiShapiroRallis1986, GelbartPiatetskiShapiroRallis1987} discovered a new construction of (twisted) standard $L$-functions for classical groups.
-Their construction, known as ``the doubling method'', does not require the representations in question to satisfy any genericity condition, and it is similar to the construction of Godement--Jacquet in some sense.
-In fact, it is closely related to the construction of Godement--Jacquet, which shows up as certain inner integrals when considering parabolically induced representations of the classical group.
-
-Thus, a promising way to obtain a well behaved exponential sum for classical groups is to consider the finite field analog of the ``doubling method'' construction of Piatetski-Shapiro--Rallis and analyzing the formula for the gamma factor that this theory yields.
-This was done for $\Sp_{2n}\left(\finiteField\right)$ by Jun Chang \cite{Chang1997} in her doctoral thesis.
-In the upcoming work of Girsch and the second author \cite{GirschZelingher2025}, the finite field theory analog of the doubling method is developed for all classical groups.
-
-The computations of \cite{Chang1997} and \cite{GirschZelingher2025} show that, generically speaking, the finite field doubling method gamma factor for classical groups is given by exponential sums that resemble Jacobi sums.
-Let $G \subset \GL\left(\hermitianSpace\right)$ be a classical group, corresponding to the space $\left(\hermitianSpace, \innerproduct{\cdot}{\cdot}\right)$, and let $\lieAlgebra \subset \EndomorphismRing\left(\hermitianSpace\right)$ be the Lie algebra of $G$.
-Given an irreducible representation $\pi$ of $G$ and a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ such that $\chi^2 \ne 1$, the exponential sums arising from the finite field doubling method gamma factor of $\pi$ are given by the formula
-$$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sizeof{\lieAlgebra}^{1 \slash 2}} \sum_{\substack{g \in G\\
-\det\left(g \pm \idmap_{\hermitianSpace}\right) \ne 0}} \pi\left(g\right) \chi\left(\det\left(\idmap_{\hermitianSpace} \pm g\right)\right).$$
-
-Notice that $$\negDblJacobiSum{\pi}{\chi} = \frac{1}{\sizeof{\lieAlgebra}^{1/2}}\sum_{\substack{g \in G, h \in \GL\left(\hermitianSpace\right)\\
-g + h = \idmap_{\hermitianSpace}}} \pi\left(g\right) \chi\left(\det h\right),$$
-which resembles a classical Jacobi sum attached to characters $\chi_1, \chi_2 \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$:
-$$\sum_{\substack{x_1,x_2 \in \multiplicativegroup{\finiteField}\\
-		x_1 + x_2 = 1}} \chi_1\left(x\right) \chi_2\left(x_2\right).$$
-
-As before, we have that $\posDblJacobiSum{\pi}{\chi}$ and $\negDblJacobiSum{\pi}{\chi}$ lie in $\Hom_G\left(\pi, \pi\right)$.
-Since $\pi$ is irreducible, by Schur's lemma there exists scalars $\dblJacobiSumScalar{\pi}{\chi} \in \multiplicativegroup{\cComplex}$ such that $$\dblJacobiSum{\pi}{\chi} = \dblJacobiSumScalar{\pi}{\chi} \cdot \idmap_{\pi}.$$
-
-In this paper, we study the doubling method Jacobi sums $\dblJacobiSum{\pi}{\chi}$.
-We compute the scalars $\dblJacobiSumScalar{\pi}{\chi}$ in terms of the Deligne--Lusztig data corresponding to $\pi$ and show that, up to some well understood factors, they match the Kondo Gauss sum of the conjectural functorial transfer of $\pi$ to a general linear group.
-This is done by combining a couple of ingredients.
-The first ingredient is a lemma of Saito--Shinoda \cite{SaitoShinoda2000} that allows us to explicitly compute the analogous character sums for Deligne--Lusztig virtual representations $R_{T, \theta}$.
-The second ingredient, which is a key ingredient for this computation, is that these Jacobi sums are well behaved, in the sense that they are constant on Lusztig series.
-To show this, we utilize a multiplicativity property of these Jacobi sums from \cite{GirschZelingher2025} and combine it with a careful analysis of the Deligne--Lusztig data corresponding to $\pi$ after functorial transfer.
-
-\elad{Write about the Braverman--Kazhdan proposal that generalizes Godement--Jacquet to all groups and all representations, but is not explicit.}
-
 \section{Preliminaries}
@@
 If $k' \mid k$, let $\FieldNorm{k}{k'} \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\finiteFieldExtension{k'}}$ be the norm map.
-
-Given a partition $\lambda = \left(\lambda_1, \dots, \lambda_\ell\right)$, we denote the \etale $\finiteField$-algebra $$\finiteFieldExtension{\lambda} = \prod_{i=1}^{\ell} \finiteFieldExtension{\lambda_i}$$ and define
-$$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$
-
-\elad{Need to define $2 \lambda$ and $\FieldNorm{2\lambda}{\lambda}$ and $\NormOneGroup{2 \lambda}$}
 
@@
 \end{center}
-Here, $\algebraicGroup{T}_{0}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
+Here, $\algebraicGroup{T}^{\mathrm{std}}_{\algebraicGroup{G}}$ is split for all rows except for the last row. We also write down the standard tori for the relevant corresponding similitude groups.
 \begin{center}
@@
 
-In the unitary group case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is conjugation by $w_n$.
-In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
+In the unitary case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\UnitaryGroup}_n}^{\mathrm{std}}\right)$ is conjugation by $w_n$.
+In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{\algebraicGroup{\SO}^{-}_{2n}}^{\mathrm{std}}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
 In our matrix representation, $\Frobenius$ acts on the Weyl group by conjugation by the matrix $$\left(-n,n\right) \coloneq \begin{pmatrix}\IdentityMatrix{n-1} & 0 & 0 & 0\\
@@
 \begin{enumerate}
-    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
-If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{T}_{0}\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class.
+    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{\UnitaryGroup}_n\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
+If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{\UnitaryGroup}_n\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class.
 Thus twisted conjugacy classes are determined by the cycle partition $\lambda \vdash n$ associated to $\dot{w} \cdot w_n$.
@@
 The corresponding algebraic torus is
-	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{i} 	\restrictionOfScalars{\finiteFieldExtension{\lambda^{+}_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \\
+	\restrictionOfScalars{\finiteFieldExtension{\lambda_i^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 	% The embedding into the unitary group requires conjugation by \diag(1,1,1,\sqrt{d},\sqrt{d},\sqrt{d}). I would rather not write it.
@@
 Then
-	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+		$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 		See also \cite[Section 3.2 Part (B)]{Zalesski2018}.
@@
         	\item (Split case): For $\algebraicGroup{\SO}_{2n}^+$ we have that
-        	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 			See also \cite[Section 3.2 Parts (C) and (D)]{Zalesski2018}.        	
@@
 Then
-        	$$^{L^{-1}w}\algebraicGroup{T}_0 \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
+        	$$^{L^{-1}w}\algebraicGroup{T}_0 = \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}.$$
 			See also \cite[Section 3.2 Part (D)]{Zalesski2018}. Notice that we differ from that \cite{Zalesski2018} since we do not incorporate the element $\left(-n, n\right)$ in the Frobenius root.
@@
     \end{enumerate}
-	The following theorem summarizes these cases.
+	We summarize all these cases in the following theorem.
 
 	\begin{theorem}
-		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to 	$$\algebraicGroup{T} \cong \restrictionOfScalars{\finiteFieldExtension{\lambda^{+}}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{\lambda^{-}}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
+		A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} = \algebraicGroup{\UnitaryGroup}_{n}, \algebraicGroup{\Sp}_{2n}, \algebraicGroup{\SO}_{2n + 1}, \algebraicGroup{\SO}_{2n}^{\pm}$ is isomorphic to $$\algebraicGroup{T} \cong \prod_{j} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_j}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^-_i}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1},$$
 		where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$, where in the unitary group case we require that $\lambda^+$ consists only of even parts and that $\lambda^-$ consists only of odd parts.
-We have that $$\algebraicGroup{T}^{\Frobenius} \cong \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y\right) \mapsto
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \NormOneGroup{2 \lambda_i^{-}}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}\right) \mapsto
 		\begin{pmatrix}
-			\iota_+\left(x\right)\\
-			& \iota_{-}\left(y\right) &\\
-			 & & \involution{\iota_+^{\ast}\left(x\right)}
+			\iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
+			& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}
+			 \right) &\\
+			 & & \involution{\iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)}
 		\end{pmatrix},$$
-		where $\iota_+ \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \NormOneGroup{2 \lambda^{-}} \to G'$ are embeddings.
+		where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\frac{\sizeof{\lambda^+}}{\grpIndex{\quadraticExtension}{\finiteField}}}\left(\quadraticExtension\right)$ and $\iota_- \colon \prod_{i} \NormOneGroup{2 \lambda_j^-} \to G'$ are embeddings.
 Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
@@
 			\begin{align*}
-				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
+				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
+				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
 			\end{align*}
@@
 			\begin{align*}
-				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
-			\end{align*}
-	\end{enumerate}
-
-	The following theorem summarizes these cases.
+				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right) \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
+				& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
+			\end{align*}
+	\end{enumerate}
+
+	We summarize these cases in the following theorem.
 	\begin{theorem}
 	A maximal rational torus $\algebraicGroup{T}$ of $\algebraicGroup{G} =  \algebraicGroup{\GSp}_{2n}, \algebraicGroup{\GSO}_{2n}^{\pm}$ is isomorphic to \begin{align*}
-				^{L^{-1}w}\algebraicGroup{T}_0 \cong& \left\{\left(x,y,z\right) \in  \restrictionOfScalars{\finiteFieldExtension{\lambda^+}}{\finiteField}{\multiplcativeScheme} \times \restrictionOfScalars{\finiteFieldExtension{2\lambda^-}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme \mid \FieldNorm{2\lambda^-}{\lambda^-}(y) = z \right\}.
+		\algebraicGroup{T} \cong& \left\{\left(\left(x_j\right)_{i=1}^{\lengthof\left(\lambda^+\right)},\left(y_j\right)_{i=1}^{\lengthof\left(\lambda^-\right)},t\right)  \mid \FieldNorm{2\lambda_i^-}{\lambda_i^-}(y_i) = t \text{ for every } i\right\} \\
+		& \subset \prod_{i} \restrictionOfScalars{\finiteFieldExtension{\lambda^+_i}}{\finiteField}{\multiplcativeScheme} \times \prod_{i} \restrictionOfScalars{\finiteFieldExtension{2\lambda^-_i}}{\finiteField}{\multiplcativeScheme}  \times \multiplcativeScheme.
 	\end{align*}
 	where $\left(\lambda^+, \lambda^-\right)$ is a pair of partitions such that $\sizeof{\lambda^+} + \sizeof{\lambda^-} = n$.
-We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(x, y, z\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(y\right) = z \right\}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(x, y, z\right) \mapsto
+We have that $$\algebraicGroup{T}^{\Frobenius} \cong \left\{\left(\left(a_j\right)_{j = 1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i = 1}^{\lengthof\left(\lambda^-\right)}, z\right) \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \subset \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \times \prod_{i} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}} \times \multiplicativegroup{\finiteField}.$$ The embedding $\algebraicGroup{T}^{\Frobenius} \to \algebraicGroup{G}^{\Frobenius}$ is of the form $$\left(\left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}, \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right) \mapsto
 	\begin{pmatrix}
-		z \cdot \iota_+ \left(x\right)\\
-		& \iota_{-}\left(y\right) &\\
-		& & \iota_+^{\ast}\left(x\right)
+		z \cdot \iota_+\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)\\
+		& \iota_{-}\left( \left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z
+		\right) &\\
+		& & \iota_+^{\ast}\left( \left(a_j\right)_{j=1}^{\lengthof\left(\lambda^+\right)}\right)
 	\end{pmatrix},$$
-	where $\iota_+ \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(y, z\right)\in \multiplicativegroup{\finiteFieldExtension{2 \lambda^-}} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda^{-}}{\lambda^{-}}\left(y\right) = z \text{ for all } i \right\} \to G'$$ are embeddings.
+	where $\iota_+ \colon \prod_{j} \multiplicativegroup{\finiteFieldExtension{\lambda_j^+}} \to \GL_{\sizeof{\lambda^+}}\left(\finiteField\right)$ and $$\iota_- \colon \left\{ \left(\left(t_i\right)_{i=1}^{\lengthof\left(\lambda^-\right)}, z\right)\in \prod_{i} \finiteFieldExtension{2\lambda^{-}_i} \times \multiplicativegroup{\finiteField} \mid \FieldNorm{2 \lambda_i^{-}}{\lambda_i^{-}}\left(t_i\right) = z \text{ for all } i \right\} \to G'$$ are embeddings.
 Here, $G'$ is a group of the same type as $\algebraicGroup{G}^{\Frobenius}$, with $n$ replaced by $\sizeof{\lambda^{-}}$.
@@
 
-\subsection{Multiplicativity property}
+\subsection{Multiplicativity}
 The goal of this section is to understand how the doubling method Jacobi sums behave under parabolic induction.
@@
 
-\subsection{Computation of character sums attached to Deligne--Lusztig data}
+\subsection{Pairing with Deligne--Lusztig characters}
+\calvin{old title: Computation of character sums attached to Deligne--Lusztig data}
 
@@
 
-\subsection{Invariance under geometric conjugacy}
-\calvin{todo:type in some motivation for class functions whose product doesn't depend on geometric conjugacy, gamma functions whatever}.
+\subsection{Invariance of $\langle \JacobiKernel{}, R_T(\theta) \rangle$ under geometric conjugacy}
 
@@
 \subsection{Computation for geometric Lusztig series}
+\calvin{retitle: Stability of Jacobi sums}
 
@@
 \calvin{start alternate writeup 2 of section 3.4/3.4.1}
-\subsection{Computation for Lusztig Series}
+\subsection{Stability}
 The goal of this section is to prove \Cref{thm:Phi_stable} in particular:

### 2025-03-29 main.tex

--- 2025-03-28 main.tex
@@
 		z \cdot \iota_+ \left(x\right)\\
-		& \iota_{-}\left(y\right) &\\
+		& \iota_{-}\left(y,z\right) &\\
 		& & \iota_+^{\ast}\left(x\right)

### 2025-03-29 main.tex
changed basis slightly in lem:cochar_computation, added a theorem statement in intro, added a few comments

@@
 
+\calvin{I think I would like to include a main theorem here even if it's not super precise just to let the reader know what we highlight what we about the sum}
+\begin{theorem}[\Cref{thm:doubling-method-gamma-factor-for-deligne-thm:doubling-method-gamma-factor-for-deligne-lusztig},\Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}]
+	For classical groups $\algebraicGroup{G}$ and $\chi \neq \pm1$, $\genJacobiKernel{\pi,\chi}$ is a stable function which acts as the scalar
+	\[
+		\dblJacobiSumScalar{\pi}{\chi} = \begin{cases}
+		\varepsilon_{\algebraicGroup{H}} c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) & + \\
+		c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right) & - \textnormal{ and } \algebraicGroup{G} \neq \algebraicGroup{SO}_{2n+1} \\
+		0 & - \textnormal{ and } \algebraicGroup{G} = \algebraicGroup{SO}_{2n+1}
+		\end{cases}
+	\]
+	on $\pi$
+where $c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)$ is an explicit factor and
+$g_T\left(\chi, \theta, \fieldCharacter\right)$ is a product of Guass sums.
+\end{theorem}
 In this paper, we study the doubling method Jacobi sums $\dblJacobiSum{\pi}{\chi}$.
@@
 \begin{proposition}[cite Digne Michel Cor 12.7]
+\label{prop:semisimple_pair_with_RTtheta}
 Treating $R_T^G(\theta)$ as a class function of $\algebraicGroup{G}(\finiteField)$ via the character of $R_T^G(\theta)$, for any class function $f$ on $\algebraicGroup{G}(\finiteField)$ which satisfies $f(g) = f(s)$ when $g=su$ is the Jordan decompositoin of $g$, we have
@@
 By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
+\calvin{does this also follow from \Cref{prop:semisimple_pair_with_RTtheta}?
+Maybe we should say something about it}
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
@@
 $$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
-Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
+Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish \calvin{It seems like the inner sum is a guass sum times $\sum_x \alpha(x)$.
+So if $\alpha$ is nontrivial it will vanish, otherwise we have some error term}.
+Hence, we have that our sum can be rewritten as
 $$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
@@
 Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
-Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+\cavlin{should the characters be from $\mathbb{E}_k$ instead of $\mathbb{F}_k$?} Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
 		x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right).$$
@@
 \label{lem:cochar_computation}
-    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-x)$.
+    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-w_n x)$.
 Then we have the following cases corresponding to conjugacy classes in the Weyl group
@@
         \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases.
-Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w_nww_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w^\ast)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
         \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
  In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
-    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} w & 0 \\
-        0 & w^{\ast}
-        \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
+    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} 0 & w \\
+        w^\ast & 0
         \end{pmatrix}$  on the image, and 
-    \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} w & 0 \\
-        0 & w_nwww_n
-        \end{pmatrix} \cdot \begin{pmatrix} 0 & I\\I & 0
-        \end{pmatrix}$ on the image , and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
+    \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w \\
+        w^\ast & 0
+        \end{pmatrix}$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
     \end{enumerate}
@@
 \begin{align*}
-	\alpha(\zeta^{((y_1-y_{n+1})+q(y_2-y_{n+2}) + \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\alpha(\zeta^{(y_1+qy_2 + \hdots +q^{n-1}y_{n})}) \alpha^{-1}(\zeta^{(y_{n+1}+qy_{n+2} + \hdots +q^{n-1}y_{2n})}) \\
-	\theta(\beta^{((y_1-y_{n+1})+q(y_2-y_{n+2}) + \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\theta(\beta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{n+1}+q^{n+1}y_{n+2} \hdots +q^{2n-1}y_{2n})}) \\
-	&=\theta'(\zeta^{(y_1+q(y_2) + \hdots +q^{2n-1}y_{2n})})\\
-	\alpha(\zeta^{((y_1-y_{n+1})-q(y_2-y_{n+2}) +q^2(y_3-y_{n+3}) \hdots -q^{n-1}(y_{n}-y_{2n}))})&= \alpha(\zeta^{(y_1+qy_{n+2}+q^2y_3 +q^3y_4 \hdots +q^{n-1}y_{2n})}) \alpha^{-1}(\zeta^{(y_{n+1}+q(y_{2}) + q^2y_{n+3}\hdots +q^{n-1}y_{n})}) \\
-	\theta(\beta^{((y_1-y_{n+1})-q(y_2-y_{n+2}) +q^2(y_3-y_{n+3}) \hdots +q^{n-1}(y_{n}-y_{2n}))})&=\theta(\beta^{(y_1+qy_{n+2} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{n+1}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{2n})}) \\
-	&=\theta'(\zeta^{(y_1+qy_2 + \hdots +q^{2n-1}y_{2n})})
+	\alpha(\zeta^{((y_1-y_{2n})+q(y_2-y_{2n-1}) + \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\alpha(\zeta^{(y_1+qy_2 + \hdots +q^{n-1}y_{n})}) \alpha^{-1}(\zeta^{(y_{2n}+qy_{2n-1} + \hdots +q^{n-1}y_{n+1})}) \\
+	\theta(\beta^{((y_1-y_{2n})+q(y_2-y_{2n-1}) + \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\theta(\beta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2n-1} \hdots +q^{2n-1}y_{n+1})}) \\
+	&=\theta'(\zeta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2n-1} \hdots +q^{2n-1}y_{n+1})})\\
+	\alpha(\zeta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots -q^{n-1}(y_{n}-y_{n+1}))})&= \alpha(\zeta^{(y_1+qy_{2n-1}+q^2y_3 +q^3y_{2n-3} \hdots +q^{n-1}y_{n+1})}) \\
+	&\quad \cdot \alpha^{-1}(\zeta^{(y_{2n}+qy_{2} + q^2y_{2n-2} + \hdots +q^{n-1}y_{n})}) \\
+	\theta(\beta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\theta(\beta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})}) \\
+	&=\theta'(\zeta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})})
 \end{align*}

### 2025-03-29 main.tex
Answering Calvin's questions

@@
 
-\begin{proposition}[cite Digne Michel Cor 12.7]
+\begin{proposition}[{\cite[Corollary 12.7]{DigneMichel1991}}]
 \label{prop:semisimple_pair_with_RTtheta}
@@
 Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
-By \cite[Proposition 13.7 (ii)]{DigneMichel2020}, we have an exact sequence
+By \cite[Proposition 13.7 (ii)]{DigneMichel1991}, we have an exact sequence
 \begin{equation}
@@
 for large enough $n$.
-This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel2020} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
+This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel1991} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
 Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
@@
 \calvin{does this also follow from \Cref{prop:semisimple_pair_with_RTtheta}?
-Maybe we should say something about it}
+Maybe we should say something about it} \elad{Can you compare the proofs?}
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
@@
 Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish \calvin{It seems like the inner sum is a guass sum times $\sum_x \alpha(x)$.
-So if $\alpha$ is nontrivial it will vanish, otherwise we have some error term}.
+So if $\alpha$ is nontrivial it will vanish, otherwise we have some error term} \elad{Note that the sum over $\alpha$ is with respect to a different variable $x$ so the sum over $y$ vanishes if $\chi \ne 1$}.
 Hence, we have that our sum can be rewritten as
@@
 \subsubsection{Split torus computation II}
-We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\finiteFieldExtension{k}}$.
+We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\quadraticFieldExtension{k}}$.
 Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
-\cavlin{should the characters be from $\mathbb{E}_k$ instead of $\mathbb{F}_k$?} Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
+Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
 		x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right).$$

### 2025-03-29 main.tex
Mild modifications

@@
 \calvin{I think I would like to include a main theorem here even if it's not super precise just to let the reader know what we highlight what we about the sum}
-\begin{theorem}[\Cref{thm:doubling-method-gamma-factor-for-deligne-thm:doubling-method-gamma-factor-for-deligne-lusztig},\Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}]
-	For classical groups $\algebraicGroup{G}$ and $\chi \neq \pm1$, $\genJacobiKernel{\pi,\chi}$ is a stable function which acts as the scalar
-	\[
-		\dblJacobiSumScalar{\pi}{\chi} = \begin{cases}
-		\varepsilon_{\algebraicGroup{H}} c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right) & + \\
-		c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right) & - \textnormal{ and } \algebraicGroup{G} \neq \algebraicGroup{SO}_{2n+1} \\
-		0 & - \textnormal{ and } \algebraicGroup{G} = \algebraicGroup{SO}_{2n+1}
-		\end{cases}
-	\]
-	on $\pi$
-where $c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)$ is an explicit factor and
-$g_T\left(\chi, \theta, \fieldCharacter\right)$ is a product of Guass sums.
+\begin{theorem}[\Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}]
+	For classical groups $\algebraicGroup{G}$ and $\chi \neq \pm1$, $\genJacobiKernel{\pi,\chi}$ is a stable function. We have that
+	$$\posDblJacobiSumScalar{\pi}{\chi} =
+		\varepsilon_{\algebraicGroup{H}} c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),$$
+		and that
+	$$\negJacobiKernel{\pi}{\chi} = \begin{dcases}
+		0 & \algebraicGroup{G} = \algebraicGroup{\SO}_{2n+1},\\
+		\centralCharacter{\pi}\left(-1\right) \posDblJacobiSumScalar{\pi}{\chi} &  \text{Otherwise.}
+	\end{dcases}$$
+Here $c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)$ is an explicit factor and
+$g_T\left(\chi, \theta, \fieldCharacter\right)$ is a product of Gauss sums, see \Cref{subsec:normalization-factor} and \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
 \end{theorem}
@@
 
-\subsubsection{Gamma factors}
+\subsubsection{Gamma factors}\label{subsec:normalization-factor}
 In order to make the computations more tolerable, it is beneficial to work with fully multiplicative functions. We introduce the doubling method gamma factors.

### 2025-03-29 main.tex
Correcting character domain

@@
 We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\quadraticFieldExtension{k}}$.
-Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
+Let $\alpha \colon \multiplicativegroup{\quadraticFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
 Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\

### 2025-03-30 main.tex
Corrections

--- 2025-03-29 main.tex
@@
 We use the results from the previous section to compute the doubling method Jacobi sum for a torus of the form $\multiplicativegroup{\quadraticFieldExtension{k}}$.
-Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
-Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right).$$
+Let $\alpha \colon \multiplicativegroup{\quadraticFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be characters such that $\involutionPlusOne{\chi} \ne 1$.
+Our goal is to compute $$\sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
+		x \ne -1}} \alpha \left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + x\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + \minusInvolution{x}\right)\right).$$
 This can be rewritten as
-$$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-		x \ne -1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\FieldNorm{k}{1}\left(x\right)\right) \involutionPlusOne{\chi}\left(\FieldNorm{k}{1}\left(1 + x\right)\right).$$
+$$\sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
+		x \ne -1}} \alpha \left(x\right) \minusInvolution{\chi}\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(x\right)\right) \involutionPlusOne{\chi}\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + x\right)\right).$$
 By the previous section, this equals
@@
 \begin{align*}
-	& \sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-			x \ne -1}} \alpha \left(x\right) \chi\left(\FieldNorm{k}{1}\left(1 + x\right)\right) \chi\left(\FieldNorm{k}{1}\left(1 + \minusInvolution{x}\right)\right) \\
+	& \sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
+			x \ne -1}} \alpha \left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + x\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + \minusInvolution{x}\right)\right) \\
 	=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.

### 2025-03-30 main.tex
Corrections

@@
 \subsubsection{Split torus computation I}
-Let $\alpha \colon \multiplicativegroup{\finiteFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ be a character and let $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
-
-The goal of this section is to compute $$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-x \ne -1}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(1+x\right)\right).$$
+Let $\alpha \colon \multiplicativegroup{\quadraticFieldExtension{k}} \to \multiplicativegroup{\cComplex}$ be a character and let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a non-trivial character.
+
+The goal of this section is to compute $$\sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
+x \ne -1}} \alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1+x\right)\right).$$
 This computation will be useful for the next section, which in turn will be useful for invoking \Cref{prop:reduction-of-gauss-sum-to-torus}.
@@
 Let us rewrite our sum as
-$$q^{-k} \sum_{z \in \finiteFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
-Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish \calvin{It seems like the inner sum is a guass sum times $\sum_x \alpha(x)$.
-So if $\alpha$ is nontrivial it will vanish, otherwise we have some error term} \elad{Note that the sum over $\alpha$ is with respect to a different variable $x$ so the sum over $y$ vanishes if $\chi \ne 1$}.
-Hence, we have that our sum can be rewritten as
-$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}}\alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(\left(y - \left(x + 1\right)\right)z\right).$$
+$$\frac{1}{\sizeof{\quadraticFieldExtension{k}}} \sum_{z \in \quadraticFieldExtension{k}} \sum_{x \in  \multiplicativegroup{\quadraticFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\quadraticFieldExtension{k}}}\alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{\quadraticFieldExtension{k}}\left(\left(y - \left(x + 1\right)\right)z\right).$$
+Since $\chi$ is non-trivial, when $z = 0$, the inner sum over $y$ will vanish. Hence, we have that our sum can be rewritten as
+$$\frac{1}{\sizeof{\quadraticFieldExtension{k}}} \sum_{z \in \multiplicativegroup{\quadraticFieldExtension{k}}} \sum_{x \in  \multiplicativegroup{\quadraticFieldExtension{k}}} \sum_{y \in \multiplicativegroup{\quadraticFieldExtension{k}}}\alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{\quadraticFieldExtension{k}}\left(\left(y - \left(x + 1\right)\right)z\right).$$
 Replacing $x$ with $-z^{-1} x$ and $y$ with $z^{-1} y$ and $z$ with $-z$, this becomes
-$$q^{-k} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\FieldNorm{k}{1}\left(z\right)\right) \fieldCharacter_k\left(z\right) \sum_{x \in  \multiplicativegroup{\finiteFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_k\left(x\right) \sum_{y \in \multiplicativegroup{\finiteFieldExtension{k}}} \chi\left(\FieldNorm{k}{1}\left(y\right)\right) \fieldCharacter_k\left(y\right).$$
+$$\frac{1}{\sizeof{\quadraticFieldExtension{k}}} \sum_{z \in \multiplicativegroup{\quadraticFieldExtension{k}}} \alpha^{-1}\left(z\right) \chi^{-1}\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(z\right)\right) \fieldCharacter_{\quadraticFieldExtension{k}}\left(z\right) \sum_{x \in  \multiplicativegroup{\quadraticFieldExtension{k}}} \alpha\left(x\right) \fieldCharacter_{\quadraticFieldExtension{k}}\left(x\right) \sum_{y \in \multiplicativegroup{\quadraticFieldExtension{k}}} \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(y\right)\right) \fieldCharacter_{\quadraticFieldExtension{k}}\left(y\right).$$
 Hence, we have the identity
-$$\sum_{\substack{x \in \multiplicativegroup{\finiteFieldExtension{k}}\\
-x \ne -1}} \alpha\left(x\right) \chi\left(\FieldNorm{k}{1}\left(x+1\right)\right) = -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_k} \tau\left(\alpha, \fieldCharacter_k\right) \tau\left(\chi \circ \FieldNorm{k}{1}, \fieldCharacter_k\right).$$
+$$\sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
+x \ne -1}} \alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(x+1\right)\right) = -\sizeof{\quadraticFieldExtension{k}}^{1/2} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\alpha, \fieldCharacter_{\quadraticFieldExtension{k}}\right) \tau\left(\chi \circ \aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}, \fieldCharacter_{\quadraticFieldExtension{k}}\right).$$
 
@@
 \begin{equation*}
-	-q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation*}
@@
 \begin{equation*}
-	-q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation*}
@@
 			x \ne -1}} \alpha \left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + x\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + \minusInvolution{x}\right)\right) \\
-	=& -q^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+	=& -\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
 \end{align*}

### 2025-03-30 main.tex
Corrections of the statement

@@
 Let $G \subset \GL\left(\hermitianSpace\right)$ be a classical group, corresponding to the space $\left(\hermitianSpace, \innerproduct{\cdot}{\cdot}\right)$, and let $\lieAlgebra \subset \EndomorphismRing\left(\hermitianSpace\right)$ be the Lie algebra of $G$.
-Given an irreducible representation $\pi$ of $G$ and a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ such that $\chi^2 \ne 1$, the exponential sums arising from the finite field doubling method gamma factor of $\pi$ are given by the formula
+Given an irreducible representation $\pi$ of $G$ and a character $\chi \colon Z\left(\GL\left(\hermitianSpace\right)\right) \to \multiplicativegroup{\cComplex}$ not trivial on the subgroup of scalars that preserve the form $\innerproduct{\cdot}{\cdot}$, the exponential sums arising from the finite field doubling method gamma factor of $\pi$ are given by the formula
 $$\dblJacobiSum{\pi}{\chi} = \frac{1}{\sizeof{\lieAlgebra}^{1 \slash 2}} \sum_{\substack{g \in G\\
@@
 \begin{theorem}[\Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}, \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}]
-	For classical groups $\algebraicGroup{G}$ and $\chi \neq \pm1$, $\genJacobiKernel{\pi,\chi}$ is a stable function. We have that
+	For a classical group $G$ and a multiplicative character $\chi$ as above, $\genHermitianJacobiKernel{\hermitianSpace}{\chi}$ are stable functions. We have that
 	$$\posDblJacobiSumScalar{\pi}{\chi} =
@@
 		and that
-	$$\negJacobiKernel{\pi}{\chi} = \begin{dcases}
-		0 & \algebraicGroup{G} = \algebraicGroup{\SO}_{2n+1},\\
-		\centralCharacter{\pi}\left(-1\right) \posDblJacobiSumScalar{\pi}{\chi} &  \text{Otherwise.}
+	$$\negDblJacobiSumScalar{\pi}{\chi} = \begin{dcases}
+		0 & $G$ \text{ is an odd special orthogonal group},\\
+		\centralCharacter{\pi}\left(-1\right) \posDblJacobiSumScalar{\pi}{\chi} &  \text{otherwise.}
 	\end{dcases}$$

### 2025-03-30 main.tex
wrote stability proof outline. flipped inverses in proof of lem:indep_geo_conj (50% chance its off)

--- 2025-03-30 main.tex
@@
 \calvin{does this also follow from \Cref{prop:semisimple_pair_with_RTtheta}?
-Maybe we should say something about it} \elad{Can you compare the proofs?}
+Maybe we should say something about it} \elad{Can you compare the proofs?}\calvin{they use the same proof: basically they just use the character formula for RTtheta}
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
@@
  In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
-    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} 0 & w \\
-        w^\ast & 0
+    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} 0 & w_nw \\
+        w w_n & 0
         \end{pmatrix}$  on the image, and 
-    \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w \\
-        w^\ast & 0
+    \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w_nw \\
+        w w_n& 0
         \end{pmatrix}$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
@@
 \[
-g_{T,\rho}(\chi,\theta,\psi)= g_{T}(\chi,\theta,\psi) \cdot \begin{cases}
+g_{T,\rho}(\chi,\theta,\fieldCharacter)= g_{T}(\chi^{-1},\theta^{-1},\fieldCharacter) \cdot \begin{cases}
         1  & G \neq Sp, GSp\\
-        \tau\left(\chi, \fieldCharacter\right) & G = Sp \textnormal{ or } GSp
+        \tau\left(\chi^{-1}, \fieldCharacter\right) & G = Sp \textnormal{ or } GSp
     \end{cases}.
@@
 \begin{enumerate}
-    \item[($\algebraicGroup{U}$)] Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$. Let $w \circ w_n$ have cycle decomposition $\lambda$ 
-	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. Then
+    \item[($\algebraicGroup{U}$)] \calvin{right now can only deal with the case that $\chi$ is a square} Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$.
+Let $w \circ w_n$ have cycle decomposition $\lambda$
+	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. 
+	Write $\chi = \chi'+\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}$ and $\chi'^{-1} = (\chi')^c$. 
+	Then
 	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
@@
 		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i} \begin{cases}
-			\GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} & \lambda_i \textnormal{ even} \\
-			\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i}} & \lambda_i \textnormal{ odd}
+			\GaussSumCharacter{\left(\alpha_i \times \chi'\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} \times \GaussSumCharacter{\left(\alpha_i^{-1}\times \chi'^c\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} & \lambda_i \textnormal{ even} \\
+			\GaussSumCharacter{\left(\theta'_i \times \chi'\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{2\lambda_i}} & \lambda_i \textnormal{ odd}
 		\end{cases}
 	\end{align*}
-	which is equal to $g_{T}(\chi,\theta,\psi)$.
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
 	\item[($\algebraicGroup{SO}_{2n+1}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
@@
 	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \times \Pi_{\lambda_i^-}\GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi,\theta,\psi)$.
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
 	\item[($\algebraicGroup{Sp}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
@@
 	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
-		\times \tau{\chi}{\psi}
-	\end{align*}
-	which is equal to $g_{T}(\chi,\theta,\psi) \cdot \tau(\chi,\psi)$.
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}} \times \tau(\chi,\psi)
+	\end{align*}
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi) \cdot \tau(\chi,\psi)$. \calvin{check inverses}
 	\item[($\algebraicGroup{SO}_{2n}^+$)] Let $T$ correspond to the signed permutation conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
@@
 	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi,\theta,\psi)$.
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
 	\item[($\algebraicGroup{SO}_{2n}^-$)] Let $T$ correspond to the $(-n,n)$-twisted permutation conjugacy class $[w]$ with cycle decompositionof $[w \cdot (-n,n)]$ equal to $(\lambda^+,\lambda^-)$ 
@@
 	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi,\theta,\psi)$.
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
 \end{enumerate}
@@
 
-\subsection{Computation for geometric Lusztig series}
-\calvin{retitle: Stability of Jacobi sums}
-
-The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
-
-\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
-	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
-	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$.
-Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.
-Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
-\end{theorem}
 \begin{comment}
@@
 \calvin{start alternate writeup 2 of section 3.4/3.4.1}
-\subsection{Stability}
-The goal of this section is to prove \Cref{thm:Phi_stable} in particular:
+\subsection{Stability (one option)}
+The goal of this section is to compute $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ proving \Cref{thm:Phi_stable}:
 \begin{theorem}
@@
 If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\chi,\theta|_{T \cap G}, \fieldCharacter\right)$$
 \end{theorem}
 \calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$, implying \Cref{thm:Phi_stable}.
+
+The proof strategy is to prove the following inductive statements
+\begin{enumerate}[(A)]
+	\item If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$.
+	\item If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$, then it holds for all cuspidal representations with $\dim_{\mathbb{E}} V = n$.
+\end{enumerate}
+The key input to (A) is the multiplicativity [CITE] of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
+The key input to (B) is \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.
+
 \subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}}
@@
 
+\subsection{Stability (another option)}
+\calvin{retitle: Stability of Jacobi sums}
+
+The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
+
+\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
+	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
+	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$.
+Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.
+Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
+\end{theorem}
 \subsubsection{Proof of the main result \calvin{\Cref{thm:Phi_stable}}}

### 2025-03-30 main.tex
minor adjustments in main theorem proof

@@
 		and that
-	$$\negDblJacobiSumScalar{\pi}{\chi} = \begin{dcases}
-		0 & $G$ \text{ is an odd special orthogonal group},\\
+	$$\negDblJacobiSumScalar{\pi}{\chi} = \begin{dcases} 0 & G \text{ is an odd special orthogonal group},\\
 		\centralCharacter{\pi}\left(-1\right) \posDblJacobiSumScalar{\pi}{\chi} &  \text{otherwise.}
@@
 \calvin{start alternate writeup 2 of section 3.4/3.4.1}
-\subsection{Stability (one option)}
+\subsection{Stability (one option)}\label{subsec:stability}
 The goal of this section is to compute $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ proving \Cref{thm:Phi_stable}:
@@
 
-Our proof will be via induction on $\dim_{\quadraticExtension} \hermitianSpace$.
-First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
+Our proof will be via induction as descriped in \ref{subsec:stability}.
+%First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
 \\
-
-\begin{proof}
+\begin{proof}[Proof of (A)]
 \calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
 \end{proof}
-
-Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
+\begin{proof}[Proof of (B)]
+
+%Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
 By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
-$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
-Subtracting our the equality for non-cupsidal $\pi$ we are left with:
+$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$Subtracting our the equality for non-cupsidal $\pi$ we are left with:
 $$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
@@
 So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is complete.
-
+\end{proof}
 \calvin{end alternate writeup 2}

### 2025-03-31 main.tex
Minor corrections
made unitary case work

@@
 		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$ \tabularnewline \hline \hline
-		$\algebraicGroup{\UnitaryGroup}_n$ & $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $(\algebraicGroup{\UnitaryGroup}_1)^{n}$ \tabularnewline \hline
-		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp_{2n}}$ &  $\multiplcativeScheme^n$ \tabularnewline \hline
+		$\algebraicGroup{\UnitaryGroup}_n$ & $\multiplcativeScheme^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $\multiplcativeScheme^{n}$ \tabularnewline \hline		 
+		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp}_{2n}$ &  $\multiplcativeScheme^n$ \tabularnewline \hline
 		$\algebraicGroup{\Sp}_{2n}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ \tabularnewline \hline		 
@@
 \end{center}
+\calvin{correct the tori and how Fr acts on cocharacters and the Weyl group}
 For all the pairs $\algebraicGroup{T} \subset \algebraicGroup{G}$ in this list, the Frobenius root $\Frobenius$ of $\algebraicGroup{G}$ acts trivially on the Weyl group $W\left(\algebraicGroup{T}\right)$.
@@
 
-For a torus character pair $(\algebraicGroup{T},\theta)$ with associated Frobenius conjugacy classes $w \in W(\algebraicGroup{T})$ and $(s) \subset \algebraicGroup{G}^*$ and an embedding $\rho:\algebraicGroup{G}^* \to \algebraicGroup{\GL}_n$.
-Fix a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and a Frobenius stable maximal torus $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$ which contains $\rho(\algebraicGroup{T}^*)$.
-Let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the Frobenius conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s)) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+We recall\[
+	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \Pi_{a \in \mathbb{Z}/n\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
+\]
+with Frobenius root action $\Frobenius(g_0,g_1, \hdots, g_{n-1}) = (\Frobenius(g_{n-1}, \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{n-2}))$.
+
+\begin{remark}
+Torus,Theta pairs in the restriction are the same as torus theta pairs before the restriction.
+\end{remark}
+
+Given a rational maximal torus $\algebraicGroup{T} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$, a character of $\algebraicGroup{T}(\mathbb{F})$, and a non-trivial additive character $\psi$ of $\finiteFieldExtension{m}$, we define a Guass sum
+\[
+	\tau_{\algebraicGroup{T}}(\theta,\psi) := \varepsilon_{\algebraicGroup{
+    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta(t)\psi(\trace(t_0)).
+\]
+\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}
+
+Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal tori $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subseteq \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 Define
 \[
-    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \varepsilon_{\algebraicGroup{
-    \tilde{\algebraicGroup{T}}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}(t)\chi(\det(t))\psi(\trace(t)).
+    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi(\det(t_0)),\psi).
 \]
+where $\chi$ is a multiplicative character of $\finiteFieldExtension{m}$ and $\psi$ and additive character of $\finiteFieldExtension{m}$.
 The following lemma shows that this is well defined.
@@
 \begin{enumerate}[(i)]
-	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $G = \GL_n$ and $\rho$ is the standard representation, $g_{T,\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s)$.
-	\item $g_{T,\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
+	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $\rho$ is the identity, $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s_{\algebraicGroup{T},\theta})$ and the character $\chi$.
+	\item $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and conjugacy class representative $w$.
 \end{enumerate}
@@
 Suppose that $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ are geometrically conjugate torus character pairs in $G$.
-Then $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T}',\rho}(\theta',\psi,\chi)$.
+Then $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T}',\rho}(\chi,\theta',\psi)$.
 \end{corollary}
@@
 \end{proof}
+
+\begin{remark}
+	The above work is not surpising as it is really a rephrasing that the eigenvalues of $\rho(s)$ are independent of conjugacy.
+\end{remark}
 
@@
  $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to \GL(2n)$  
+  $U(n)$  & $U(n) \to \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n}$  
 \end{tabular}
 \end{center}
-Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
+%Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
 In the $Sp,GSp$ cases the map is similar: the induced map of cocharacters sends $x \mapsto (x,1,-x)$.
@@
 
-In particular to analyze $g_{T,\rho}(\chi,\theta,\psi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
+%In particular 
+%To analyze $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ for these $\rho$, we need to understand what torus character pair of $\GL$ corresponds to $\phi((s))$ under a map $\phi(x) = (x,-x)$:
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
@@
         \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases.
-Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w^\ast)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha})$$
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w^\ast)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
         \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
- In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
+ In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$
     \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} 0 & w_nw \\
@@
         \end{pmatrix}$  on the image, and 
+		$$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
     \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w_nw \\
@@
 	\alpha(\zeta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots -q^{n-1}(y_{n}-y_{n+1}))})&= \alpha(\zeta^{(y_1+qy_{2n-1}+q^2y_3 +q^3y_{2n-3} \hdots +q^{n-1}y_{n+1})}) \\
-	&\quad \cdot \alpha^{-1}(\zeta^{(y_{2n}+qy_{2} + q^2y_{2n-2} + \hdots +q^{n-1}y_{n})}) \\
+	&\quad \cdot \alpha^{-1}(\zeta^{(qy_{2} + q^2y_{2n-2} + \hdots +q^{n-1}y_{n}+q^ny_{2n})}) \\
 	\theta(\beta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\theta(\beta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})}) \\
@@
 \end{align*}
+where $\zeta = \zeta_n = 1/(q^n-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and $\beta = \beta_n = \zeta_{2n}^{1-q^n}$.
 %Now the results follow from checking that
@@
 \begin{enumerate}
-    \item[($\algebraicGroup{U}$)] \calvin{right now can only deal with the case that $\chi$ is a square} Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$.
+    \item[($\algebraicGroup{U}$)] Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$. Let $w \circ w_n$ have cycle decomposition $\lambda$ 
+	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. Then
+	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
+	and applying \Cref{lem:cochar_computation}
+    \begin{align*}
+		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-q}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+	\end{align*}
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
+	\begin{comment}old hacky version
+	\calvin{right now can only deal with the case that $\chi$ is a square} Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$.
 Let $w \circ w_n$ have cycle decomposition $\lambda$
@@
 	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
+	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.\
+	\end{comment}
 	\item[($\algebraicGroup{SO}_{2n+1}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 

### 2025-03-31 main.tex
Correcting tori but not actions
Minor correction

@@
 			& \involution{\left(a^{\ast}\right)}
-		\end{pmatrix}  \mid a \in \algebraicGroup{A}_n \right\}$ \tabularnewline
+		\end{pmatrix}  \mid a \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{A}_n} \right\}$ \tabularnewline
 		\hline 
@@
 	& & \involution{\left(a^{\ast}\right)}
-\end{pmatrix}  \mid a \in \algebraicGroup{A}_n,\,\, t \in \algebraicGroup{U}_1 \right\}$ \tabularnewline
+\end{pmatrix}  \mid a \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{A}_n},\,\, t \in \algebraicGroup{U}_1 \right\}$ \tabularnewline
 \hline 
@@
 		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$ \tabularnewline \hline \hline
-		$\algebraicGroup{\UnitaryGroup}_n$ & $\multiplcativeScheme^{n}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_n$ &  $\multiplcativeScheme^{n}$ \tabularnewline \hline		 
+		$\algebraicGroup{\UnitaryGroup}_{2n}$ & $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_{2n}$ &  $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}}$ \tabularnewline \hline
+		$\algebraicGroup{\UnitaryGroup}_{2n+1}$ & $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_{2n+1}$ &  $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n} \times \algebraicGroup{\UnitaryGroup}}_1$ \tabularnewline \hline
 		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp}_{2n}$ &  $\multiplcativeScheme^n$ \tabularnewline \hline
@@
 We recall\[
-	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \Pi_{a \in \mathbb{Z}/n\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
+	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
 \]
-with Frobenius root action $\Frobenius(g_0,g_1, \hdots, g_{n-1}) = (\Frobenius(g_{n-1}, \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{n-2}))$.
+with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$
 
 \begin{remark}
-Torus,Theta pairs in the restriction are the same as torus theta pairs before the restriction.
+Torus character pairs for $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ are the same as torus character pairs for $\algebraicGroup{\GL}_n$ as a group over $\finiteFieldExtension{m}$.
 \end{remark}

### 2025-03-31 main.tex
added (bad) remark on choice of generator
later should update to make readable

@@
 \end{proof}
+
+\begin{remark}\calvin{figure out how to type out better}
+There is some ambiguity in choice of generator of each toris: for instance I could $\alpha \times \alpha^{-1}$ with $\alpha \times \alpha^{-q}$ in the first equality using the coordinate $y_{2n-1}$ instead of $y_{2n}$ for the second coordinate.
+In the type B,C,D case this ambiguity does not effect our sums since $\chi,\psi$ are defined over $\finiteField$ and hence stable under Frobenius i.e.
+$q$-th powers.
+In the type A unitary case, it is important to know which generators are in the first component which is any $y_i$ with $i\leq n$ since our characters $\chi$ take as input these entries.
+\end{remark}
+
 We let $\phi_{B,\lambda_i^+}, \phi_{B,\lambda_i^-}$ denote the $\phi$'s above in cases 1 and 2 respectivitly with $n = |\lambda_i|$. 

### 2025-03-31 main.tex
Chaos. Replacing \alpha with \alpha^{-1} in the Gauss sum

--- 2025-03-31 main.tex
@@
 \newcommand{\involutionPlusOne}[1]{#1^{1+c}}
+\newcommand{\minusInvolutionMinusOne}[1]{#1^{-1-c}}
 \newcommand{\IdentityMatrix}[1]{I_{#1}}
@@
 \newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
+\newcommand{\GaussSumSingleCharacter}[2]{\tau\left(#1, #2\right)}
 \newcommand{\dblJacobiSum}[2]{\mathcal{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
@@
 Given a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ the normalized Gauss sum corresponding to the data $\left(\chi, \fieldCharacter\right)$ is defined by the formula
-$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \fieldCharacter\left(x\right).$$
+$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(x\right) \fieldCharacter\left(x\right).$$
 
@@
 Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$.
-Then the sum $$\GaussSum{\pi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace g\right) \pi\left(g\right)$$
+Then the sum $$\GaussSum{\pi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace g^{-1}\right) \pi\left(g\right)$$
 defines an operator in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$.
@@
 For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
-$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
+$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g^{-1}\right).$$
 This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
@@
 
-If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha^{-1}\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
 If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
-$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
+$$\GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_n} = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha^{-1}\left(x\right) \chi^{-1}\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$
 
@@
 	We have the identity
-	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
+	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi^{-1}_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
 			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
@@
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
+	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \left(-\tau\left(\chi^{-1},\fieldCharacter\right)\right)^k \GaussSumScalar{\tau^{\vee}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
 \end{theorem}
@@
 Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
-	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(\pm 1\right) \chi\left(\pm 1\right)^k \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
+	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(\pm 1\right) \chi\left(\pm 1\right)^k \left(-\GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}\right)^k \GaussSumScalar{\involution{\left(\Contragradient{\tau}\right)} \times \chi}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\tau \times \chi}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
 \end{theorem}
@@
 We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
-	\chi\left(2\right) \tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
-	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
+	\tau\left(\chi^{-2}, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
+	\chi\left(2\right) \tau\left(\chi^{-2}, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
+	\tau\left(\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
 \end{dcases}$$
-Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.
-
-For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
+Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.
+
+For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\Contragradient{\tau} \times \involution{\chi}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
 For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
@@
 				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
-				\left(-1\right)^{n+1} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
+				\left(-1\right)^{n+1} \tau\left(\chi, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
 				1 & \text{otherwise.}
@@
 Probably needs a sign modification (the formula needs to be $\left(-1\right)^{\text{dual group dimension}} \times \text{product of Gauss sums}$).
-$\varepsilon_{\algebraicGroup{G}}$ contributes half of the dimension so that's why we add another half here.}
+$\varepsilon_{\algebraicGroup{G}}$ contributes half of the dimension so that's why we add another half here.} \elad{Maybe this is the better version for Calvin's computations}
 \end{remark}
@@
 $$\sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
-x \ne -1}} \alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(x+1\right)\right) = -\sizeof{\quadraticFieldExtension{k}}^{1/2} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\alpha, \fieldCharacter_{\quadraticFieldExtension{k}}\right) \tau\left(\chi \circ \aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}, \fieldCharacter_{\quadraticFieldExtension{k}}\right).$$
+x \ne -1}} \alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(x+1\right)\right) = -\sizeof{\quadraticFieldExtension{k}}^{1/2} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\alpha^{-1}, \fieldCharacter_{\quadraticFieldExtension{k}}\right) \tau\left(\chi^{-1} \circ \aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}, \fieldCharacter_{\quadraticFieldExtension{k}}\right).$$
 
@@
 \begin{equation*}
-	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha}{\minusInvolution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha^{-1}}{\involution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation*}
@@
 \begin{equation*}
-	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\involution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\minusInvolution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
 \end{equation*}
@@
 			x \ne -1}} \alpha \left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + x\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + \minusInvolution{x}\right)\right) \\
-	=& -\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\involution{\alpha}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+	=& -\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\minusInvolution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
 \end{align*}
@@
 \begin{align*}
-	q^{\frac{m}{2}} \tau\left(\chi^{-1} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right)^2 \tau\left(\chi^{2} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
+	q^{\frac{m}{2}} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right)^2 \tau\left(\chi^{-2} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
 \end{align*}
@@
 			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) \\
-		=& q^{\frac{m}{2}} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right),
+		=& q^{\frac{m}{2}} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi^{-2}, \fieldCharacter\right)^m \tau\left(\left(\theta'\right)^{-1} \times \chi, \fieldCharacter_{2m}\right),
 \end{align*}
 where $\theta'\left(t\right) = \theta\left(t^{1-q^m}\right)$.
-Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, this implies the following. \begin{theorem}
+Since $\tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right) \conjugate{\tau\left(\chi, \fieldCharacter\right)}$ and since $\chi \ne 1$, we have that $\tau\left(\chi, \fieldCharacter\right) \tau\left(\chi^{-1}, \fieldCharacter\right) = \chi\left(-1\right)$.
+Combining this with the fact that $\left(\theta'\right)^{-1} = \left(\theta'\right)^{q^m}$ lies in the same Frobenius orbit as $\theta'$, we get the following theorem.
+\begin{theorem}
 	We have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi^{-1}, \fieldCharacter_{2m}\right).$$
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi, \fieldCharacter_{2m}\right).$$
 \end{theorem}
@@
 By the appendix, this equals
-$$q^{\frac{m}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
+$$q^{\frac{m}{2}} \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}} \circ \FieldNorm{m}{1}, \fieldCharacter_m\right),$$
 which equals
-$$q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}.$$
+$$q^{\frac{m}{2}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}}.$$
 
@@
 	We have the following identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m}}$$
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}}.$$
 \end{theorem}
@@
 		g_T\left(\chi, \theta, \fieldCharacter\right)
-		= & \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
+		= & \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\minusInvolution{\alpha_j}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
 	\end{align*} Then
@@
 
-	Hence our theorem follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\frac{\dim_{\finiteField} \hermitianSpace}{2}},$$
+	Hence our theorem follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
 	and the fact \begin{equation*}
@@
 	\tau_{\algebraicGroup{T}}(\theta,\psi) := \varepsilon_{\algebraicGroup{
-    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta(t)\psi(\trace(t_0)).
+    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta^{-1}(t)\psi(\trace(t)).
 \]
@@
 Replacing $x$ with $y^{-1}x$, and using the Hasse--Davenport relation, we arrive at the sum
-$$q^{\frac{1}{2}} \left(q-1\right) \tau\left(\chi, \fieldCharacter\right)^2 \tau\left(\chi^{-2}, \fieldCharacter\right).$$
+$$q^{\frac{1}{2}} \left(q-1\right) \tau\left(\chi^{-1}, \fieldCharacter\right)^2 \tau\left(\chi^{2}, \fieldCharacter\right).$$
 
@@
 	which by changing variables $x \mapsto x^q$ equals
-	$$q^{\frac{1}{2}} \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2}} \tau\left(\chi \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
+	$$q^{\frac{1}{2}} \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right).$$
 

### 2025-03-31 main.tex
Using macro for Gauss sum of single character

@@
 Given a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ the normalized Gauss sum corresponding to the data $\left(\chi, \fieldCharacter\right)$ is defined by the formula
-$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(x\right) \fieldCharacter\left(x\right).$$
+$$\GaussSumSingleCharacter{\chi}{\fieldCharacter} = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(x\right) \fieldCharacter\left(x\right).$$
 
@@
 
-If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha^{-1}\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
+If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\GaussSumSingleCharacter{\alpha}{\fieldCharacter_n} = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha^{-1}\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$.
 If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
@@
 \begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
-	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \left(-\tau\left(\chi^{-1},\fieldCharacter\right)\right)^k \GaussSumScalar{\tau^{\vee}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
+	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \left(-\GaussSumSingleCharacter{\chi^{-1}}{\fieldCharacter}\right)^k \GaussSumScalar{\tau^{\vee}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
 \end{theorem}
@@
 We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\tau\left(\chi^{-2}, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
-	\chi\left(2\right) \tau\left(\chi^{-2}, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
-	\tau\left(\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
+	\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
+	\chi\left(2\right) \GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
+	\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
 \end{dcases}$$
-Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.
+Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}^{2} = \GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}} {\fieldCharacter_{\quadraticExtension}}$.
 
@@
 				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
-				\left(-1\right)^{n+1} \tau\left(\chi, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
+				\left(-1\right)^{n+1} \GaussSumSingleCharacter{\chi} {\fieldCharacter} & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
 				1 & \text{otherwise.}
@@
 $$\sum_{\substack{x \in \multiplicativegroup{\quadraticFieldExtension{k}}\\
-x \ne -1}} \alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(x+1\right)\right) = -\sizeof{\quadraticFieldExtension{k}}^{1/2} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\alpha^{-1}, \fieldCharacter_{\quadraticFieldExtension{k}}\right) \tau\left(\chi^{-1} \circ \aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}, \fieldCharacter_{\quadraticFieldExtension{k}}\right).$$
+x \ne -1}} \alpha\left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(x+1\right)\right) = -\sizeof{\quadraticFieldExtension{k}}^{1/2} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumSingleCharacter{\alpha^{-1}} {\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumSingleCharacter{\chi^{-1} \circ \aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}}{\fieldCharacter_{\quadraticFieldExtension{k}}}.$$
 
@@
 \begin{equation*}
-	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha^{-1}}{\involution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\alpha^{-1}}{\involution{\chi}}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k,
 \end{equation*}
@@
 \begin{equation*}
-	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\involution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\minusInvolution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k,
+	-\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\involution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\minusInvolution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k.
 \end{equation*}
@@
 			x \ne -1}} \alpha \left(x\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + x\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k} \slash \quadraticExtension}\left(1 + \minusInvolution{x}\right)\right) \\
-	=& -\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\minusInvolution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)^k.
+	=& -\sizeof{\quadraticExtension}^{\frac{k}{2}} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumCharacter{\minusInvolution{\alpha}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k}}} \GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k.
 \end{align*}
@@
 If $z=0$ then the sum over $y$ will vanish. Hence we can reduce the sum to $z \in \multiplicativegroup{\finiteFieldExtension{2m}}$. Replacing $y$ with $z^{-1} y$ and $z$ with $-z$, we get the sum
-$$-q^{-m} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}, \fieldCharacter_{2m}\right) \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right).$$
+$$-q^{-m} \GaussSumSingleCharacter{\chi \circ \aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}}{\fieldCharacter_{2m}} \sum_{z \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(z\right)\right) \fieldCharacter_{2m}\left(z\right)  \sum_{x \in \NormOneGroup{2m}} \theta \left(x\right) \fieldCharacter_{2m}\left(xz\right).$$
 To proceed, we use the Hilbert 90 map $\multiplicativegroup{\finiteFieldExtension{2m}} \to \NormOneGroup{2m}$ given by $t \mapsto t^{1 - q^m}$.
@@
 \begin{align*}
-	q^{\frac{m}{2}} \tau\left(\chi \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right)^2 \tau\left(\chi^{-2} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}, \fieldCharacter_m\right) \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
+	q^{\frac{m}{2}} \GaussSumSingleCharacter{\chi \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}}{\fieldCharacter_m}^2 \GaussSumSingleCharacter{\chi^{-2} \circ \aFieldNorm_{\finiteFieldExtension{m} \slash \finiteField}}{\fieldCharacter_m} \left(\sum_{t \in \multiplicativegroup{\finiteFieldExtension{2m}}} \chi^{-1}\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(t\right)\right) \theta' \left(t\right) \fieldCharacter_{2m}\left(t\right)\right).
 \end{align*}
@@
 			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) \\
-		=& q^{\frac{m}{2}} \tau\left(\chi, \fieldCharacter\right)^{2m} \tau\left(\chi^{-1}, \fieldCharacter\right)^{2m} \tau\left(\chi^{-2}, \fieldCharacter\right)^m \tau\left(\left(\theta'\right)^{-1} \times \chi, \fieldCharacter_{2m}\right),
+		=& q^{\frac{m}{2}} \GaussSumSingleCharacter{\chi}{\fieldCharacter}^{2m} \GaussSumSingleCharacter{\chi^{-1}}{\fieldCharacter}^{2m} \GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}^m \GaussSumCharacter{\left(\theta'\right)^{-1}}{\chi}{\fieldCharacter_{2m}},
 \end{align*}
@@
 	We have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-2}, \fieldCharacter\right)^m \tau\left(\theta' \times \chi, \fieldCharacter_{2m}\right).$$
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteField}\left(1 + x\right)\right) = q^{\frac{m}{2}} \GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}}.$$
 \end{theorem}
@@
 	We have the following identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
-			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = q^{\frac{m}{2}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}}.$$
+			x \ne -1}} \theta \left(x\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{2m} \slash \finiteFieldExtension{2}}\left(1 + x\right)\right) = q^{\frac{m}{2}} \GaussSumSingleCharacter{\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}}.$$
 \end{theorem}

### 2025-03-31 main.tex
Comments about the normalization

@@
 For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
+\elad{I don't normalize by the sign that appears in the $\left(-\GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}\right)^k$.
+Is that a problem?
+maybe I should normalize by it and it will get rid of the $\varepsilon_{\algebraicGroup{H}}$ in \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.}
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 	where $n = \left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2} \right\rfloor$.
-	However, we will not need this version for our purposes.
-\elad{Check odd orthogonal case.
-Probably needs a sign modification (the formula needs to be $\left(-1\right)^{\text{dual group dimension}} \times \text{product of Gauss sums}$).
-$\varepsilon_{\algebraicGroup{G}}$ contributes half of the dimension so that's why we add another half here.} \elad{Maybe this is the better version for Calvin's computations}
+	However, we will not need this version for our purposes. \elad{Maybe this is the better version for Calvin's computations}
 \end{remark}

### 2025-03-31 main.tex
Correcting references and macros

@@
 
-\begin{proposition}[{\cite[Corollary 12.7]{DigneMichel1991}}]
+\begin{proposition}[{\cite[Corollary 12.6]{DigneMichel1991}}]
 \label{prop:semisimple_pair_with_RTtheta}
-Treating $R_T^G(\theta)$ as a class function of $\algebraicGroup{G}(\finiteField)$ via the character of $R_T^G(\theta)$, for any class function $f$ on $\algebraicGroup{G}(\finiteField)$ which satisfies $f(g) = f(s)$ when $g=su$ is the Jordan decompositoin of $g$, we have
+Treating $R_T^G(\theta)$ as a class function of $\algebraicGroup{G}(\finiteField)$ via the character of $R_T^G(\theta)$, for any class function $f$ on $\algebraicGroup{G}(\finiteField)$ which satisfies $f(g) = f(s)$ when $g=su$ is the Jordan decomposition of $g$, we have
 \[
-	\langle R_T^G(\theta),f \rangle_{\algebraicGroup{G}(\finiteField)} = \langle \theta, f|_{\algebraicGroup{T}(\finiteField)}\rangle_{\algebraicGroup{T}(\finiteField)}
+	\innerproduct{R_T^G(\theta)}{f}_{\algebraicGroup{G}(\finiteField)} = \innerproduct{\theta}{f\restriction_{\algebraicGroup{T}(\finiteField)}}_{\algebraicGroup{T}(\finiteField)}.
 \]
-in other words:
+Alternatively,
 \[
-	\frac{1}{|\algebraicGroup{G}(\finiteField)|}\sum_{g \in \algebraicGroup{G}(\finiteField)}\left(R_T^G(\theta)\right)(g)f(g) = \frac{1}{|\algebraicGroup{T}(\finiteField)|}\sum_{t \in  \algebraicGroup{T}(\finiteField)} \theta(t)f(t)
+	\frac{1}{\sizeof{\algebraicGroup{G}(\finiteField)}}\sum_{g \in \algebraicGroup{G}(\finiteField)}\left(R_T^G(\theta)\right)(g)\conjugate{f(g)} = \frac{1}{\sizeof{\algebraicGroup{T}(\finiteField)}}\sum_{t \in  \algebraicGroup{T}(\finiteField)} \theta(t)\conjugate{f(t)}.
 \]

### 2025-04-01 main.tex
corrected Frob action in unitary case in dual group table

@@
 
-\subsubsection{Rational Tori}
+\subsubsection{Rational Tori}\label{subsubsec:rational-tori}
 A \emph{rational torus} $\algebraicGroup{T} \subset \algebraicGroup{G}$ over $\finiteField$ is a torus defined over $\finiteField$. 
@@
 In the unitary group case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is conjugation by $w_n$.
-In the $\algebraicGroup{\SO}^-_{2n}$ case, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
+In the $\algebraicGroup{\SO}^-_{2n}$ and $\algebraicGroup{\GSO}^-_{2n}$ cases, the action of $\Frobenius$ on the Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is the outer automorphism on the Dynkin diagram of type $D_n$.
 In our matrix representation, $\Frobenius$ acts on the Weyl group by conjugation by the matrix $$\left(-n,n\right) \coloneq \begin{pmatrix}\IdentityMatrix{n-1} & 0 & 0 & 0\\
@@
 		$\algebraicGroup{G}$ & $\algebraicGroup{T} \subset \algebraicGroup{G}$ & $\Frobenius$ action on $\CharacterLattice{\algebraicGroup{T}}$ & $\algebraicGroup{G}^{\ast}$ & $\algebraicGroup{T}^{\ast} \subset \algebraicGroup{G}^{\ast}$ \tabularnewline \hline \hline
-		$\algebraicGroup{\UnitaryGroup}_{2n}$ & $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}}$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_{2n}$ &  $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}}$ \tabularnewline \hline
-		$\algebraicGroup{\UnitaryGroup}_{2n+1}$ & $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}} \times \algebraicGroup{\UnitaryGroup}_1$ & $\left(-1\right)^{\times n}$ & $\algebraicGroup{\UnitaryGroup}_{2n+1}$ &  $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n} \times \algebraicGroup{\UnitaryGroup}}_1$ \tabularnewline \hline
+		$\algebraicGroup{\UnitaryGroup}_{2n}$ & $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}}$ & $-1\circ w_{2n}$ & $\algebraicGroup{\UnitaryGroup}_{2n}$ &  $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}}$ \tabularnewline \hline
+		$\algebraicGroup{\UnitaryGroup}_{2n+1}$ & $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n}} \times \algebraicGroup{\UnitaryGroup}_1$ & $-1 \circ w_{2n+1}$ & $\algebraicGroup{\UnitaryGroup}_{2n+1}$ &  $\restrictionOfScalars{\quadraticExtension}{\finiteField}{\multiplcativeScheme^{n} \times \algebraicGroup{\UnitaryGroup}}_1$ \tabularnewline \hline
 		$\algebraicGroup{\SO}_{2n+1}$ & $\multiplcativeScheme^n$ & 1 &$\algebraicGroup{\Sp}_{2n}$ &  $\multiplcativeScheme^n$ \tabularnewline \hline
@@
 \end{center}
-\calvin{correct the tori and how Fr acts on cocharacters and the Weyl group}
-For all the pairs $\algebraicGroup{T} \subset \algebraicGroup{G}$ in this list, the Frobenius root $\Frobenius$ of $\algebraicGroup{G}$ acts trivially on the Weyl group $W\left(\algebraicGroup{T}\right)$.
+\calvin{maybe we don't need to mention how $\Frobenius$ acts on the Weyl group because we stated it in section 2.3.4}
 In the last row, $\sigma \colon \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \to \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ is the automorphism $a + b\sqrt{d} \mapsto a - b\sqrt{d}$ where $d \in \multiplicativegroup{\finiteField}$ is a non-square.
+The Frobenius root acts on the Weyl group is described in section \ref{subsubsec:rational-tori}.
 

### 2025-04-01 main.tex
Defining notation

@@
 \newcommand{\SymmetricGroup}{\mathfrak{S}}
+\newcommand{\Kernel}{\operatorname{Ker}}
 
@@
 
+Given an integer $m \ge 1$ we define $$\NormOneGroup{2m} = \Kernel \FieldNorm{2m}{m} = \left\{ x \in \multiplicativegroup{\finiteFieldExtension{2m}} \mid \FieldNorm{2m}{m}\left(x\right) = 1\right\}.$$
+
 Given a partition $\lambda = \left(\lambda_1, \dots, \lambda_\ell\right)$, we denote the \etale $\finiteField$-algebra $$\finiteFieldExtension{\lambda} = \prod_{i=1}^{\ell} \finiteFieldExtension{\lambda_i}$$ and define
 $$\multiplicativegroup{\finiteFieldExtension{\lambda}} = \prod_{i=1}^{\ell} \multiplicativegroup{\finiteFieldExtension{\lambda_i}}.$$
-
-\elad{Need to define $2 \lambda$ and $\FieldNorm{2\lambda}{\lambda}$ and $\NormOneGroup{2 \lambda}$}
+We also define $2 \lambda = \left(2 \lambda_1, \dots, 2 \lambda_{\ell}\right)$ and $\aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}} \colon \multiplicativegroup{\finiteFieldExtension{2 \lambda}} \to \multiplicativegroup{\finiteFieldExtension{\lambda}}$ by $$\aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}}\left(x_1,\dots,x_{\ell}\right) = \left(\FieldNorm{2\lambda_1}{\lambda_1}\left(x_1\right), \dots, \FieldNorm{2\lambda_{\ell}}{\lambda_{\ell}}\left(x_{\ell}\right)\right).$$
+This is the restriction to $\multiplicativegroup{\finiteFieldExtension{2 \lambda}}$ of the norm map given by viewing $\finiteFieldExtension{2\lambda}$ as an algebra over $\finiteFieldExtension{\lambda}$.
+We define $$\NormOneGroup{2\lambda} = \Kernel \aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}} = \left\{x \in \multiplicativegroup{\finiteFieldExtension{2\lambda}} \mid \aFieldNorm_{\finiteFieldExtension{2\lambda} \slash \finiteFieldExtension{\lambda}}\left(x\right) = 1\right\},$$
+where $\multiplicativegroup{\finiteField} \to \multiplicativegroup{\finiteFieldExtension{\lambda}}$ is embedded diagonally.
+It is clear that $$\NormOneGroup{2\lambda} = \prod_{i=1}^{\ell} \NormOneGroup{2 \lambda_j}.$$
 

### 2025-04-02 main.tex
cleaning up invariants section

@@
 %test
-\begin{theorem}[Kondo {\cite{Kondo1963}}]
+\begin{theorem}[Kondo {\cite{Kondo1963}}]\label{thm:KondoClassical}
 	Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\theta_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$.
@@
 \begin{proof}
-By \cite[Lemma 2.2]{Malle2007}, if $\pi$ and $\pi'$ lie in the same geometric Lusztig series, then they have the same central character. The result now immediately follows.
+By \cite[Lemma 2.2]{Malle2007}, if $\pi$ and $\pi'$ lie in the same geometric Lusztig series, then they have the same central character.
+The result now immediately follows.\calvin{central character means (center of $G$)($\mathbb{F}$) not center of ($G(\mathbb{F})$)?}
 \end{proof}
@@
 \end{theorem}
-In the $\GL_n$ case this follows from \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo} along with \calvin{Hasse-Davenport? Something else?}.
-In this section we prove a slightly weaker result:
+%In the $\GL_n$ case, \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo}
 
@@
 	\[
-	g_{T,\rho}(\chi,\theta,\psi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}),
+	g_{T,\rho}(\chi,\theta,\psi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}) = (-1)^nq^{-n/2}G(\tau \times \chi,\psi)
 	\]
-	which by the Hasse-Davenport relation depends only on the geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$ \calvin{maybe write more or less?}. 
+	where $\tau$ is any subrepresentation of $R_{T,\theta}$.
+By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$.
 	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
@@
 The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate $\rho$ in the table below.
+
 \begin{center}
-\begin{tabular}{ c c}
- Group & Dual group representations $\rho$ \\ 
- $Sp(2n)$ &$SO(2n+1) \to \GL(2n+1)$\\  
- $GSp(2n)$  &$GSpin(2n+1) \to \GL(2n+1)$ \\
- $SO(2n)$ &$SO(2n) \to \GL(2n)$ \\
- $GO(2n)$ & ? \\
- $SO(2n+1)$ &$Sp(2n) \to \GL(2n)$ \\
- $GO(2n+1)$ & ? \\ 
-  $U(n)$  & $U(n) \to \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n}$  
+	\begin{tabular}{|c|c|} \hline
+		$\algebraicGroup{G}$ & $\algebraicGroup{G}^*$ representation  \tabularnewline \hline \hline
+		$\algebraicGroup{GL}_n$ &  $\algebraicGroup{\GL}_n \to \algebraicGroup{GL}_{2n}$ \tabularnewline \hline
+		$\algebraicGroup{\UnitaryGroup}_{n}$ &  $\algebraicGroup{\UnitaryGroup}_{n} \to \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{GL}_n}$\tabularnewline \hline		 				 
+		$\algebraicGroup{\SO}_{2n+1}$ &$\algebraicGroup{\Sp}_{2n} \to \algebraicGroup{\GL}_{2n}$ \tabularnewline \hline
+		$\algebraicGroup{\Sp}_{2n}$  &$\algebraicGroup{\SO}_{2n+1}\to \algebraicGroup{\GL}_{2n+1}$\tabularnewline \hline		 
+		$\algebraicGroup{\SO}^{+}_{2n}$ &$\algebraicGroup{\SO}^{+}_{2n}\to \algebraicGroup{\GL}_{2n}$\tabularnewline \hline
+		$\algebraicGroup{\SO}^{-}_{2n}$ &$\algebraicGroup{\SO}^{-}_{2n}\to \algebraicGroup{\GL}_{2n}$\tabularnewline \hline
+		$\algebraicGroup{\GSp}_{2n}$  &$\algebraicGroup{GSpin}_{2n+1}\to \algebraicGroup{\GL}_{2n+1}$ \tabularnewline \hline
+		$\algebraicGroup{\GSO}^{+}_{2n}$ & $\algebraicGroup{GSpin}_{2n}^{+}\to\algebraicGroup{\GL}_{2n}$ \tabularnewline \hline
+		$\algebraicGroup{\GSO}^{-}_{2n}$& $\algebraicGroup{GSpin}_{2n}^{-}\to\algebraicGroup{\GL}_{2n}$\tabularnewline \hline
 	\end{tabular}
 \end{center}
+Where in each case the map on cocharacters $\rho_*:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-w_n x)$ \calvin{in the GSpin cases might scale up by 2}
 %Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
@@
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
+Our proof of \Cref{lem:cochar_computation} will check that $\rho(s_{T,\theta}) = (s_{\Tilde{T},\Tilde{\theta}})$ with $g_{T}(\chi,\theta,\psi)$ equal to $\tau_{\Tilde{T}}(\Tilde{\theta} \times \chi,\psi)$ up to a few factors.
+We will do this by breaking our tori into irreducible rational factors with the following lemma handling each possible factor
 
@@
 \label{lem:cochar_computation}
-    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-w_n x)$.
-Then we have the following cases corresponding to conjugacy classes in the Weyl group
+    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-w_n x)$ be a $\Frobenius$ equivariant map.
+Then:
     \begin{enumerate}
@@
 		$$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
+		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus
+		\[
+\left(\begin{pmatrix}
+x_0 & 0\\
+0 & y_0
+\end{pmatrix},\begin{pmatrix}
+	F(x_0) & 0\\
+	0 & F(y_0)
+	\end{pmatrix} \right) \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{GL}_n
+		\]
+		with character $\alpha(x_0)\alpha^{-q}(y_0)$.
     \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w_nw \\
@@
 
-\begin{remark}\calvin{figure out how to type out better}
-There is some ambiguity in choice of generator of each toris: for instance I could $\alpha \times \alpha^{-1}$ with $\alpha \times \alpha^{-q}$ in the first equality using the coordinate $y_{2n-1}$ instead of $y_{2n}$ for the second coordinate.
-In the type B,C,D case this ambiguity does not effect our sums since $\chi,\psi$ are defined over $\finiteField$ and hence stable under Frobenius i.e.
-$q$-th powers.
-In the type A unitary case, it is important to know which generators are in the first component which is any $y_i$ with $i\leq n$ since our characters $\chi$ take as input these entries.
-\end{remark}
-
 We let $\phi_{B,\lambda_i^+}, \phi_{B,\lambda_i^-}$ denote the $\phi$'s above in cases 1 and 2 respectivitly with $n = |\lambda_i|$. 
@@
 Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ and geometric Frobeinus action on $X_*(\algebraicGroup{T})$.
-
+\calvin{add in GL case}
 \begin{enumerate}

### 2025-04-02 main.tex
more explicit matrices in unitary case

@@
 
-The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate $\rho$ in the table below.
+The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.
 
@@
 		$$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
-		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus
+		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus character pair
 		\[
 \left(\begin{pmatrix}
-x_0 & 0\\
-0 & y_0
+x_0 & 0 & 0 & 0 & \hdots & 0 \\
+0 & y_0 & 0 & 0 & \hdots & 0 \\
+0 & 0 & F^2(x_0) & 0 & \hdots & 0 \\
+0 & 0 & 0 & F^2(y_0) & \hdots & 0 \\
+\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
+0 & 0 & 0 & 0 & \hdots & F^{n-2}(y_0) \\
 \end{pmatrix},\begin{pmatrix}
-	F(x_0) & 0\\
-	0 & F(y_0)
-	\end{pmatrix} \right) \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{GL}_n
+	F(x_0) & 0 & 0 & 0 & \hdots & 0 \\
+	0 & F(y_0) & 0 & 0 & \hdots & 0 \\
+	0 & 0 & F^3(x_0) & 0 & \hdots & 0 \\
+	0 & 0 & 0 & F^3(y_0) & \hdots & 0 \\
+	\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
+	0 & 0 & 0 & 0 & \hdots & F^{n-1}(y_0) \\
+	\end{pmatrix} \right)
 		\]
-		with character $\alpha(x_0)\alpha^{-q}(y_0)$.
+		mapping to $\alpha(x_0)\alpha^{-q}(y_0)$.
     \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w_nw \\

### 2025-04-02 main.tex
Polish

@@
 
-\begin{proposition}[{\cite[Corollary 12.6]{DigneMichel1991}}]
+\begin{proposition}[{\cite[Corollary 12.6]{DigneMichel1991} or \cite[Theorem 1.2]{SaitoShinoda2000}}]
 \label{prop:semisimple_pair_with_RTtheta}
@@
 Notice that the assignments $g \mapsto \posJacobiKernel{\chi}\left(g\right)$ and $g \mapsto \negJacobiKernel{\chi}\left(g\right)$ only depend on the semisimple part of $g \in H$.
-By \cite[Theorem in Section 1.2]{SaitoShinoda2000}, we have the following result.
-\calvin{does this also follow from \Cref{prop:semisimple_pair_with_RTtheta}?
-Maybe we should say something about it} \elad{Can you compare the proofs?}\calvin{they use the same proof: basically they just use the character formula for RTtheta}
+By \Cref{prop:semisimple_pair_with_RTtheta}, we have the following result.
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
@@
 \label{prop:central_char}
-    If $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ is supported on the center $\algebraicGroup{Z}^{\Frobenius}$ of $\algebraicGroup{G}^{\Frobenius}$, then $f$ is a stable function.
+If $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ is supported on $\algebraicGroup{Z}^{\Frobenius}$, where $\algebraicGroup{Z}$ is the center of $\algebraicGroup{G}$, then $f$ is a stable function.
 \end{proposition}
 \begin{proof}
-By \cite[Lemma 2.2]{Malle2007}, if $\pi$ and $\pi'$ lie in the same geometric Lusztig series, then they have the same central character.
-The result now immediately follows.\calvin{central character means (center of $G$)($\mathbb{F}$) not center of ($G(\mathbb{F})$)?}
+By \cite[Lemma 2.2]{Malle2007}, if $\pi$ and $\pi'$ lie in the same geometric Lusztig series, then the restrictions of their central characters to $\algebraicGroup{Z}^{\Frobenius}$ coincide.
+The result now immediately follows.
 \end{proof}

### 2025-04-02 main.tex
Changing normalization so we don't have epsilon H

@@
 We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
-	\chi\left(2\right) \GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
-	\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
+	\left(-\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
+	\chi\left(2\right) \left(-\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
+	\left(-\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
 \end{dcases}$$
@@
 For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
-\elad{I don't normalize by the sign that appears in the $\left(-\GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}\right)^k$.
-Is that a problem?
-maybe I should normalize by it and it will get rid of the $\varepsilon_{\algebraicGroup{H}}$ in \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.}
+
 Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
@@
 		$$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \dblGammaFactor{\tau_1}{\chi}{\fieldCharacter} \dblGammaFactor{\tau_2}{\chi}{\fieldCharacter}.$$
-		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\chi \ne 1$, then
+		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\involutionPlusOne{\chi} \ne 1$, then
 		$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \dblGammaFactor{\tau}{\chi}{\fieldCharacter}.$$
@@
 	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
-				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
-				\left(-1\right)^{n+1} \GaussSumSingleCharacter{\chi} {\fieldCharacter} & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
-				1 & \text{otherwise.}
-	\end{dcases},$$
-	where $n = \left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2} \right\rfloor$.
+				1 & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
+				-\GaussSumSingleCharacter{\chi} {\fieldCharacter} & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
+				\left(-1\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \text{otherwise.}
+	\end{dcases}$$
 	However, we will not need this version for our purposes. \elad{Maybe this is the better version for Calvin's computations}
@@
 \begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$.
-Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
+	Suppose that $T = T_G \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$ and let $T_H$ be the unique maximal torus of $H$ such that $T_H \cap G = T_G$.
+Suppose that $\theta \colon T_G \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
 Denote \begin{align*}
@@
 \begin{proof}
-	Notice that if $\dim_{\finiteField} \hermitianSpace$ is odd then $\negJacobiKernel{\chi}\left(t\right) = 0$ for any $t \in T$, as $\idmap_{\hermitianSpace} - t$ always has determinant zero.
-
-	We have that if $t$ corresponds to $\left(a_1,\dots,a_r,t_1,\dots,t_s\right) \in \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \NormOneGroup{2m_i}$ such that $\idmap_{\hermitianSpace} + t$ is invertible then \begin{align*}
+	Notice that if $\dim_{\finiteField} \hermitianSpace$ is odd then $\negJacobiKernel{\chi}\left(t\right) = 0$ for any $t \in T_{G}$, as $\idmap_{\hermitianSpace} - t$ always has determinant zero.
+
+	We have that if $t \in T_G$ corresponds to $\left(a_1,\dots,a_r,t_1,\dots,t_s\right) \in \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \NormOneGroup{2m_i}$ such that $\idmap_{\hermitianSpace} + t$ is invertible then \begin{align*}
 		\posJacobiKernel{\chi}\left(t\right) =& \prod_{i=1}^s \chi\left(\FieldNorm{2m_i}{1}\left(1 + t_i\right)\right) \cdot \prod_{j=1}^r \chi\left(\aFieldNorm_{\quadraticFieldExtension{k_j} / \quadraticExtension}\left(1 + a_j\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k_j} / \quadraticExtension}\left(1 + \minusInvolution{a_j}\right)\right) \\
@@
 
-	Hence our theorem follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
-	and the fact \begin{equation*}
-		\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^r.
+	Hence our theorem follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
+	the fact that \begin{equation*}
+		\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} = \varepsilon_{\algebraicGroup{G}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{G}}},
 	\end{equation*}
+	and the facts
+	\begin{align*}
+		\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor \frac{1}{2}\dim_{\finiteField} \hermitianSpace \right\rfloor} & \,\,\,\,\,\text{and}\,\,\,\,\, \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{G}}} = \left(-1\right)^r.
+	\end{align*}
 \end{proof}

### 2025-04-02 main.tex
And I forgot to remove \epsilon_H
Explaining the signs

@@
 Thus we obtained the following.
-\begin{theorem}We have the identity
+\begin{theorem}\label{thm:split-case-deligne-lusztig-computation}We have the identity
 \begin{align*}
@@
 	\begin{align*}
-		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),
+		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),
 	\end{align*}
@@
 	\end{align*}
+	In this computation, the factor $\varepsilon_{\algebraicGroup{T}_{\algebraicGroup{G}}}$ comes from \Cref{thm:split-case-deligne-lusztig-computation} while the factor $\varepsilon_{\algebraicGroup{G}}$ comes from the definition of the normalization factor $c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)$.
 \end{proof}

### 2025-04-02 main.tex
Remove remark

@@
 \begin{remark}
-	We have $$\varepsilon_{\algebraicGroup{G}} = \left(-1\right)^{\left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}.$$ If $\finiteField = \quadraticExtension$ and $\dim_{\finiteField} \hermitianSpace$ is even then we also have $$\varepsilon_{\algebraicGroup{\GroupExtension{G}}} = \left(-1\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2} + 1}.$$
-\end{remark}
-\begin{remark}
 	Suppose that $\pi$ is any irreducible representation of $H$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies

### 2025-04-02 main.tex
Slight change title
Adding notation for characters and lifts

@@
 which equals
-$$q^{\frac{m}{2}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}}.$$
+$$q^{\frac{m}{2}} \tau\left(\chi^{-1} \restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^m \GaussSumCharacter{\theta'}{\chi}{\fieldCharacter_{2m}},$$
+where we recall that $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2m}} \to \multiplicativegroup{\cComplex}$ is given by $\theta'\left(x\right) = \theta\left(x^{1-q^m}\right)$.
 
@@
 
+\subsubsection{Some notation}
+Recall that by \Cref{subsubsec:rational-tori} maximal rational tori of $\algebraicGroup{G}$ correspond to certain pairs of partitions $\left(\lambda^+, \lambda^-\right)$ and we have that the $\Frobenius$ fixed points of a maximal torus $\algebraicGroup{T}$ corresponding to the pair $\left(\lambda^+, \lambda^-\right)$ are of the form $$T = \algebraicGroup{T}^{\Frobenius} \cong \prod_{j=1}^{\lengthof(\lambda^+)} \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \prod_{i=1}^{\lengthof(\lambda^-)} \NormOneGroup{2 \lambda_i^{-}},$$
+where if $\algebraicGroup{G}$ is a unitary group then $\lambda_j^{+}$ is even for every $j$, and thus $\finiteFieldExtension{\lambda^+_j}$ is always a field extension of $\quadraticExtension$.
+
+Given a character $$\theta = \prod_{j=1}^{\lengthof(\lambda^+)} \alpha_j \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta_i \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex},$$ we choose a torus of $T'$ of $\GL_{2 \left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}\left(\quadraticExtension\right)$ of the form $$T' \cong \prod_{j=1}^{\lengthof(\lambda^+)} \left(\multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}}\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}}$$ and define a character $\theta' \colon T' \to \multiplicativegroup{\cComplex}$ by the formula
+$$\theta' = \prod_{j=1}^{\lengthof(\lambda^+)} \left(\alpha_j \times \minusInvolution{\alpha}_j\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta'_j,$$
+where we recall that $\theta'_j \colon \multiplicativegroup{\finiteFieldExtension{2 \lambda_j^{-}}} \to \multiplicativegroup{\cComplex}$ is given by $$\theta'_j\left(x\right) = \theta_j\left(x^{1-q^{\lambda_j^-}}\right).$$
+
 \subsubsection{Computation for Deligne--Lusztig characters}
@@
 \begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $T = T_G \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $G$ and let $T_H$ be the unique maximal torus of $H$ such that $T_H \cap G = T_G$.
-Suppose that $\theta \colon T_G \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$.
-Denote \begin{align*}
-		g_T\left(\chi, \theta, \fieldCharacter\right)
-		= & \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\minusInvolution{\alpha_j}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
-	\end{align*} Then
-	\begin{align*}
-		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),
+	Suppose that $\algebraicGroup{T}_{\algebraicGroup{H}}$ is a maximal rational torus of $\algebraicGroup{H}$ that corresponds to the pair of partitions $\left(\lambda^+, \lambda^-\right)$ and let $\algebraicGroup{T}_{\algebraicGroup{G}} \coloneq \algebraicGroup{G} \cap \algebraicGroup{T}_{\algebraicGroup{H}}$ and $T = T_G = \algebraicGroup{T}_{\algebraicGroup{G}}^{\Frobenius}$.
+Suppose that $\theta_{H} \colon \algebraicGroup{T}_{\algebraicGroup{H}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character and let $$\theta = \theta_{\algebraicGroup{G}} \coloneq \theta_{\algebraicGroup{H}} \restriction_{T_G} \colon T_G \to \multiplicativegroup{\cComplex}.$$ Then
+	\begin{align*}
+		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_{T'}\left(\chi, \theta', \fieldCharacter\right),
 	\end{align*}
@@
 			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd.}\\
-			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right) & \text{ otherwise.}
+			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \theta\left(-1\right) & \text{ otherwise.}
 		\end{dcases}
@@
 
-	We have that if $t \in T_G$ corresponds to $\left(a_1,\dots,a_r,t_1,\dots,t_s\right) \in \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \NormOneGroup{2m_i}$ such that $\idmap_{\hermitianSpace} + t$ is invertible then \begin{align*}
-		\posJacobiKernel{\chi}\left(t\right) =& \prod_{i=1}^s \chi\left(\FieldNorm{2m_i}{1}\left(1 + t_i\right)\right) \cdot \prod_{j=1}^r \chi\left(\aFieldNorm_{\quadraticFieldExtension{k_j} / \quadraticExtension}\left(1 + a_j\right)\right) \chi\left(\aFieldNorm_{\quadraticFieldExtension{k_j} / \quadraticExtension}\left(1 + \minusInvolution{a_j}\right)\right) \\
+	We have that if $t \in T_G$ corresponds to $\left(x,y\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}$ such that $\idmap_{\hermitianSpace} + t$ is invertible then \begin{align*}
+		\posJacobiKernel{\chi}\left(t\right) =& \prod_{i=1}^{\lengthof(\lambda^-)} \chi\left(\FieldNorm{2 \lambda^-_i}{1}\left(1 + y_i\right)\right) \cdot \prod_{j=1}^{\lengthof(\lambda^+)} \chi\left(\aFieldNorm_{\finiteFieldExtension{\lambda_j^+} / \quadraticExtension}\left(1 + x_j\right)\right) \chi\left(\aFieldNorm_{\finiteFieldExtension{\lambda_j^+} / \quadraticExtension}\left(1 + \minusInvolution{x_j}\right)\right) \\
 		& \times  \begin{dcases}
@@
 	\end{align*}
-	If $t$ corresponds to $\left(a_1,\dots,a_r,t_1,\dots,t_s\right) \in \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \NormOneGroup{2m_i}$ such that $\idmap_{\hermitianSpace} - t$ is invertible then \begin{align*}
+	If $t$ corresponds to $\left(x,y\right) \in \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \times \NormOneGroup{2 \lambda^{-}}$ such that $\idmap_{\hermitianSpace} - t$ is invertible then \begin{align*}
 		\negJacobiKernel{\chi}\left(t\right) =& \begin{dcases}
@@
 	\begin{align*}
-		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right) =& \prod_{j=1}^r \alpha_j\left(-1\right) \cdot \prod_{i=1}^s \theta_i\left(-1\right).
+		\centralCharacter{\pi}\left(-1\right) = \theta\left(-1\right).
 	\end{align*}
 	Thus \begin{align*}
-		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_T\left(\chi, \theta, \fieldCharacter\right).
+		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_{T'}\left(\chi, \theta', \fieldCharacter\right).
 	\end{align*}
@@
 
-\subsection{Invariance of $\langle \JacobiKernel{}, R_T(\theta) \rangle$ under geometric conjugacy}
+\subsection{Invariance of $\innerproduct{\genHermitianJacobiKernel{\hermitianSpace}{\chi}}{R_{T,\theta}}$ under geometric conjugacy}
 

### 2025-04-02 main.tex
Adjustments for the unitary case :(

@@
 
-Given a character $$\theta = \prod_{j=1}^{\lengthof(\lambda^+)} \alpha_j \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta_i \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex},$$ we choose a torus of $T'$ of $\GL_{2 \left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}\left(\quadraticExtension\right)$ of the form $$T' \cong \prod_{j=1}^{\lengthof(\lambda^+)} \left(\multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}}\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}}$$ and define a character $\theta' \colon T' \to \multiplicativegroup{\cComplex}$ by the formula
+Given a character $$\theta = \prod_{j=1}^{\lengthof(\lambda^+)} \alpha_j \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta_i \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\cComplex},$$ we choose a torus of $T'$ of $\GL_{\frac{2}{\grpIndex{\quadraticExtension}{\finiteField}} \left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor}\left(\quadraticExtension\right)$ of the form $$T' \cong \prod_{j=1}^{\lengthof(\lambda^+)} \left(\multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}}\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \multiplicativegroup{\finiteFieldExtension{2 \lambda_i^{-}}}$$ and define a character $\theta' \colon T' \to \multiplicativegroup{\cComplex}$ by the formula
 $$\theta' = \prod_{j=1}^{\lengthof(\lambda^+)} \left(\alpha_j \times \minusInvolution{\alpha}_j\right) \times \prod_{i=1}^{\lengthof(\lambda^-)} \theta'_j,$$

### 2025-04-02 main.tex
Adding notation for Gauss sums of Tori

@@
 \newcommand{\GaussSumSingleCharacter}[2]{\tau\left(#1, #2\right)}
+\newcommand{\GaussSumSingleTorusCharacter}[3]{\tau_{#1}\left(#2, #3\right)}
 \newcommand{\dblJacobiSum}[2]{\mathcal{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
@@
 \newcommand{\GaussSumCharacter}[3]{\tau\left(#1 \times #2, #3\right)}
+\newcommand{\GaussSumTorusCharacter}[4]{\tau_{#1}\left(#2 \times #3, #4\right)}
 \newcommand{\ladicnumbers}{\algebraicClosure{\mathbb{Q}_{\ell}}}
@@
 
+Given a torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
+Notice that if $\alpha = \alpha_1 \times \dots \times \alpha_{\lengthof\left(\lambda\right)}$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{\lambda_j}} \to \multiplicativegroup{\cComplex}$ is a character for every $j$, then
+$$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\lambda_j}}.$$
+
 We are now ready to state Kondo's result.
-%test
 \begin{theorem}[Kondo {\cite{Kondo1963}}]\label{thm:KondoClassical}
@@
 	$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\theta_j}{\chi}{\fieldCharacter_{n_j}}.$$
+
+	If $\tau$ is an irreducible representation such that $\innerproduct{\trace \tau}{R_{T, \alpha}} \ne 0$ for some maximal torus $T$ of $\GL_n\left(\finiteField\right)$ and some character $\alpha \colon T \to \multiplicativegroup{\cComplex}$ then $$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter}.$$
 \end{theorem}
@@
 	\begin{align*}
-		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_{T'}\left(\chi, \theta', \fieldCharacter\right),
+		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter},
 	\end{align*}
@@
 		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \begin{dcases}
-			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd.}\\
+			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd,}\\
 			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \theta\left(-1\right) & \text{ otherwise.}

### 2025-04-02 main.tex
\theta => \alpha

@@
 \begin{theorem}[Kondo {\cite{Kondo1963}}]\label{thm:KondoClassical}
-	Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\theta_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$.
+	\begin{enumerate}
+		\item Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ with cuspidal support $\left\{\tau_1,\dots, \tau_r\right\}$, where $n_1 + \dots + n_r = n$, and where for every $j$, $\tau_j$ is an irreducible cuspidal representation of $\GL_{n_j}\left(\finiteField\right)$ corresponding to the Frobenius orbit of a regular character $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{n_j}} \to \multiplicativegroup{\cComplex}$.
 Then
-	$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\theta_j}{\chi}{\fieldCharacter_{n_j}}.$$
-
-	If $\tau$ is an irreducible representation such that $\innerproduct{\trace \tau}{R_{T, \alpha}} \ne 0$ for some maximal torus $T$ of $\GL_n\left(\finiteField\right)$ and some character $\alpha \colon T \to \multiplicativegroup{\cComplex}$ then $$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter}.$$
+		$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi}{\fieldCharacter_{n_j}}.$$
+		\item Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $\innerproduct{\trace \tau}{R_{T, \alpha}} \ne 0$ for some maximal torus $T$ of $\GL_n\left(\finiteField\right)$ and some character $\alpha \colon T \to \multiplicativegroup{\cComplex}$.
+Then $$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter}.$$
+	\end{enumerate}
 \end{theorem}

### 2025-04-02 main.tex
Adding a notation without \chi

@@
 Given a torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
+We also define $$\GaussSumSingleTorusCharacter{T}{\alpha}{\fieldCharacter} = \GaussSumTorusCharacter{T}{\alpha}{1}{\fieldCharacter}.$$
 Notice that if $\alpha = \alpha_1 \times \dots \times \alpha_{\lengthof\left(\lambda\right)}$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{\lambda_j}} \to \multiplicativegroup{\cComplex}$ is a character for every $j$, then

### 2025-04-02 main.tex
Notation

@@
 \[
-    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi(\det(t_0)),\psi).
+    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi_0 \circ \det,\psi).
 \]
-where $\chi$ is a multiplicative character of $\finiteFieldExtension{m}$ and $\psi$ and additive character of $\finiteFieldExtension{m}$.
+Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters and $\chi_0 \circ \det \colon \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$ is given by $$\left(\chi \circ \det\right)\left(g_0,\dots,g_{m-1}\right) = \chi\left(\det g_0\right)$$ \elad{This is weird.
+Maybe we should just say that we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) = \GL_n\left(\finiteFieldExtension{m}\right)$ by $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$?}.
 The following lemma shows that this is well defined.
@@
 \begin{enumerate}[(i)]
-	\item In this case when $T = \prod_{i} \multiplicativegroup{\finiteFieldExtension{n_i}}$ and $\theta = \prod_{i} \alpha_i$, we recover the Gauss sum
+	\item In this case when $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$, we recover the Gauss sum
 	\[
-	g_{T,\rho}(\chi,\theta,\psi)  = \prod_i \tau(\alpha_i \times \chi, \fieldCharacter_{n_i}) = (-1)^nq^{-n/2}G(\tau \times \chi,\psi)
+	g_{T,\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T}{\theta}{\chi}{\fieldCharacter} = \left(-1\right)^n \GaussSumScalar{\tau \times \chi}{\fieldCharacter},
 	\]

### 2025-04-03 main.tex
wrote out details in proof of main theorem

--- 2025-04-02 main.tex
@@
 \usepackage{mathtools}
+%\usepackage{xcolor}
 
@@
 \begin{document}
+%\pagecolor{black}
+%\color{white}
 
@@
 Given a torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
+We also define $$\GaussSumSingleTorusCharacter{T}{\alpha}{\fieldCharacter} = \GaussSumTorusCharacter{T}{\alpha}{1}{\fieldCharacter}.$$
 Notice that if $\alpha = \alpha_1 \times \dots \times \alpha_{\lengthof\left(\lambda\right)}$, where $\alpha_j \colon \multiplicativegroup{\finiteFieldExtension{\lambda_j}} \to \multiplicativegroup{\cComplex}$ is a character for every $j$, then
-$$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\lambda_j}}.$$
+\begin{align}
+	\label{eq:Gauss_multiplicitive}
+	\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\lambda_j}}.
+\end{align}
 
@@
 
-\subsection{Multiplicativity}
+\subsection{Multiplicativity}\label{subsec:multiplicativity}
 The goal of this section is to understand how the doubling method Jacobi sums behave under parabolic induction.
@@
 \]
-with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$
+with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ Thus we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \algebraicGroup{\GL}_n(\finiteFieldExtension{m})$ via the first coordinate $g_0$.
 
@@
 
-Given a rational maximal torus $\algebraicGroup{T} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$, a character of $\algebraicGroup{T}(\mathbb{F})$, and a non-trivial additive character $\psi$ of $\finiteFieldExtension{m}$, we define a Guass sum
-\[
-	\tau_{\algebraicGroup{T}}(\theta,\psi) := \varepsilon_{\algebraicGroup{
-    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta^{-1}(t)\psi(\trace(t)).
-\]
-\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}
+%Given a rational maximal torus $\algebraicGroup{T} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$, a character of $\algebraicGroup{T}(\mathbb{F})$, and a non-trivial additive character $\psi$ of $\finiteFieldExtension{m}$, we define a Guass sum
+%\[
+%	\tau_{\algebraicGroup{T}}(\theta,\psi) := \varepsilon_{\algebraicGroup{
+%    \algebraicGroup{T}}}\sum_{t\in \tilde{\algebraicGroup{T}}^{\Frobenius}} \theta^{-1}(t)\psi(\trace(t)).
+%\]
+%\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}
 
@@
 \[
-    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi(\det(t_0)),\psi).
+    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = q^{-(nm)/2}\epsilon_{\Tilde{\algebraicGroup{T}}}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}(\det(t)) \psi(\trace(t)).
 \]
-where $\chi$ is a multiplicative character of $\finiteFieldExtension{m}$ and $\psi$ and additive character of $\finiteFieldExtension{m}$.
+\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$?}
+Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters and $\chi_0 \circ \det \colon \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$ is given by $$\left(\chi \circ \det\right)\left(g_0,\dots,g_{m-1}\right) = \chi\left(\det g_0\right)$$ \elad{This is weird.
+Maybe we should just say that we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) = \GL_n\left(\finiteFieldExtension{m}\right)$ by $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$?}\calvin{yeah that makes sense}.
 The following lemma shows that this is well defined.
@@
 \end{enumerate}
-The key input to (A) is the multiplicativity [CITE] of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
-The key input to (B) is \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.
+The key input to (A) is the multiplicativity of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
+The key input to (B) \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.
 
@@
 We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center.
-For any irreducible representation $\pi$ of $G$ which is the a component of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
+For any irreducible representation $\pi$ of $G$ which is subrepresentation of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
 \[
@@
 
-The following proposition implies that if $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{G}}{\tilde{s}}$ for $\tilde{s}$ only depending on $s$.
-Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$ (see section 3.2).
+Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, the following proposition implies that there exists $\tilde{s}$ depending on $s$ such that each $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ is an irreducible subrepresentation of some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ restricted to $G$.
+Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.
 
@@
 
-Our proof will be via induction as descriped in \ref{subsec:stability}.
+Our proof will be via induction as described in \ref{subsec:stability}.
 %First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
@@
 \begin{proof}[Proof of (A)]
-\calvin{should be short proof. Might not even need to put--just need to say both are multiplicative}
+	Since every proper parabolic of $H$ is contained in a proper parabolic of the form $\algebraicGroup{\GL}_n \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
+\\
+	For the right hand side, first the following result of Lusztig tells us that if $\pi \in \LusztigSeries{
+		\algebraicGroup{G}^{\Frobenius}}{(s)}$ is contained in the parabolical induction of $\sigma$ from a Levi $L$, then $\sigma \in \LusztigSeries{
+		\algebraicGroup{L}^{\Frobenius}}{(s)}$.
+		\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]
+			For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
+		\end{proposition}
+	Thus if $\pi$ is contained in the parabolical induction from a proper Levi $L$ then $(T,\theta)$ is geometrically conjugate to $(T_1 \times T_2,\theta_1 \times \theta_2)$ for $T_1 \times T_2$ a torus of $L$.
+As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}(\chi,\theta|_{T \cap G},\psi) = g_{(T_1 \times T_2) \cap G}(\chi,\left(\theta_1\times \theta_2\right)|_{(T_1 \times T_2) \cap G},\psi).$$ The right hand of the above is multiplicative since Gauss sums are multiplicative by \Cref{eq:Gauss_multiplicitive}.
 \end{proof}
 \begin{proof}[Proof of (B)]
-
 %Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.

### 2025-04-05 main.tex
Typo
minor adjustments to DL background

@@
 	\label{eq:Gauss_multiplicitive}
-	\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_{\lambda_j}}.
+	\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \prod_{j=1}^{\lengthof\left(\lambda\right)} \GaussSumCharacter{\alpha_j}{\chi}{\fieldCharacter_{\lambda_j}}.
 \end{align}
@@
 Over a finite field, $\algebraicGroup{G}(\finiteField)$ conjugacy classes of maximal rank rational tori \calvin{check if we need connected or something} are parameterized by  Frobenius order twisted conjugacy classes in the Weyl group.
-In particular if we fix a rational torus $\algebraicGroup{T}_0$ with rank $\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that $g^{-1}\Frobenius(g) \in N(\algebraicGroup{T}_0)$ then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and its $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of the image of the Lang map $L \colon \algebraicGroup{G}\left(\algebraicClosure{\finiteField}\right) \to \algebraicGroup{G}\left(\algebraicClosure{\finiteField}\right)$ defined as $L\left(g\right) = g^{-1}\Frobenius(g)$ in $W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.
+In particular if we fix a rational torus $\algebraicGroup{T}_0$ with rank $\mathrm{rk} \algebraicGroup{G}$ and an element $g \in \algebraicGroup{G}(\algebraicClosure{\finiteField})$ such that the image of the Lang map $L(g):\algebraicGroup{\algebraicClosure{\finiteField}} \to \algebraicGroup{\algebraicClosure{\finiteField}}$ defined as $g^{-1}\Frobenius(g)$ lies in $N(\algebraicGroup{T}_0)$, then the torus $g\algebraicGroup{T}_0g^{-1}$ is rational, and its $\algebraicGroup{G}(\finiteField)$-conjugacy class is determined  by the Frobeinus-twisted conjugacy class of $L\left(g\right) \in W(\algebraicGroup{T}_0)(\algebraicClosure{\mathbb{F}})$, see \cite[Section 3.3]{Carter1985}.
 
@@
 \begin{example}
-	\elad{Correct example or remove it}\calvin{They are geo conjugate in $\algebraicGroup{Sp}_4$}
-	Take $\algebraicGroup{G}' = \algebraicGroup{\GL}_2$.
+	%\elad{Correct example or remove it}\calvin{They are geo conjugate in $\algebraicGroup{Sp}_4$}
 	Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
@@
 Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
+	Both the tori $\algebraicGroup{T}_2 \times \algebraicGroup{T}_2$ and $\algebraicGroup{T}_2'$ are tori inside $\algebraicGroup{Sp}_4$.
 	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.

### 2025-04-08 main.tex
Answering a question

@@
 \]
-\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$?}
+\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$? \elad{$q^{-nm/2}$}}
 Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters and $\chi_0 \circ \det \colon \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$ is given by $$\left(\chi \circ \det\right)\left(g_0,\dots,g_{m-1}\right) = \chi\left(\det g_0\right)$$ \elad{This is weird.

### 2025-04-08 main.tex
Correction

@@
 \label{thm:Phi_stable}
-	The assignments $H \to \cComplex$ given by $$h \mapsto \genHermitianJacobiKernel{\hermitianSpace}{h}$$ are stable functions.
+	The assignments $H \to \cComplex$ given by $$h \mapsto \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(h\right)$$ are stable functions.
 Equivalently, the assignments $$\pi \mapsto \dblJacobiSumScalar{\pi}{\chi}$$ are constant on geometric Lusztig series.

### 2025-04-08 main.tex
Some cleanup

@@
 \end{center}
-\calvin{maybe we don't need to mention how $\Frobenius$ acts on the Weyl group because we stated it in section 2.3.4}
 In the last row, $\sigma \colon \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \to \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ is the automorphism $a + b\sqrt{d} \mapsto a - b\sqrt{d}$ where $d \in \multiplicativegroup{\finiteField}$ is a non-square.
-The Frobenius root acts on the Weyl group is described in section \ref{subsubsec:rational-tori}.
+The Frobenius root action on the Weyl group is described in \Cref{subsubsec:rational-tori}.
+
+We will need the following facts about Lusztig series.
+
+The first fact tells us that Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ are unions of Harish-Chandra series, and establishes a relation between the corresponding semisimple conjugacy classes.
+\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]\label{prop:lusztig-series-are-unions-of-harish-chandra-series}
+	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
+\end{proposition}
+
+The next fact establishes a relation between the Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ and of $\algebraicGroup{G}$.
+\elad{Explain $i^{\ast}$}\elad{Should we deprecate the notation $\Frobenius^{\ast}$?}
+
+\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]\label{prop:lusztig-series-and-restriction}
+	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
+	\begin{enumerate}
+		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
+Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
+	\end{enumerate}
+\end{proposition}
+
+Finally, the next fact concerns the number of cuspidal representations in a Lusztig series of $\GroupExtension{\algebraicGroup{G}}$.
+
+\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]\label{prop:at-most-one-cuspidal-lusztig-series}
+	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
+\end{proposition}
 
@@
 The proof strategy is to prove the following inductive statements
-\begin{enumerate}[(A)]
-	\item If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$.
-	\item If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non cuspidal representations with $\dim_{\mathbb{E}} V = n$, then it holds for all cuspidal representations with $\dim_{\mathbb{E}} V = n$.
-\end{enumerate}
-The key input to (A) is the multiplicativity of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
-The key input to (B) \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.
+\begin{enumerate}[(a)]
+	\item \label{item:follows-for-non-cuspidal}If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$.
+	\item \label{item:follows-for-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$, then it holds for all irreducible cuspidal representations of $H$ with $\dim_{\mathbb{E}} V = n$.
+\end{enumerate}
+The key input to (\ref{item:follows-for-non-cuspidal}) is the multiplicativity of the $\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter}$ factor.
+The key input to (\ref{item:follows-for-cuspidal}) is \Cref{lem:indep_geo_conj} along with results of Lusztig controlling the cupsidal elements in a Lusztig series.
 
@@
 We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center.
-For any irreducible representation $\pi$ of $G$ which is subrepresentation of an irreducible representation $\tilde{\pi}$ of $\GroupExtension{G}$ restricted to $\pi$,
-\[
-    \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.
-\]
-
-Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, the following proposition implies that there exists $\tilde{s}$ depending on $s$ such that each $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ is an irreducible subrepresentation of some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ restricted to $G$.
+Suppose that $\tilde{\pi}$ is an irreducible representation of $\GroupExtension{G}$ and that $\pi$ is an irreducible representation of $G$ that appears as a subrepresentation of the restriction of $\tilde{\pi}$ to $G$.
+Then since $\dblJacobiSum{\tilde{\pi}}{\chi}$ and $\dblJacobiSum{\pi}{\chi}$ are scalar operators and the restriction of $\dblJacobiSum{\tilde{\pi}}{\chi}$ to $\pi$ is $\dblJacobiSum{\pi}{\chi}$, we have that $$\dblJacobiSumScalar{\pi}{\chi} = \dblJacobiSumScalar{\tilde{\pi}}{\chi}$$ and thus
+$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.$$
+
+Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that each $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ is an irreducible subrepresentation of the restriction to $G$ of some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$.
 Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.
 
-\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
-	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
-	\begin{enumerate}
-		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
-	\end{enumerate}
-\end{proposition}
-
 We now prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the extension $\GroupExtension{G}$.
-
-Our proof will be via induction as described in \ref{subsec:stability}.
-%First we will use \Cref{thm:multiplicativity-in-terms-of-gamma-factors}  and MULTIPLICAATIVITY-OF-GTTHETA to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for any non cuspidal $\pi$ assuming \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for all Levi factors.
-\\
-\begin{proof}[Proof of (A)]
-	Since every proper parabolic of $H$ is contained in a proper parabolic of the form $\algebraicGroup{\GL}_n \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
-\\
-	For the right hand side, first the following result of Lusztig tells us that if $\pi \in \LusztigSeries{
-		\algebraicGroup{G}^{\Frobenius}}{(s)}$ is contained in the parabolical induction of $\sigma$ from a Levi $L$, then $\sigma \in \LusztigSeries{
+Henceforth we denote $H = \GroupExtension{G}$.
+Our proof will be via induction as described above.
+
+\begin{proof}[Proof of \eqref{item:follows-for-non-cuspidal}]
+	Since every proper parabolic subgroup of $H = \GroupExtension{G}$ is contained in a proper parabolic subgroup group with Levi part of the form $\GL_n\left(\quadraticExtension\right) \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
+
+	For the right hand side, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
+		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{(s)}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\pi}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
 		\algebraicGroup{L}^{\Frobenius}}{(s)}$.
-		\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]
-			For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
-		\end{proposition}
-	Thus if $\pi$ is contained in the parabolical induction from a proper Levi $L$ then $(T,\theta)$ is geometrically conjugate to $(T_1 \times T_2,\theta_1 \times \theta_2)$ for $T_1 \times T_2$ a torus of $L$.
-As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}(\chi,\theta|_{T \cap G},\psi) = g_{(T_1 \times T_2) \cap G}(\chi,\left(\theta_1\times \theta_2\right)|_{(T_1 \times T_2) \cap G},\psi).$$ The right hand of the above is multiplicative since Gauss sums are multiplicative by \Cref{eq:Gauss_multiplicitive}.
+
+	Thus if $\pi$ is a subrepresentation of a parabolically induced representation as above, then $(T_H,\theta_H)$ is geometrically conjugate to $(T_1 \times T_2,\theta_1 \times \theta_2)$ for $T_1 \times T_2$ a torus of $L$.
+As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}(\chi,\theta|_{T \cap G},\psi) = g_{(T_1 \times T_2) \cap G}(\chi,\left(\theta_1\times \theta_2\right)|_{(T_1 \times T_2) \cap G},\psi).$$ The right hand of the above is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
 \end{proof}
-\begin{proof}[Proof of (B)]
-%Combining this with our inductive hypothesis implies \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for non cupsidal $\pi$.
-By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum c_{\pi} \pi$, 
-$$\sum c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$Subtracting our the equality for non-cupsidal $\pi$ we are left with:
-$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right)$$.
-
-But it is well known that there is only one cuspidal $\pi$ appearing in our sum:
-\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
-	Let $\GroupExtension{G}$ be a classical group with connected center.
-For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
-\end{proposition}
-
-So the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is complete.
-\end{proof}
-\calvin{end alternate writeup 2}
-
-\subsection{Stability (another option)}
-\calvin{retitle: Stability of Jacobi sums}
-
-The goal of this section is to use \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and results of Lusztig to determine $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for any irreducible representation $\pi$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$.
-
-\begin{theorem}\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
-	Let $T \subset H$ be a maximal torus and let $\theta \colon T \to \multiplicativegroup{\cComplex}$ be a character. Write $$R_{T,\theta} = \sum_{\Pi} c_{\Pi} \trace \Pi,$$
-	where $\Pi$ goes over all the irreducible representations of $H$ and $c_{\Pi} \in \zIntegers$.
-Suppose that $\pi$ is an irreducible representation such that $c_{\pi} \ne 0$.
-Then $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_T\left(\theta, \fieldCharacter\right).$$
-\end{theorem}
-\subsubsection{Proof of the main result \calvin{\Cref{thm:Phi_stable}}}
-
-\elad{Merge with Calvin's stuff}
-The \emph{Lusztig series} $\LusztigSeries{G}{s}$ consists of (equivalence classes of) the irreducible representations $\pi$ of $R_{T, \theta}$ with $c_{\pi} \ne 0$ as in the theorem.
-
-Let $L \subset G$ be a Levi subgroup of $G$, and suppose that $L \cong \prod_{j=1}^\ell \GL_{t_j}\left(\finiteField\right) \times G'$ where $G' = \IsometryGroup\left(\hermitianSpace'\right)$ where $\hermitianSpace'$ is a non-degenerate hermitian subspace and $\hermitianSpace = \xIsotropic \oplus \hermitianSpace' \oplus \yIsotropic$, where $\xIsotropic$ and $\yIsotropic$ are totally isotropic subspace in duality.
-Suppose that $s \in L$, and denote by $s_i$ the projection of $s$ to $\GL_{t_i}\left(\finiteField\right)$ for $1 \le i \le \ell$ and by $s_0$ the projection of $s$ to $G'$.
-We denote
-$$\LusztigSeries{L}{s} = \left(\bigotimes_{j=1}^{\ell} \LusztigSeries{\GL_{t_j}\left(\finiteField\right)}{s_j}\right) \otimes \LusztigSeries{G'}{s_0}.$$
-
-We collect some facts that will be used for proving \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}.
-
-The following proposition allows us to make use of the multiplicativity property (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}) for non-cuspidal elements in a given Lusztig series.
-\begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]
-	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
-\end{proposition}
-
-The following Proposition shows that is suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for the group $\GroupExtension{G}$.
-\begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]
-	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
-	\begin{enumerate}
-		\item If $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ and if $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$, then $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-		\item Let $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$.
-Then there exists $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $\FrobeniusFixedPoints{G}$.
-	\end{enumerate}
-\end{proposition}
-
-Finally, the following proposition shows that the multiplicativity property takes care of all but at most one element in a given Lusztig series.
-\begin{proposition}[{\cite[Page 172]{Lusztig1977}}]
-	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
-\end{proposition}
-
-\Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is now equivalent to the following statement.
-\begin{proposition}\label{prop:gamma-factor-is-constant-on-lusztig-series}
-	Keep the notations as above.
-Suppose that $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$.
-Then for any irreducible cuspidal $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ and for any irreducible subrepresentation $\pi \subset \Ind{\FrobeniusFixedPoints{P}}{\FrobeniusFixedPoints{\GroupExtension{G}}}{\sigma}$, $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \tau_{\GroupExtension{G}, \chi, \fieldCharacter}\left(s\right).$$
-	\elad{Many things are not defined anymore. Need to define $\tau_{\GroupExtension{G}, \chi, \fieldCharacter}\left(s\right)$, etc.}
-\end{proposition}
-\begin{proof}
-	The proof is by induction on $\dim_{\quadraticExtension} \hermitianSpace$.
-
-	Suppose first that $L \ne G$.
-Then by using the multiplicativity property repeatedly (\Cref{thm:multiplicativity-in-terms-of-gamma-factors}), we have $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \cdot \prod_{j=1}^r \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j\right) \tau_{\GL_{t_j}\left(\finiteField\right), \chi, \fieldCharacter}\left(s_j^{-1}\right),$$
-	where $\pi'$ is an irreducible cuspidal representation of $G'$ that lies in the Lusztig series $\LusztigSeries{\pi'}{s_0}$.
-By the induction hypothesis, we have $$\dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} = \tau_{G', \chi, \fieldCharacter}\left(s_0\right),$$
-	which implies the result.
-
-	Next, suppose that $L = G$ and that $\pi = \sigma$ is an irreducible cuspidal representation. Let us write $$R_{T, \theta} = \sum_{\Pi} c_\Pi \trace \Pi,$$
-	where $\Pi$ goes over all the irreducible representations of $G$ and $c_{\Pi} \in \zIntegers$.
-For every $\Pi$ with $c_{\Pi} \ne 0$ and $\Pi \ne \pi$, we have that $\Pi$ lies in a Harish--Chandra series with $L \ne G$ as above, and therefore $$\dblVirtualJacobiSumScalar{\trace \Pi}{\chi} = \dim \Pi \cdot \centralCharacter{\Pi}\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, we have $$\dblVirtualJacobiSumScalar{R_{T,\theta}}{\fieldCharacter} = R_{T,\theta}\left(1\right) \cdot \theta\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $\centralCharacter{\Pi}\left(-1\right) = \theta\left(-1\right)$ for every $\Pi$ with $c_{\Pi} \ne 0$,
-	$$c_{\pi} \cdot \dblVirtualJacobiSumScalar{\trace \pi}{\fieldCharacter} = \left(R_{T,\theta}\left(1\right) - \sum_{\substack{\Pi \ne \pi\\
-	c_{\Pi} \ne 0}} c_{\Pi} \dim \Pi\right) \cdot \theta\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $$R_{T,\theta}\left(1\right) = \sum_{\Pi} c_{\Pi} \trace \Pi,$$ it follows that $$\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \centralCharacter{\pi}\left(-1\right) \cdot c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \cdot \tau_{G, \chi, \fieldCharacter}\left(s\right).$$
-	Since $\dblVirtualJacobiSumScalar{\trace \pi}{\chi} = \dim \pi \cdot \dblJacobiSumScalar{\pi}{\chi}$, the result follows.
+\begin{proof}[Proof of \eqref{item:follows-for-cuspidal}]
+By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum_{\pi} c_{\pi} \pi$, 
+$$\sum_{\pi} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum_{\pi} c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$
+Subtracting the equality for non-cuspidal $\pi$ established by (\ref{item:follows-for-non-cuspidal}), we are left with the equality
+$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$
+But by \Cref{prop:at-most-one-cuspidal-lusztig-series} there is at most one cuspidal $\pi$ appearing in our sum.
+Thus the proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} is complete.
 \end{proof}

### 2025-04-08 main.tex
Minor
Distinguishing between virtual representation and its character

@@
 \newcommand{\Kernel}{\operatorname{Ker}}
+\newcommand{\RTTheta}[2]{R_{#1, #2}}
+\newcommand{\RTGTheta}[3]{R_{#1}^{#2}(#3)}
+\newcommand{\RTThetaVirtual}[3]{\mathcal{R}_{#1}^{#2}(#3)}
 
@@
 This is done by combining a couple of ingredients.
-The first ingredient is a lemma of Saito--Shinoda \cite{SaitoShinoda2000} that allows us to explicitly compute the analogous character sums for Deligne--Lusztig virtual representations $R_{T, \theta}$.
+The first ingredient is a lemma of Saito--Shinoda \cite{SaitoShinoda2000} that allows us to explicitly compute the analogous character sums for Deligne--Lusztig virtual representations $\RTTheta{T}{\theta}$.
 The second ingredient, which is a key ingredient for this computation, is that these Jacobi sums are well behaved, in the sense that they are constant on Lusztig series.
@@
 		$$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \cdot \prod_{j=1}^r \GaussSumCharacter{\alpha_j}{\chi}{\fieldCharacter_{n_j}}.$$
-		\item Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $\innerproduct{\trace \tau}{R_{T, \alpha}} \ne 0$ for some maximal torus $T$ of $\GL_n\left(\finiteField\right)$ and some character $\alpha \colon T \to \multiplicativegroup{\cComplex}$.
+		\item Suppose that $\tau$ is an irreducible representation of $\GL_n\left(\finiteField\right)$ such that $\innerproduct{\trace \tau}{\RTTheta{T}{\alpha}} \ne 0$ for some maximal torus $T$ of $\GL_n\left(\finiteField\right)$ and some character $\alpha \colon T \to \multiplicativegroup{\cComplex}$.
 Then $$\GaussSumScalar{\tau \times \chi}{\fieldCharacter} = \left(-1\right)^n \GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter}.$$
@@
 For each maximal rational torus $\algebraicGroup{T}$ in $\algebraicGroup{G}$, Deligne and Lusztig contructed a geometric space with commuting actions of $\algebraicGroup{T}(\finiteField)$ and $\algebraicGroup{G}$.
-The $\ell$-adic \'etale Euler characteristic of this space is a $\algebraicGroup{T}(\finiteField) \times \algebraicGroup{G}(\finiteField)$ virtual representation, and taking the $\algebraicGroup{T}(\finiteField)$ $\theta$-invariants gives a $\algebraicGroup{G}(\finiteField)$ virtual representation $R_T^G(\theta)$.
-The $R_T^G(\theta)$ only depends on the $\algebraicGroup{G}(\finiteField)$-conjugacy class of $(\algebraicGroup{T},\theta)$ and
-the collection of virtual representations $\{R_T^G(\theta)\}$ contain every irreducible $\algebraicGroup{G}(\finiteField)$-representation as a sub-virtual representation.
+The $\ell$-adic \'etale Euler characteristic of this space is a $\algebraicGroup{T}(\finiteField) \times \algebraicGroup{G}(\finiteField)$ virtual representation, and taking the $\left(\algebraicGroup{T}(\finiteField),\theta\right)$-equiviariant subspace gives a $\algebraicGroup{G}(\finiteField)$ virtual representation $\RTThetaVirtual{T}{G}{\theta}$.
+The virtual representation $\RTThetaVirtual{T}{G}{\theta}$ only depends on the $\algebraicGroup{G}(\finiteField)$-conjugacy class of $(\algebraicGroup{T},\theta)$ and
+the collection of virtual representations $\{\RTThetaVirtual{T}{G}{\theta}\}$ contain every irreducible $\algebraicGroup{G}(\finiteField)$-representation as a sub-virtual representation.
+We denote by $\RTGTheta{T}{G}{\theta}$ (and sometimes by $\RTTheta{T}{\theta}$) the virtual character corresponding to the virtual representation $\RTThetaVirtual{T}{G}{\theta}$.
 
@@
 \label{prop:semisimple_pair_with_RTtheta}
-Treating $R_T^G(\theta)$ as a class function of $\algebraicGroup{G}(\finiteField)$ via the character of $R_T^G(\theta)$, for any class function $f$ on $\algebraicGroup{G}(\finiteField)$ which satisfies $f(g) = f(s)$ when $g=su$ is the Jordan decomposition of $g$, we have
+For any class function $f \colon \algebraicGroup{G}(\finiteField) \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $\algebraicGroup{G}\left(\finiteField\right)$) with the property that $f(g)$ only depends on the semisimple part of $g$, that is, $f(g) = f(s)$ where $g=su$ is a Jordan decomposition of $g$, we have
 \[
-	\innerproduct{R_T^G(\theta)}{f}_{\algebraicGroup{G}(\finiteField)} = \innerproduct{\theta}{f\restriction_{\algebraicGroup{T}(\finiteField)}}_{\algebraicGroup{T}(\finiteField)}.
+	\innerproduct{\RTGTheta{T}{G}{\theta}}{f}_{\algebraicGroup{G}(\finiteField)} = \innerproduct{\theta}{f\restriction_{\algebraicGroup{T}(\finiteField)}}_{\algebraicGroup{T}(\finiteField)}.
 \]
@@
 \[
-	\frac{1}{\sizeof{\algebraicGroup{G}(\finiteField)}}\sum_{g \in \algebraicGroup{G}(\finiteField)}\left(R_T^G(\theta)\right)(g)\conjugate{f(g)} = \frac{1}{\sizeof{\algebraicGroup{T}(\finiteField)}}\sum_{t \in  \algebraicGroup{T}(\finiteField)} \theta(t)\conjugate{f(t)}.
+	\frac{1}{\sizeof{\algebraicGroup{G}(\finiteField)}}\sum_{g \in \algebraicGroup{G}(\finiteField)}\left(\RTGTheta{T}{G}{\theta}\right)(g)\conjugate{f(g)} = \frac{1}{\sizeof{\algebraicGroup{T}(\finiteField)}}\sum_{t \in  \algebraicGroup{T}(\finiteField)} \theta(t)\conjugate{f(t)}.
 \]
@@
 
-The virtual representations $R_T^G(\theta)$ and $R_{T'}^G(\theta')$ share an irreducible representation only if $(T,\theta),(T',\theta')$ are geometrically conjugate.
-This yields a natural partitioning of the irreducible representations of $\algebraicGroup{G}(\finiteField)$: the \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $R_{\algebraicGroup{T}, \theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
+The virtual representations $\RTThetaVirtual{T}{G}{\theta}$ and $\RTThetaVirtual{T'}{G}{\theta'}$ share an irreducible subrepresentation only if $(T,\theta),(T',\theta')$ are geometrically conjugate.
+This yields a natural partitioning of the irreducible representations of $\algebraicGroup{G}(\finiteField)$: the \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $\RTTheta{T}{\theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
 
@@
 
-The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual character $R_{T,\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
-
-In this section, we focus on the computing the analogous character sum corresponding to $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for the virtual character $R_{T,\theta}$.
+The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual representation $\RTThetaVirtual{T}{G}{\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
+
+In this section, we focus on the computing the analogous character sum corresponding to $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for the virtual character $\RTTheta{T}{\theta}$.
 
@@
 
-Given a class function $F \colon H \to \cComplex$ (i.e., a function that is invariant under conjugation by elements of $G$), let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right).$$
+Given a class function $F \colon H \to \cComplex$, let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right).$$
 
@@
 	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{H}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
+	$$ \dblVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
 \end{proposition}
-In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} R_{T, \theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
+In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \RTTheta{T}{\theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
 $$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
@@
 	\begin{align*}
-		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter},
+		 \dblPosVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} = \RTTheta{T}{\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter},
 	\end{align*}
 	and \begin{align*}
-		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \begin{dcases}
+		\dblNegVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} = \begin{dcases}
 			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd,}\\
-			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \theta\left(-1\right) & \text{ otherwise.}
+			\dblPosVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} \cdot \theta\left(-1\right) & \text{ otherwise.}
 		\end{dcases}
@@
 
-	Hence our theorem follows from the results mentioned above and from the formula $$R_T\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
+	Hence our theorem follows from the results mentioned above and from the formula $$\RTTheta{T}{\theta}\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
 	the fact that \begin{equation*}
@@
 \begin{remark}
-	Suppose that $\pi$ is any irreducible representation of $H$ such that $\trace \pi$ appears with non-zero coefficient in $R_{T,\theta}$. Then the central character of $\pi$ satisfies
+	Suppose that $\pi$ is any irreducible representation of $H$ such that $\pi$ appears as a subrepresentation of $\RTThetaVirtual{T}{H}{\theta}$. Then the central character of $\pi$ satisfies
 	\begin{align*}
@@
 	Thus \begin{align*}
-		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} =& R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_{T'}\left(\chi, \theta', \fieldCharacter\right).
+		\dblNegVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} =& \RTTheta{T}{\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_{T'}\left(\chi, \theta', \fieldCharacter\right).
 	\end{align*}
@@
 
-\subsection{Invariance of $\innerproduct{\genHermitianJacobiKernel{\hermitianSpace}{\chi}}{R_{T,\theta}}$ under geometric conjugacy}
+\subsection{Invariance of $\innerproduct{\genHermitianJacobiKernel{\hermitianSpace}{\chi}}{\RTTheta{T}{\theta}}$ under geometric conjugacy}
 
@@
 \label{lem:indep_geo_conj}
-    If $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}}{R_{T,\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{R_{T', \theta'}}{\chi}}{R_{T',\theta'}(1)}.$$
+    If $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi}}{\RTTheta{T}{\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{\RTTheta{T'}{\theta'}}{\chi}}{\RTTheta{T'}{\theta'}\left(1\right)}.$$
 \end{lemma}
 
-We recall\[
+We recall that \[
 	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
 \]
-with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ Thus we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \algebraicGroup{\GL}_n(\finiteFieldExtension{m})$ via the first coordinate $g_0$.
+with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \algebraicGroup{\GL}_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
 
@@
 \[
-    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = q^{-(nm)/2}\epsilon_{\Tilde{\algebraicGroup{T}}}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}(\det(t)) \psi(\trace(t)).
+    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = \epsilon_{\Tilde{\algebraicGroup{T}}} q^{-nm/2}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}({\det}_{\finiteFieldExtension{m}}t) \psi(\trace_{\finiteFieldExtension{m}}t).
 \]
 \calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$? \elad{$q^{-nm/2}$}}
-Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters and $\chi_0 \circ \det \colon \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) \to \multiplicativegroup{\cComplex}$ is given by $$\left(\chi \circ \det\right)\left(g_0,\dots,g_{m-1}\right) = \chi\left(\det g_0\right)$$ \elad{This is weird.
-Maybe we should just say that we identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteField\right) = \GL_n\left(\finiteFieldExtension{m}\right)$ by $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$?}\calvin{yeah that makes sense}.
+Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters.
 The following lemma shows that this is well defined.
@@
 \begin{enumerate}[(i)]
-	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case $\rho$ is the identity, $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s_{\algebraicGroup{T},\theta})$ and the character $\chi$.
-	\item $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined i.e. independent of choice of $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and conjugacy class representative $w$.
+	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case that $\rho$ is the identity map, $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s_{\algebraicGroup{T},\theta})$ and the character $\chi$.
+	\item The value $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined, i.e., independent of choice of $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and the conjugacy class representative $w$.
 \end{enumerate}
@@
 	\]
-	where $\tau$ is any subrepresentation of $R_{T,\theta}$.
+	where $\tau$ is any irreducible subrepresentation of $\RTThetaVirtual{T}{\GL_n\left(\finiteField\right)}{\theta}$.
 By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$.
@@
 
-The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.
+The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi}/\RTTheta{T}{\theta}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.
 
@@
 \calvin{start alternate writeup 2 of section 3.4/3.4.1}
-\subsection{Stability (one option)}\label{subsec:stability}
-The goal of this section is to compute $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ proving \Cref{thm:Phi_stable}:
+\subsection{Stability}\label{subsec:stability}
+The goal of this section is to compute $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ proving \Cref{thm:Phi_stable}.
+
 \begin{theorem}
-\label{thm:doubling-method-gamma-factor-for-deligne-lusztig} For either $G=G$ or its extension $\GroupExtension{G}$.
-If $c_{\pi}$ is nonzero in the virtual representation $R_T(\theta) = \sum c_{\pi} \pi$ then
+\label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
+Let $H \in \{G, \GroupExtension{G}\}$.  If $c_{\pi}$ is non-zero in the virtual representation $\RTThetaVirtual{T}{G}{\theta} = \sum_{\pi} c_{\pi} \pi$ then
 $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\chi,\theta|_{T \cap G}, \fieldCharacter\right)$$
@@
 Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that each $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ is an irreducible subrepresentation of the restriction to $G$ of some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$.
-Thus \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $G$ follows from \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.
+It thus suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.
 
@@
 \begin{proof}[Proof of \eqref{item:follows-for-cuspidal}]
-By \Cref{lem:indep_geo_conj}, we know that for $R_T(\theta) = \sum_{\pi} c_{\pi} \pi$, 
+By \Cref{lem:indep_geo_conj}, we know that for $\RTThetaVirtual{T}{G}{\theta} = \sum_{\pi} c_{\pi} \pi$, 
 $$\sum_{\pi} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum_{\pi} c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$

### 2025-04-08 main.tex
T and T_H business...

@@
 
-The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual representation $\RTThetaVirtual{T}{G}{\theta}$ for a suitable maximal torus $T$ and $\theta \colon T \to \multiplicativegroup{\cComplex}$.
-
-In this section, we focus on the computing the analogous character sum corresponding to $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for the virtual character $\RTTheta{T}{\theta}$.
+The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual representation $\RTThetaVirtual{T}{H}{\theta_H}$ for a suitable maximal torus $T_H$ and $\theta_H \colon T_H \to \multiplicativegroup{\cComplex}$.
+
+In this section, we focus on the computing the analogous character sum corresponding to $\dblJacobiSumScalar{\pi}{\fieldCharacter}$ for the virtual character $\RTGTheta{T_H}{H}{\theta_H}$.
 
@@
 
-Given a class function $F \colon H \to \cComplex$, let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right).$$
+Given a class function $F \colon H \to \cComplex$, let us define $$\dblVirtualJacobiSumScalar{F}{\chi} = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in H} F\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right) =  \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} F\left(g\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g\right).$$
 
@@
 \begin{proposition}\label{prop:reduction-of-gauss-sum-to-torus}
-	For any $\Frobenius$-stable maximal torus $\algebraicGroup{T}$ of $\algebraicGroup{H}$, and any character $\theta \colon T \to \multiplicativegroup{\cComplex}$, where $T = \algebraicGroup{T}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
+	For any $\Frobenius$-stable rational maximal torus $\algebraicGroup{T}_{\algebraicGroup{H}}$ of $\algebraicGroup{H}$, and any character $\theta_{H} \colon T_{H} \to \multiplicativegroup{\cComplex}$, where $T_H = \algebraicGroup{T}_{\algebraicGroup{H}}^{\Frobenius}$, we have
+	$$ \dblVirtualJacobiSumScalar{\RTTheta{T_H}{\theta_H}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T_H} \theta_H\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
 \end{proposition}
-In the special case that $\theta$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \RTTheta{T}{\theta}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
-$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T} \theta\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
-Here $\varepsilon_{\algebraicGroup{H}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{H}}$ and $\varepsilon_{\algebraicGroup{T}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}}$, and $\sizeof{H}_p$ is the size of the $p$-Sylow group of $H$, where $p$ is the characteristic of $\finiteField$.
+In the special case that $\theta_H$ is in general position, the virtual character $\varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \RTTheta{T_H}{\theta_H}$ equals $\trace \pi$ for some irreducible representation $\pi$ of $H$ and we have that for this $\pi$,
+$$\dblJacobiSumScalar{\pi}{\chi} = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \frac{\sizeof{H}_p}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T_H} \theta_H\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
+Here $\varepsilon_{\algebraicGroup{H}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{H}}$ and $\varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} = \left(-1\right)^{\mathrm{rel.rank} \algebraicGroup{T}_{\algebraicGroup{H}}}$ \elad{These should probably be introduced earlier in the article}, and $\sizeof{H}_p$ is the size of the $p$-Sylow group of $H$, where $p$ is the characteristic of $\finiteField$.
 
@@
 \begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
-	Suppose that $\algebraicGroup{T}_{\algebraicGroup{H}}$ is a maximal rational torus of $\algebraicGroup{H}$ that corresponds to the pair of partitions $\left(\lambda^+, \lambda^-\right)$ and let $\algebraicGroup{T}_{\algebraicGroup{G}} \coloneq \algebraicGroup{G} \cap \algebraicGroup{T}_{\algebraicGroup{H}}$ and $T = T_G = \algebraicGroup{T}_{\algebraicGroup{G}}^{\Frobenius}$.
-Suppose that $\theta_{H} \colon \algebraicGroup{T}_{\algebraicGroup{H}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ is a character and let $$\theta = \theta_{\algebraicGroup{G}} \coloneq \theta_{\algebraicGroup{H}} \restriction_{T_G} \colon T_G \to \multiplicativegroup{\cComplex}.$$ Then
-	\begin{align*}
-		 \dblPosVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} = \RTTheta{T}{\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter},
+	Suppose that $\algebraicGroup{T}_{\algebraicGroup{H}}$ is a maximal rational torus of $\algebraicGroup{H}$ that corresponds to the pair of partitions $\left(\lambda^+, \lambda^-\right)$ and let $\algebraicGroup{T}_{\algebraicGroup{G}} \coloneq \algebraicGroup{G} \cap \algebraicGroup{T}_{\algebraicGroup{H}}$.
+Denote $T_H = \algebraicGroup{T}_{\algebraicGroup{H}}^{\Frobenius}$ and $T = T_G = \algebraicGroup{T}_{\algebraicGroup{G}}^{\Frobenius}$.
+Suppose that $\theta_{H} \colon T_H \to \multiplicativegroup{\cComplex}$ is a character and let $$\theta = \theta_{G} \coloneq \theta_{H} \restriction_{T_G} \colon T_G \to \multiplicativegroup{\cComplex}.$$ Then
+	\begin{align*}
+		 \dblPosVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi} = \RTGTheta{T_H}{H}{\theta_H}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter},
 	\end{align*}
 	and \begin{align*}
-		\dblNegVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} = \begin{dcases}
+		\dblNegVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi} = \begin{dcases}
 			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd,}\\
-			\dblPosVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} \cdot \theta\left(-1\right) & \text{ otherwise.}
+			\dblPosVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi} \cdot \theta\left(-1\right) & \text{ otherwise.}
 		\end{dcases}
@@
 
-	Hence our theorem follows from the results mentioned above and from the formula $$\RTTheta{T}{\theta}\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \frac{\grpIndex{H}{T}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
+	Hence our theorem follows from the results mentioned above and from the formula $$\RTGTheta{T_H}{H}{\theta_H}\left(1\right) = \varepsilon_{\algebraicGroup{H}} \varepsilon_{\algebraicGroup{T}_{\algebraicGroup{H}}} \frac{\grpIndex{H}{T_H}}{\sizeof{H}_p},$$ the fact that $$ \sizeof{\lieAlgebra} = \sizeof{H}_p^2 \cdot q^{\left\lfloor\frac{\dim_{\finiteField} \hermitianSpace}{2}\right\rfloor},$$
 	the fact that \begin{equation*}
@@
 \begin{remark}
-	Suppose that $\pi$ is any irreducible representation of $H$ such that $\pi$ appears as a subrepresentation of $\RTThetaVirtual{T}{H}{\theta}$. Then the central character of $\pi$ satisfies
+	Suppose that $\pi$ is any irreducible representation of $H$ such that $\pi$ appears as a subrepresentation of $\RTThetaVirtual{T_H}{H}{\theta_H}$. Then the central character of $\pi$ satisfies
 	\begin{align*}
@@
 	Thus \begin{align*}
-		\dblNegVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi} =& \RTTheta{T}{\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) g_{T'}\left(\chi, \theta', \fieldCharacter\right).
+		\dblNegVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi} =& \RTTheta{T_H}{H}{\theta_H}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.
 	\end{align*}
@@
 	where $\tau$ is any irreducible subrepresentation of $\RTThetaVirtual{T}{\GL_n\left(\finiteField\right)}{\theta}$.
-By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ hence the semisimple conjugacy class of $(s_{T,\theta})$.
+By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ and hence on the semisimple conjugacy class of $(s_{T,\theta})$.
 	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
@@
 \label{thm:doubling-method-gamma-factor-for-deligne-lusztig}
-Let $H \in \{G, \GroupExtension{G}\}$.  If $c_{\pi}$ is non-zero in the virtual representation $\RTThetaVirtual{T}{G}{\theta} = \sum_{\pi} c_{\pi} \pi$ then
-$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = g_{T \cap G}\left(\chi,\theta|_{T \cap G}, \fieldCharacter\right)$$
+Let $H \in \{G, \GroupExtension{G}\}$.
+Using the same notation as in \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}, if $\pi$ is an irreducible representation of $H$ that appears as a subrepresentation of the virtual representation $\RTThetaVirtual{T_H}{H}{\theta_{H}}$ then \begin{equation}\label{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift}
+	\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.
+\end{equation}
 \end{theorem}
-\calvin{add in $\chi$} the right hand side of which we showed in \Cref{lem:indep_geo_conj} only depends on the geometric conjugacy class of $(T,\theta)$ hence on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$, implying \Cref{thm:Phi_stable}.
+Recall that in \Cref{lem:indep_geo_conj}, we showed that the right hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} only depends on the geometric conjugacy class of $(T,\theta)$ and hence only on the Lusztig series $\LusztigSeries{G}{s}$ which contains $\pi$, implying \Cref{thm:Phi_stable}.
 
@@
 \subsubsection{Proof of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig}}
-We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $G$ has connected center.
+We first reduce \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} to the case $H = \GroupExtension{G}$.
+We start with the following observation.
 Suppose that $\tilde{\pi}$ is an irreducible representation of $\GroupExtension{G}$ and that $\pi$ is an irreducible representation of $G$ that appears as a subrepresentation of the restriction of $\tilde{\pi}$ to $G$.
-Then since $\dblJacobiSum{\tilde{\pi}}{\chi}$ and $\dblJacobiSum{\pi}{\chi}$ are scalar operators and the restriction of $\dblJacobiSum{\tilde{\pi}}{\chi}$ to $\pi$ is $\dblJacobiSum{\pi}{\chi}$, we have that $$\dblJacobiSumScalar{\pi}{\chi} = \dblJacobiSumScalar{\tilde{\pi}}{\chi}$$ and thus
+Then since $\dblJacobiSum{\tilde{\pi}}{\chi}$ and $\dblJacobiSum{\pi}{\chi}$ are scalar operators and the restriction of $\dblJacobiSum{\tilde{\pi}}{\chi}$ to the subspace $\pi$ is $\dblJacobiSum{\pi}{\chi}$, we have that $$\dblJacobiSumScalar{\pi}{\chi} = \dblJacobiSumScalar{\tilde{\pi}}{\chi}$$ and thus
 $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\tilde{\pi}}{\chi}{\fieldCharacter}.$$
 
-Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that each $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$ is an irreducible subrepresentation of the restriction to $G$ of some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$.
+Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that for every $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$, the exists some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction to $G$ of $\tilde{\pi}$.
 It thus suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.
@@
 \begin{proof}[Proof of \eqref{item:follows-for-non-cuspidal}]
-	Since every proper parabolic subgroup of $H = \GroupExtension{G}$ is contained in a proper parabolic subgroup group with Levi part of the form $\GL_n\left(\quadraticExtension\right) \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
+	We will show that both sides of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} have a multiplicativity property.
+Since every proper parabolic subgroup of $H = \GroupExtension{G}$ is contained in a proper parabolic subgroup group with Levi part of the form $\GL_n\left(\quadraticExtension\right) \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
 
 	For the right hand side, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
-		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{(s)}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\pi}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
+		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{(s)}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\sigma}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
 		\algebraicGroup{L}^{\Frobenius}}{(s)}$.
@@
 \begin{proof}[Proof of \eqref{item:follows-for-cuspidal}]
-By \Cref{lem:indep_geo_conj}, we know that for $\RTThetaVirtual{T}{G}{\theta} = \sum_{\pi} c_{\pi} \pi$, 
-$$\sum_{\pi} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = (\sum_{\pi} c_{\pi})g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$
+By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and \Cref{lem:indep_geo_conj}, we have that if $\RTThetaVirtual{T_H}{H}{\theta_H} = \sum_{\pi} c_{\pi} \pi$, where $\pi$ goes over all the irreducible representations of $H$ and $c_{\pi} \in \zIntegers$, then
+$$\sum_{\pi} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \RTGTheta{T_H}{H}{\theta_H}\left(1\right) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \left(\sum_{\pi} c_{\pi}\right).$$
 Subtracting the equality for non-cuspidal $\pi$ established by (\ref{item:follows-for-non-cuspidal}), we are left with the equality
-$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)g_{T \cap G}\left(\theta|_{T \cap G}, \fieldCharacter\right).$$
+$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)\GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.$$
 But by \Cref{prop:at-most-one-cuspidal-lusztig-series} there is at most one cuspidal $\pi$ appearing in our sum.

### 2025-04-08 main.tex
T => T_H

@@
 \begin{proof}[Proof of \eqref{item:follows-for-non-cuspidal}]
-	We will show that both sides of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} have a multiplicativity property.
-Since every proper parabolic subgroup of $H = \GroupExtension{G}$ is contained in a proper parabolic subgroup group with Levi part of the form $\GL_n\left(\quadraticExtension\right) \times H'$ where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
-
-	For the right hand side, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
+	We will show that both sides of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} satisfy a multiplicativity property.
+Since every proper parabolic subgroup of $H = \GroupExtension{G}$ is contained in a proper maximal parabolic subgroup group with Levi part of the form $L = \GL_k\left(\quadraticExtension\right) \times H'$, where $H'$ is as in \Cref{subsec:multiplicativity}, the multiplicativity of the left hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift} follows from \Cref{thm:multiplicativity-in-terms-of-gamma-factors}.
+
+	For the right hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift}, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
 		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{(s)}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\sigma}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
@@
 
-	Thus if $\pi$ is a subrepresentation of a parabolically induced representation as above, then $(T_H,\theta_H)$ is geometrically conjugate to $(T_1 \times T_2,\theta_1 \times \theta_2)$ for $T_1 \times T_2$ a torus of $L$.
-As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}(\chi,\theta|_{T \cap G},\psi) = g_{(T_1 \times T_2) \cap G}(\chi,\left(\theta_1\times \theta_2\right)|_{(T_1 \times T_2) \cap G},\psi).$$ The right hand of the above is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
+	Thus if $\pi$ is a subrepresentation of a parabolically induced representation as above, then $(T_H,\theta_H)$ is geometrically conjugate to $(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}, \theta_{\GL_k\left(\quadraticExtension\right)} \times \theta_{H'})$ for $T_{\GL_k\left(\quadraticExtension\right)} \times H'$ a torus of $L = \GL_k\left(\quadraticExtension\right) \times H'$.
+As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}\left(\chi,\theta\restriction_{T \cap G},\psi\right) = g_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H}'\right) \cap G}\left(\chi,\left(\theta_{\GL_k\left(\quadraticExtension\right)}\times \theta_{H'}\right)\restriction_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}\right) \cap G},\psi\right).$$ The right hand of the last equality is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
 \end{proof}
 \begin{proof}[Proof of \eqref{item:follows-for-cuspidal}]
-By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and \Cref{lem:indep_geo_conj}, we have that if $\RTThetaVirtual{T_H}{H}{\theta_H} = \sum_{\pi} c_{\pi} \pi$, where $\pi$ goes over all the irreducible representations of $H$ and $c_{\pi} \in \zIntegers$, then
+By \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} and \Cref{lem:indep_geo_conj}, we have that if $\RTThetaVirtual{T_H}{H}{\theta_H} = \sum_{\pi} c_{\pi} \pi$, where $\pi$ goes over all (equivalence classes of) irreducible representations of $H$ and $c_{\pi} \in \zIntegers$, then
 $$\sum_{\pi} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \RTGTheta{T_H}{H}{\theta_H}\left(1\right) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \left(\sum_{\pi} c_{\pi}\right).$$

### 2025-04-08 main.tex
Moving section about gamma factors

@@
 
-\subsubsection{Gamma factors}\label{subsec:normalization-factor}
-In order to make the computations more tolerable, it is beneficial to work with fully multiplicative functions. We introduce the doubling method gamma factors.
-
-Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex}$ be a character.
-
-We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
-	\left(-\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
-	\chi\left(2\right) \left(-\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
-	\left(-\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
-\end{dcases}$$
-Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}^{2} = \GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}} {\fieldCharacter_{\quadraticExtension}}$.
-
-For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\Contragradient{\tau} \times \involution{\chi}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
-For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
-
-Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
-
-\begin{theorem}\label{thm:multiplicativity-in-terms-of-gamma-factors}
-	\begin{enumerate}
-		\item If $\tau_1$ and $\tau_2$ are irreducible representations of $\GL_{k_1}\left(\finiteField\right)$ and $\GL_{k_2}\left(\finiteField\right)$, respectively, then for any irreducible subrepresentation $\tau$ of the parabolic induction $\tau_1 \circ \tau_2$, we have
-		$$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \dblGammaFactor{\tau_1}{\chi}{\fieldCharacter} \dblGammaFactor{\tau_2}{\chi}{\fieldCharacter}.$$
-		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\involutionPlusOne{\chi} \ne 1$, then
-		$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \dblGammaFactor{\tau}{\chi}{\fieldCharacter}.$$
-	\end{enumerate}
-\end{theorem}
-
-\begin{remark}
-	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
-				1 & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
-				-\GaussSumSingleCharacter{\chi} {\fieldCharacter} & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
-				\left(-1\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \text{otherwise.}
-	\end{dcases}$$
-	However, we will not need this version for our purposes. \elad{Maybe this is the better version for Calvin's computations}
-\end{remark}
-
 \subsection{Pairing with Deligne--Lusztig characters}
-\calvin{old title: Computation of character sums attached to Deligne--Lusztig data}
 
@@
 Combining this with the fact that $\left(\theta'\right)^{-1} = \left(\theta'\right)^{q^m}$ lies in the same Frobenius orbit as $\theta'$, we get the following theorem.
-\begin{theorem}
+\begin{theorem}\label{thm:computation-norm-one-case}
 	We have the identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
@@
 Thus, we obtained the following.
-\begin{theorem}
+\begin{theorem}\label{thm:computation-unitary-norm-one-case}
 	We have the following identity $$\sum_{\substack{x \in \NormOneGroup{2m}\\
@@
 \end{theorem}
+
+\subsubsection{Gamma factors}\label{subsec:normalization-factor}
+The multiplicativity property (\Cref{thm:multiplicativity-in-terms-of-gauss-sums}) and the computations performed above (Theorems \ref{thm:split-case-deligne-lusztig-computation}-\ref{thm:computation-unitary-norm-one-case}) suggest to normalize our Jacobi sums correctly so that they will satisfy a full multiplicativity property.
+
+Let $\chi \colon \multiplicativegroup{\quadraticExtension} \to \multiplicativegroup{\cComplex} $ be a character.
+We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
+	\left(-\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
+	\chi\left(2\right) \left(-\GaussSumSingleCharacter{\chi^{-2}}{\fieldCharacter}\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
+	\left(-\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
+\end{dcases}$$
+Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\GaussSumSingleCharacter{\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}}{\fieldCharacter}^{2} = \GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}} {\fieldCharacter_{\quadraticExtension}}$.
+The factor on the left hand side appears in \Cref{thm:computation-unitary-norm-one-case}, while the one on the right hand side appears in \Cref{thm:multiplicativity-in-terms-of-gauss-sums}.
+
+For an irreducible representation $\tau$ of $\GL_k\left(\quadraticExtension\right)$ define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\Contragradient{\tau} \times \involution{\chi}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
+For an irreducible representation $\pi$ of $H$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
+
+Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.
+
+\begin{theorem}\label{thm:multiplicativity-in-terms-of-gamma-factors}
+	\begin{enumerate}
+		\item If $\tau_1$ and $\tau_2$ are irreducible representations of $\GL_{k_1}\left(\finiteField\right)$ and $\GL_{k_2}\left(\finiteField\right)$, respectively, then for any irreducible subrepresentation $\tau$ of the parabolic induction $\tau_1 \circ \tau_2$, we have
+		$$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \dblGammaFactor{\tau_1}{\chi}{\fieldCharacter} \dblGammaFactor{\tau_2}{\chi}{\fieldCharacter}.$$
+		\item If $\tau$, $\pi'$ and $\pi$ are as in \Cref{thm:multiplicativity-in-terms-of-gauss-sums} and $\involutionPlusOne{\chi} \ne 1$, then
+		$$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace'}{\pi'}{\chi}{\fieldCharacter} \dblGammaFactor{\tau}{\chi}{\fieldCharacter}.$$
+	\end{enumerate}
+\end{theorem}
+
+\begin{remark}
+	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
+		1 & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
+		-\GaussSumSingleCharacter{\chi} {\fieldCharacter} & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
+		\left(-1\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \text{otherwise.}
+	\end{dcases}$$
+	However, we will not need this version for our purposes. \elad{Maybe this is the better version for Calvin's computations}
+\end{remark}
 
@@
 Subtracting the equality for non-cuspidal $\pi$ established by (\ref{item:follows-for-non-cuspidal}), we are left with the equality
-$$ \sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right)\GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.$$
+$$\sum_{\pi \textnormal{ cuspidal}} c_{\pi} \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \left(\sum_{\pi \textnormal{ cuspidal}} c_{\pi}\right).$$
 But by \Cref{prop:at-most-one-cuspidal-lusztig-series} there is at most one cuspidal $\pi$ appearing in our sum.

### 2025-04-08 main.tex
\theta_H

@@
 	Thus if $\pi$ is a subrepresentation of a parabolically induced representation as above, then $(T_H,\theta_H)$ is geometrically conjugate to $(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}, \theta_{\GL_k\left(\quadraticExtension\right)} \times \theta_{H'})$ for $T_{\GL_k\left(\quadraticExtension\right)} \times H'$ a torus of $L = \GL_k\left(\quadraticExtension\right) \times H'$.
-As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}\left(\chi,\theta\restriction_{T \cap G},\psi\right) = g_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H}'\right) \cap G}\left(\chi,\left(\theta_{\GL_k\left(\quadraticExtension\right)}\times \theta_{H'}\right)\restriction_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}\right) \cap G},\psi\right).$$ The right hand of the last equality is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
+As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}\left(\chi,\theta_H\restriction_{T \cap G},\psi\right) = g_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H}'\right) \cap G}\left(\chi,\left(\theta_{\GL_k\left(\quadraticExtension\right)}\times \theta_{H'}\right)\restriction_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}\right) \cap G},\psi\right).$$ The right hand of the last equality is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
 \end{proof}

### 2025-04-08 main.tex
Minors

@@
 \begin{enumerate}[(a)]
-	\item \label{item:follows-for-non-cuspidal}If for all representations with $\dim_{\mathbb{E}} V < n$, \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$.
-	\item \label{item:follows-for-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$, then it holds for all irreducible cuspidal representations of $H$ with $\dim_{\mathbb{E}} V = n$.
+	\item \label{item:follows-for-non-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all representations of $H'$ where $H'$ corresponds to $\left(\hermitianSpace', \innerproduct{\cdot}{\cdot}\right)$ with $\dim_{\quadraticExtension} V' < n$, then \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$ with $\dim_{\mathbb{E}} V = n$.
+	\item \label{item:follows-for-cuspidal}If \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} holds for all non-cuspidal irreducible representations of $H$, then it holds for all irreducible cuspidal representations of $H$.
 \end{enumerate}
@@
 
-Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that for every $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$, the exists some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction to $G$ of $\tilde{\pi}$.
-It thus suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $\GroupExtension{G}$.
+Since the map $\algebraicGroup{\GroupExtension{G}}^*(\finiteField) \to \algebraicGroup{G}^*(\finiteField)$ is surjective \calvin{check this!}, by \Cref{prop:lusztig-series-and-restriction} there exists $\tilde{s}$ depending on $s$ such that for every $\pi \in \LusztigSeries{\FrobeniusFixedPoints{G}}{s}$, there exists some $\tilde{\pi} \in \LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{\tilde{s}}$ such that $\pi$ is an irreducible subrepresentation of the restriction of $\tilde{\pi}$ to $G$.
+It thus suffices to prove \Cref{thm:doubling-method-gamma-factor-for-deligne-lusztig} for $H = \GroupExtension{G}$.
 
@@
 	For the right hand side of \eqref{eq:doubling-method-gamma-factor-is-gauss-sum-of-functorial-lift}, first \Cref{prop:lusztig-series-are-unions-of-harish-chandra-series} tells us that if $\pi \in \LusztigSeries{
-		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{(s)}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\sigma}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
-		\algebraicGroup{L}^{\Frobenius}}{(s)}$.
+		\GroupExtension{\algebraicGroup{G}}^{\Frobenius}}{s}$ is a subrepresentation of the parabolically induced representation $\Ind{H}{G}{\sigma}$ where $\sigma$ is an irreducible representation of the Levi part $L$ of $P$, then $\sigma \in \LusztigSeries{
+		\algebraicGroup{L}^{\Frobenius}}{s}$.
 

### 2025-04-08 main.tex
Remove algebraic group

@@
 \]
-with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \algebraicGroup{\GL}_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
+with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \GL_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
 

### 2025-04-08 main.tex
Torus

@@
 
-Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal tori $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subseteq \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 Define

### 2025-04-09 main.tex
Typo
Add comment about the factor \chi(2)
Changes with Calvin

@@
 This is done by combining a couple of ingredients.
-The first ingredient is a lemma of Saito--Shinoda \cite{SaitoShinoda2000} that allows us to explicitly compute the analogous character sums for Deligne--Lusztig virtual representations $\RTTheta{T}{\theta}$.
+The first ingredient is a lemma of Saito--Shinoda \cite{SaitoShinoda2000} that allows us to explicitly compute the analogous character sums for Deligne--Lusztig virtual representations $\RTThetaVirtual{T}{G}{\theta}$.
 The second ingredient, which is a key ingredient for this computation, is that these Jacobi sums are well behaved, in the sense that they are constant on Lusztig series.
@@
 
-Given a torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
+Given a maximal torus $T \subset \GL_n\left(\finiteField\right)$ of the form $T \cong \multiplicativegroup{\finiteFieldExtension{\lambda}}$ where $\lambda \vdash n$ is a partition and given characters $\alpha \colon \multiplicativegroup{\finiteFieldExtension{\lambda}} \to \multiplicativegroup{\cComplex}$ and $\chi \colon T \to \multiplicativegroup{\cComplex}$, we define $$\GaussSumTorusCharacter{T}{\alpha}{\chi}{\fieldCharacter} = \left(-1\right)^{\lengthof\left(\lambda\right)} q^{-\frac{n}{2}} \sum_{t \in T} \alpha^{-1}\left(t\right) \chi^{-1}\left(\det t\right) \fieldCharacter\left(\trace t\right).$$
 We also define $$\GaussSumSingleTorusCharacter{T}{\alpha}{\fieldCharacter} = \GaussSumTorusCharacter{T}{\alpha}{1}{\fieldCharacter}.$$
@@
 
+\subsubsection{Algebraic groups}
+\elad{Tell the reader that the notation $\algebraicGroup{G}$ refers to an algebraic group, which can be thought of as the $\algebraicClosure{\finiteField}$ points of a variety over $\finiteField$ with an action of $\Frobenius$}
+
 \subsubsection{$\epsilon$-sesquilinear spaces}
@@
 \end{pmatrix} \in \GL_n\left(\finiteField\right)$$ be the longest Weyl element.
-\calvin{we should standardize an order between Unitary, Special Orthogonal Symplectic and try to kinda stick with it throughout.}
 \begin{enumerate}
+	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
+Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
+In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
 	\item (Special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.
@@
 	\end{pmatrix}\right\}.$$
-	\item (Unitary groups): $\quadraticExtension \ne \finiteField$.
-Denote $\dim_{\quadraticExtension} \hermitianSpace = n$.
-In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
 \end{enumerate}
@@
 
-The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual representation $\RTThetaVirtual{T}{H}{\theta_H}$ for a suitable maximal torus $T_H$ and $\theta_H \colon T_H \to \multiplicativegroup{\cComplex}$.
+The goal of the next two sections is to compute $\dblJacobiSumScalar{\pi}{\chi}$ for $\pi$ that appears in a Deligne--Lusztig virtual representation $\RTThetaVirtual{T_H}{H}{\theta_H}$ for a suitable maximal torus $T_H$ and $\theta_H \colon T_H \to \multiplicativegroup{\cComplex}$.
 
@@
 The factor on the left hand side appears in \Cref{thm:computation-unitary-norm-one-case}, while the one on the right hand side appears in \Cref{thm:multiplicativity-in-terms-of-gauss-sums}.
+The factor $\chi\left(2\right)$ in the odd-dimensional special orthogonal case will be explained in the proof of \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}.
 
@@
 	Thus \begin{align*}
-		\dblNegVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi} =& \RTTheta{T_H}{H}{\theta_H}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.
+		\dblNegVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi} =& \RTGTheta{T_H}{H}{\theta_H}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) \centralCharacter{\pi}\left(-1\right) \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.
 	\end{align*}
@@
 
-	Thus if $\pi$ is a subrepresentation of a parabolically induced representation as above, then $(T_H,\theta_H)$ is geometrically conjugate to $(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}, \theta_{\GL_k\left(\quadraticExtension\right)} \times \theta_{H'})$ for $T_{\GL_k\left(\quadraticExtension\right)} \times H'$ a torus of $L = \GL_k\left(\quadraticExtension\right) \times H'$.
-As proved in \Cref{lem:indep_geo_conj}, $$g_{T \cap G}\left(\chi,\theta_H\restriction_{T \cap G},\psi\right) = g_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H}'\right) \cap G}\left(\chi,\left(\theta_{\GL_k\left(\quadraticExtension\right)}\times \theta_{H'}\right)\restriction_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}\right) \cap G},\psi\right).$$ The right hand of the last equality is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
+	Thus if $\pi$ is a subrepresentation of a parabolically induced representation as above, then $(T_H,\theta_H)$ is geometrically conjugate to $(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}, \theta_{\GL_k\left(\quadraticExtension\right)} \times \theta_{H'})$ for $T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}$ a torus of $L = \GL_k\left(\quadraticExtension\right) \times H'$.
+As proved in \Cref{lem:indep_geo_conj}, $$g_{T}\left(\chi,\theta_H\restriction_{T \cap G},\psi\right) = g_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H}'\right) \cap G}\left(\chi,\left(\theta_{\GL_k\left(\quadraticExtension\right)}\times \theta_{H'}\right)\restriction_{\left(T_{\GL_k\left(\quadraticExtension\right)} \times T_{H'}\right) \cap G},\psi\right).$$ The right hand of the last equality is multiplicative since Gauss sums are multiplicative by \eqref{eq:Gauss_multiplicitive}.
 \end{proof}

### 2025-04-09 main.tex
alg groups section (missing citation)

@@
 
-\subsubsection{Algebraic groups}
+\subsubsection{Algebraic groups over finite fields}
 \elad{Tell the reader that the notation $\algebraicGroup{G}$ refers to an algebraic group, which can be thought of as the $\algebraicClosure{\finiteField}$ points of a variety over $\finiteField$ with an action of $\Frobenius$}
+Each of our classical groups $G$ in the proceeding sections are defined by polynomial equations in entries in a matrix which yield an \emph{algebraic group}-an algebraic variety with a group structure (see cite something).
+We will denote the algebraic group by the bold $\algebraicGroup{G}$. 
+It can be thought of as its $\algebraicClosure{\finiteField}$ points together with an action of $\Frobenius$ on these points whose fixed points is $\algebraicGroup{G}(\finiteField)$. 
+Thus we will often denote $\algebraicGroup{G}(\finiteField)$ by $\algebraicGroup{G}^{\Frobenius}$ or just by the non-bold $G$.
 

### 2025-04-09 main.tex
Adding reference to Digne-Michel

--- 2025-04-09 main.tex
@@
 
-\subsubsection{Algebraic groups}
-\elad{Tell the reader that the notation $\algebraicGroup{G}$ refers to an algebraic group, which can be thought of as the $\algebraicClosure{\finiteField}$ points of a variety over $\finiteField$ with an action of $\Frobenius$}
+\subsubsection{Algebraic groups over finite fields}
+Each of our classical groups $G$ in the proceeding sections are defined by polynomial equations in entries of a matrix which yield an \emph{affine algebraic group}, that is, an affine algebraic variety with a group structure (see \cite[Section 0]{DigneMichel1991}).
+We will denote the algebraic group by the bold symbol $\algebraicGroup{G}$. 
+It can be thought of as its $\algebraicClosure{\finiteField}$ points together with an action of $\Frobenius$ on these points whose fixed points is $\algebraicGroup{G}(\finiteField)$. 
+Thus we will often denote $\algebraicGroup{G}(\finiteField)$ by $\algebraicGroup{G}^{\Frobenius}$ or just by the non-bold symbol $G$.
 

### 2025-04-09 main.tex
Explaining a bit what restriction of scalars is

@@
 In this case, the group $G = \GroupExtension{G}$ is isomorphic to the group $\UnitaryGroup_n\left(\finiteField\right) \subset\GL_{n}\left(\quadraticExtension\right)$ defined as the $\finiteField$-points of $$\algebraicGroup{\UnitaryGroup}_n = \left\{ g \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{\algebraicGroup{\GL}_n} \mid \involution{\left(\transpose{g}\right)} w_n g = w_n \right\}.$$
+	Here $\restrictionOfScalars{\quadraticExtension}{\finiteField} {\algebraicGroup{\GL}}_n = \algebraicGroup{\GL}_n \times \algebraicGroup{\GL}_n$, equipped with the involution $\involution{\left(g_1,g_2\right)} = \left(g_2, g_1\right)$ and the Frobenius root $\Frobenius \left(g_1, g_2\right) = \involution{\left(\Frobenius g_1, \Frobenius g_2\right)}$, and we realize $w_n$ embedded diagonally as $\left(w_n, w_n\right)$.
 	\item (Special orthogonal groups): $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = 1$.

### 2025-04-09 main.tex
Removing dual group Frobenius

@@
 such that the isomorphism respects the Frobenius actions on $\CharacterLattice{\cdot}$ and $\CocharacterLattice{\cdot}$.
+Some authors distinguish the Frobenius actions on $\algebraicGroup{G}$ and $\algebraicGroup{G}^{\ast}$ by writing $\Frobenius$ and $\Frobenius^{\ast}$, respectively, but we will not do so and simply denote both actions by $\Frobenius$.
 
@@
 
-We will need the following facts about Lusztig series.
+Let us specialize to the classical groups $\algebraicGroup{G}$ and their extensions $\GroupExtension{\algebraicGroup{G}}$ from Sections \ref{subsec:isometry-groups} and \ref{subsec:similitute-groups}.
+We will need the following facts about Lusztig series of $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$.
 
@@
 \begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]\label{prop:lusztig-series-are-unions-of-harish-chandra-series}
-	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \DualFrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
+	For any semisimple element $s \in \FrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ is a union of Harrish--Chandra series corresponding to Harrish-Chandra data of the form $\left(\FrobeniusFixedPoints{\algebraicGroup{P}},\sigma\right)$ where $\algebraicGroup{P}$ is a parabolic subgroup of $\algebraicGroup{\GroupExtension{G}}$ with Levi part $\algebraicGroup{L}$ with $s \in \FrobeniusFixedPoints{L}$ and $\sigma \in \LusztigSeries{\FrobeniusFixedPoints{L}}{s}$ is an irreducible cuspidal representation.
 \end{proposition}
@@
 The next fact establishes a relation between the Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ and of $\algebraicGroup{G}$.
-\elad{Explain $i^{\ast}$}\elad{Should we deprecate the notation $\Frobenius^{\ast}$?}
+\elad{Explain $i^{\ast}$}
 
 \begin{proposition}[{\cite[Proposition 11.7]{Bonnafe2006}}]\label{prop:lusztig-series-and-restriction}
-	Let $\tilde{s}$ be a semisimple element of $\DualFrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
+	Let $\tilde{s}$ be a semisimple element of $\FrobeniusFixedPoints{\GroupExtension{G}}$ and let $s = i^{\ast}\left(\tilde{s}\right)$. Then
 	\begin{enumerate}
@@
 \begin{proposition}[{\cite[Page 172]{Lusztig1977}}]\label{prop:at-most-one-cuspidal-lusztig-series}
-	For any semisimple element $s \in \DualFrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
+	For any semisimple element $s \in \FrobeniusFixedPoints{\GroupExtension{G}}$, the Lusztig series $\LusztigSeries{\FrobeniusFixedPoints{\GroupExtension{G}}}{s}$ contains at most one cuspidal element.
 \end{proposition}

### 2025-04-09 main.tex
Typo

@@
 	For any $\Frobenius$-stable rational maximal torus $\algebraicGroup{T}_{\algebraicGroup{H}}$ of $\algebraicGroup{H}$, and any character $\theta_{H} \colon T_{H} \to \multiplicativegroup{\cComplex}$, where $T_H = \algebraicGroup{T}_{\algebraicGroup{H}}^{\Frobenius}$, we have
-	$$ \dblVirtualJacobiSumScalar{\RTTheta{T_H}{\theta_H}}{\chi} = \frac{\grpIndex{H}{T}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T_H} \theta_H\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
+	$$ \dblVirtualJacobiSumScalar{\RTTheta{T_H}{\theta_H}}{\chi} = \frac{\grpIndex{H}{T_H}}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{t \in T_H} \theta_H\left(t\right) \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(t\right).$$
 \end{proposition}

### 2025-04-10 main.tex
Moving multiplicativity to appendix

@@
 
-\elad{TODO: work on section}
-
 Let $\xIsotropic$ and $\yIsotropic$ be isotropic spaces of $\hermitianSpace$ of dimension $k$, such that $\xIsotropic$ and $\yIsotropic$ are in duality with respect to form $\innerproduct{\cdot}{\cdot}$.
@@
 
-This theorem was proved in \cite{GirschZelingher2025} under the assumption that $\pi' \subset \Ind{P}{H'}{\tau' \overline{\otimes} \pi''}$, where $\pi''$ is an irreducible cuspidal representation of $H''$ and $\tau'$ is an irreducible representation of $\GL_{k'}\left(\finiteField\right)$ such that $\chi$ nor $\minusInvolution{\chi}$ appear in the cuspidal support of $\tau''$.
-\elad{TODO: check the exact condition.
-The Gauss sums appearing here suggest that we should replace $\chi$ with $\involution{\chi}$ and $\minusInvolution{\chi}$ with $\chi^{-1}$}
-
-In order to prove a more general form of this theorem, let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$.
-Consider $f \in \rho$ defined as follows.
-The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$.
-The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
-We claim the following.
-\begin{proposition}\label{prop:multiplicativity-of-jacobi-sum-given-support}
-	Suppose that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. Then \Cref{thm:multiplicativity-in-terms-of-gauss-sums} is true.
-\end{proposition}
-\begin{proof}
-	We compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
-	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
-		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
-				\detQuadratic\left(\idmap_{\hermitianSpace}\pm p\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
-	\end{equation}
-	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right) = \left(\pm 1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} \pm a\right) \det\left(\involution{\left(\IdentityMatrix{k} \pm a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} \pm g'\right),$$
-	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
-	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
-	\begin{equation}
-		\chi\left(\pm 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
-	\end{equation}
-	which in turn is
-	\begin{align*}
-		&\chi\left(\pm 1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
-		=& \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
-	\end{align*}
-
-	It follows that $$\dblJacobiSum{\rho}{\chi} f = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f.$$
-
-	Write $\rho = \bigoplus_i \sigma_i$ where $\sigma_i$ are irreducible representations of $\sigma_i$ and the $\sigma_i$'s need not be non-isomorphic.
-By writing $f = \sum_{i} f_i$ where $0 \ne f_i \in \sigma_i$, we have that $$\sum_i \dblJacobiSum{\sigma_i}{\chi} f_i = \dblJacobiSum{\rho}{\chi} f,$$
-	and therefore $$\dblJacobiSum{\sigma_i}{\chi} f_i = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f_i,$$
-	for every $i$. The result now follows.
-\end{proof}
-The assumption in \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds in certain cases.
-For example, if $\rho$ is an irreducible representation, this assumption holds.
-It seems difficult to prove that this assumption holds in general.
-However, it is possible in a special case which suffices given the results of \cite{GirschZelingher2025}.
-
-\begin{proposition}
-	Suppose that $k=1$. Then the assumption of \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds.
-\end{proposition}
-\begin{proof}\elad{Work on this}
-	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
-	which can be rewritten as
-	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
-	As before, we may write
-	$$\genJacobiKernel{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm g - h \right)\right)\right).$$
-	Hence, \begin{align*}
-		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Assume that $\chi \ne 1$.
-By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
-Let us replace $h$ with $-A^{-1} h$.
-We get the sum
-	\begin{align*}
-		& \chi\left(-1\right)^k \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right)\\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1}p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(\pm A x^{-1} l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
-	The inner sum over $N$ will vanish unless $\pm Ax^{-1} \in P$ \elad{This is not true in general}. Thus we have
-	\begin{align*}
-		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
-		& \times \sum_{p' \in G \cap P} \sum_{p \in G \cap P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left( p \mp x  \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p \mp x \in P$, which implies that $x \in P \cap G$.
-
-	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. 
-\end{proof}
+This theorem follows from the results of \cite{GirschZelingher2025}. See \Cref{appendix:multiplicativity-of-jacobi-sums} for more information.
 
@@
 
+\section{Multiplicativity of Jacobi sums} \label{appendix:multiplicativity-of-jacobi-sums}
+\elad{TODO: Work on appendix}
+
+\Cref{thm:multiplicativity-in-terms-of-gauss-sums} was proved in \cite{GirschZelingher2025} under the assumption that $\pi' \subset \Ind{P}{H'}{\tau' \overline{\otimes} \pi''}$, where $\pi''$ is an irreducible cuspidal representation of $H''$ and $\tau'$ is an irreducible representation of $\GL_{k'}\left(\finiteField\right)$ such that $\chi^{-1}$ nor $\involution{\chi}$ appear in the cuspidal support of $\tau'$.
+
+In order to prove a more general form of this theorem, let $v_{\pi'} \in \pi'$ and $v_{\tau} \in \tau$.
+Consider $f \in \rho$ defined as follows.
+The function $f \in \rho$ is the unique element supported on $P$, such that $f\left(\idmap_{\hermitianSpace}\right) = v_{\tau} \otimes v_{\pi'}$.
+The projection $f$ to any non-zero invariant subspace of $\rho$ is non-zero.
+We claim the following.
+\begin{proposition}\label{prop:multiplicativity-of-jacobi-sum-given-support}
+	Suppose that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. Then \Cref{thm:multiplicativity-in-terms-of-gauss-sums} is true.
+\end{proposition}
+\begin{proof}
+	We compute $\left(\dblJacobiSum{\rho}{\chi} f\right)\left(\idmap_{\hermitianSpace}\right)$. It is given by
+	\begin{equation}\label{eq:recursive-doubling-gauss-sum}
+		\frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{\substack{p \in P \cap G\\
+				\detQuadratic\left(\idmap_{\hermitianSpace}\pm p\right) \ne 0}} \chi\left(\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_{\tau} \otimes v_{\pi'}.
+	\end{equation}
+	Decomposing the sum \eqref{eq:recursive-doubling-gauss-sum} as a sum over $L$ and $N$, and using the fact that if $p \in P \cap G$ has Levi part with image $\left(a, g'\right) \in \GL_k\left(\quadraticExtension\right) \times G'$ then $$\detQuadratic\left(\idmap_{\hermitianSpace} \pm p\right) = \left(\pm 1\right)^k \detQuadratic\left(\involution{a}\right)^{-1}\detQuadratic\left(\IdentityMatrix{k} \pm a\right) \det\left(\involution{\left(\IdentityMatrix{k} \pm a\right)}\right) \detQuadratic\left(\idmap_{\hermitianSpace'} \pm g'\right),$$
+	and using the fact that $\sizeof{\lieAlgebra} = \sizeof{\lieAlgebra'} \sizeof{\squareMatrix_k\left(\finiteField\right)} \sizeof{N}^2$, where $\lieAlgebra'$ is the Lie algebra of $G'$,
+	we get that \eqref{eq:recursive-doubling-gauss-sum} equals
+	\begin{equation}
+		\chi\left(\pm 1\right)^k q^{-\frac{k^2}{2}} \sum_{a \in \GL_k\left(\quadraticExtension\right)} \genJacobiKernel{\involutionPlusOne{\chi}}\left(a\right) \minusInvolution{\chi}\left(\detQuadratic a\right) \tau\left(a\right) v_{\tau} \otimes \frac{1}{\sqrt{\sizeof{\lieAlgebra'}}} \sum_{g' \in G'} \genHermitianJacobiKernel{\hermitianSpace}{\chi}\left(g'\right) \pi'\left(g'\right) v_{\pi'},
+	\end{equation}
+	which in turn is
+	\begin{align*}
+		&\chi\left(\pm 1\right)^k \dblJacobiSum{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} v_{\tau} \otimes \dblJacobiSum{\pi'}{\chi} v_{\pi'}\\
+		=& \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} v_{\tau} \otimes v_{\pi'}.
+	\end{align*}
+
+	It follows that $$\dblJacobiSum{\rho}{\chi} f = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f.$$
+
+	Write $\rho = \bigoplus_i \sigma_i$ where $\sigma_i$ are irreducible representations of $\sigma_i$ and the $\sigma_i$'s need not be non-isomorphic.
+By writing $f = \sum_{i} f_i$ where $0 \ne f_i \in \sigma_i$, we have that $$\sum_i \dblJacobiSum{\sigma_i}{\chi} f_i = \dblJacobiSum{\rho}{\chi} f,$$
+	and therefore $$\dblJacobiSum{\sigma_i}{\chi} f_i = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f_i,$$
+	for every $i$. The result now follows.
+\end{proof}
+The assumption in \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds in certain cases.
+For example, if $\rho$ is an irreducible representation, this assumption holds.
+It seems difficult to prove that this assumption holds in general.
+However, it is possible in a special case which suffices given the results of \cite{GirschZelingher2025}.
+
+\begin{proposition}
+	Suppose that $k=1$. Then the assumption of \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds.
+\end{proposition}
+\begin{proof}\elad{Work on this}
+	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
+	which can be rewritten as
+	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
+	As before, we may write
+	$$\genJacobiKernel{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm g - h \right)\right)\right).$$
+	Hence, \begin{align*}
+		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Assume that $\chi \ne 1$.
+By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
+Let us replace $h$ with $-A^{-1} h$.
+We get the sum
+	\begin{align*}
+		& \chi\left(-1\right)^k \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right)\\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1}p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(\pm A x^{-1} l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
+	The inner sum over $N$ will vanish unless $\pm Ax^{-1} \in P$ \elad{This is not true in general}. Thus we have
+	\begin{align*}
+		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)}  \chi\left(\detQuadratic\left(xh\right)\right) \fieldCharacter_{\quadraticExtension}\left(\trace h\right) \\
+		& \times \sum_{p' \in G \cap P} \sum_{p \in G \cap P} \chi^{-1}\left(\detQuadratic p'\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(p' \left( p \mp x  \right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	By decomposing the sum over $p' \in P$ into a sum over $N$ and $L$, we see that the inner sum over $N$ will vanish unless $p \mp x \in P$, which implies that $x \in P \cap G$.
+
+	Hence, we have that $\dblJacobiSum{\rho}{\chi} f$ is supported on $P$. 
+\end{proof}
+
 \bibliographystyle{abbrv}

### 2025-04-10 main.tex
Some modifications and questions

@@
 Let $f \colon \algebraicGroup{G}^{\Frobenius} \to \cComplex$ be a class function.
-Then by Schur's lemma for any irreducible representation $\pi$, there exists $\gamma_{f}\left(\pi\right) \in \cComplex$ such that $$\sum_{g \in G} f(g)\pi(g) = \gamma_{f}\left(\pi\right) \cdot \idmap_{\pi}.$$
+Then by Schur's lemma for any irreducible representation $\pi$, there exists $\gamma_{f}\left(\pi\right) \in \cComplex$ such that $$\sum_{g \in \algebraicGroup{G}^{\Frobenius}} f(g)\pi(g) = \gamma_{f}\left(\pi\right) \cdot \idmap_{\pi}.$$
 
@@
 
-We recall that \[
-	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
-\]
+We recall that $$
+	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a,
+$$
 with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \GL_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
@@
 
-Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ and $\tilde{\theta}$ such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
-Define
+Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ \elad{of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$?} corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
+Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{A_n}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+We define
 \[
@@
 \]
-\calvin{should the power be $q^{(-nm)/2}$ or $q^{-n/2}$? \elad{$q^{-nm/2}$}}
 Here $\chi \colon \multiplicativegroup{\finiteFieldExtension{m}} \to \multiplicativegroup{\cComplex}$ and $\fieldCharacter \colon \finiteFieldExtension{m} \to \multiplicativegroup{\cComplex}$ are characters.
@@
 	\item \label{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined} In the case that $\rho$ is the identity map, $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ depends only on the semisimple conjugacy class of $(s_{\algebraicGroup{T},\theta})$ and the character $\chi$.
-	\item The value $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined, i.e., independent of choice of $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and the conjugacy class representative $w$.
+	\item The value $g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi)$ is well defined, i.e., it is independent of the choices $\algebraicGroup{T}_0$, $\algebraicGroup{T}^*$ and of the conjugacy class representative $w$.
 \end{enumerate}
@@
 	where $\tau$ is any irreducible subrepresentation of $\RTThetaVirtual{T}{\GL_n\left(\finiteField\right)}{\theta}$.
-By \Cref{thm:KondoClassical}, this only depends on geometric conjugacy class of $(T,\theta)$ and hence on the semisimple conjugacy class of $(s_{T,\theta})$.
+By \Cref{thm:KondoClassical}, this only depends on the geometric conjugacy class of $(T,\theta)$ and hence only on the semisimple conjugacy class of $(s_{T,\theta})$.
 	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
-	\[
-	g_{(s)}(\psi,\chi) := g_{T,\rho}(\chi,\theta,\psi) \textnormal{ for some } (T,\theta) \textnormal{ such that } (s_{T,\theta}) = (s)
-	\]
+	$$
+	g_{(s)}(\chi,\fieldCharacter) := g_{T,\rho}(\chi,\theta,\fieldCharacter)$$
+	where $(T,\theta)$ is a torus character pair such that $\left(s_{T,\theta}\right) = (s)$.
 	By (\ref{item:gl-n-hasse-davenport-gauss-sum-implies-well-defined}) this is well defined. Then
-	\[
-	g_{T,\rho}(\chi,\theta,\psi)  = g_{(\rho(s_{T,\theta}))}(\psi,\chi)
-	\]
-	which is independent of of choice of $\algebraicGroup{T}^* \subset G^*$ and $\algebraicGroup{T} \subset \GL_n$.
+	$$
+	g_{T,\rho}(\chi,\theta,\fieldCharacter)  = g_{(\rho(s_{T,\theta}))}(\chi,\fieldCharacter),
+	$$
+	which is independent of the choices $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$.
 \end{enumerate}

### 2025-04-10 main.tex
Minors

@@
 
-We recall that $$
+We recall that \elad{Maybe we can help the reader and tell them that $m=1,2$} $$
 	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a,
@@
 	\begin{tabular}{|c|c|} \hline
-		$\algebraicGroup{G}$ & $\algebraicGroup{G}^*$ representation  \tabularnewline \hline \hline
+		$\algebraicGroup{G}$ & $\rho \colon \algebraicGroup{G}^{\ast} \to \left(\restrictionOfScalars{\quadraticExtension}{\finiteField}{}\right) \algebraicGroup{\GL}_N$  \tabularnewline \hline \hline
 		$\algebraicGroup{GL}_n$ &  $\algebraicGroup{\GL}_n \to \algebraicGroup{GL}_{2n}$ \tabularnewline \hline
@@
 \end{center}
-Where in each case the map on cocharacters $\rho_*:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-w_n x)$ \calvin{in the GSpin cases might scale up by 2}
+In each of the cases in the table, the map on cocharacters $\rho_{\ast}:\CocharacterLattice{\algebraicGroup{T}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to \CocharacterLattice{\tilde{\algebraicGroup{T}}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ sends $x$ to $(x,-w_n x)$.
+\calvin{in the GSpin cases might scale up by 2}
 %Note that in the $SO$ and $GSO$ case, the map $\rho$ sends the split torus of $G^*$ into the split torus of $\GL(2n)$ and the induced map of cocharacters sends $x \mapsto (x,-x)$.
@@
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
-Our proof of \Cref{lem:cochar_computation} will check that $\rho(s_{T,\theta}) = (s_{\Tilde{T},\Tilde{\theta}})$ with $g_{T}(\chi,\theta,\psi)$ equal to $\tau_{\Tilde{T}}(\Tilde{\theta} \times \chi,\psi)$ up to a few factors.
-We will do this by breaking our tori into irreducible rational factors with the following lemma handling each possible factor
+We will prove \Cref{lem:cochar_computation} by checking that if $\rho(s_{T,\theta}) = (s_{\Tilde{T},\Tilde{\theta}})$ then $g_{T}(\chi,\theta,\psi)$ equals to $\GaussSumTorusCharacter{\tilde{T}}{\tilde{\theta}}{\chi}{\fieldCharacter}$ up to some factors.
+We will do so by breaking our tori into irreducible rational factors with the following lemma handling each possible factor.
 

### 2025-04-10 main.tex
n => N

@@
 \end{theorem}
-%In the $\GL_n$ case, \Cref{thm:gln-doubling-gauss-sum-in-terms-of-kondo}
-
+This result will be proved in \Cref{subsec:stability}. Our next goal is to prove the following intermediate result.
 \begin{lemma}
 \label{lem:indep_geo_conj}
-    If $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}', \theta)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi}}{\RTTheta{T}{\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{\RTTheta{T'}{\theta'}}{\chi}}{\RTTheta{T'}{\theta'}\left(1\right)}.$$
+    If $(\algebraicGroup{T}_H,\theta_H)$ and $(\algebraicGroup{T}'_H, \theta_H)$ are geometrically conjugate, then $$\frac{\dblVirtualJacobiSumScalar{\RTTheta{T_H}{\theta_H}}{\chi}}{\RTTheta{T_H}{\theta}(1)} = \frac{\dblVirtualJacobiSumScalar{\RTTheta{T'_H}{\theta'}}{\chi}}{\RTTheta{T'_H}{\theta'_H}\left(1\right)}.$$
 \end{lemma}
@@
 We recall that \elad{Maybe we can help the reader and tell them that $m=1,2$} $$
-	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a,
+	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_N\right)_a,
 $$
-with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \GL_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
+with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}(\finiteField) = \GL_N(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
 
 \begin{remark}
-Torus character pairs for $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ are the same as torus character pairs for $\algebraicGroup{\GL}_n$ as a group over $\finiteFieldExtension{m}$.
+Torus character pairs for $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ are the same as torus character pairs for $\algebraicGroup{\GL}_N$ as a group over $\finiteFieldExtension{m}$.
 \end{remark}
@@
 
-Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_n$ \elad{of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}$?} corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
-Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{A_n}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_N$ \elad{of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$?} corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
+Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{A_N}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 We define
@@
 	\]
-	where $\tau$ is any irreducible subrepresentation of $\RTThetaVirtual{T}{\GL_n\left(\finiteField\right)}{\theta}$.
+	where $\tau$ is any irreducible subrepresentation of $\RTThetaVirtual{T}{\GL_N\left(\finiteField\right)}{\theta}$.
 By \Cref{thm:KondoClassical}, this only depends on the geometric conjugacy class of $(T,\theta)$ and hence only on the semisimple conjugacy class of $(s_{T,\theta})$.
-	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_n$, we define
+	\item For a Frobenius stable semisimple conjugacy class $(s)$ in $\GL_N$, we define
 	$$
@@
 	$$
-	which is independent of the choices $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and $\algebraicGroup{T} \subset \algebraicGroup{\GL}_n$.
+	which is independent of the choices $\algebraicGroup{T}^* \subset \algebraicGroup{G}^*$ and $\algebraicGroup{T} \subset \algebraicGroup{\GL}_N$.
 \end{enumerate}
@@
 
-The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTTheta{T}{\theta}}{\chi}/\RTTheta{T}{\theta}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.
+The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi}/\RTGTheta{T_H}{H}{\theta_H}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.
 
@@
 	\begin{tabular}{|c|c|} \hline
-		$\algebraicGroup{G}$ & $\rho \colon \algebraicGroup{G}^{\ast} \to \left(\restrictionOfScalars{\quadraticExtension}{\finiteField}{}\right) \algebraicGroup{\GL}_N$  \tabularnewline \hline \hline
+		$\algebraicGroup{G}$ & $\rho \colon \algebraicGroup{G}^{\ast} \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$  \tabularnewline \hline \hline
 		$\algebraicGroup{GL}_n$ &  $\algebraicGroup{\GL}_n \to \algebraicGroup{GL}_{2n}$ \tabularnewline \hline
@@
 \end{center}
-In each of the cases in the table, the map on cocharacters $\rho_{\ast}:\CocharacterLattice{\algebraicGroup{T}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to \CocharacterLattice{\tilde{\algebraicGroup{T}}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ sends $x$ to $(x,-w_n x)$.
+In each of the cases in the table, $m = 1$, except for the unitary group case where $m=2$.
+In each case, the map on cocharacters $\rho_{\ast}:\CocharacterLattice{\algebraicGroup{T}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to \CocharacterLattice{\tilde{\algebraicGroup{T}}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ sends $x$ to $(x,-w_n x)$.
 \calvin{in the GSpin cases might scale up by 2}

### 2025-04-10 main.tex
Minors

@@
 \begin{proof}
-Both are equal to $g_{(\rho(s_{T,\theta}))}(\psi,\chi) = g_{(\rho(s_{T',\theta'}))}(\psi,\chi)$.
+Both are equal to $$g_{(\rho(s_{T,\theta}))}\left(\chi, \fieldCharacter\right) = g_{(\rho(s_{T',\theta'}))}\left(\chi, \fieldCharacter\right).$$
 \end{proof}
@@
 \begin{remark}
-	The above work is not surpising as it is really a rephrasing that the eigenvalues of $\rho(s)$ are independent of conjugacy.
+	The above work is not surprising as it is really a rephrasing that the eigenvalues of $\rho(s)$ are independent of conjugacy.
 \end{remark}
 
-The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi}/\RTGTheta{T_H}{H}{\theta_H}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.
+The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{\RTGTheta{T_H}{H}{\theta_H}}{\chi}/\RTGTheta{T_H}{H}{\theta_H}\left(1\right)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate standard representation $\rho$ in the table below.
 

### 2025-04-10 main.tex
Explaining the cocharacter notation

@@
 \newcommand{\RTThetaVirtual}[3]{\mathcal{R}_{#1}^{#2}(#3)}
+\newcommand{\Cocharacter}{\mathrm{cochar}}
 
@@
 \[
-    \exp(\langle x_{T,\theta},y\rangle) = \theta((N_{T(\finiteField_m):T(\finiteField)}(y(\zeta_m))).
+    \exp\left(\innerproduct{x_{T,\theta}}{y}\right) = \theta\left(\aFieldNorm_{\algebraicGroup{T}(\finiteField_m):\algebraicGroup{T}(\finiteField)}\left(y(\zeta_m\right)\right).
 \]
+In the following computations, we will choose $m$ to be sufficiently large so such that the torus $\algebraicGroup{T}\left(\finiteField_m\right)$ is isomorphic to $\left(\multiplicativegroup{\finiteFieldExtension{m}}\right)^N$.
+We will then identify the cocharacter lattice $\CocharacterLattice{\algebraicGroup{T}}$ with $\zIntegers^N$ by the map $\Cocharacter \colon \zIntegers^N \to \CocharacterLattice{\algebraicGroup{T}}$ given by $\left(y_1,\dots,y_N\right) \mapsto \left(\Cocharacter_{(y_1,\dots,y_N)}\left(t\right) = \left(t^{y_1},\dots,t^{y_N}\right)\right)$.
 For different tori with Frob action we get
 \begin{enumerate}
-    \item ($n$-cycle) $\algebraicGroup{T}(\finiteField) \cong \finiteField_n^\times$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{mn}) = (\zeta_n)^{y_1+qy_2+q^2y_3 \hdots +q^{n-1}y_n}$$
-    \item ($n$-cycle with one negative) $\algebraicGroup{T}(\finiteField) \cong \{x \in \finiteField_{2n}^\times: \FieldNorm{2n}{n}(x) = 1\}$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{2mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{2mn}) = (\beta_n)^{y_1+qy_2+q^2y_3 \hdots +q^{n-1}y_n}$$
+    \item (cycle of length $n$) $\algebraicGroup{T}(\finiteField) \cong \finiteField_n^\times$ and $\algebraicGroup{T}\left(\finiteFieldExtension{nm}\right) \cong \left(\multiplicativegroup{\finiteFieldExtension{m}}\right)^n$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{mn})}{\algebraicGroup{T}(\finiteField)}\left(\Cocharacter_{(y_1,\dots,y_n)}(\zeta_{mn})\right) = \prod_{i=0}^{n-1} \left(\zeta_n\right)^{q^{i} y_{i+1}}.$$
+    \item (cycle of length $n$ with one negative sign) $\algebraicGroup{T}(\finiteField) \cong \NormOneGroup{2n}$ and $\algebraicGroup{T}\left(\finiteFieldExtension{2mn}\right) \cong \left(\multiplicativegroup{\finiteFieldExtension{2mn}}\right)^{n}$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{2mn})}{\algebraicGroup{T}(\finiteField)}\left(\Cocharacter_{(y_1,\dots, y_n)}\left(\zeta_{2mn}\right)\right) = \prod_{i=0}^{n-1}(\beta_n)^{q^{i} y_{i+1}},$$
     where $\beta_n = \zeta_{2n}^{1-q^n}$.
-    \item ($(-1) \cdot n$-cycle, $n$ even) $\algebraicGroup{T}(\finiteField) \cong \finiteField_n^\times$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{mn}) = (\zeta_n)^{y_1-qy_2+q^2y_3-q^3y_4 \hdots -q^{n-1}y_n}$$
-    \item ($(-1) \cdot n$-cycle, $n$ odd) $\algebraicGroup{T}(\finiteField) \cong \{x \in \finiteField_{2n}^\times: \FieldNorm{2n}{n}(x) = 1\}$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{2mn})}{\algebraicGroup{T}(\finiteField)}(y_1,y_2 \hdots y_n)(\zeta_{2mn}) = (\beta_n)^{y_1-qy_2+q^2y_3-q^3y_4 \hdots +q^{n-1}y_n}$$
+    \item (cycle of length $n$ with $n$ negative signs, $n$ even) $\algebraicGroup{T}(\finiteField) \cong \finiteField_n^\times$ and $\algebraicGroup{T}\left(\finiteFieldExtension{mn}\right) \cong \left(\multiplicativegroup{\finiteFieldExtension{nm}}\right)^n$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{mn})}{\algebraicGroup{T}(\finiteField)}\left(\Cocharacter_{(y_1,\dots,y_n)}(\zeta_{mn})\right) = \prod_{i=0}^{n-1} (\zeta_n)^{\left(-1\right)^{i} q^{i} y_{i+1}}.$$
+    \item (cycle of length $n$ with $n$ negative signs, $n$ odd) $\algebraicGroup{T}(\finiteField) \cong \NormOneGroup{2n}$ and $\algebraicGroup{T}\left(\finiteFieldExtension{2mn}\right) \cong \left(\multiplicativegroup{\finiteFieldExtension{2mn}}\right)^{n}$ with $$\FieldNorm{\algebraicGroup{T}(\finiteField_{2mn})}{\algebraicGroup{T}(\finiteField)}\left(\Cocharacter_{(y_1,\dots, y_n)}\left(\zeta_{2mn}\right)\right) = \prod_{i=0}^{n-1} (\beta_n)^{\left(-1\right)^{i}q^{i}y_{i+1}},$$
     where $\beta_n = \zeta_{2n}^{1-q^n}$.
 \end{enumerate}
-Now the results follow from the equalities
+The results now follow from the equalities
 \begin{align*}

### 2025-04-11 main.tex
Rewriting equalities

@@
 \newcommand{\Cocharacter}{\mathrm{cochar}}
-
+\newcommand{\Character}{\mathrm{char}}
 \newcommand{\calvin}[1]{\textcolor{orange}{\sffamily ((CALVIN: #1))}}
@@
 In each of the cases in the table, $m = 1$, except for the unitary group case where $m=2$.
-In each case, the map on cocharacters $\rho_{\ast}:\CocharacterLattice{\algebraicGroup{T}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to \CocharacterLattice{\tilde{\algebraicGroup{T}}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ sends $x$ to $(x,-w_n x)$.
+In each case, the map on cocharacters $\rho_{\ast}:\CocharacterLattice{\algebraicGroup{T}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to \CocharacterLattice{\tilde{\algebraicGroup{T}}^{\ast}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ sending $x$ to $(x,-w_n x)$.
 \calvin{in the GSpin cases might scale up by 2}
@@
 We will then identify the cocharacter lattice $\CocharacterLattice{\algebraicGroup{T}}$ with $\zIntegers^N$ by the map $\Cocharacter \colon \zIntegers^N \to \CocharacterLattice{\algebraicGroup{T}}$ given by $\left(y_1,\dots,y_N\right) \mapsto \left(\Cocharacter_{(y_1,\dots,y_N)}\left(t\right) = \left(t^{y_1},\dots,t^{y_N}\right)\right)$.
+Similarly using the above identifications denote for $\left(x_1,\dots,x_N\right) \in \zIntegers^N$ the character $\Character_{(x_1,\dots,x_{N})}$ given by the formula $$\Character_{(x_1,\dots,x_{N})}\left(\Cocharacter_{(y_1,\dots, y_N)}\left(t\right)\right) = t^{\sum_{i=1}^N x_i y_i}.$$
+
+We have that $$\innerproduct{\phi \Character_{(x_1,\dots,x_{n})}}{\Cocharacter_{(y_1,\dots, y_{2n})}\left(t\right)} = \innerproduct{\Character_{(x_1,\dots,x_n, -x_n,\dots,-x_1)}}{\Cocharacter_{(y_1,\dots, y_{2n})}\left(t\right)},$$
+which equals $$\innerproduct{\Character_{(x_1,x_2,\dots,x_{n})}}{\Cocharacter_{(y_1-y_{2n},y_2-y_{2n-1},\dots, y_n-y_{n+1})}\left(t\right)}.$$
 For different tori with Frob action we get
@@
 The results now follow from the equalities
-\begin{align*}
-	\alpha(\zeta^{((y_1-y_{2n})+q(y_2-y_{2n-1}) + \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\alpha(\zeta^{(y_1+qy_2 + \hdots +q^{n-1}y_{n})}) \alpha^{-1}(\zeta^{(y_{2n}+qy_{2n-1} + \hdots +q^{n-1}y_{n+1})}) \\
-	\theta(\beta^{((y_1-y_{2n})+q(y_2-y_{2n-1}) + \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\theta(\beta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2n-1} \hdots +q^{2n-1}y_{n+1})}) \\
-	&=\theta'(\zeta^{(y_1+qy_2 + \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2n-1} \hdots +q^{2n-1}y_{n+1})})\\
+\begin{enumerate}
+	\item $$\prod_{i=0}^{n-1} \alpha\left(\zeta_n^{q^i \left(y_{i+1}-y_{2n-i}\right)}\right) = \prod_{i=0}^{n-1} \alpha\left(\zeta_n^{q^i y_{i+1}}\right) \cdot \prod_{i=0}^{n-1} \alpha^{-1}\left(\zeta_n^{q^i y_{2n-i}}\right).$$
+	\item \begin{align*}
+		\prod_{i=0}^{n-1} \theta\left(\beta_n^{ q^i \left(y_{i+1}-y_{2n-i}\right)}\right) &= \prod_{i=0}^{n-1} \theta\left(\beta_n^{ q^i y_{i+1}}\right) \cdot \prod_{i=0}^{n-1} \theta\left(\beta_n^{ q^{i+n} y_{2n-i}}\right) \\
+		&= \prod_{i=0}^{n-1} \theta'\left(\zeta_n^{q^i y_{i+1}}\right) \cdot \prod_{i=0}^{n-1} \theta'\left(\zeta_n^{q^{n+i} y_{2n-i}}\right).
+	\end{align*}
+	\item \begin{align*}
+		\prod_{i=0}^{n-1} \alpha\left(\zeta_n^{\left(-1\right)^i q^i \left(y_{i+1} - y_{2n-i}\right)}\right) =& \prod_{i=0}^{\frac{n}{2}-1} \alpha\left(\zeta_n^{q^{2i} y_{2i+1} + q^{2i+1} y_{2n-2i-1}}\right) \\
+		& \times \prod_{i=0}^{\frac{n}{2}-1} \alpha^{-q}\left(\zeta_n^{q^{2i} y_{2i+2} + q^{2i+1} y_{2n-2i-2}}\right).
+	\end{align*}
+	\item \begin{align*}
+		&\prod_{i=0}^{n-1} \theta\left( \beta_n^{\left(-1\right)^i q^i \left(y_{i+1} - y_{2n - i}\right)}\right)\\
+		 = & \prod_{\substack{0 \le i \le n-1\\
+				i \text{ is even}}} \theta\left(\beta_n^{q^{i} y_{i+1} + q^{i+n} y_{2n-i}}\right) \cdot \prod_{\substack{0 \le i \le n-1\\
+				i \text{ is odd}}} \theta\left(\beta_n^{q^{i+n} y_{i+1} + q^{i} y_{2n-i}}\right)\\
+			= &\prod_{\substack{0 \le i \le n-1\\
+			i \text{ is even}}} \theta'\left(\zeta_n^{q^{i} y_{i+1} + q^{n-i} y_{n+i}}\right) \cdot \prod_{\substack{0 \le i \le n-1\\
+		i \text{ is odd}}} \theta'\left(\zeta_n^{q^{i+n} y_{i+1} + q^{2n-i} y_{n+i}}\right).
+	\end{align*}
+\end{enumerate}
+\begin{align*}
 	\alpha(\zeta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots -q^{n-1}(y_{n}-y_{n+1}))})&= \alpha(\zeta^{(y_1+qy_{2n-1}+q^2y_3 +q^3y_{2n-3} \hdots +q^{n-1}y_{n+1})}) \\
@@
 \end{align*}
-where $\zeta = \zeta_n = 1/(q^n-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and $\beta = \beta_n = \zeta_{2n}^{1-q^n}$.
+
+=
 %Now the results follow from checking that

### 2025-04-11 main.tex
Explaining why the proposition follows from the equalities

@@
 \end{enumerate}
-The results now follow from the equalities
+Notice that we have the following equalities:
 \begin{enumerate}
@@
 \end{enumerate}
-\begin{align*}
-	\alpha(\zeta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots -q^{n-1}(y_{n}-y_{n+1}))})&= \alpha(\zeta^{(y_1+qy_{2n-1}+q^2y_3 +q^3y_{2n-3} \hdots +q^{n-1}y_{n+1})}) \\
-	&\quad \cdot \alpha^{-1}(\zeta^{(qy_{2} + q^2y_{2n-2} + \hdots +q^{n-1}y_{n}+q^ny_{2n})}) \\
-	\theta(\beta^{((y_1-y_{2n})-q(y_2-y_{2n-1}) +q^2(y_3-y_{2n-2}) \hdots +q^{n-1}(y_{n}-y_{n+1}))})&=\theta(\beta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})}) \\
-	&=\theta'(\zeta^{(y_1+qy_{2n-1} +q^2y_3 \hdots + q^{n-1}y_{n} + q^ny_{2n}+q^{n+1}y_{2} \hdots +q^{2n-1}y_{n+1})})
-\end{align*}
-
-=
+The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition.
+This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that the coefficient of $q^i$ is $y_{i+1}$ for every $0 \le i \le 2n-1$.
 %Now the results follow from checking that

### 2025-04-11 main.tex
Rewrite statement

@@
     \begin{enumerate}
-        \item[B,C,D Case 1)] $w$ is conjugate to an $n$-cycle: \calvin{Add in note about the two type B cases.
-Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $w$ on the preimage and the cycle $(w,w^\ast)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
-        \item[B,C,D Case 2)] $w$ is conjugate to an $n$-cycle with one negative:
- In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $w$ on the preimage and by a $2n$ cycle on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$
-    \item[$G=\algebraicGroup{U}$ Case 1)] $w$ is conjugate to $(1,2 \hdots n)$ an even cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{G}_m$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the product of two $n$ cycles $\begin{pmatrix} 0 & w_nw \\
+        \item (Types B,C,D Case 1) $w$ is conjugate to a cycle of length $n$.
+\calvin{Add in note about the two type B cases.
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
+        \item (Types B,C,D Case 2) $w$ is conjugate to a cycle of length $n$ with one negative sign.
+ In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $w$ on the domain and by a cycle of length $2n$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$
+    \item ($\algebraicGroup{G}=\algebraicGroup{U}$ Case 1) $w$ is conjugate to cycle of length $n$, where $n$ is even.
+In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $-1\cdot w$ on the domain and by the cycle $\left(\begin{smallmatrix} 0 & w_nw \\
         w w_n & 0
-        \end{pmatrix}$  on the image, and 
-		$$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
-		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus character pair
-		\[
-\left(\begin{pmatrix}
-x_0 & 0 & 0 & 0 & \hdots & 0 \\
-0 & y_0 & 0 & 0 & \hdots & 0 \\
-0 & 0 & F^2(x_0) & 0 & \hdots & 0 \\
-0 & 0 & 0 & F^2(y_0) & \hdots & 0 \\
-\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
-0 & 0 & 0 & 0 & \hdots & F^{n-2}(y_0) \\
-\end{pmatrix},\begin{pmatrix}
-	F(x_0) & 0 & 0 & 0 & \hdots & 0 \\
-	0 & F(y_0) & 0 & 0 & \hdots & 0 \\
-	0 & 0 & F^3(x_0) & 0 & \hdots & 0 \\
-	0 & 0 & 0 & F^3(y_0) & \hdots & 0 \\
-	\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
-	0 & 0 & 0 & 0 & \hdots & F^{n-1}(y_0) \\
-	\end{pmatrix} \right)
-		\]
-		mapping to $\alpha(x_0)\alpha^{-q}(y_0)$.
-    \item[$G=\algebraicGroup{U}$ Case 2)] $w$ is conjugate to $(1,2 \hdots n)$ an odd cycle: In this case $\algebraicGroup{T} = \mathrm{Res}_{\mathbb{F}_n:\mathbb{F}}\algebraicGroup{U}(1)$ with $\Frobenius$ acting by $-1\cdot w$ on the preimage and by the $2n$ cycle $\begin{pmatrix} 0 & w_nw \\
+        \end{smallmatrix}\right)$ on the image, and 
+		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
+		Here $\left(\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}\right)$ is realized explicitly as follows.
+For $z = \left(x,y\right) \in \multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ denote $Dz = \left(\begin{smallmatrix}
+			x & 0\\
+			0 & y
+		\end{smallmatrix}\right) \in \GL_2\left(\finiteFieldExtension{n}\right)$and $$\Frobenius\left(z\right) = \left(\Frobenius x, \Frobenius y\right) = \left(x^q,y^q\right).$$ Then $\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ is realized as the subgroup of $\GL_{2n}\left(\finiteFieldExtension{n}\right) \times \GL_{2n}\left(\finiteFieldExtension{n}\right)$ given by the image of the map $$z \mapsto \left(\diag\left(Dz,D\Frobenius^2 z,\dots, D\Frobenius^{n-2} z\right), \diag\left(D\Frobenius z, D\Frobenius^3 z, \dots, D\Frobenius^{n-1} z\right)\right),$$
+		and the character $\alpha \times \alpha^{-q}$ is given by $$z = \left(x,y\right) \mapsto \alpha\left(x\right) \alpha^{-q}\left(y\right).$$
+    \item ($\algebraicGroup{G}=\algebraicGroup{\UnitaryGroup}_n$ Case 2) $w$ is conjugate a cycle of length $n$ where $n$ is odd.
+In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $-1\cdot w$ on the domain and by the cycle $\left(\begin{smallmatrix} 0 & w_nw \\
         w w_n& 0
-        \end{pmatrix}$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
+        \end{smallmatrix}\right)$ on the image, and $$x_{\multiplicativegroup{\finiteFieldExtension{2n}},\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
     \end{enumerate}
@@
 Recall that $x_{T,\theta}$ is defined by for sufficiently large $m$ with $\zeta_m = 1/(q^m-1)$ under the fixed identification $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$
-\[
-    \exp\left(\innerproduct{x_{T,\theta}}{y}\right) = \theta\left(\aFieldNorm_{\algebraicGroup{T}(\finiteField_m):\algebraicGroup{T}(\finiteField)}\left(y(\zeta_m\right)\right).
-\]
+$$
+    \exp\left(\innerproduct{x_{T,\theta}}{y}\right) = \theta\left(\aFieldNorm_{\algebraicGroup{T}(\finiteField_m):\algebraicGroup{T}(\finiteField)}\left(y\left(\zeta_m\right)\right)\right).
+$$
 In the following computations, we will choose $m$ to be sufficiently large so such that the torus $\algebraicGroup{T}\left(\finiteField_m\right)$ is isomorphic to $\left(\multiplicativegroup{\finiteFieldExtension{m}}\right)^N$.
@@
 The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition.
-This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that the coefficient of $q^i$ is $y_{i+1}$ for every $0 \le i \le 2n-1$.
+This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that $q^i$ is the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation for every $0 \le i \le 2n-1$.
 %Now the results follow from checking that
@@
 \end{comment}
-\calvin{start alternate writeup 2 of section 3.4/3.4.1}
+
 \subsection{Stability}\label{subsec:stability}

### 2025-04-11 main.tex
Typos

@@
 \calvin{Add in note about the two type B cases.
-Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$
         \item (Types B,C,D Case 2) $w$ is conjugate to a cycle of length $n$ with one negative sign.
@@
         \end{smallmatrix}\right)$ on the image, and 
-		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\finiteFieldExtension{n},\alpha}).$$
+		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$
 		Here $\left(\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}\right)$ is realized explicitly as follows.

### 2025-04-11 main.tex
Corrections/clarifications

@@
 			0 & y
-		\end{smallmatrix}\right) \in \GL_2\left(\finiteFieldExtension{n}\right)$and $$\Frobenius\left(z\right) = \left(\Frobenius x, \Frobenius y\right) = \left(x^q,y^q\right).$$ Then $\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ is realized as the subgroup of $\GL_{2n}\left(\finiteFieldExtension{n}\right) \times \GL_{2n}\left(\finiteFieldExtension{n}\right)$ given by the image of the map $$z \mapsto \left(\diag\left(Dz,D\Frobenius^2 z,\dots, D\Frobenius^{n-2} z\right), \diag\left(D\Frobenius z, D\Frobenius^3 z, \dots, D\Frobenius^{n-1} z\right)\right),$$
+		\end{smallmatrix}\right) \in \GL_2\left(\finiteFieldExtension{n}\right)$and $$\Frobenius\left(z\right) = \left(\Frobenius x, \Frobenius y\right) = \left(x^q,y^q\right).$$ Then $\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}}$ is realized as the subgroup of $\restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\algebraicGroup{\GL}_n}\left(\finiteFieldExtension{n}\right) = \GL_{n}\left(\finiteFieldExtension{n}\right) \times \GL_{n}\left(\finiteFieldExtension{n}\right)$ given by the image of the map $$z \mapsto \left(\diag\left(Dz,D\Frobenius^2 z,\dots, D\Frobenius^{n-2} z\right), \diag\left(D\Frobenius z, D\Frobenius^3 z, \dots, D\Frobenius^{n-1} z\right)\right),$$
 		and the character $\alpha \times \alpha^{-q}$ is given by $$z = \left(x,y\right) \mapsto \alpha\left(x\right) \alpha^{-q}\left(y\right).$$
@@
 which equals $$\innerproduct{\Character_{(x_1,x_2,\dots,x_{n})}}{\Cocharacter_{(y_1-y_{2n},y_2-y_{2n-1},\dots, y_n-y_{n+1})}\left(t\right)}.$$
-For different tori with Frob action we get
+For different tori with $\Frobenius$ actions we get
 \begin{enumerate}
@@
 \end{enumerate}
-The results now follow from these equalities, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition.
+The results now follow from these equalities and the norm computations, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition.
 This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that $q^i$ is the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation for every $0 \le i \le 2n-1$.

### 2025-04-11 main.tex
Parenthesis

@@
 \calvin{Add in note about the two type B cases.
-Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$
+Maybe really should just talk about $\Frobenius$ action} In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\multiplcativeScheme}$ with $\Frobenius$ acting by $w$ on the domain and by the cycle $(w,w_n w w_n)$ on the image, and $$x_{\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-1}} = \phi\left(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}\right).$$
         \item (Types B,C,D Case 2) $w$ is conjugate to a cycle of length $n$ with one negative sign.
- In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $w$ on the domain and by a cycle of length $2n$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n}).$
+ In this case $\algebraicGroup{T} = \restrictionOfScalars{\finiteFieldExtension{n}}{\finiteField}{\algebraicGroup{\UnitaryGroup}_1}$ with $\Frobenius$ acting by $w$ on the domain and by a cycle of length $2n$ on the image, and $$x_{\finiteField_{2n}^\times,\theta'}=\phi \left(x_{\NormOneGroup{2n},\theta}\right)$$ where $\theta'\left(t\right) = \theta\left(t^{1-q^n}\right).$
     \item ($\algebraicGroup{G}=\algebraicGroup{U}$ Case 1) $w$ is conjugate to cycle of length $n$, where $n$ is even.
@@
         \end{smallmatrix}\right)$ on the image, and 
-		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}).$$
+		$$x_{\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}} = \phi\left(x_{\multiplicativegroup{\finiteFieldExtension{n}},\alpha}\right).$$
 		Here $\left(\multiplicativegroup{\finiteFieldExtension{n}} \times \multiplicativegroup{\finiteFieldExtension{n}},\alpha \times \alpha^{-q}\right)$ is realized explicitly as follows.
@@
         w w_n& 0
-        \end{smallmatrix}\right)$ on the image, and $$x_{\multiplicativegroup{\finiteFieldExtension{2n}},\theta'}=\phi(x_{\NormOneGroup{2n},\theta})$$ where $\theta'(t) = \theta(t^{1-q^n})$
+        \end{smallmatrix}\right)$ on the image, and $$x_{\multiplicativegroup{\finiteFieldExtension{2n}},\theta'}=\phi\left(x_{\NormOneGroup{2n},\theta}\right)$$ where $\theta'\left(t\right) = \theta\left(t^{1-q^n}\right)$.
     \end{enumerate}

### 2025-04-11 main.tex
\algebraicGroup{A}

@@
 Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_N$ \elad{of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$?} corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
-Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{A_N}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{A}_N}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 We define

### 2025-04-11 main.tex
The permutation matrix I wrote is not always correct

@@
 	\item \begin{align*}
-		\prod_{i=0}^{n-1} \alpha\left(\zeta_n^{\left(-1\right)^i q^i \left(y_{i+1} - y_{2n-i}\right)}\right) =& \prod_{i=0}^{\frac{n}{2}-1} \alpha\left(\zeta_n^{q^{2i} y_{2i+1} + q^{2i+1} y_{2n-2i-1}}\right) \\
-		& \times \prod_{i=0}^{\frac{n}{2}-1} \alpha^{-q}\left(\zeta_n^{q^{2i} y_{2i+2} + q^{2i+1} y_{2n-2i-2}}\right).
+		& \prod_{i=0}^{n-1} \alpha\left(\zeta_n^{\left(-1\right)^i q^i \left(y_{i+1} - y_{2n-i}\right)}\right)\\
+		=& \prod_{\substack{0 \le i \le n-1\\
+				i \text{ is even}}} \alpha\left(\zeta_n^{q^{i} y_{i+1} - q^{i} y_{2n-i}}\right) \cdot \prod_{\substack{0 \le i \le n-1\\
+				i \text{ is odd}}} \alpha\left(\zeta_n^{-q^{i} y_{i+1} + q^{i} y_{2n-i}}\right) \\
+			=& \prod_{\substack{0 \le i \le n-1\\
+					i \text{ is even}}} \alpha\left(\zeta_n^{q^{i} y_{i+1} + q^{i + 1} y_{2n-i-1}}\right) \cdot \prod_{\substack{0 \le i \le n-1\\
+					i \text{ is even}}} \alpha^{-q}\left(\zeta_n^{q^{i} y_{i+2} + q^{i-1} y_{2n-i}}\right).
 	\end{align*}
@@
 The results now follow from these equalities and the norm computations, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition.
-This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that $q^i$ is the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation for every $0 \le i \le 2n-1$.
+This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation matches the one of the desired character.
+For example, in the norm one cases it is the permutation matrix that permutes the $y_i$'s so that the coefficient of $y_{i+1}$ is $q^{i}$ for every $0 \le i \le n-1$.
 %Now the results follow from checking that

### 2025-04-11 main.tex
Lemma

@@
 \end{enumerate}
-The results now follow from these equalities and the norm computations, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the proposition.
+The results now follow from these equalities and the norm computations, since we can easily find a permutation matrix in $\GL_{2n}$ that conjugates the character that corresponds to $\phi\left(x_{T,\bullet}\right)$ to the desired character from the lemma.
 This permutation matrix simply corresponds to the permutation that permutes the $y_i$'s so that the coefficient of $y_{i+1}$ in the exponent of the right hand side of the corresponding equation matches the one of the desired character.

### 2025-04-11 main.tex
fixed the description of the construction of tilde(T)

@@
 \usepackage{mathtools}
-%\usepackage{xcolor}
+\usepackage{xcolor}
 
@@
 \begin{document}
-%\pagecolor{black}
-%\color{white}
+\pagecolor{black}
+\color{white}
 
@@
 \end{lemma}
-
-We recall that \elad{Maybe we can help the reader and tell them that $m=1,2$} $$
+Although will we only use resitrictions of scalars from $\quadraticExtension$,
+we recall in general that $$
 	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_N\right)_a,
@@
 %\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}
-
-Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_N$ \elad{of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$?} corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
-Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{A}_N}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ and a Frobenius stable maximal torus $\algebraicGroup{T}_{0,\rho} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}_{0,\rho}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$?
+corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T}_{0,\rho})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
+Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{A}_N}\right)$?}\calvin{I guess I want the dual of $T^*$ technically speaking.
+I switched the notation to give the GLn a standard torus T0 too so now hopefully it makes sense.} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 We define

### 2025-04-11 main.tex
(back to default color scheme)
I edit a lot of times in black background, write text
Typos

--- 2025-04-11 main.tex
@@
 \end{lemma}
-
-We recall that \elad{Maybe we can help the reader and tell them that $m=1,2$} $$
+Although will we only use restriction of scalars from $\quadraticExtension$,
+we recall in general that $$
 	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_N\right)_a,
@@
 %\calvin{maybe should do inverses in the definition. Not sure if $\tau$ or $g$ make more sense.}
-
-Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ and a Frobenius stable maximal torus $\algebraicGroup{T}^* \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\algebraicGroup{\GL}_N$ \elad{of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$?} corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T})$ \elad{of $W\left(\algebraicGroup{T}^{\ast}\right)$?
-Or maybe $W\left(\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{A}_N}\right)$?} and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
+Given a torus character pair $(\algebraicGroup{T},\theta)$ with associated $\Frobenius$-twisted conjugacy class $(w) \in W(\algebraicGroup{T}_0)$ along with an embedding $\rho:\algebraicGroup{G}^* \to \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ and a Frobenius stable maximal torus $\algebraicGroup{T}_{0,\rho} \subset \restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ such that $\rho(\algebraicGroup{T}_0^*) \subset \algebraicGroup{T}_{0,\rho}^*$, let $\tilde{\algebraicGroup{T}}$ be the torus of $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_N}$ corresponding to the $\Frobenius$-twisted conjugacy class of $\rho(w) \in W(\algebraicGroup{T}_{0,\rho})$ and let $\tilde{\theta} \colon \tilde{\algebraicGroup{T}}^{\Frobenius} \to \multiplicativegroup{\cComplex}$ be a character such that $(\rho(s_{\algebraicGroup{T},\theta})) = (s_{\tilde{\algebraicGroup{T}},\tilde{\theta}})$.
 We define
 \[
-    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi \circ \det,\psi) = \epsilon_{\Tilde{\algebraicGroup{T}}} q^{-nm/2}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}({\det}_{\finiteFieldExtension{m}}t) \psi(\trace_{\finiteFieldExtension{m}}t).
+    g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) := \tau_{\Tilde{\algebraicGroup{T}}}(\tilde{\theta} \times \chi,\psi) = \epsilon_{\Tilde{\algebraicGroup{T}}} q^{-nm/2}\sum_{t \in \tilde{\algebraicGroup{T}}^{\Frobenius}} \tilde{\theta}^{-1}(t)\chi^{-1}({\det}_{\finiteFieldExtension{m}}t) \psi(\trace_{\finiteFieldExtension{m}}t).
 \]

### 2025-04-18 main.tex
Alternative write up for the proof of geometric conjugacy invariance

@@
 \begin{enumerate}
-    \item Unitary groups: The Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
+    \item (Unitary groups) The Weyl group $W\left(\algebraicGroup{T}_{0}\right)$ is isomorphic to the symmetric group $\SymmetricGroup_n$.
 If $\dot{w} \in \algebraicGroup{\UnitaryGroup}_n$ is a lift of $w \in W\left(\algebraicGroup{T}_{0}\right)$, the map $w \mapsto \dot{w} \cdot w_n$ sends a $w_n$-twisted $\SymmetricGroup_n$ conjugacy class to a $\SymmetricGroup_n$ conjugacy class.
@@
 
-\subsubsection{Some notation}
+\subsubsection{Some notation}\label{subsec:some-notation}
 Recall that by \Cref{subsubsec:rational-tori} maximal rational tori of $\algebraicGroup{G}$ correspond to certain pairs of partitions $\left(\lambda^+, \lambda^-\right)$ and we have that the $\Frobenius$ fixed points of a maximal torus $\algebraicGroup{T}$ corresponding to the pair $\left(\lambda^+, \lambda^-\right)$ are of the form $$T = \algebraicGroup{T}^{\Frobenius} \cong \prod_{j=1}^{\lengthof(\lambda^+)} \multiplicativegroup{\finiteFieldExtension{\lambda_j^{+}}} \times \prod_{i=1}^{\lengthof(\lambda^-)} \NormOneGroup{2 \lambda_i^{-}},$$
@@
 %The following computation in the proof of theorem \ref{lem:indep_geo_conj}.
-We will prove \Cref{lem:cochar_computation} by checking that if $\rho(s_{T,\theta}) = (s_{\Tilde{T},\Tilde{\theta}})$ then $g_{T}(\chi,\theta,\psi)$ equals to $\GaussSumTorusCharacter{\tilde{T}}{\tilde{\theta}}{\chi}{\fieldCharacter}$ up to some factors.
+We will prove \Cref{lem:indep_geo_conj} by checking that if $\rho(s_{T,\theta}) = (s_{\Tilde{T},\Tilde{\theta}})$ then $g_{T}(\chi,\theta,\psi)$ equals to $\GaussSumTorusCharacter{\tilde{T}}{\tilde{\theta}}{\chi}{\fieldCharacter}$ up to some factors.
 We will do so by breaking our tori into irreducible rational factors with the following lemma handling each possible factor.
@@
 \label{lem:cochar_computation}
-    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ send $x$ to $(x,-w_n x)$ be a $\Frobenius$ equivariant map.
+    Let $\phi:X_*(\algebraicGroup{T}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^n \to X_*(\tilde{\algebraicGroup{T}}^*) \cong (\mathbb{Q}/\mathbb{Z})_{p'}^{2n}$ be the $\Frobenius$ equivariant map sending $x$ to $(x,-w_n x)$.
 Then:
@@
 
-We let $\phi_{B,\lambda_i^+}, \phi_{B,\lambda_i^-}$ denote the $\phi$'s above in cases 1 and 2 respectivitly with $n = |\lambda_i|$. 
-Let $\phi_{U,\lambda_i}$ denote the $\phi$'s above in cases 3 and 4 with $n = |\lambda_i|$.
-
 \begin{proof}[Proof of \Cref{lem:indep_geo_conj}] 
@@
 \[
-g_{T,\rho}(\chi,\theta,\fieldCharacter)= g_{T}(\chi^{-1},\theta^{-1},\fieldCharacter) \cdot \begin{cases}
-        1  & G \neq Sp, GSp\\
-        \tau\left(\chi^{-1}, \fieldCharacter\right) & G = Sp \textnormal{ or } GSp
-    \end{cases}.
+g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \cdot \begin{cases}
+        \GaussSumSingleCharacter{\chi}{\fieldCharacter} & \algebraicGroup{G} = \algebraicGroup{\Sp}_{2n} \textnormal{ or } \algebraicGroup{G} = \algebraicGroup{GSp}_{2n},\\
+        1 & \text{otherwise.}        
+    \end{cases}
 \]
-\calvin{$\chi$ or $\chi^{-1}$? Check throughout proof!}
-We will do this casewise, demonstrating in each case that the Frobeinus equivariant map $X_*(\algebraicGroup{T}) \to X_*(\algebraicGroup{G})$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}.
-Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subseteq \algebraicGroup{G}$ and geometric Frobeinus action on $X_*(\algebraicGroup{T})$.
-\calvin{add in GL case}
-\begin{enumerate}
-    \item[($\algebraicGroup{U}$)] Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$. Let $w \circ w_n$ have cycle decomposition $\lambda$ 
-	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. Then
-	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
-	and applying \Cref{lem:cochar_computation}
-    \begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-q}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
-	\begin{comment}old hacky version
-	\calvin{right now can only deal with the case that $\chi$ is a square} Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$.
+
+We prove this by showing that the Frobeinus equivariant map $\CharacterLattice{\algebraicGroup{T}} \to \CharacterLattice{\algebraicGroup{G}}$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}.
+Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subset \algebraicGroup{G}$ and the geometric Frobeinus action on $\CocharacterLattice{\algebraicGroup{T}}$.
+
+Assume that $\left(T, \theta\right)$ corresponds to the pair of partitions $\left(\lambda^+, \lambda^-\right)$ and to the characters $\alpha_1 \times \dots \times \alpha_{\lengthof\left(\lambda^+\right)} \colon \multiplicativegroup{\finiteFieldExtension{\lambda^+}} \to \multiplicativegroup{\cComplex}$ and $\theta_1 \times \dots \times \theta_{\lengthof\left(\lambda^-\right)} \colon \NormOneGroup{2 \lambda^{-}} \to \multiplicativegroup{\cComplex}$ as in \Cref{subsubsec:rational-tori} and \Cref{subsec:some-notation}.
+
+Let $\algebraicGroup{T}_{i,+} \subset \algebraicGroup{T}$ be the component corresponding to $\multiplicativegroup{\finiteFieldExtension{\lambda_i}}$ in the description above.
+Similarly, let $\algebraicGroup{T}_{i,-} \subset \algebraicGroup{T}$ and be the component corresponding to $\NormOneGroup{2 \lambda_i^{-}}$.
+Let us denote by $\tilde{\algebraicGroup{T}}_{i,+} \subset \tilde{\algebraicGroup{T}}$ the component corresponding to $\multiplicativegroup{\finiteFieldExtension{\lambda_i^+}} \times \multiplicativegroup{\finiteFieldExtension{\lambda_i^+}}$ and by $\tilde{\algebraicGroup{T}}_{i,-} \subset \tilde{\algebraicGroup{T}}$ the component corresponding $\multiplicativegroup{\finiteFieldExtension{2 \lambda_i^-}}$.
+Let $$\phi_{\pm,i} \colon \CocharacterLattice{\algebraicGroup{T}^{\ast}_{i,\pm}} \to \CocharacterLattice{\tilde{\algebraicGroup{T}}^{\ast}_{i,\pm}}$$ be the map as in \Cref{lem:cochar_computation}.
+
+In all cases except for the case where $\algebraicGroup{G} = \algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{G} = \algebraicGroup{\GSp}_{2n}$, we have that $\phi \colon \CocharacterLattice{\algebraicGroup{T^{\ast}}} \to \CocharacterLattice{\algebraicGroup{\tilde{T}^{\ast}}}$ is given by $$\phi = \left(\bigoplus_{i = 1}^{\lengthof\left(\lambda^+\right)} \phi_{+,i}\right) \oplus \left(\bigoplus_{i=1}^{\lengthof\left(\lambda^-\right)} \phi_{-,i}\right).$$
+By \Cref{lem:cochar_computation}, we have in these cases $\left(\tilde{\algebraicGroup{T}}, \tilde{\theta}\right) = \left(T', \theta'\right)$ and thus
+$$g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter}.$$
+
+If $\algebraicGroup{G} = \algebraicGroup{\Sp}_{2n}$ or $\algebraicGroup{G} = \algebraicGroup{\GSp}_{2n}$ then we have that $\phi \colon \CocharacterLattice{\algebraicGroup{T^{\ast}}} \to \CocharacterLattice{\algebraicGroup{\tilde{T}^{\ast}}}$ is given by $$\phi = \left(\bigoplus_{i = 1}^{\lengthof\left(\lambda^+\right)} \phi_{+,i}\right) \oplus \left(\bigoplus_{i=1}^{\lengthof\left(\lambda^-\right)} \phi_{-,i}\right) \oplus 0.$$ This comes from the fact that the split torus of $\algebraicGroup{\SO}_{2n + 1}$ has one as its middle component.
+Thus by \Cref{lem:cochar_computation}, we have in this case $\left(\tilde{\algebraicGroup{T}}, \tilde{\theta}\right) = \left(T' \times \multiplcativeScheme, \theta' \times 1\right)$ and therefore
+$$g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \GaussSumSingleCharacter{\chi}{\fieldCharacter}.$$
+\end{proof}
+
+%\begin{proof}
+%We let $\phi_{B,\lambda_i^+}, \phi_{B,\lambda_i^-}$ denote the $\phi$'s above in cases 1 and 2 respectivitly with $n = |\lambda_i|$. 
+%Let $\phi_{U,\lambda_i}$ denote the $\phi$'s above in cases 3 and 4 with $n = |\lambda_i|$.
+%
+%
+%\calvin{add in GL case}
+%\begin{enumerate}
+%    \item[($\algebraicGroup{U}$)] Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$. Let $w \circ w_n$ have cycle decomposition $\lambda$ 
+%	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. Then
+%	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
+%	and applying \Cref{lem:cochar_computation}
+%    \begin{align*}
+%		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-q}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+%	\end{align*}
+%	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
+%	\begin{comment}old hacky version
+%	\calvin{right now can only deal with the case that $\chi$ is a square} Given $(T,\theta)$, let $T$ correspond to the $w_n$-twisted conjugacy class $[w]$.
 Let $w \circ w_n$ have cycle decomposition $\lambda$
-	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. 
-	Write $\chi = \chi'+\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}$ and $\chi'^{-1} = (\chi')^c$. 
-	Then
-	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
-	and applying \Cref{lem:cochar_computation}
-	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i} \begin{cases}
-			\GaussSumCharacter{\left(\alpha_i \times \chi'\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} \times \GaussSumCharacter{\left(\alpha_i^{-1}\times \chi'^c\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} & \lambda_i \textnormal{ even} \\
-			\GaussSumCharacter{\left(\theta'_i \times \chi'\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{2\lambda_i}} & \lambda_i \textnormal{ odd}
-		\end{cases}
-	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.\
-	\end{comment}
-	\item[($\algebraicGroup{SO}_{2n+1}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
-	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
-	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} $$
-	and applying \Cref{lem:cochar_computation}
-	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
-	\item[($\algebraicGroup{Sp}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
-	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
-	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} \oplus \left(0:X_*(\algebraicGroup{T}) \to \mathbb{Z}\right)$$
-	applying \Cref{lem:cochar_computation}
-	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}} \times \tau(\chi,\psi)
-	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi) \cdot \tau(\chi,\psi)$. \calvin{check inverses}
-	\item[($\algebraicGroup{SO}_{2n}^+$)] Let $T$ correspond to the signed permutation conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
-	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
-	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
-	applying \Cref{lem:cochar_computation}
-	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
-	\item[($\algebraicGroup{SO}_{2n}^-$)] Let $T$ correspond to the $(-n,n)$-twisted permutation conjugacy class $[w]$ with cycle decompositionof $[w \cdot (-n,n)]$ equal to $(\lambda^+,\lambda^-)$ 
-	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
-	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
-	applying \Cref{lem:cochar_computation}
-	\begin{align*}
-		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
-	\end{align*}
-	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
-\end{enumerate}
+%	and $\theta$ decompose as a product over $\lambda_i$ of $\alpha_i$ if $\lambda_i$ is even and $\theta_i$ if $\lambda_i$ is odd. 
+%	Write $\chi = \chi'+\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}$ and $\chi'^{-1} = (\chi')^c$. 
+%	Then
+%	$$\rho_* = \bigoplus_{\lambda_i} \phi_{U,\lambda_i}$$
+%	and applying \Cref{lem:cochar_computation}
+%	\begin{align*}
+%		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i} \begin{cases}
+%			\GaussSumCharacter{\left(\alpha_i \times \chi'\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} \times \GaussSumCharacter{\left(\alpha_i^{-1}\times \chi'^c\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i/2}}} & \lambda_i \textnormal{ even} \\
+%			\GaussSumCharacter{\left(\theta'_i \times \chi'\right)}{\left(\chi_{\mathbb{F}}\circ \FieldNorm{\quadraticExtension}{\mathbb{F}}\right)}{\fieldCharacter_{2\lambda_i}} & \lambda_i \textnormal{ odd}
+%		\end{cases}
+%	\end{align*}
+%	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.\
+%	\end{comment}
+%	\item[($\algebraicGroup{SO}_{2n+1}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
+%	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+%	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} $$
+%	and applying \Cref{lem:cochar_computation}
+%	\begin{align*}
+%		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+%	\end{align*}
+%	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
+%	\item[($\algebraicGroup{Sp}$)] Given $(T,\theta)$, let $T$ correspond to the conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
+%	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+%	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-} \oplus \left(0:X_*(\algebraicGroup{T}) \to \mathbb{Z}\right)$$
+%	applying \Cref{lem:cochar_computation}
+%	\begin{align*}
+%		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}} \times \tau(\chi,\psi)
+%	\end{align*}
+%	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi) \cdot \tau(\chi,\psi)$. \calvin{check inverses}
+%	\item[($\algebraicGroup{SO}_{2n}^+$)] Let $T$ correspond to the signed permutation conjugacy class $[w]$ with cycle decomposition $(\lambda^+,\lambda^-)$ 
+%	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+%	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
+%	applying \Cref{lem:cochar_computation}
+%	\begin{align*}
+%		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+%	\end{align*}
+%	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
+%	\item[($\algebraicGroup{SO}_{2n}^-$)] Let $T$ correspond to the $(-n,n)$-twisted permutation conjugacy class $[w]$ with cycle decompositionof $[w \cdot (-n,n)]$ equal to $(\lambda^+,\lambda^-)$ 
+%	and $\theta$ decompose as a product $\Pi_{\lambda_i^+ }\alpha_{i+} \times \Pi_{\lambda_i^-}\theta_{i-}$. Then
+%	$$\rho_* = \bigoplus_{\lambda_i^+} \phi_{B,\lambda_i^+} \oplus \bigoplus_{\lambda_i^-} \phi_{B,\lambda_i^-}$$
+%	applying \Cref{lem:cochar_computation}
+%	\begin{align*}
+%		g_{T,\rho}(\chi,\theta,\psi) &= \Pi_{\lambda_i^+} \GaussSumCharacter{\alpha_i}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \GaussSumCharacter{\alpha_i^{-1}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{\lambda_i^+}}} \times \Pi_{\lambda_i^-} \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2\lambda_i^-}}
+%	\end{align*}
+%	which is equal to $g_{T}(\chi^{-1},\theta^{-1},\psi)$.
+%\end{enumerate}
 
@@
 \end{comment}
-\end{proof}
+%\end{proof}
 

### 2025-04-18 main.tex
added Cor 9.7 Bon to DL section and moved some things around in there. Added covering group case to the proof of lemma 3.15

@@
 Some authors distinguish the Frobenius actions on $\algebraicGroup{G}$ and $\algebraicGroup{G}^{\ast}$ by writing $\Frobenius$ and $\Frobenius^{\ast}$, respectively, but we will not do so and simply denote both actions by $\Frobenius$.
-
-Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
-By \cite[Proposition 13.7 (ii)]{DigneMichel1991}, we have an exact sequence
-\begin{equation}
-	\label{eq:DL}
-	\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T} \ar[r] & 0}
-\end{equation}
-with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n))$
-for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
-Here, $$\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$$ is the torus norm map.
-
-We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\ladicnumbers}$ is a character.
-By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
-\[
-\exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
-\]
-for large enough $n$.
-This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel1991} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
-Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
-
-Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
-Similarly, denote the $\Frobenius$-stable Weyl group orbit in $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
-
-We say that the torus character pairs $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ for $\algebraicGroup{G}$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{\algebraicGroup{T},\theta})$ and $(s_{\algebraicGroup{T}',\theta'})$ are equal.
-This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
-
-\begin{example}
-	%\elad{Correct example or remove it}\calvin{They are geo conjugate in $\algebraicGroup{Sp}_4$}
-	Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
-	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
-Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
-	Both the tori $\algebraicGroup{T}_2 \times \algebraicGroup{T}_2$ and $\algebraicGroup{T}_2'$ are tori inside $\algebraicGroup{Sp}_4$.
-	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.
-Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$.
-The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$.
-We thus have
-	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
-\end{example}
-
-The virtual representations $\RTThetaVirtual{T}{G}{\theta}$ and $\RTThetaVirtual{T'}{G}{\theta'}$ share an irreducible subrepresentation only if $(T,\theta),(T',\theta')$ are geometrically conjugate.
-This yields a natural partitioning of the irreducible representations of $\algebraicGroup{G}(\finiteField)$: the \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $\RTTheta{T}{\theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
-
+\begin{table}
 \begin{center}
+\caption{Dual groups for $\algebraicGroup{G}$ and $\algebraicGroup{\GroupExtension{G}}$.}
 	\begin{tabular}{|c|c|c|c|c|c|} \hline
@@
 The Frobenius root action on the Weyl group is described in \Cref{subsubsec:rational-tori}. 
-
-Let us specialize to the classical groups $\algebraicGroup{G}$ and their extensions $\GroupExtension{\algebraicGroup{G}}$ from Sections \ref{subsec:isometry-groups} and \ref{subsec:similitute-groups}.
-We will need the following facts about Lusztig series of $\algebraicGroup{G}$ and $\GroupExtension{\algebraicGroup{G}}$.
-
-The first fact tells us that Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ are unions of Harish-Chandra series, and establishes a relation between the corresponding semisimple conjugacy classes.
+\end{table}
+
+Fix an isomorphism $\multiplicativegroup{\algebraicClosure{\finiteField}} \cong (\mathbb{Q}/\mathbb{Z})_{p'}$ and an embedding $\exp:(\mathbb{Q}/\mathbb{Z})_{p'} \to \overline{\mathbb{Q}_\ell}^\times$.
+By \cite[Proposition 13.7 (ii)]{DigneMichel1991}, we have an exact sequence
+\begin{equation}
+	\label{eq:DL}
+	\xymatrix{0 \ar[r] & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r]^{\Frobenius-\idmap} & \CocharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}} \ar[r] & \algebraicGroup{T} \ar[r] & 0}
+\end{equation}
+with the last map being $y \mapsto \aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n))$
+for $\zeta_n$ being a $q^n-1$ root of unity corresponding to $1/(q^n-1) \in (\mathbb{Q}/\mathbb{Z})_{p'}$ and sufficiently large $n$ (large enough so that $\algebraicGroup{T}\left(\finiteFieldExtension{n}\right)$ is split).
+Here, $$\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(t) = t\cdot \Frobenius(t)\cdot \Frobenius^2(t)\cdot  \hdots \cdot \Frobenius^{n-1}(t)$$ is the torus norm map.
+
+We say that $(\algebraicGroup{T},\theta)$ is a \emph{torus character pair} for $\algebraicGroup{G}^{\Frobenius}$ if $\algebraicGroup{T} \subset \algebraicGroup{G}$ is a maximal torus and $\theta \colon \algebraicGroup{T}^{\Frobenius} \to \multiplicativegroup{\ladicnumbers}$ is a character.
+By the discussion above, given a torus character pair  $(\algebraicGroup{T},\theta)$ for $\algebraicGroup{G}^{\Frobenius}$, we may conjugate $\algebraicGroup{T}$ to a fixed torus $\algebraicGroup{T}'$ and associate to $\theta$ a twisted Frobenius (twisted by an element of $W\left(\algebraicGroup{T}\right)$ in the twisted Weyl group conjugacy class corresponding to $\algebraicGroup{T}$) stable element $x_{\algebraicGroup{T},\theta}$ of $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ via the equality
+\[
+\exp(\innerproduct{x_{\algebraicGroup{T},\theta}}{y}) = \theta(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}(y(\zeta_n)))
+\]
+for large enough $n$.
+This $x_{\algebraicGroup{T},\theta}$ is well defined up to the Weyl group, and in fact, by \cite[Corollary 13.9]{DigneMichel1991} there is a correspondence between torus character pairs $(\algebraicGroup{T},\theta)$ and $\Frobenius$-stable Weyl group orbits in $\CharacterLattice{\algebraicGroup{T}'}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$.
+Using the given the identification $\CharacterLattice{\algebraicGroup{T}} = \CocharacterLattice{\algebraicGroup{T}^{\ast}}$ and composing with \eqref{eq:DL} (with $\algebraicGroup{T}$ replaced with $\algebraicGroup{T}^{\ast}$), we associate to a torus character pair a Frobenius stable semisimple conjugacy class in $\algebraicGroup{G}^*$.
+
+Denote the Frobenius semisimple conjugacy class associated to a torus character pair $(\algebraicGroup{T},\theta)$ by $(s_{\algebraicGroup{T},\theta})$.
+Similarly, denote the $\Frobenius$-stable Weyl group orbit in $\CharacterLattice{\algebraicGroup{T}}_{(\mathbb{Q}/\mathbb{Z})_{p'}}$ corresponding to $(\algebraicGroup{T},\theta)$ by $(x_{\algebraicGroup{T},\theta}).$
+
+We say that the torus character pairs $(\algebraicGroup{T},\theta)$ and $(\algebraicGroup{T}',\theta')$ for $\algebraicGroup{G}$ are \emph{geometrically conjugate} if the geometric conjugacy classes $(s_{\algebraicGroup{T},\theta})$ and $(s_{\algebraicGroup{T}',\theta'})$ are equal.
+This is equivalent to the following: there exists $n \ge 1$ and $h \in {\algebraicGroup{G}}^{\Frobenius^n}$ such that $h \algebraicGroup{T}^{\Frobenius^n} h^{-1} = \left(\algebraicGroup{T}'\right)^{\Frobenius^n}$ and such that $$\theta\left(\aFieldNorm_{\algebraicGroup{T}^{\Frobenius^n}:\algebraicGroup{T}^{\Frobenius}}\left(t\right)\right) = \theta'\left(\aFieldNorm_{\left(\algebraicGroup{T}'\right)^{\Frobenius^n}:\left(\algebraicGroup{T}'\right)^{\Frobenius}}\left(h t h^{-1}\right)\right),$$ for any $t \in \algebraicGroup{T}^{\Frobenius^n}$.
+
+\begin{example}
+	%\elad{Correct example or remove it}\calvin{They are geo conjugate in $\algebraicGroup{Sp}_4$}
+	Let $\algebraicGroup{T}'_2 = \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme}$ and $$\algebraicGroup{T}_2 = \left\{x \in \restrictionOfScalars{\finiteFieldExtension{2}}{\finiteField}{\multiplcativeScheme} \mid x \involution{x} = 1 \right\}.$$
+	Then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius} = \multiplicativegroup{\finiteFieldExtension{2}}$ and $\algebraicGroup{T}_2^{\Frobenius} = \NormOneGroup{2}$.
+Let $\theta \colon \NormOneGroup{2} \to \multiplicativegroup{\ladicnumbers}$ be a character, and let $\theta' \colon \multiplicativegroup{\finiteFieldExtension{2}} \to \multiplicativegroup{\ladicnumbers}$ be the character given bv $$\theta'\left(x\right) = \theta\left(x^{1-q}\right).$$
+	Both the tori $\algebraicGroup{T}_2 \times \algebraicGroup{T}_2$ and $\algebraicGroup{T}_2'$ are tori inside $\algebraicGroup{Sp}_4$.
+	We claim that the torus character pairs $\left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2, \theta \times \theta\right)$ and $\left(\algebraicGroup{T}'_2, \theta'\right)$ are geometrically conjugate.
+Indeed, if $m \ge 2$ is even, then $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} = \multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}}$ and $\algebraicGroup{T}_2^{\Frobenius^m} = \multiplicativegroup{\finiteFieldExtension{m}}$.
+The norm map $\left(\algebraicGroup{T}'_2\right)^{\Frobenius^{m}} \to \left(\algebraicGroup{T}'_2\right)^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \times \multiplicativegroup{\finiteFieldExtension{m}} \ni \left(x,y\right) \mapsto \FieldNorm{m}{2}\left(x\right) \FieldNorm{m}{2}\left(y\right)$, while the norm map $\algebraicGroup{T}_2^{\Frobenius^{m}} \to \algebraicGroup{T}_2^{\Frobenius}$ is given by $\multiplicativegroup{\finiteFieldExtension{m}} \ni x \mapsto \FieldNorm{m}{2}\left(x\right)^{1-q}$.
+We thus have
+	$$\left(\theta \times \theta\right) \circ \aFieldNorm_{ \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius^m} : \left(\algebraicGroup{T}_2 \times \algebraicGroup{T}_2\right)^{\Frobenius} } = \theta' \circ \aFieldNorm_{\left(\algebraicGroup{T}'_2\right)^{\Frobenius^m} \colon \left(\algebraicGroup{T}'_2\right)^{\Frobenius}}.$$
+\end{example}
+
+The virtual representations $\RTThetaVirtual{T}{G}{\theta}$ and $\RTThetaVirtual{T'}{G}{\theta'}$ share an irreducible subrepresentation only if $(T,\theta),(T',\theta')$ are geometrically conjugate.
+This yields a natural partitioning of the irreducible representations of $\algebraicGroup{G}(\finiteField)$: the \emph{geometric Lusztig series} $\LusztigSeries{\algebraicGroup{G}^{\Frobenius}}{s}$ associated to a Frobenius stable geometric conjugacy class $(s) \subset \algebraicGroup{G}^*$ consists of all (equivalence classes of) irreducible representations $\pi$ which appear with non-zero multiplicity in $\RTTheta{T}{\theta}$ for some $(T,\theta)$ such that $(s_{\algebraicGroup{T},\theta}) = (s)$.
+
+For later use, we note Lusztig series are a coarsening of Harish-Chandra series.
+%The first fact tells us that Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ are unions of Harish-Chandra series, and establishes a relation between the corresponding semisimple conjugacy classes.
 \begin{proposition}[{\cite[Proof of Corollary 3.3.21]{GeckMalle2020}}]\label{prop:lusztig-series-are-unions-of-harish-chandra-series}
@@
 
-The next fact establishes a relation between the Lusztig series of $\GroupExtension{\algebraicGroup{G}}$ and of $\algebraicGroup{G}$.
-\elad{Explain $i^{\ast}$}
+Let us now specialize to the classical groups $\algebraicGroup{G}$ and their extensions $\GroupExtension{\algebraicGroup{G}}$ from Sections \ref{subsec:isometry-groups} and \ref{subsec:similitute-groups}.
+
+In these cases, the map $i:\algebraicGroup{G} \to \GroupExtension{\algebraicGroup{G}}$ yields a pullback map $i^*:\GroupExtension{\algebraicGroup{G}}^* \to \algebraicGroup{G}^*$ well defined up to composing with an inner automorphism induced by an $\Frobenius$-stable element of the maximal torus.
+From chasing definitions, one finds
+
+\begin{proposition}[{\cite[Corollary 9.7]{Bonnafe2006}}]
+	\label{prop:i*isrestriction}
+	$i^*(s_{\algebraicGroup{T},\theta}) = s_{\algebraicGroup{T} \cap G, \theta|_{G}}$.
+\end{proposition}
+
+This gives a natural \calvin{check that this is correct} $|\algebraicGroup{Z}(\GroupExtension{\algebraicGroup{G}})(\finiteField)|/|\algebraicGroup{Z}(\algebraicGroup{G}
+)(\finiteField)|$-to-one map from Lusztig packets for $\GroupExtension{\algebraicGroup{G}}$ to those for $\algebraicGroup{G}$.
+
+The following proposition explains how $i^*$ relates irreducible representations of $\GroupExtension{\algebraicGroup{G}}$ with their restriction to $\algebraicGroup{G}$.
 
@@
 
-Finally, the next fact concerns the number of cuspidal representations in a Lusztig series of $\GroupExtension{\algebraicGroup{G}}$.
+For our later arguments, it is useful to only have one cuspidal representation in a Lusztig packet.
+Unfortunately, this is rarely the case for $\algebraicGroup{G}$.
+However, it is true for  $\GroupExtension{\algebraicGroup{G}}$.
 
@@
 g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \cdot \begin{cases}
-        \GaussSumSingleCharacter{\chi}{\fieldCharacter} & \algebraicGroup{G} = \algebraicGroup{\Sp}_{2n} \textnormal{ or } \algebraicGroup{G} = \algebraicGroup{GSp}_{2n},\\
+        \GaussSumSingleCharacter{\chi}{\fieldCharacter} & \algebraicGroup{H} = \algebraicGroup{\Sp}_{2n} \textnormal{ or } \algebraicGroup{H} = \algebraicGroup{GSp}_{2n},\\
         1 & \text{otherwise.}        
@@
 
-We prove this by showing that the Frobeinus equivariant map $\CharacterLattice{\algebraicGroup{T}} \to \CharacterLattice{\algebraicGroup{G}}$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}.
+In the $\algebraicGroup{G}$ case, we prove this by showing that the Frobeinus equivariant map $\CharacterLattice{\algebraicGroup{T}} \to \CharacterLattice{\algebraicGroup{G}}$ decomposes into a direct sum of $\phi$'s appearing in \Cref{lem:cochar_computation}.
 Useful here is the description of the rational maximal tori $\algebraicGroup{T} \subset \algebraicGroup{G}$ and the geometric Frobeinus action on $\CocharacterLattice{\algebraicGroup{T}}$.
@@
 $$g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \GaussSumSingleCharacter{\chi}{\fieldCharacter}.$$
+
+In the general $\GroupExtension{\algebraicGroup{G}}$ case, $\rho$ factors as
+\[
+	\GroupExtension{\algebraicGroup{G}}^* \to_{i^*} \algebraicGroup{G}^* \to_{\rho_{\algebraicGroup{G}}} \algebraicGroup{GL}_n.
+\]
+By \Cref{prop:i*isrestriction}, $\rho(s_{\algebraicGroup{T},\theta}) = \rho_{\algebraicGroup{G}}(s_{\algebraicGroup{T} \cap \algebraicGroup{G},\theta|_{\algebraicGroup{T} \cap \algebraicGroup{G}}})$ and so
+\[
+	g_{\algebraicGroup{T},\rho}(\chi,\theta,\psi) = g_{\algebraicGroup{T} \cap \algebraicGroup{G},\rho}(\chi,\theta|_{\algebraicGroup{T} \cap \algebraicGroup{G}},\psi)
+\]
+which aplying our above work on $\algebraicGroup{G}$ and $\rho_{\algebraicGroup{G}}$ is equal to
+\begin{align*}
+	g_{\algebraicGroup{T} \cap \algebraicGroup{G},\rho_{\algebraicGroup{G}}}(\chi,\theta|_{\algebraicGroup{T} \cap \algebraicGroup{G}},\psi) = \GaussSumTorusCharacter{T'}{\theta'}{\chi}{\fieldCharacter} \cdot \begin{cases}
+        \GaussSumSingleCharacter{\chi}{\fieldCharacter} & \algebraicGroup{G} = \algebraicGroup{\Sp}_{2n} \textnormal{ or } \algebraicGroup{G} = \algebraicGroup{GSp}_{2n},\\
+        1 & \text{otherwise.}        
+    \end{cases}
+\end{align*}
 \end{proof}

### 2025-04-21 main.tex
Minor changes

@@
 In these cases, the map $i:\algebraicGroup{G} \to \GroupExtension{\algebraicGroup{G}}$ yields a pullback map $i^*:\GroupExtension{\algebraicGroup{G}}^* \to \algebraicGroup{G}^*$ well defined up to composing with an inner automorphism induced by an $\Frobenius$-stable element of the maximal torus.
-From chasing definitions, one finds
+From chasing definitions, one finds the following.
 
@@
 	\label{prop:i*isrestriction}
-	$i^*(s_{\algebraicGroup{T},\theta}) = s_{\algebraicGroup{T} \cap G, \theta|_{G}}$.
+	$i^*(s_{\algebraicGroup{T},\theta}) = s_{\algebraicGroup{T} \cap G, \theta\restriction_{\algebraicGroup{T} \cap G}}$.
 \end{proposition}
@@
 This gives a natural \calvin{check that this is correct} $|\algebraicGroup{Z}(\GroupExtension{\algebraicGroup{G}})(\finiteField)|/|\algebraicGroup{Z}(\algebraicGroup{G}
-)(\finiteField)|$-to-one map from Lusztig packets for $\GroupExtension{\algebraicGroup{G}}$ to those for $\algebraicGroup{G}$.
+)(\finiteField)|$-to-one map from geometric Lusztig series for $\GroupExtension{\algebraicGroup{G}}$ to those for $\algebraicGroup{G}$.
 

### 2025-04-25 main.tex
Tried fixing multiplicativity. Not successful so far

@@
 \section{Multiplicativity of Jacobi sums} \label{appendix:multiplicativity-of-jacobi-sums}
-\elad{TODO: Work on appendix}
-
+
+In this section, we explain how to deduce \Cref{thm:multiplicativity-in-terms-of-gauss-sums} from the results of \cite{GirschZelingher2025}.
+
+Let us keep the notations as in \Cref{subsec:multiplicativity}.
 \Cref{thm:multiplicativity-in-terms-of-gauss-sums} was proved in \cite{GirschZelingher2025} under the assumption that $\pi' \subset \Ind{P}{H'}{\tau' \overline{\otimes} \pi''}$, where $\pi''$ is an irreducible cuspidal representation of $H''$ and $\tau'$ is an irreducible representation of $\GL_{k'}\left(\finiteField\right)$ such that $\chi^{-1}$ nor $\involution{\chi}$ appear in the cuspidal support of $\tau'$.
@@
 	\end{align*}	
-
 	It follows that $$\dblJacobiSum{\rho}{\chi} f = \chi\left(\pm 1\right)^k\dblJacobiSumScalar{\tau \otimes \minusInvolution{\chi_{\GL_k}}}{\involutionPlusOne{\chi}} \dblJacobiSumScalar{\pi'}{\chi} f.$$
@@
 \end{proof}
+\begin{remark}
+	This proof is similar to the one in \cite{Chang1997}.
+\end{remark}
 The assumption in \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds in certain cases.
@@
 
-\begin{proposition}
+\begin{theorem}\label{prop:when-k-equals-one-hypothesis-holds}
 	Suppose that $k=1$. Then the assumption of \Cref{prop:multiplicativity-of-jacobi-sum-given-support} holds.
-\end{proposition}
-\begin{proof}\elad{Work on this}
+\end{theorem}
+
+Before the proof, we prove a lemma.
+\begin{lemma}
+	Suppose that $k = 1$.
+Then for any $B \in \EndomorphismRing\left(\hermitianSpace\right)$ with $B \notin P$, there exists $t \in \multiplicativegroup{\quadraticExtension}$ such that $$\sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(t \trace\left(B u\right)\right) = 0.$$
+\end{lemma}
+\begin{proof}
+	We have that $\xIsotropic$ and $\yIsotropic$ are one-dimensional spaces over $\quadraticExtension$.
+Let $b_{+}$ and $b_{-}$ be bases of $\xIsotropic$ and $\yIsotropic$, respectively, such that $\innerproduct{b_{+}}{b_{-}} = 1$.
+Let us choose a basis $\mathcal{B'}$ for $\hermitianSpace'$.
+Then with respect to the basis $\mathcal{B} = (b_{+}) \vee \mathcal{B'} \vee (b_{-})$, elements in $N$ are represented by matrices of the form
+	$$\begin{pmatrix}
+		1 & X & z\\
+		& \IdentityMatrix{\dim_{\quadraticExtension}\hermitianSpace'} & Y\\
+		& & 1
+	\end{pmatrix},$$
+	where $X,Y$ and $z$ satisfy certain relations. The center of $N$ denoted $Z\left(N\right)$ consists of matrices of the form
+	$$c\left(z\right) = \begin{pmatrix}
+	1 &  & z\\
+	& \IdentityMatrix{\dim_{\quadraticExtension}\hermitianSpace'} & \\
+	& & 1
+\end{pmatrix},$$ where	
+	\begin{enumerate}
+		\item $z \in \quadraticExtension$ and $z + \epsilon_{\hermitianSpace} \cdot \involution{z} = 0$ if $\quadraticExtension \ne \finiteField$.
+		\item $z = 0$ if $\epsilon_{\hermitianSpace} = 1$ and $\quadraticExtension = \finiteField$.
+		\item $z \in \finiteField$ if $\epsilon_{\hermitianSpace} = -1$ and $\quadraticExtension = \finiteField$.
+	\end{enumerate}
+	Let us write 
+	$$\sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(t \trace\left(B u\right)\right) = \sum_{u \in N \slash Z\left(N\right)} \sum_{z} \fieldCharacter_{\quadraticExtension}\left(t \trace\left(B u c\left(z\right)\right)\right).$$
+	Fix $u$. Let us write $$Bu = \begin{pmatrix}
+		a_{1 \times 1} & b_{1 \times \dim_{\quadraticExtension}\hermitianSpace'} & c_{1 \times 1}\\
+		a'_{\dim_{\quadraticExtension}\hermitianSpace' \times 1} & b'_{\dim_{\quadraticExtension}\hermitianSpace' \times \dim_{\quadraticExtension}\hermitianSpace'} & c'_{\dim_{\quadraticExtension}\hermitianSpace' \times 1}\\
+		a''_{1 \times 1} & b''_{1 \times \dim_{\quadraticExtension}\hermitianSpace'} & c''_{1 \times 1}\\		
+	\end{pmatrix}.$$
+	Then $$\trace\left(B u c \left(z\right)\right) = \trace\left(B u\right) + a''_{1 \times 1} z.$$
+	Suppose that $a''_{1 \times 1} \ne 0$.
+We claim that except for the case $\left(\epsilon_{\hermitianSpace}, \quadraticExtension\right) = \left(1,\finiteField\right)$ we can find $t \in \multiplicativegroup{\quadraticExtension}$ such that the inner sum $$\sum_{z} \fieldCharacter_{\quadraticExtension}\left(t a_{1 \times 1}'' z\right)$$ vanishes.
+	\begin{enumerate}
+		\item If $\quadraticExtension \ne \finiteField$ and $\epsilon_{\hermitianSpace} = -1$, take $t = \left(a''_{1 \times 1}\right)^{-1}$.
+Since $z = \involution{z}$ it follows that $z \in \finiteField$ and $\trace_{\quadraticExtension \slash \finiteField}\left(z\right) = 2z$ and thus the inner sum will vanish.
+		\item If $\quadraticExtension \ne \finiteField$ and $\epsilon_{\hermitianSpace} = 1$, let $\delta \in \multiplicativegroup{\quadraticExtension}$ be a trace zero element.
+Then $\delta \cdot z = \involution{\left(\delta \cdot z\right)}$ and thus $\delta \cdot z \in \finiteField$.
+Taking $t = \delta \left(a_{1 \times 1}''\right)^{-1}$ gives a sum of a non-trivial character of $\finiteField$ over $\finiteField$ and thus this sum vanishes.
+		\item $\quadraticExtension = \finiteField$ and $\epsilon_{\hermitianSpace} = -1$. In this case we simply take $t =
+		\left(a''_{1 \times 1}\right)^{-1}$ and get an inner sum of a non-trivial character of $\finiteField$ over $\finiteField$ and thus it vanishes.
+	\end{enumerate}
+	Thus in all cases except for the case $\left(\epsilon_{\hermitianSpace}, \quadraticExtension\right) = \left(1,\quadraticExtension\right)$ we showed that $a''_{1 \times 1} = 0$.
+We have in all cases that $N \slash N\left(Z\right)$ is isomorphic to the additive group $\quadraticExtension^{\dim_{\quadraticExtension}\hermitianSpace'}$.
+\end{proof}
+
+\begin{proof}[Proof of \Cref{prop:when-k-equals-one-hypothesis-holds}]
 	Notice that for $x \in G$, $$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{g \in G} f\left(xg\right) \genJacobiKernel{\chi}\left(g\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P} f\left(p\right) \genJacobiKernel{\chi}\left(x^{-1} p\right),$$
@@
 	$$\left(\dblJacobiSum{\rho}{\chi} f\right)\left(x\right) = \frac{1}{\sqrt{\sizeof{\lieAlgebra}}} \sum_{p \in G \cap P}  \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) v_\tau \otimes v_{\pi'}.$$
-	As before, we may write
-	$$\genJacobiKernel{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm g - h \right)\right)\right).$$
+	Let $t \in \multiplicativegroup{\quadraticExtension}$. As before, we can write
+	$$\genJacobiKernel{\chi}\left(g\right) = q^{-k^2} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right) \fieldCharacter_{\quadraticExtension}\left(t \trace\left(A \left(\idmap_{\hermitianSpace} \pm g - h \right)\right)\right).$$
 	Hence, \begin{align*}
-		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(xp\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace\left(-Ah\right)\right) \\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Assume that $\chi \ne 1$.
-By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
+		q^{k^2} \sum_{p \in G \cap P} \genJacobiKernel{\chi}\left(x^{-1} p\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right) =& \sum_{A \in \EndomorphismRing_{\quadraticExtension}\left(\hermitianSpace\right)} \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(t \trace\left(-Ah\right)\right) \\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(t \trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1} p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Since $\chi \ne 1$, by \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)$.
 Let us replace $h$ with $-A^{-1} h$.
@@
 	\begin{align*}
-		& \chi\left(-1\right)^k \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(\trace h\right)\\
-		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(\trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1}p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
-	\end{align*}
-	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(\trace\left(\pm A x^{-1} l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
-	The inner sum over $N$ will vanish unless $\pm Ax^{-1} \in P$ \elad{This is not true in general}. Thus we have
+		& \chi\left(-1\right)^k \sum_{A \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi^{-1}\left(\detQuadratic A\right) \sum_{h \in \GL_{\quadraticExtension}\left(\hermitianSpace\right)} \chi\left(\detQuadratic h\right)\fieldCharacter_{\quadraticExtension}\left(t \trace h\right)\\
+		& \times \sum_{p \in P} \fieldCharacter_{\quadraticExtension}\left(t \trace\left(A \left(\idmap_{\hermitianSpace} \pm x^{-1}p\right)\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(p\right).
+	\end{align*}
+	Consider the inner sum over $P$, written as $$\sum_{l \in L} \sum_{u \in N} \fieldCharacter_{\quadraticExtension}\left(t \trace\left(\idmap_{\hermitianSpace} \pm A x^{-1} l u\right)\right) \left(\tau \overline{\otimes} \pi'\right)\left(l\right).$$
+	The inner sum over $N$ will vanish unless $\pm Ax^{-1} l \in P$ which is equivalent to $A x^{-1} \in P$. Thus we have
 	\begin{align*}
